### 2018-01-03 paper/paper.tex
First draft

\documentclass[sigconf]{acmart}
\sloppy
\usepackage{graphicx}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\makeatletter
\renewcommand\@formatdoi[1]{\ignorespaces}
\makeatother
\settopmatter{printacmref=false}

\usepackage{booktabs} % For formal tables
\setcopyright{none}

\newcommand{\MITAffiliation}{
\affiliation{%
  \institution{Massachussets Institute of Technology}
  \streetaddress{32 Vassar Street}
  \city{Cambridge}
  \state{Massachussets}
  \country{USA}
  \postcode{02139}
}}

 \newcommand{\EPFLAffiliation}{
\affiliation{%
  \institution{Swiss Federal Institute of Technology in Lausanne (EPFL)}
  \streetaddress{Route Cantonale}
  \city{Lausanne}
  \country{Switzerland}
  \postcode{02139}
}}

\begin{document}
\title{ShrinkNets}

\author{Guillaume Leclerc}
\authornote{Visiting Student}
\MITAffiliation
\email{leclerc@mit.edu}

\author{Raul Castro Fernandez}
\MITAffiliation
\email{raulcf@csail.mit.edu}

\author{Samuel Madden}
\MITAffiliation
\email{madden@csail.mit.edu}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{G. Leclerc et al.}

\begin{abstract}
  Write the abstract at the end !
\end{abstract}

\maketitle

\section{Introduction}

When designing Neural Netowrks, finding the apropriate size (width and depth) is key. Indeed, these hyper parameters have a strong correlation with over/underfitting. The main problem is that we have no reliable way to find them [ref]. Decades of experimentation led to some heuristics [ref] that try to prune that immense space of possible network sizes, but we are still bound to use costly and sometimes complex methods to find reasonable values for these hyper-parameters.

% \subsection{Main Contributions}
% 
% The main contribution of this article are:
% \begin{itemize}
%   \item The Filter layer, a neural network layer which puropose is to allow feature selection
%   \item To the best of our knowledge, the first attempts to dynamically change the number of channels in deep convolutional neural networks
%   \item A deep learning library built on top of PyTorch that allow partictionners to train shrinking networks (Feed-Forward and Convolutional)
% \end{itemize}
% 
\section{Related Work}

\par In the litterature we can see different ways of approaching this issue. The first one is to select parameters, train the model, evaluate it, repeat and pick the best one. There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], parsen trees[ref], gaussian processes [ref] etc... but they all suffer from one major drawback: we have to train and evaluate countless models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still important.
\par To reduce the number of models trained, another approach emerged: train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model. Notable contributions are Optimal Brain Dammage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article). These techniques are very interesting but they still require a reasonable network size to start with, so they usually have to be combined with classic hyper-optimization techniques.
\par However, some recent contributions like Non-Parametric Neural Netowrks [ref] and [ref] try to learn the network size (width for the former and depth for the latter) during the training process and without any prior assumption about the network size.

\section{The Filter Layer}
\subsection{Motivation}

The method described in [ref] grows and shrink the network over time. Though it seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions. Their method also required a new optimizer \textit{AdaRad}. Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy. Therefore, designing a new layer that only allow seemed to be best approach.

\subsection{Definition}

In this section we define the \textit{Filter Layer}. It takes an input of size $\left(B \times C \times D_1 \times \dots \times D_n\right)$. So it is compatible with fully connected layers with $n=0$ or convolutional layers with $n=2$. This layer has a parameter $\theta \in \mathbb{R}^C$ and is defined the following way.
\begin{equation}
  Filter(I;\theta) = I \circ \max(0, \theta)
\end{equation}

Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$ is expanded in all dimensions except the second one to match the input size. It is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be $0$. We can use this property to devise a training procedure.
\subsection{The training procedure}

To train networks we need start with a clearly oversized network, then we insert \textit{Filter Layers} in the architecture (usually after every Linear or Convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution. We could train this network as it is and it would be equivalent to a normal neural netork. However, our goal is to find the smallest network with reasonable performance. We can achieve that by introducing sparsity in the parameters of the \textit{Filter Layers}. Indeed, having a negative value is equivalent to zeroing an entire row and column in the surrounding layers. These disabled neurons/channels can be removed from the network without changing its output. To obtain this sparsity we simply redefine the loss function:

\begin{equation}
  L'(x,y;\theta) = L(x, y) + \lambda|\theta|
\end{equation}

The $\lambda$ parameter controls the tradeof between optimizing the original loss or the size of the network.

\section{Software architecture}

To obtain good performance using this approach, it is key to remove neurons and channels from the network as soon as possible. This task usually is cubbersome using existing machine learning frameworks. To enable the reproducibility of our results and let people use this method on their own dataset and architectures, we implemented a small library on top of \textit{PyTorch}. It makes it very easy to design and train networks that contains \textit{Filter Layers}. We will briefly describe the software architecture.
\par The key operation we want to perform is warn layers when a feature is removed so they can resize themselves. Therefore, we need to know what are the child and parents of a given layers. Since there is no concept of computation graph in \textit{PyTorch} we had to build it. Layers are augmented with a list of incoming modules (parents) and outgoing modules (children).
\par Edges in the graph carry features from parent to children. When a \textit{Filter Layer} removes a feature, edges need to be able to warn layers so we implemented them as an event hubs that maintain the list of features to keep; we called them \texttt{FeatureBags}. In many cases, layers do not change the number of features (eg. \textit{Dropout}, \textit{BatchNorm}), therefore, events needs to propagate through them to warn all layers that share the same number of features. To solve this problem, such layers instantiate \texttt{MirrorFeatureBags} which role is to relay events to and from the root \texttt{FeatureBag}. With this event-base approach are able to keep all the layers in sync. Adding layers becomes straightforward: programmers just have to react to three events: input removal, output removal and garbage collection. During our tests we ran the garbage collection every epoch.

\section{Evaluation}
\subsection{Convergence}

To demonstrate that the approach is viable, we will first show that Shrinking Networks converge. For this experiment we trained a one hidden layer neural network with one filter layer to control the number of hidden units. We initialized the models with $10000$ neurons and trained them on \texttt{MNIST} using different regularization factors ($\lambda$). We summarized the results on \autoref{convergence_plot}. [Should we explain the results ?]

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{convergence}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.5\textwidth]{hyper_opt}
\caption{Distributions of the testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
\end{center}
\end{figure}

\subsection{Comparison between Shrinking and classic Networks}

To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider a \textit{LeNet-5} architecture and assume we do not know the number of channels and neurons. We try to find the best architecture by performing random search on the parameters that define the size. For classic neural networks these parameters are the number of channels for the first two layers and the number of hidden units of the linear layer. For ShrinkNets there is only one parameter $\lambda$. We sampled 50 models of each and trained them, picked the best epoch using the validation accuracy and measured their accuracy on the testing set. Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly). We summarized the accuracy we obtained on \autoref{hyper_opt_res}. [Should we explain the results]

\section{Future work}

\par Even though the firsts results this techique yields seem promising, there are many area that we could explore to improve it. In the current implementation we only "learn" the number of features (neurons or channels). We could try to augment it with dynamic number of layers as seen in [ref] to be able to determine the entire architecture.
\par We saw on Figure \ref{convergence_plot} that the loss temporarly suffers from the removal of neurons. It is likely that the loss would be more stable if the number of neurons converged faster or neurons disapeared more progressively. This is why we think we should explore proximal gradient methods to optimize the filter vectors and/or randomize neuron removals.
\par During our evaluation we picked small datasets mainly to be able to train many models and have statistically significant distributions. With more computation resources and time, we could see if it generalises to bigger datasets and other architectures like \texttt{ResNet} [ref] (small modifications to the existing code base are required to support them)

\section{Conclusion}
Do the conclusion at the end

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}

### 2018-01-03 paper/convergence_experiment_plot.py

@@ -80,9 +80,9 @@ for m, lamb in zip(reversed(markers), reversed(lambdas)):
     lines.append(l)
 for m, lamb in zip(reversed(markers), reversed(lambdas)):
     file = load_file(
-        './experiments_results/conv_MNIST_bs256128_lamb%s.dat' % lamb)
+        './experiments_results/conv_MNIST_bs256_lamb%s.dat' % lamb)
     ax_loss.plot(np.arange(0, 100, 1 / len(file) * 100), file['loss'], m + '-', markevery=int(len(file) / 5))
 ax_size.legend(handles=lines , labels=reversed(tex_labels) ,loc='lower center', bbox_to_anchor=(0.5, 1), ncol=3, columnspacing=0.5)
 f.set_size_inches(5, 5)
 plt.show()
-plt.savefig('test.pdf', bbox_inches='tight')
+plt.savefig('convergence.pdf', bbox_inches='tight')

### 2018-01-03 paper/paper.tex
Some fix

@@
 Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy.
-Therefore, designing a new layer that only allow seemed to be best approach.
+Therefore, designing a new layer that only allow shrinking seemed to be best approach.
 
@@
 
-To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider a \textit{LeNet-5} architecture and assume we do not know the number of channels and neurons.
-We try to find the best architecture by performing random search on the parameters that define the size.
-For classic neural networks these parameters are the number of channels for the first two layers and the number of hidden units of the linear layer.
-For ShrinkNets there is only one parameter $\lambda$.
-We sampled 50 models of each and trained them, picked the best epoch using the validation accuracy and measured their accuracy on the testing set.
+To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider two different architecture, a three hidden layer feed forward network and a \textit{LeNet-5} [ref].
+We assume we do not know the number of channels and neurons and we want to find the best architecture by performing random search on the parameters that define the size.
+For classic neural networks these parameters are the number of channels and/or neurons; for ShrinkNets there is only one parameter $\lambda$.
+We sampled 50 models of each and trained them, picked the best epoch according to the validation accuracy and measured their performance on the testing set.
 Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly).

### 2018-01-04 paper/hyper_opt_epxeriment.py
Fix error in the experiment
- And remove the bad results

@@ -1,18 +1,20 @@
 import torch
 import numpy as np
 from torch.utils.data import DataLoader, TensorDataset
-from torch.nn import ReLU, CrossEntropyLoss
+from torch.nn import ReLU, CrossEntropyLoss, MaxPool2d
 from torch.nn.functional import relu
 from torch.autograd import Variable
 from torch.optim import Adam
 from torchvision import transforms
 from torchvision.datasets import MNIST, FashionMNIST, CIFAR10
 from dynnet.graph import Graph
-from dynnet.layers import Input, Linear
 from dynnet.filters import SimpleFilter
 from sklearn.model_selection import train_test_split
 from uuid import uuid4
 import sys
+from dynnet.layers import (
+    Input, Linear, Conv2d, Flatten
+)
 
 SEED = 0
 COUNT = 50
@@ -29,8 +31,8 @@ SIZES = {
     CIFAR10: (3, 32, 32)
 }
 REGULARIZATIONS = {
-    MNIST: [1, 5],
-    FashionMNIST: [1, 5],
+    MNIST: [2, 5],
+    FashionMNIST: [2, 5],
     CIFAR10: [2, 6]
 }
 
@@ -74,10 +76,12 @@ def prepare_loaders(dataset, batch_sizes):
 
 def init_model(model):
     for parameter in model.parameters():
-        if len(parameter.size()) == 2:
+        if len(parameter.size()) > 1:
             torch.nn.init.xavier_normal(parameter.data, gain=np.sqrt(2))
-        else:
-            parameter.data.uniform_(0, 1)
+    for l in model:
+        if isinstance(l, SimpleFilter):
+            l.weight.data.uniform_(0, 1)
+
 
 def create_dynamic_model(start_size=5000, size=(1, 28, 28), conv=False):
     graph = Graph()
@@ -88,16 +92,50 @@ def create_dynamic_model(start_size=5000, size=(1, 28, 28), conv=False):
             l = graph.add(SimpleFilter)(l)
             l = graph.add(ReLU)(l)
         graph.add(Linear, out_features=10)(l)
+    else:
+        l = graph.add(Input, *size)()
+        l = graph.add(Conv2d, out_channels=start_size[0], kernel_size=5)(l)
+        l = graph.add(SimpleFilter)(l)
+        l = graph.add(ReLU)(l)
+        l = graph.add(MaxPool2d, kernel_size=2)(l)
[…]

### 2018-01-04 paper/paper.tex
pass by sam

@@
 \usepackage{graphicx}
+\usepackage{color}
 \settopmatter{printacmref=false} % Removes citation information below abstract
@@
 
+\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
 \begin{document}
@@
 
-When designing Neural Netowrks, finding the apropriate size (width and depth) is key.
-Indeed, these hyper parameters have a strong correlation with over/underfitting.
+When designing Neural Networks, finding the appropriate size (width and depth) is key.
+In particular, these hyper parameters have a strong correlation with over/underfitting \srm{give reference}.
 The main problem is that we have no reliable way to find them [ref].
 Decades of experimentation led to some heuristics [ref] that try to prune that immense space of possible network sizes, but we are still bound to use costly and sometimes complex methods to find reasonable values for these hyper-parameters.
+
+\srm{In this paper, we describe ... -- need to give a high level idea of solution, and its benefits.  Would be good to give your system/approach a name.}
 
@@
 
-\par In the litterature we can see different ways of approaching this issue.
+\par In the literature we can see different ways of approaching this issue.
 The first one is to select parameters, train the model, evaluate it, repeat and pick the best one.
-There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], parsen trees[ref], gaussian processes [ref] etc...
-but they all suffer from one major drawback: we have to train and evaluate countless models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still important.
-\par To reduce the number of models trained, another approach emerged: train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model.
-Notable contributions are Optimal Brain Dammage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article).
+There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref], Gaussian processes [ref] etc...
+but they all suffer from one major drawback: we have to train and evaluate a very large number of models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still very significant.
+\par To reduce the number of models trained, another approach is to train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model.
+Notable contributions are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article).
 These techniques are very interesting but they still require a reasonable network size to start with, so they usually have to be combined with classic hyper-optimization techniques.
 \par However, some recent contributions like Non-Parametric Neural Netowrks [ref] and [ref] try to learn the network size (width for the former and depth for the latter) during the training process and without any prior assumption about the network size.
+\srm{Give a short sentence about how our approach is different than these previous approaches.}
 
@@
 
-The method described in [ref] grows and shrink the network over time.
-Though it seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions.
-Their method also required a new optimizer \textit{AdaRad}.
+\srm{This makes what we have done sound like an incremental change over prior work.
+Instead, move this description to prior work and say why its not a good approach there, then describe what we do as a new method.
+}
+The method described in [ref] grows and shrinks the network over time.
+Though this seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions.
+Their method also requires a new optimizer \textit{AdaRad}.
 Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy.
 Therefore, designing a new layer that only allow shrinking seemed to be best approach.
+\srm{How is this shrinking approach different than previous approaches like Optimal Brain Damage, Deep Compression,e tc?}
 
+\srm{Describe our key approach at a high level -- i.e., add a new layer to the network, called the {\it filter layer}, which ... }
 \subsection{Definition}
@@
 This layer has a parameter $\theta \in \mathbb{R}^C$ and is defined the following way.
+\srm{Need to define B, C, D}.
 \begin{equation}
@@
 We can use this property to devise a training procedure.
+\srm{Give an English description of what this formalism achieves -- what does the filter layer do, why is it significant.}
+
 \subsection{The training procedure}
 
-To train networks we need start with a clearly oversized network, then we insert \textit{Filter Layers} in the architecture (usually after every Linear or Convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution.
-We could train this network as it is and it would be equivalent to a normal neural netork.
+To train networks we need start with a substantially oversized network, then we insert \textit{Filter Layers}  (usually after every linear or convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution.
+We could train this network directly and it would be equivalent to a normal neural network.
 However, our goal is to find the smallest network with reasonable performance.
 We can achieve that by introducing sparsity in the parameters of the \textit{Filter Layers}.
-Indeed, having a negative value is equivalent to zeroing an entire row and column in the surrounding layers.
-These disabled neurons/channels can be removed from the network without changing its output.
+Indeed, \srm{having a negative value where?} having a negative value is equivalent to zeroing an entire row and column in the surrounding layers.
+These disabled neurons/channels can be removed from the network without changing its output (we describe how we perform this removal below).
 To obtain this sparsity we simply redefine the loss function:
@@
 
-The $\lambda$ parameter controls the tradeof between optimizing the original loss or the size of the network.
+The $\lambda$ parameter controls the trade-off between optimizing the original loss or the size of the network.
+\srm{Again give some intuitive description of what is novel / important about this choice of loss function and learning process.
+It's hard to understand what is interesting/important about what you have done without you explicitly calling it out.}
 
@@
 
-To obtain good performance using this approach, it is key to remove neurons and channels from the network as soon as possible.
-This task usually is cubbersome using existing machine learning frameworks.
-To enable the reproducibility of our results and let people use this method on their own dataset and architectures, we implemented a small library on top of \textit{PyTorch}.
-It makes it very easy to design and train networks that contains \textit{Filter Layers}.
+To obtain good performance using this approach, it is essential to be able to remove neurons and channels from the network as quickly as possible.
+This task usually is cumbersome using existing machine learning frameworks.
+To enable this, we implemented a small library on top of \textit{PyTorch} which makes it very easy to design and train networks that contains \textit{Filter Layers}.
 We will briefly describe the software architecture.
-\par The key operation we want to perform is warn layers when a feature is removed so they can resize themselves.
-Therefore, we need to know what are the child and parents of a given layers.
-Since there is no concept of computation graph in \textit{PyTorch} we had to build it.
-Layers are augmented with a list of incoming modules (parents) and outgoing modules (children).
-\par Edges in the graph carry features from parent to children.
-When a \textit{Filter Layer} removes a feature, edges need to be able to warn layers so we implemented them as an event hubs that maintain the list of features to keep; we called them \texttt{FeatureBags}.
-In many cases, layers do not change the number of features (eg.
-\textit{Dropout}, \textit{BatchNorm}), therefore, events needs to propagate through them to warn all layers that share the same number of features.
-To solve this problem, such layers instantiate \texttt{MirrorFeatureBags} which role is to relay events to and from the root \texttt{FeatureBag}.
-With this event-base approach are able to keep all the layers in sync.
+\par The key operation we want to perform is to notify layers when a feature is removed so they can resize themselves.
+Therefore, we need to track the child and parents each layer.
+Since there is no concept of computation graph in \textit{PyTorch} we had to build it;  specifically,  layers are augmented with a list of incoming modules (parents) and outgoing modules (children).
+\par Edges in the graph carry features from parent to children. When a \textit{Filter Layer} removes a feature, edges need to notify layers of the change.  We implemented a simple event-based
+architecture where edges send events about features to layers. 
+\srm{Suggest cutting the following: Each  edge maintains a list of features to keep, and called a \texttt{FeatureBag}.
+In many cases, layers do not change the number of features (e.g., \textit{Dropout}, \textit{BatchNorm}), therefore, event needs to propagate through them to notify all layers that share the same number of features.
+To solve this problem, such layers instantiate \texttt{MirrorFeatureBags} which role is to relay events to and from the root \texttt{FeatureBag}.} With this event-based approach are able to keep all the layers in sync.
 Adding layers becomes straightforward: programmers just have to react to three events: input removal, output removal and garbage collection.
-During our tests we ran the garbage collection every epoch.
+\srm{What does garbage collection do?} During our tests we ran the garbage collection every epoch.
 
@@
 We initialized the models with $10000$ neurons and trained them on \texttt{MNIST} using different regularization factors ($\lambda$).
-We summarized the results on \autoref{convergence_plot}.
-[Should we explain the results ?]
+We summarized the results in \autoref{convergence_plot}.
+[Should we explain the results ?] \srm{Yes, you need to explain in detail -- what does this show?
+How does it prove that your approach works / is a good idea?}
 
@@
 
-To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider two different architecture, a three hidden layer feed forward network and a \textit{LeNet-5} [ref].
-We assume we do not know the number of channels and neurons and we want to find the best architecture by performing random search on the parameters that define the size.
-For classic neural networks these parameters are the number of channels and/or neurons; for ShrinkNets there is only one parameter $\lambda$.
+To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider two different architectures, a three hidden layer feed forward network and a \textit{LeNet-5} [ref].
+We do not know the number of channels and neurons and we want to find the best architecture by performing random search on the parameters that define the size.
+For classic neural networks these parameters are the number of channels and/or neurons; for ShrinkNets there is only one parameter, $\lambda$.
 We sampled 50 models of each and trained them, picked the best epoch according to the validation accuracy and measured their performance on the testing set.
-Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly).
+Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly) \srm{L2 regularization over what?}.
 We summarized the accuracy we obtained on \autoref{hyper_opt_res}.
-[Should we explain the results]
+[Should we explain the results] \srm{Yes, need to describe in detail -- how does this prove that your method works/ is a good idea?
+What are the key takeaways?}
 
@@
 
-\par Even though the firsts results this techique yields seem promising, there are many area that we could explore to improve it.
+\par Even though the firsts results this technique yields seem promising, there are many area that we could explore to improve it.
 In the current implementation we only "learn" the number of features (neurons or channels).
 We could try to augment it with dynamic number of layers as seen in [ref] to be able to determine the entire architecture.
-\par We saw on Figure \ref{convergence_plot} that the loss temporarly suffers from the removal of neurons.
-It is likely that the loss would be more stable if the number of neurons converged faster or neurons disapeared more progressively.
-This is why we think we should explore proximal gradient methods to optimize the filter vectors and/or randomize neuron removals.
+\par We saw on Figure \ref{convergence_plot} that the loss temporarily suffers from the removal of neurons.
+It is likely that the loss would be more stable if the number of neurons converged faster or neurons disappeared slower.
+For this reason we plan to explore proximal gradient methods to optimize the filter vectors and/or randomize neuron removals.
 \par During our evaluation we picked small datasets mainly to be able to train many models and have statistically significant distributions.
-With more computation resources and time, we could see if it generalises to bigger datasets and other architectures like \texttt{ResNet} [ref] (small modifications to the existing code base are required to support them)
+With more computation resources and time, we could see if it generalizes to bigger datasets and other architectures like \texttt{ResNet} [ref] (small modifications to the existing code base are required to support them)
 

### 2018-01-04 paper/paper.tex

@@
 \newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
+\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
 \begin{document}
@@
 
-\begin{abstract}
-  Write the abstract at the end !
-\end{abstract}
+%\begin{abstract}
+%  Write the abstract at the end !
+%\end{abstract}
 
@@
 
-When designing Neural Networks, finding the appropriate size (width and depth) is key.
-In particular, these hyper parameters have a strong correlation with over/underfitting \srm{give reference}.
-The main problem is that we have no reliable way to find them [ref].
-Decades of experimentation led to some heuristics [ref] that try to prune that immense space of possible network sizes, but we are still bound to use costly and sometimes complex methods to find reasonable values for these hyper-parameters.
+When designing Neural Networks, finding the appropriate size (width and depth)
+is key. In particular, these hyper parameters have a strong correlation with
+over/underfitting \srm{give reference}. The main problem is that we have no
+reliable way to find them [ref]. Decades of experimentation led to some
+heuristics [ref] that try to prune that immense space of possible network sizes.
+For example, researchers have used strategies such as random search,
+meta-gradient descent and parser trees to reduce find good parameters without
+exhaustively exploring the entire hyper-parameter space. Although these
+strategies help with finding a good set of hyper-parameters, they still require
+a compute-intensive search of the space.
 
-\srm{In this paper, we describe ... -- need to give a high level idea of solution, and its benefits.  Would be good to give your system/approach a name.}
+%However, we are still bound to use costly and sometimes complex methods to find
+%reasonable values for these hyper-parameters.
+
+\srm{In this paper, we describe ... -- need to give a high level idea of
+solution, and its benefits.  Would be good to give your system/approach a name.}
+
+In this paper we present a method to automatically find an appropriate network
+size without paying the compute and time cost of searching through a large
+hyper-parameter space. The key idea is to \emph{learn} the right network size at
+the same time that the network is learning the main task. For example, for an
+image classification task, with our approach we can provide the training data to
+a network---without sizing it a priori---and expect to end up with a network
+that has learnt the task without overfitting. This approach has two main
+benefits. First, we do no longer need to choose a network size before training.
+Second, the final network size will be appropriate for the task at hand, and not
+larger. This is important because oversized networks have a lower inference
+throughput.
+
+Our approach has two main challenges. First, on how to dynamically size the
+network during training. Second, on how to find a loss function that optimizes
+for the additional task of sizing, without deteriorating the learning
+performance of the main task. We describe next ShrinkNets, which cope with both
+challenges:
 
@@
 %
-\section{Related Work}
 
-\par In the literature we can see different ways of approaching this issue.
-The first one is to select parameters, train the model, evaluate it, repeat and pick the best one.
-There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref], Gaussian processes [ref] etc...
-but they all suffer from one major drawback: we have to train and evaluate a very large number of models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still very significant.
-\par To reduce the number of models trained, another approach is to train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model.
-Notable contributions are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article).
-These techniques are very interesting but they still require a reasonable network size to start with, so they usually have to be combined with classic hyper-optimization techniques.
-\par However, some recent contributions like Non-Parametric Neural Netowrks [ref] and [ref] try to learn the network size (width for the former and depth for the latter) during the training process and without any prior assumption about the network size.
-\srm{Give a short sentence about how our approach is different than these previous approaches.}
+\section{ShrinkNets}
 
-\section{The Filter Layer}
-\subsection{Motivation}
+\srm{Describe our key approach at a high level -- i.e., add a new layer to the
+network, called the {\it filter layer}, which ... }
 
-\srm{This makes what we have done sound like an incremental change over prior work.
-Instead, move this description to prior work and say why its not a good approach there, then describe what we do as a new method.
-}
-The method described in [ref] grows and shrinks the network over time.
-Though this seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions.
-Their method also requires a new optimizer \textit{AdaRad}.
-Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy.
-Therefore, designing a new layer that only allow shrinking seemed to be best approach.
-\srm{How is this shrinking approach different than previous approaches like Optimal Brain Damage, Deep Compression,e tc?}
+Our approach consists of starting the training process for the task of interest
+with an explicitly oversized network. Then, as training progresses, we learn
+which neurons are not contributing to learning the main task and remove them
+dynamically, thus shrinking the network size. This method requires two building
+blocks. First, a way of identifying neurons that are not contributing to the
+learning process, and second a way of balancing the network size and the
+generalization capability for the main task. We introduce a new layer, called
+\textsf{Filter}, which takes care of \emph{deactivating} neurons. We also modify
+existing loss functions to incorporate a new term that takes care of balancing
+network sizing and generalization capability appropriately. We explain them
+next:
 
-\srm{Describe our key approach at a high level -- i.e., add a new layer to the network, called the {\it filter layer}, which ... }
-\subsection{Definition}
+%\subsection{Motivation}
+%
+%\srm{This makes what we have done sound like an incremental change over prior
+%work.  Instead, move this description to prior work and say why its not a good
+%approach there, then describe what we do as a new method.  }
+%
+%The method described in [ref] grows and shrinks the network over time. Though
+%this seems to be an attractive property to have, during our experiments and
+%according to their results, models are very slow to train and sometimes
+%converge to suboptimal solutions. Their method also requires a new optimizer
+%\textit{AdaRad}.  Our goal was to provide a solution that can easily be
+%integrated in existing machine learning systems and provide similar convergence
+%speed and accuracy. Therefore, designing a new layer that only allow shrinking
+%seemed to be best approach.
+%
 
-In this section we define the \textit{Filter Layer}.
-It takes an input of size $\left(B \times C \times D_1 \times \dots \times D_n\right)$.
-So it is compatible with fully connected layers with $n=0$ or convolutional layers with $n=2$.
-This layer has a parameter $\theta \in \mathbb{R}^C$ and is defined the following way.
-\srm{Need to define B, C, D}.
+%\subsection{Definition}
+
+\textbf{Filter Layer: }
+
+Filter layers have weights in the range $[0,1]$ and are placed after linear and
+convolutional layers of traditional deep networks. The \textit{Filter Layer}
+takes an input of size $\left(B \times C \times D_1 \times \dots \times
+D_n\right)$ so it is compatible with fully connected layers with $n=0$ or
+convolutional layers with $n=2$. Their crucial property is a parameter $\theta \in
+\mathbb{R}^C$, defined as follows: \srm{Need to define B, C, D}.
+
 \begin{equation} 
@@
 
-Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$ is expanded in all dimensions except the second one to match the input size.
-It is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be $0$.
-We can use this property to devise a training procedure.
-\srm{Give an English description of what this formalism achieves -- what does the filter layer do, why is it significant.}
+Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
+is expanded in all dimensions except the second one to match the input size. It
+is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
+feature/channel will forever be $0$. When this happens, we say the Filter layer
+disables the neuron. These disabled neurons/channels can be removed from the
+network without changing its output (we describe how we perform this removal
+below). We explain next how the weights of the Filter Layer are
+adjusted during training.
 
-\subsection{The training procedure}
+%We can use this property to devise a training procedure.
 
-To train networks we need start with a substantially oversized network, then we insert \textit{Filter Layers}  (usually after every linear or convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution.
-We could train this network directly and it would be equivalent to a normal neural network.
-However, our goal is to find the smallest network with reasonable performance.
-We can achieve that by introducing sparsity in the parameters of the \textit{Filter Layers}.
-Indeed, \srm{having a negative value where?} having a negative value is equivalent to zeroing an entire row and column in the surrounding layers.
-These disabled neurons/channels can be removed from the network without changing its output (we describe how we perform this removal below).
-To obtain this sparsity we simply redefine the loss function:
+\srm{Give an English description of what this formalism
+achieves -- what does the filter layer do, why is it significant.}
+
+%To train networks we need start with a substantially oversized network, then we
+%insert \textit{Filter Layers}  (usually after every linear or convolutional
+%layer except the last one) and we sample their weight from the
+%$\text{Uniform}(0, 1)$ distribution.
+
+%The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
+%\times \dots \times D_n\right)$ so it is compatible with fully connected layers
+%with $n=0$ or convolutional layers with $n=2$. This layer has a parameter
+%$\theta \in \mathbb{R}^C$ and is defined the following way. \srm{Need to define
+%B, C, D}.  
+%
+%\begin{equation} 
+%Filter(I;\theta) = I \circ \max(0, \theta)
+%\end{equation}
+%
+%Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
+%is expanded in all dimensions except the second one to match the input size. It
+%is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
+%feature/channel will forever be $0$. We can use this property to devise a
+%training procedure.  
+%
+%\srm{Give an English description of what this formalism
+%achieves -- what does the filter layer do, why is it significant.}
+
+%\subsection{The training procedure}
+\textbf{Training Procedure: } Once Filter layers are placed in a deep network, 
+%To train networks we need start with a substantially oversized network, then we
+%insert \textit{Filter Layers}  (usually after every linear or convolutional
+%layer except the last one) and we sample their weight from the
+%$\text{Uniform}(0, 1)$ distribution. 
+we could train it directly and it
+would be equivalent to a normal neural network. However, our goal is to find the
+smallest network with reasonable performance. We achieve that by introducing
+sparsity in the parameters of the \textit{Filter Layers}. Indeed, \srm{having a
+negative value where?} having a negative value is equivalent to zeroing an
+entire row and column in the surrounding layers. To obtain this sparsity, we
+simply redefinte the loss function:
 
@@
 
-The $\lambda$ parameter controls the trade-off between optimizing the original loss or the size of the network.
-\srm{Again give some intuitive description of what is novel / important about this choice of loss function and learning process.
-It's hard to understand what is interesting/important about what you have done without you explicitly calling it out.}
+The $\lambda$ parameter controls the trade-off between optimizing the original
+loss or the size of the network.  \srm{Again give some intuitive description of
+what is novel / important about this choice of loss function and learning
+process.  It's hard to understand what is interesting/important about what you
+have done without you explicitly calling it out.}
+
+Next, we explain how to implement ShrinkNets efficiently.
 
@@
 
-To obtain good performance using this approach, it is essential to be able to remove neurons and channels from the network as quickly as possible.
-This task usually is cumbersome using existing machine learning frameworks.
-To enable this, we implemented a small library on top of \textit{PyTorch} which makes it very easy to design and train networks that contains \textit{Filter Layers}.
-We will briefly describe the software architecture.
-\par The key operation we want to perform is to notify layers when a feature is removed so they can resize themselves.
-Therefore, we need to track the child and parents each layer.
-Since there is no concept of computation graph in \textit{PyTorch} we had to build it;  specifically,  layers are augmented with a list of incoming modules (parents) and outgoing modules (children).
-\par Edges in the graph carry features from parent to children. When a \textit{Filter Layer} removes a feature, edges need to notify layers of the change.  We implemented a simple event-based
-architecture where edges send events about features to layers. 
-\srm{Suggest cutting the following: Each  edge maintains a list of features to keep, and called a \texttt{FeatureBag}.
-In many cases, layers do not change the number of features (e.g., \textit{Dropout}, \textit{BatchNorm}), therefore, event needs to propagate through them to notify all layers that share the same number of features.
-To solve this problem, such layers instantiate \texttt{MirrorFeatureBags} which role is to relay events to and from the root \texttt{FeatureBag}.} With this event-based approach are able to keep all the layers in sync.
-Adding layers becomes straightforward: programmers just have to react to three events: input removal, output removal and garbage collection.
-\srm{What does garbage collection do?} During our tests we ran the garbage collection every epoch.
+\ra{this can be shorter. I'd add it as a third paragraph above, immediately
+above the eval}
+
+To obtain good performance using this approach, it is essential to be able to
+remove neurons and channels from the network as quickly as possible. This task
+usually is cumbersome using existing machine learning frameworks. To enable
+this, we implemented a small library on top of \textit{PyTorch} which makes it
+very easy to design and train networks that contains \textit{Filter Layers}. We
+will briefly describe the software architecture.  \par The key operation we want
+to perform is to notify layers when a feature is removed so they can resize
+themselves. Therefore, we need to track the child and parents each layer. Since
+there is no concept of computation graph in \textit{PyTorch} we had to build it;
+specifically,  layers are augmented with a list of incoming modules (parents)
+and outgoing modules (children).  \par Edges in the graph carry features from
+parent to children. When a \textit{Filter Layer} removes a feature, edges need
+to notify layers of the change.  We implemented a simple event-based
+architecture where edges send events about features to layers.  \srm{Suggest
+cutting the following: Each  edge maintains a list of features to keep, and
+called a \texttt{FeatureBag}. In many cases, layers do not change the number of
+features (e.g., \textit{Dropout}, \textit{BatchNorm}), therefore, event needs to
+propagate through them to notify all layers that share the same number of
+features. To solve this problem, such layers instantiate
+\texttt{MirrorFeatureBags} which role is to relay events to and from the root
+\texttt{FeatureBag}.} With this event-based approach are able to keep all the
+layers in sync. Adding layers becomes straightforward: programmers just have to
+react to three events: input removal, output removal and garbage collection.
+\srm{What does garbage collection do?} During our tests we ran the garbage
+collection every epoch.
 
@@
 
-To demonstrate that the approach is viable, we will first show that Shrinking Networks converge.
-For this experiment we trained a one hidden layer neural network with one filter layer to control the number of hidden units.
-We initialized the models with $10000$ neurons and trained them on \texttt{MNIST} using different regularization factors ($\lambda$).
-We summarized the results in \autoref{convergence_plot}.
-[Should we explain the results ?] \srm{Yes, you need to explain in detail -- what does this show?
-How does it prove that your approach works / is a good idea?}
+To demonstrate that the approach is viable, we will first show that Shrinking
+Networks converge. For this experiment we trained a one hidden layer neural
+network with one filter layer to control the number of hidden units. We
+initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
+using different regularization factors ($\lambda$). We summarized the results in
+\autoref{convergence_plot}. [Should we explain the results ?] \srm{Yes, you need
+to explain in detail -- what does this show?  How does it prove that your
+approach works / is a good idea?}
 
@@
 
-To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider two different architectures, a three hidden layer feed forward network and a \textit{LeNet-5} [ref].
-We do not know the number of channels and neurons and we want to find the best architecture by performing random search on the parameters that define the size.
-For classic neural networks these parameters are the number of channels and/or neurons; for ShrinkNets there is only one parameter, $\lambda$.
-We sampled 50 models of each and trained them, picked the best epoch according to the validation accuracy and measured their performance on the testing set.
-Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly) \srm{L2 regularization over what?}.
-We summarized the accuracy we obtained on \autoref{hyper_opt_res}.
-[Should we explain the results] \srm{Yes, need to describe in detail -- how does this prove that your method works/ is a good idea?
-What are the key takeaways?}
+To demonstrate the value of ShrinkNets in the context of hyper-parameter
+optimization we set up the following experiment: We consider two different
+architectures, a three hidden layer feed forward network and a \textit{LeNet-5}
+[ref]. We do not know the number of channels and neurons and we want to find the
+best architecture by performing random search on the parameters that define the
+size. For classic neural networks these parameters are the number of channels
+and/or neurons; for ShrinkNets there is only one parameter, $\lambda$. We
+sampled 50 models of each and trained them, picked the best epoch according to
+the validation accuracy and measured their performance on the testing set. Since
+ShrinkNets can be considered to be regularized in some sense, to make the
+comparison fair we also considered static networks with an $L2$ regularization
+factor (also drawn randomly) \srm{L2 regularization over what?}. We summarized
+the accuracy we obtained on \autoref{hyper_opt_res}. [Should we explain the
+results] \srm{Yes, need to describe in detail -- how does this prove that your
+method works/ is a good idea?  What are the key takeaways?}
+
+\section{Related Work}
+
+\ra{I'd remove this paragraph because we used it in the motivation already}
+\par In the literature we can see different ways of approaching this issue. The
+first one is to select parameters, train the model, evaluate it, repeat and pick
+the best one. There are many different ways of selecting parameters: random
+search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref],
+Gaussian processes [ref] etc... but they all suffer from one major drawback: we
+have to train and evaluate a very large number of models; and even if some
+algorithms allow parallel evaluations [ref] to reduce the overall training time,
+the hardware and energy cost is still very significant.
+
+\ra{I'd argue these techniques are aimed to improve inference time and not to
+avoid hyper-parameter optimization}
+\par To reduce the number of models trained, another approach is to train a
+slightly bigger model and after convergence, remove as many parameters as
+possible without impacting the performance of the model. Notable contributions
+are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref]
+(this one is especially related to this article). These techniques are very
+interesting but they still require a reasonable network size to start with, so
+they usually have to be combined with classic hyper-optimization techniques.
+
+\srm{How is this shrinking
+approach different than previous approaches like Optimal Brain Damage, Deep
+Compression,e tc?}
+
+\par However, some recent contributions like Non-Parametric Neural Netowrks
+[ref] and [ref] try to learn the network size (width for the former and depth
+for the latter) during the training process and without any prior assumption
+about the network size. \ra{revise next}This method dynamically grows and shrinks the network
+over time. Though this seems to be an attractive property to have, during our
+experiments and according to their results, models are very slow to train and
+sometimes converge to suboptimal solutions. Their method also requires a new
+optimizer \textit{AdaRad}. \ra{explain how difficult is to get the optimizer
+stable. that's a drawback of the method} \ra{Instead, ShrinkNets work out of the
+box with existing libraries and does not need any changes to the optimizer.}
+
+\srm{Give a short sentence about how our approach is
+different than these previous approaches.}
 
@@
 
-\par Even though the firsts results this technique yields seem promising, there are many area that we could explore to improve it.
-In the current implementation we only "learn" the number of features (neurons or channels).
-We could try to augment it with dynamic number of layers as seen in [ref] to be able to determine the entire architecture.
-\par We saw on Figure \ref{convergence_plot} that the loss temporarily suffers from the removal of neurons.
-It is likely that the loss would be more stable if the number of neurons converged faster or neurons disappeared slower.
-For this reason we plan to explore proximal gradient methods to optimize the filter vectors and/or randomize neuron removals.
-\par During our evaluation we picked small datasets mainly to be able to train many models and have statistically significant distributions.
-With more computation resources and time, we could see if it generalizes to bigger datasets and other architectures like \texttt{ResNet} [ref] (small modifications to the existing code base are required to support them)
+\ra{this can be shorted, and used as conclusions}
+
+\par Even though the firsts results this technique yields seem promising, there
+are many area that we could explore to improve it. In the current implementation
+we only "learn" the number of features (neurons or channels). We could try to
+augment it with dynamic number of layers as seen in [ref] to be able to
+determine the entire architecture.  \par We saw on Figure \ref{convergence_plot}
+that the loss temporarily suffers from the removal of neurons. It is likely that
+the loss would be more stable if the number of neurons converged faster or
+neurons disappeared slower. For this reason we plan to explore proximal gradient
+methods to optimize the filter vectors and/or randomize neuron removals.  \par
+During our evaluation we picked small datasets mainly to be able to train many
+models and have statistically significant distributions. With more computation
+resources and time, we could see if it generalizes to bigger datasets and other
+architectures like \texttt{ResNet} [ref] (small modifications to the existing
+code base are required to support them)
 

### 2018-01-04 paper/paper.tex
New pass up to Evaluation

@@
 \newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
+\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
 \begin{document}
@@
 is key. In particular, these hyper parameters have a strong correlation with
-over/underfitting \srm{give reference}. The main problem is that we have no
-reliable way to find them [ref]. Decades of experimentation led to some
-heuristics [ref] that try to prune that immense space of possible network sizes.
-For example, researchers have used strategies such as random search,
-meta-gradient descent and parser trees to reduce find good parameters without
-exhaustively exploring the entire hyper-parameter space. Although these
-strategies help with finding a good set of hyper-parameters, they still require
-a compute-intensive search of the space.
+over/underfitting \srm{give reference} \gl{I did some litterature review and
+  actually this statement is quite controversial, should we rephrase ?}. The
+main problem is that we have no reliable way to find them [ref]. Decades of
+experimentation led to some heuristics [ref] that try to prune that immense
+space of possible network sizes.  For example, researchers have used strategies
+such as random search \gl{Should we also move the references here if we remove
+  the pargraph from the related work ?}, meta-gradient descent and parser trees
+to reduce find good parameters without exhaustively exploring the entire
+hyper-parameter space. Although these strategies help with finding a good set
+of hyper-parameters, they still require a compute-intensive search of the
+space.
 
-%However, we are still bound to use costly and sometimes complex methods to find
-%reasonable values for these hyper-parameters.
+%However, we are still bound to use costly and sometimes complex methods to
+%find reasonable values for these hyper-parameters.
 
 \srm{In this paper, we describe ... -- need to give a high level idea of
-solution, and its benefits.  Would be good to give your system/approach a name.}
+  solution, and its benefits.  Would be good to give your system/approach a
+  name.}
 
 In this paper we present a method to automatically find an appropriate network
-size without paying the compute and time cost of searching through a large
-hyper-parameter space. The key idea is to \emph{learn} the right network size at
-the same time that the network is learning the main task. For example, for an
-image classification task, with our approach we can provide the training data to
-a network---without sizing it a priori---and expect to end up with a network
-that has learnt the task without overfitting. This approach has two main
-benefits. First, we do no longer need to choose a network size before training.
-Second, the final network size will be appropriate for the task at hand, and not
-larger. This is important because oversized networks have a lower inference
-throughput.
+size from a single parameter, drastically reducing the hyper-parameter
+dimensionality. The key idea is to \emph{learn} the right network size at the
+same time that the network is learning the main task. For example, for an image
+classification task, with our approach we can provide the training data to a
+network---without sizing it a priori---and expect to end up with a network that
+has learnt the task without overfitting \gl{too strong, we do not really have
+  any guarantee on the generalization, how about changing it to: to end up with
+  a network that learnt a tradeoff between size and accuracy}. This approach
+has two main benefits. First, we do no longer need to choose a network size
+before training.  Second, the final network size will be appropriate for the
+task at hand, and not larger \gl{Should we talk about the fact that it automatically gets rid of dead neurons ?}. This is important because oversized networks have
+a lower inference throughput and higher  memory footprint.
 
@@
 
-Filter layers have weights in the range $[0,1]$ and are placed after linear and
-convolutional layers of traditional deep networks. The \textit{Filter Layer}
-takes an input of size $\left(B \times C \times D_1 \times \dots \times
-D_n\right)$ so it is compatible with fully connected layers with $n=0$ or
-convolutional layers with $n=2$. Their crucial property is a parameter $\theta \in
-\mathbb{R}^C$, defined as follows: \srm{Need to define B, C, D}.
+Filter layers have weights in the range $[0,+\infty]$ and are placed after
+linear and convolutional layers of traditional deep networks \gl{This is how I
+  used it but with the new implementation we can be more creative and put them
+  anywhere, should we say "usually placed" insdead ?}. The \textit{Filter
+  Layer} takes an input of size $\left(B \times C \times D_1 \times \dots
+  \times D_n\right)$, where $B$ is the batch size, $C$ the number of features
+(or channels), and $D$ any additional dimension. This structure makes it
+compatible with fully connected layers with $n=0$ or convolutional layers with
+$n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$, defined
+as follows: \srm{Need to define B, C, D} \gl{=> done}.
 
-\begin{equation} 
-Filter(I;\theta) = I \circ \max(0, \theta)
-\end{equation}
+\begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
 
-Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
-is expanded in all dimensions except the second one to match the input size. It
-is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
-feature/channel will forever be $0$. When this happens, we say the Filter layer
-disables the neuron. These disabled neurons/channels can be removed from the
-network without changing its output (we describe how we perform this removal
-below). We explain next how the weights of the Filter Layer are
-adjusted during training.
+Where $\circ$ is the Hadamard product (pointwise multiplication) \gl{Should we
+  keep only one of them to be more concise ?}, and $\theta$ is expanded in all
+dimensions except the second one to match the input size. It is easy to see
+that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel
+will forever be $0$. When this happens, we say the Filter layer disables the
+neuron. These disabled neurons/channels can be removed from the network without
+changing its output (we describe how we perform this removal below). We explain
+next how the weights of the Filter Layer are adjusted during training.
 
@@
 smallest network with reasonable performance. We achieve that by introducing
-sparsity in the parameters of the \textit{Filter Layers}. Indeed, \srm{having a
-negative value where?} having a negative value is equivalent to zeroing an
-entire row and column in the surrounding layers. To obtain this sparsity, we
-simply redefinte the loss function:
+sparsity in the parameters of the \textit{Filter Layers}.
+Indeed, having a negative component in the $\theta$ parameter of the filter layer permamently disable its associated feature \gl{Maybe redundant ?
+we talked about that in the previous paragraph}
+. To obtain this sparsity, we simply redefine the loss function:
 
@@
 
-The $\lambda$ parameter controls the trade-off between optimizing the original
-loss or the size of the network.  \srm{Again give some intuitive description of
-what is novel / important about this choice of loss function and learning
-process.  It's hard to understand what is interesting/important about what you
-have done without you explicitly calling it out.}
+This choice come from the Lasso loss [ref] and we use it for the same reason:
+it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
+are set to zer, and since zeros entries in $\theta$ correspond to dead neurons,
+lambda effectively control the number of neurons/channels in the entire
+network. \srm{Again give some intuitive description of what is novel /
+  important about this choice of loss function and learning process.  It's hard 
+  to understand what is interesting/important about what you have done without
+  you explicitly calling it out.} \gl{Is it better this way ?}
 
@@
 
-To obtain good performance using this approach, it is essential to be able to
-remove neurons and channels from the network as quickly as possible. This task
-usually is cumbersome using existing machine learning frameworks. To enable
-this, we implemented a small library on top of \textit{PyTorch} which makes it
-very easy to design and train networks that contains \textit{Filter Layers}. We
-will briefly describe the software architecture.  \par The key operation we want
-to perform is to notify layers when a feature is removed so they can resize
-themselves. Therefore, we need to track the child and parents each layer. Since
-there is no concept of computation graph in \textit{PyTorch} we had to build it;
-specifically,  layers are augmented with a list of incoming modules (parents)
-and outgoing modules (children).  \par Edges in the graph carry features from
-parent to children. When a \textit{Filter Layer} removes a feature, edges need
-to notify layers of the change.  We implemented a simple event-based
-architecture where edges send events about features to layers.  \srm{Suggest
-cutting the following: Each  edge maintains a list of features to keep, and
-called a \texttt{FeatureBag}. In many cases, layers do not change the number of
-features (e.g., \textit{Dropout}, \textit{BatchNorm}), therefore, event needs to
-propagate through them to notify all layers that share the same number of
-features. To solve this problem, such layers instantiate
-\texttt{MirrorFeatureBags} which role is to relay events to and from the root
-\texttt{FeatureBag}.} With this event-based approach are able to keep all the
-layers in sync. Adding layers becomes straightforward: programmers just have to
-react to three events: input removal, output removal and garbage collection.
-\srm{What does garbage collection do?} During our tests we ran the garbage
-collection every epoch.
+\gl{Here is a shorter (clearer ?) version:}
+
+\par \textit{Filter Vectors} can easily be implemented in a few lines of code
+in many existing deep learning frameworks. However, in ShrinkNets we assume
+that we start with obviously oversized networks. If disabled neurons are not
+quickly removed, the overhead might caused the training process to be
+significantly slower than classic neural networks. This is why we want to
+support what we call garbage collection: removing the weights in the layers
+that are responsible(or using) features that are disabled.
+\par To be able to catpure this relationship between layers we agumented
+\textit{Pytorch} (the framework we used as the foundation of our implementation)
+with a graph structure very similar to the one available in Keras [ref].
+In this graph edges are effectively event hubs responsible for propagating
+\textit{feature removal} events to subscribing layers. ShrinkNet layers are
+agumented to emit and react to these events but also propagate the event
+further if has an impact at the other endpoint of the layer (input or output).
+\par This event-based implementation coordinated by edges makes it very easy
+to integrate new layers in the library. We even provide automatic wrapping
+for layers from pytorch if they have no internal state. For more complex ones,
+we provide utilitaries that makes the implementation very concise.
 

### 2018-01-04 paper/paper.tex
Writing pass up to Related Work

@@
 To demonstrate that the approach is viable, we will first show that Shrinking
-Networks converge. For this experiment we trained a one hidden layer neural
-network with one filter layer to control the number of hidden units. We
+Networks converge properly. For this experiment we trained a one hidden layer
+neural network with one filter layer to control the number of hidden units. We
 initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
-using different regularization factors ($\lambda$). We summarized the results in
-\autoref{convergence_plot}. [Should we explain the results ?] \srm{Yes, you need
-to explain in detail -- what does this show?  How does it prove that your
-approach works / is a good idea?}
-
+using different regularization factors ($\lambda$). We summarized the results
+in \autoref{convergence_plot}. We can see on this plot is that
+for a given $\lambda$ the number of hidden units seems to always converge to
+some value. It has two implications: it seems that $\lambda$ is, as we would think,
+a proxy of the network size (bigger $\lambda$ imply smaller networks). Secondly,
+it indicates that the spikes we see in the regular spikes we see in the loss that occur when neurons are disabled will eventually disapear because the number of neurons reach a plateau.
+\gl{I feel we should give a conclusion for this paragraph but
+I am not sure what to say}
 \begin{figure}
@@
 
+\subsection{Relevance in the context of hyper-parameter optimization}
+
+\gl{I rewrote the entire section}
+
+One of our main goal is to help finding neural network architectures that
+perform reasonably well faster than existing techniques. For simplicity,
+we will try to see how ShrinkNets perform when doing random search. However,
+we believe that the results generalize to more complex methods, most of them
+might actually benefit a lot from the reduction in the dimensionality of the
+hyper-parameter space.
+
+\par To isolate the effect of ShrinkNets we will consider very simple architectures
+We will be using multi-layer perceptrons (with three hidden layers) and
+convolutional neural networks (With the LeNet-5 architecture). For this experiment
+we will assume we have no information about the size except an upper bound of
+$50$ channels per convolutional layer and $5000$ neuron for fully connected layers.
+We try to find the appropriate size of the network using classical neural networks
+and ShrinkNets. To make sure that we are as fair as possible and since one might
+argue that ShrinkNets is also regularizing the network in addition to finding the
+size, we will also considered regualrized classic networks using the most commonly
+used technique the $L_2$ penalty [ref].
+\par The experiment consist in sampling parameters randomly for each class of
+network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation accuracy and evaluate it
+on the testing set. We repeat the process for 50 models. This evaluation was done
+on \texttt{MNIST} [ref], \texttt{FashionMNIST} [ref] and \texttt{CIFAR10} [ref]. The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.
+
+We can see that the distributions for ShrinkNets are consistently better than the
+others for all datasets and both architectures. It shows that by training fewer
+networks, we are likely to obtain on-par or even better models which effectively
+reduces the cost of hyper-parameter optimization. In some cases the best ShrinkNets
+models outperforms the best model of the other techniques.
+
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Comparison between Shrinking and classic Networks}
-
-To demonstrate the value of ShrinkNets in the context of hyper-parameter
-optimization we set up the following experiment: We consider two different
-architectures, a three hidden layer feed forward network and a \textit{LeNet-5}
-[ref]. We do not know the number of channels and neurons and we want to find the
-best architecture by performing random search on the parameters that define the
-size. For classic neural networks these parameters are the number of channels
-and/or neurons; for ShrinkNets there is only one parameter, $\lambda$. We
-sampled 50 models of each and trained them, picked the best epoch according to
-the validation accuracy and measured their performance on the testing set. Since
-ShrinkNets can be considered to be regularized in some sense, to make the
-comparison fair we also considered static networks with an $L2$ regularization
-factor (also drawn randomly) \srm{L2 regularization over what?}. We summarized
-the accuracy we obtained on \autoref{hyper_opt_res}. [Should we explain the
-results] \srm{Yes, need to describe in detail -- how does this prove that your
-method works/ is a good idea?  What are the key takeaways?}
 

### 2018-01-05 paper/paper.tex
Finish my writing pass on the paper

@@
 
-\srm{In this paper, we describe ... -- need to give a high level idea of
-  solution, and its benefits.  Would be good to give your system/approach a
-  name.}
-
 In this paper we present a method to automatically find an appropriate network
@@
 
-\srm{Describe our key approach at a high level -- i.e., add a new layer to the
-network, called the {\it filter layer}, which ... }
-
 Our approach consists of starting the training process for the task of interest
@@
 
-\textbf{Filter Layer: }
-
-Filter layers have weights in the range $[0,+\infty]$ and are placed after
+\textbf{Filter Layers: } They have weights in the range $[0,+\infty]$ and are placed after
 linear and convolutional layers of traditional deep networks \gl{This is how I
@@
 $n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$, defined
-as follows: \srm{Need to define B, C, D} \gl{=> done}.
+as follows:
 
@@
 
-Where $\circ$ is the Hadamard product (pointwise multiplication) \gl{Should we
-  keep only one of them to be more concise ?}, and $\theta$ is expanded in all
+Where $\circ$ is the Hadamard product (pointwise multiplication \gl{Should we
+  keep only one of them to be more concise ?}), and $\theta$ is expanded in all
 dimensions except the second one to match the input size. It is easy to see
@@
 %We can use this property to devise a training procedure.
-
-\srm{Give an English description of what this formalism
-achieves -- what does the filter layer do, why is it significant.}
 
@@
 lambda effectively control the number of neurons/channels in the entire
-network. \srm{Again give some intuitive description of what is novel /
-  important about this choice of loss function and learning process.  It's hard 
-  to understand what is interesting/important about what you have done without
-  you explicitly calling it out.} \gl{Is it better this way ?}
-
+network.
 Next, we explain how to implement ShrinkNets efficiently.
 
-\section{Software architecture}
-
-\ra{this can be shorter. I'd add it as a third paragraph above, immediately
-above the eval}
-
-\gl{Here is a shorter (clearer ?) version:}
-
-\par \textit{Filter Vectors} can easily be implemented in a few lines of code
+\textbf{Software architecture\footnote{The code is available as Python/PyTorch library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename the repository ?}} :}\textit{Filter Vectors} can easily be implemented in a few lines of code
 in many existing deep learning frameworks. However, in ShrinkNets we assume
@@
 
-\gl{I rewrote the entire section}
-
 One of our main goal is to help finding neural network architectures that
@@
 
-\ra{I'd remove this paragraph because we used it in the motivation already}
-\par In the literature we can see different ways of approaching this issue. The
-first one is to select parameters, train the model, evaluate it, repeat and pick
-the best one. There are many different ways of selecting parameters: random
-search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref],
-Gaussian processes [ref] etc... but they all suffer from one major drawback: we
-have to train and evaluate a very large number of models; and even if some
-algorithms allow parallel evaluations [ref] to reduce the overall training time,
-the hardware and energy cost is still very significant.
-
-\ra{I'd argue these techniques are aimed to improve inference time and not to
-avoid hyper-parameter optimization}
-\par To reduce the number of models trained, another approach is to train a
-slightly bigger model and after convergence, remove as many parameters as
-possible without impacting the performance of the model. Notable contributions
-are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref]
-(this one is especially related to this article). These techniques are very
-interesting but they still require a reasonable network size to start with, so
-they usually have to be combined with classic hyper-optimization techniques.
-
-\srm{How is this shrinking
-approach different than previous approaches like Optimal Brain Damage, Deep
-Compression,e tc?}
-
-\par However, some recent contributions like Non-Parametric Neural Netowrks
-[ref] and [ref] try to learn the network size (width for the former and depth
-for the latter) during the training process and without any prior assumption
-about the network size. \ra{revise next}This method dynamically grows and shrinks the network
-over time. Though this seems to be an attractive property to have, during our
-experiments and according to their results, models are very slow to train and
-sometimes converge to suboptimal solutions. Their method also requires a new
-optimizer \textit{AdaRad}. \ra{explain how difficult is to get the optimizer
-stable. that's a drawback of the method} \ra{Instead, ShrinkNets work out of the
-box with existing libraries and does not need any changes to the optimizer.}
-
-\srm{Give a short sentence about how our approach is
-different than these previous approaches.}
-
-\section{Future work}
-
-\ra{this can be shorted, and used as conclusions}
-
-\par Even though the firsts results this technique yields seem promising, there
-are many area that we could explore to improve it. In the current implementation
-we only "learn" the number of features (neurons or channels). We could try to
-augment it with dynamic number of layers as seen in [ref] to be able to
-determine the entire architecture.  \par We saw on Figure \ref{convergence_plot}
-that the loss temporarily suffers from the removal of neurons. It is likely that
-the loss would be more stable if the number of neurons converged faster or
-neurons disappeared slower. For this reason we plan to explore proximal gradient
-methods to optimize the filter vectors and/or randomize neuron removals.  \par
-During our evaluation we picked small datasets mainly to be able to train many
-models and have statistically significant distributions. With more computation
-resources and time, we could see if it generalizes to bigger datasets and other
-architectures like \texttt{ResNet} [ref] (small modifications to the existing
-code base are required to support them)
+\par There are many methods in the litterature that try to simplify the neural
+network. Most of them focuses on removing connections (eg: [ref], [ref]).
+However, most hardware (GPU's, TPUS, TensorCores) do not really leverage sparsity
+in the connections efficiently. On the other side, ShrinkNets and some others [ref]
+and [ref] try to remove entire neuron instead of connections. This is very
+usefull because it reduce the size of the matrices, producing speed-up on
+every device. ShrinkNets improves on [ref] because it removes neurons during
+training, speeding up the rest of the process and beats [ref] on convergence
+speed and because it does not need to change the optimizer. To the best of our
+knowledge this is also the first contribution that tries to learn the number of
+channels of a convolutional neural network.
 
 \section{Conclusion}
-Do the conclusion at the end
+
+In this paper we presented a novel technique to guess a resonable network size
+based on single parameter $\lambda$ that control the tradeof between loss and
+the size. We demonstrated that it works both on fully connected networks and
+convolutional neural networks.  Even though the firsts results seem promising,
+there are many ways we could improve. In the current
+implementation we only "learn" the number of features (neurons or channels). We
+could try to augment it with dynamic number of layers as seen in [ref] to be
+able to determine the entire architecture. \par We saw on Figure
+\ref{convergence_plot} that the loss temporarily suffers from the removal of
+neurons. It is likely that the loss would be more stable if the number of
+neurons converged faster or neurons disappeared slower. For this reason we plan
+to explore proximal gradient methods to optimize the filter vectors and/or
+randomize neuron removals. \par During our evaluation we picked small datasets
+mainly to be able to train many models and have statistically significant
+distributions. With more computation resources and time, we could see if it
+generalizes to bigger datasets and other architectures like \texttt{ResNet}
+[ref] (small modifications to the existing code base are required to support
+them)
 

### 2018-01-05 paper/paper.tex
Some typos

@@
 it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
-are set to zer, and since zeros entries in $\theta$ correspond to dead neurons,
+are set to zer0, and since zero entries in $\theta$ correspond to dead neurons,
 lambda effectively control the number of neurons/channels in the entire
@@
 
-\textbf{Software architecture\footnote{The code is available as Python/PyTorch library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename the repository ?}} :}\textit{Filter Vectors} can easily be implemented in a few lines of code
-in many existing deep learning frameworks. However, in ShrinkNets we assume
-that we start with obviously oversized networks. If disabled neurons are not
-quickly removed, the overhead might caused the training process to be
-significantly slower than classic neural networks. This is why we want to
-support what we call garbage collection: removing the weights in the layers
-that are responsible(or using) features that are disabled.
-\par To be able to catpure this relationship between layers we agumented
-\textit{Pytorch} (the framework we used as the foundation of our implementation)
-with a graph structure very similar to the one available in Keras [ref].
-In this graph edges are effectively event hubs responsible for propagating
-\textit{feature removal} events to subscribing layers. ShrinkNet layers are
-agumented to emit and react to these events but also propagate the event
-further if has an impact at the other endpoint of the layer (input or output).
-\par This event-based implementation coordinated by edges makes it very easy
-to integrate new layers in the library. We even provide automatic wrapping
-for layers from pytorch if they have no internal state. For more complex ones,
-we provide utilitaries that makes the implementation very concise.
+\textbf{Software architecture\footnote{The code is available as Python/PyTorch
+    library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
+      the repository ?}}: }\textit{Filter Vectors} can easily be implemented in
+a few lines of code in many existing deep learning frameworks. However, in
+ShrinkNets, we assume that we start with obviously oversized networks. If
+disabled neurons are not quickly removed, the overhead might cause the training
+process to be significantly slower than classic neural networks. This is why we
+want to support what we call garbage collection: removing the weights in the
+layers that are responsible (or using) features that are disabled.  \par To be
+able to catpure this relationship between layers, we agumented \textit{Pytorch}
+(the framework we used as the foundation of our implementation) with a graph
+structure very similar to the one available in Keras [ref].  In this graph,
+edges are effectively event hubs responsible for propagating \textit{feature
+  removal} events to its endpoints. ShrinkNet layers are designed to emit and
+react to these events but also propagate the event further if has an impact at
+the other endpoint of the layer (input or output) \gl{What I mean here is: if
+  the event comes from the output, it might be propagated to the inputs, and
+  the other way around}.  \par This event-based implementation coordinated by
+edges makes it very easy to integrate new layers in the library. We even
+provide automatic wrapping for layers from \textit{PyTorch} if they have no
+internal state. For more complex ones, we provide utilitaries that makes the
+implementation very concise.
 
@@
 One of our main goal is to help finding neural network architectures that
-perform reasonably well faster than existing techniques. For simplicity,
-we will try to see how ShrinkNets perform when doing random search. However,
-we believe that the results generalize to more complex methods, most of them
-might actually benefit a lot from the reduction in the dimensionality of the
-hyper-parameter space.
+perform reasonably well faster than existing techniques. For simplicity, we
+will try to see how ShrinkNets perform when doing random search over a sub set
+of the hyper-parameter space (we will fix everything except the size-related
+parameters). However, we believe that the results generalize to more complex
+methods, most of them might actually benefit a lot from the reduction of the
+dimensionality of the hyper-parameter space.
 
-\par To isolate the effect of ShrinkNets we will consider very simple architectures
-We will be using multi-layer perceptrons (with three hidden layers) and
-convolutional neural networks (With the LeNet-5 architecture). For this experiment
-we will assume we have no information about the size except an upper bound of
-$50$ channels per convolutional layer and $5000$ neuron for fully connected layers.
-We try to find the appropriate size of the network using classical neural networks
-and ShrinkNets. To make sure that we are as fair as possible and since one might
-argue that ShrinkNets is also regularizing the network in addition to finding the
-size, we will also considered regualrized classic networks using the most commonly
-used technique the $L_2$ penalty [ref].
+\par To isolate the effect of ShrinkNets we will consider two very simple
+architectures: multi-layer perceptrons (with three hidden layers) and the
+\textit{LeNet-5} model. For this experiment we assume we have no prior
+information about the size except an upper bound of $50$ channels per
+convolutional layer and $5000$ neuron for fully connected layers.  We try to
+find the appropriate size of the network using classical neural networks and
+ShrinkNets. To make sure that we are as fair as possible and since one might
+argue that ShrinkNets is also regularizing the network in addition to finding
+the size, we will also considered regularized classic networks using the most
+commonly used technique: the $L_2$ penalty [ref].
 \par The experiment consist in sampling parameters randomly for each class of
-network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation accuracy and evaluate it
+network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation set and evaluate it
 on the testing set. We repeat the process for 50 models. This evaluation was done
@@
 reduces the cost of hyper-parameter optimization. In some cases the best ShrinkNets
-models outperforms the best model of the other techniques.
+models even outperforms the best model of the other techniques.
 
@@
 \par There are many methods in the litterature that try to simplify the neural
-network. Most of them focuses on removing connections (eg: [ref], [ref]).
-However, most hardware (GPU's, TPUS, TensorCores) do not really leverage sparsity
-in the connections efficiently. On the other side, ShrinkNets and some others [ref]
-and [ref] try to remove entire neuron instead of connections. This is very
-usefull because it reduce the size of the matrices, producing speed-up on
-every device. ShrinkNets improves on [ref] because it removes neurons during
-training, speeding up the rest of the process and beats [ref] on convergence
-speed and because it does not need to change the optimizer. To the best of our
-knowledge this is also the first contribution that tries to learn the number of
-channels of a convolutional neural network.
+network structure. Most of them focuses on removing connections (eg: [ref],
+[ref]).  However, most hardware (GPU's, TPUS, TensorCores) do not really
+leverage sparsity in the connections efficiently. On the other side, ShrinkNets
+and some others [ref] and [ref] try to remove entire neuron instead of
+connections. This is very usefull because it reduces the size of the matrices,
+producing speed-up on every device. ShrinkNets improves on [ref] because it
+removes neurons during training, speeding up the rest of the process and beats
+[ref] on convergence speed and because it does not need to change the
+optimizer. To the best of our knowledge this is also the first contribution
+that tries to learn the number of channels of a convolutional neural network.
 

### 2018-01-05 paper/hyper_opt_epxeriment_plot.py
Resolve bibliograph, fc experiments and updated scripts

@@ -9,9 +9,9 @@ rc('font',**{'family':'serif','serif':['Palatino']})
 rc('text', usetex=True)
 
 nice_boundaries = {
-    'MNIST': (94.5, 99),
-    'FashionMNIST': (80, 91),
-    'CIFAR10': (45, 56)
+    'MNIST': (97, 98.75),
+    'FashionMNIST': (86, 90),
+    'CIFAR10': (46, 56)
 }
 
 conv_nice_boundaries = {
@@ -47,12 +47,16 @@ def load_files(dataset, mode, max_samples=50, conv=False):
     # assert len(all_files) == max_samples, "Not enough experiments"
     return np.stack([load_single_file(f) for f in all_files])
 
-for conv in [True]:
+for conv in [True, False]:
+    if conv:
+        print("Convolutional:")
+    else:
+        print("Fully Connected")
     for dataset in nice_boundaries.keys():
         print(dataset)
         for mode in modes:
             infos = load_files(dataset, mode, 50000, conv)[:, [1, 3]]
-            bests_indices = infos[:, 0].argsort()[::-1]
+            bests_indices = infos[:, 0].argsort()[::-1][:10]
             res = np.percentile(infos[bests_indices], 50, axis=0)
             print('\t'.join(map(str, [mode] + list(res))))
 
@@ -60,7 +64,9 @@ for conv in [True]:
 def sub_plot(ax, dataset, first, conv=False, ff=False):
     try:
         infos = [load_files(dataset, mode, 50, conv)[:, 2] * 100 for mode in modes]
-        result = ax.boxplot(infos, patch_artist=True, widths=0.7)
+        result = ax.boxplot(infos, patch_artist=True, widths=0.7,
+                            medianprops={'color': (250/255, 49/255,0, 1), 'linewidth': 2}
+                            )
     except:
         result = {'boxes': []}
         pass

### 2018-01-05 paper/paper.tex

@@
 over/underfitting \srm{give reference} \gl{I did some litterature review and
-  actually this statement is quite controversial, should we rephrase ?}. The
-main problem is that we have no reliable way to find them [ref]. Decades of
-experimentation led to some heuristics [ref] that try to prune that immense
-space of possible network sizes.  For example, researchers have used strategies
-such as random search \gl{Should we also move the references here if we remove
-  the pargraph from the related work ?}, meta-gradient descent and parser trees
-to reduce find good parameters without exhaustively exploring the entire
-hyper-parameter space. Although these strategies help with finding a good set
-of hyper-parameters, they still require a compute-intensive search of the
-space.
+  actually this statement is quite controversial, should we rephrase ?}. We
+have no reliable way to find them but decades of experimentation led to some
+heuristics ~\cite{Bengio2012a} that try to prune that immense space of possible
+network sizes and suggest range of values to explore. To select the best
+candidates , researchers have used strategies such as random search \gl{Should
+  we also move the references here if we remove the pargraph from the related
+  work ?}, meta-gradient descent ~\cite{Pedregosa2016} and Parzen Estimators
+~\cite{Bergstra2011a} to reduce find good parameters without exhaustively
+exploring the entire hyper-parameter space. Although these strategies help with
+finding a good set of hyper-parameters, they still require a compute-intensive
+search of the space.
 
@@
 
-This choice come from the Lasso loss [ref] and we use it for the same reason:
+This choice come from the Lasso loss ~\cite{Tibshirani1996} and we use it for the same reason:
 it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
@@
 able to catpure this relationship between layers, we agumented \textit{Pytorch}
-(the framework we used as the foundation of our implementation) with a graph
-structure very similar to the one available in Keras [ref].  In this graph,
-edges are effectively event hubs responsible for propagating \textit{feature
-  removal} events to its endpoints. ShrinkNet layers are designed to emit and
-react to these events but also propagate the event further if has an impact at
-the other endpoint of the layer (input or output) \gl{What I mean here is: if
-  the event comes from the output, it might be propagated to the inputs, and
-  the other way around}.  \par This event-based implementation coordinated by
-edges makes it very easy to integrate new layers in the library. We even
-provide automatic wrapping for layers from \textit{PyTorch} if they have no
-internal state. For more complex ones, we provide utilitaries that makes the
-implementation very concise.
+~\cite{paszke2017automatic} (the framework we used as the
+foundation of our implementation) with a graph structure very similar to the
+one available in Keras ~\cite{chollet2015keras}.  In this graph, edges are
+effectively event hubs responsible for propagating \textit{feature removal}
+events to its endpoints. ShrinkNet layers are designed to emit and react to
+these events but also propagate the event further if has an impact at the other
+endpoint of the layer (input or output) \gl{What I mean here is: if the event
+  comes from the output, it might be propagated to the inputs, and the other
+  way around}.  \par This event-based implementation coordinated by edges makes
+it very easy to integrate new layers in the library.  We even provide automatic
+wrapping for layers from \textit{PyTorch} if they have no internal state. For
+more complex ones, we provide utilitaries that
+makes the implementation very concise.
 
@@
 initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
-using different regularization factors ($\lambda$). We summarized the results
-in \autoref{convergence_plot}. We can see on this plot is that
-for a given $\lambda$ the number of hidden units seems to always converge to
-some value. It has two implications: it seems that $\lambda$ is, as we would think,
-a proxy of the network size (bigger $\lambda$ imply smaller networks). Secondly,
-it indicates that the spikes we see in the regular spikes we see in the loss that occur when neurons are disabled will eventually disapear because the number of neurons reach a plateau.
-\gl{I feel we should give a conclusion for this paragraph but
-I am not sure what to say}
+~\cite{Lecun1998} using different regularization factors ($\lambda$). We
+summarized the results in \autoref{convergence_plot}. We can see on this plot
+is that for a given $\lambda$ the number of hidden units seems to always
+converge to some value. It has two implications: it seems that $\lambda$ is, as
+we would think, a proxy of the network size (bigger $\lambda$ imply smaller
+networks). Secondly, it indicates that the spikes we see in the regular spikes
+we see in the loss that occur when neurons are disabled will eventually
+disapear because the number of neurons reach a plateau. \gl{I feel we should
+  give a conclusion for this paragraph but I am not sure what to say}
 \begin{figure}
@@
 architectures: multi-layer perceptrons (with three hidden layers) and the
-\textit{LeNet-5} model. For this experiment we assume we have no prior
+\textit{LeNet-5} model ~\cite{Lecun1998}. For this experiment we assume we have no prior
 information about the size except an upper bound of $50$ channels per
@@
 the size, we will also considered regularized classic networks using the most
-commonly used technique: the $L_2$ penalty [ref].
+commonly used technique: the $L_2$ penalty ~\cite{Ng2004}.
 \par The experiment consist in sampling parameters randomly for each class of
@@
 on the testing set. We repeat the process for 50 models. This evaluation was done
-on \texttt{MNIST} [ref], \texttt{FashionMNIST} [ref] and \texttt{CIFAR10} [ref]. The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.
+on \texttt{MNIST} ~\cite{Lecun1998}, \texttt{FashionMNIST} ~\cite{Xiao2017} and \texttt{CIFAR10} ~\cite{Krizhevsky2009}.
+The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.
 
@@
 \par There are many methods in the litterature that try to simplify the neural
-network structure. Most of them focuses on removing connections (eg: [ref],
-[ref]).  However, most hardware (GPU's, TPUS, TensorCores) do not really
-leverage sparsity in the connections efficiently. On the other side, ShrinkNets
-and some others [ref] and [ref] try to remove entire neuron instead of
+network structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
+~\cite{Han2015}).  However, most hardware (GPU's, TPUS ~\cite{Jouppi2017}, TensorCores) do not really
+leverage sparsity in the connections efficiently (as explained in ~\cite{Han2016}). On the other side, ShrinkNets
+and some others ~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neuron instead of
 connections. This is very usefull because it reduces the size of the matrices,
-producing speed-up on every device. ShrinkNets improves on [ref] because it
-removes neurons during training, speeding up the rest of the process and beats
-[ref] on convergence speed and because it does not need to change the
-optimizer. To the best of our knowledge this is also the first contribution
-that tries to learn the number of channels of a convolutional neural network.
+producing speed-up on every device. ShrinkNets improves on
+~\cite{Scardapane2017} because it removes neurons during training, speeding up
+the rest of the process and beats ~\cite{Philipp} on convergence speed and because it
+does not need to change the optimizer. To the best of our knowledge this is
+also the first contribution that tries to learn the number of channels of a
+convolutional neural network.
 
@@
 convolutional neural networks.  Even though the firsts results seem promising,
-there are many ways we could improve. In the current
-implementation we only "learn" the number of features (neurons or channels). We
-could try to augment it with dynamic number of layers as seen in [ref] to be
-able to determine the entire architecture. \par We saw on Figure
-\ref{convergence_plot} that the loss temporarily suffers from the removal of
-neurons. It is likely that the loss would be more stable if the number of
-neurons converged faster or neurons disappeared slower. For this reason we plan
-to explore proximal gradient methods to optimize the filter vectors and/or
-randomize neuron removals. \par During our evaluation we picked small datasets
-mainly to be able to train many models and have statistically significant
-distributions. With more computation resources and time, we could see if it
-generalizes to bigger datasets and other architectures like \texttt{ResNet}
-[ref] (small modifications to the existing code base are required to support
-them)
+there are many ways we could improve. In the current implementation we only
+"learn" the number of features (neurons or channels). We could try to augment
+it with dynamic number of layers as seen in ~\cite{meier} to be able to
+determine the entire architecture. \par We saw on Figure \ref{convergence_plot}
+that the loss temporarily suffers from the removal of neurons. It is likely
+that the loss would be more stable if the number of neurons converged faster or
+neurons disappeared slower. For this reason we plan to explore proximal
+gradient methods to optimize the filter vectors and/or randomize neuron
+removals. \par During our evaluation we picked small datasets mainly to be able
+to train many models and have statistically significant distributions. With
+more computation resources and time, we could see if it generalizes to bigger
+datasets and other architectures like \texttt{ResNet} ~\cite{He2016} (small
+modifications to the existing code base are required to support them)
 
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-bibliography}
+\bibliography{bib,custom}
 

### 2018-01-05 paper/hyper_opt_epxeriment_plot.py
Final plot

@@ -10,7 +10,7 @@ rc('text', usetex=True)
 
 nice_boundaries = {
     'MNIST': (97, 98.75),
-    'FashionMNIST': (86, 90),
+    'FashionMNIST': (86, 90.2),
     'CIFAR10': (46, 56)
 }
 
@@ -44,7 +44,7 @@ def load_files(dataset, mode, max_samples=50, conv=False):
     pat = './experiments_results/hyper_opt_%s%s_%s*' % (p, dataset, mode)
     all_files = glob(pat)
     all_files = all_files[:max_samples]
-    # assert len(all_files) == max_samples, "Not enough experiments"
+    assert len(all_files) == max_samples, "Not enough experiments"
     return np.stack([load_single_file(f) for f in all_files])
 
 for conv in [True, False]:
@@ -55,7 +55,7 @@ for conv in [True, False]:
     for dataset in nice_boundaries.keys():
         print(dataset)
         for mode in modes:
-            infos = load_files(dataset, mode, 50000, conv)[:, [1, 3]]
+            infos = load_files(dataset, mode, 50, conv)[:, [1, 3]]
             bests_indices = infos[:, 0].argsort()[::-1][:10]
             res = np.percentile(infos[bests_indices], 50, axis=0)
             print('\t'.join(map(str, [mode] + list(res))))

### 2018-01-05 paper/paper.tex
Add ref to Gaussian process and some typos

@@
   we also move the references here if we remove the pargraph from the related
-  work ?}, meta-gradient descent ~\cite{Pedregosa2016} and Parzen Estimators
-~\cite{Bergstra2011a} to reduce find good parameters without exhaustively
-exploring the entire hyper-parameter space. Although these strategies help with
-finding a good set of hyper-parameters, they still require a compute-intensive
-search of the space.
+  work ?}, meta-gradient descent ~\cite{Pedregosa2016} , gaussian processes
+~\cite{Bergstra2011a}, and Parzen Estimators ~\cite{Bergstra2011a} to reduce
+find good parameters without exhaustively exploring the entire hyper-parameter
+space. Although these strategies help with finding a good set of
+hyper-parameters, they still require a compute-intensive search of the space.
 
@@
 it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
-are set to zer0, and since zero entries in $\theta$ correspond to dead neurons,
+are set to zero, and since zero entries in $\theta$ correspond to dead neurons,
 lambda effectively control the number of neurons/channels in the entire
@@
 layers that are responsible (or using) features that are disabled.  \par To be
-able to catpure this relationship between layers, we agumented \textit{Pytorch}
+able to catpure this relationship between layers, we augmented \textit{Pytorch}
 ~\cite{paszke2017automatic} (the framework we used as the
@@
 we would think, a proxy of the network size (bigger $\lambda$ imply smaller
-networks). Secondly, it indicates that the spikes we see in the regular spikes
-we see in the loss that occur when neurons are disabled will eventually
-disapear because the number of neurons reach a plateau. \gl{I feel we should
-  give a conclusion for this paragraph but I am not sure what to say}
+networks). Secondly, it indicates that the  the regular spikes we see in the
+loss function that occur when neurons are disabled will eventually disappear
+because the number of neurons reach a plateau. \gl{I feel we should give a
+  conclusion for this paragraph but I am not sure what to say}
 \begin{figure}

### 2018-01-05 paper/paper.tex
pass up to 3.1 included

--- 2018-01-05 paper/paper.tex
@@
 
-\author{Guillaume Leclerc}
-\authornote{Visiting Student}
-\MITAffiliation
-\email{leclerc@mit.edu}
+\author{Guillaume Leclerc, Raul Castro Fernandez, Samuel Madden}
+\affiliation{%
+  \institution{Massachussets Institute of Technology}
+}
+\email{[leclerc, raulcf, madden]@mit.edu}
 
-\author{Raul Castro Fernandez}
-\MITAffiliation
-\email{raulcf@csail.mit.edu}
-
-\author{Samuel Madden}
-\MITAffiliation
-\email{madden@csail.mit.edu}
+%\author{Guillaume Leclerc}
+%\authornote{Visiting Student}
+%\MITAffiliation
+%\email{leclerc@mit.edu}
+%
+%\author{Raul Castro Fernandez}
+%\MITAffiliation
+%\email{raulcf@csail.mit.edu}
+%
+%\author{Samuel Madden}
+%\MITAffiliation
+%\email{madden@csail.mit.edu}
 
@@
 
-When designing Neural Networks, finding the appropriate size (width and depth)
-is key. In particular, these hyper parameters have a strong correlation with
-over/underfitting \srm{give reference} \gl{I did some litterature review and
-  actually this statement is quite controversial, should we rephrase ?}. We
-have no reliable way to find them but decades of experimentation led to some
-heuristics ~\cite{Bengio2012a} that try to prune that immense space of possible
-network sizes and suggest range of values to explore. To select the best
-candidates , researchers have used strategies such as random search \gl{Should
-  we also move the references here if we remove the pargraph from the related
-  work ?}, meta-gradient descent ~\cite{Pedregosa2016} and Parzen Estimators
-~\cite{Bergstra2011a} to reduce find good parameters without exhaustively
-exploring the entire hyper-parameter space. Although these strategies help with
+When designing Neural Networks, finding the appropriate size
+%, number of layers
+%and number of neuros per layer, 
+%(width and depth)
+is key. It consists of determining the number of layers and neurons per layer
+that lead to the best accuracy.
+%In particular, these hyper parameters have a strong correlation with
+%over/underfitting \srm{give reference} \gl{I did some litterature review and
+%actually this statement is quite controversial, should we rephrase ?}. 
+Unfortunately, we have no reliable way to find the best parameters. Decades of
+experimentation led to search strategies and heuristics~\cite{Bengio2012a} that prune
+the immense space of possible network sizes and suggest range of values to
+explore. Examples of search strategies are
+%To select the best candidates, researchers have used strategies such
+%as 
+random search,
+%\gl{Should we also move the references here if we remove the
+%pargraph from the related work ?}, 
+meta-gradient descent~\cite{Pedregosa2016},
+gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}. 
+%to find good parameters without exhaustively
+%exploring the entire hyper-parameter space. 
+Although these strategies help with
 finding a good set of hyper-parameters, they still require a compute-intensive
@@
 In this paper we present a method to automatically find an appropriate network
-size from a single parameter, drastically reducing the hyper-parameter
-dimensionality. The key idea is to \emph{learn} the right network size at the
-same time that the network is learning the main task. For example, for an image
-classification task, with our approach we can provide the training data to a
-network---without sizing it a priori---and expect to end up with a network that
-has learnt the task without overfitting \gl{too strong, we do not really have
-  any guarantee on the generalization, how about changing it to: to end up with
-  a network that learnt a tradeoff between size and accuracy}. This approach
-has two main benefits. First, we do no longer need to choose a network size
-before training.  Second, the final network size will be appropriate for the
-task at hand, and not larger \gl{Should we talk about the fact that it automatically gets rid of dead neurons ?}. This is important because oversized networks have
-a lower inference throughput and higher  memory footprint.
+size, thus
+%from a single parameter, 
+drastically reducing the hyper-parameter optimization time.
+%dimensionality. 
+The key idea is to
+\emph{learn} the right network size at the same time that the network is
+learning the main task. For example, for an image classification task, with our
+approach we can provide the training data to a network---without sizing it a
+priori---and expect to end up with a network that has learnt to classify images
+with an accuracy similar to a manually engineered network.
+%\gl{too strong, we do not really have
+%  any guarantee on the generalization, how about changing it to: to end up with
+%  a network that learnt a tradeoff between size and accuracy}. 
+This approach has two main benefits. First, we do no longer need to choose a
+network size before training. Second, the final network size will be
+appropriate for the task at hand, and not larger. 
+%Because the sizing occurs
+%dynamically, while the
+%network is training, we remove the useless neurons 
+%implement a new mechanism that removes
+%the deactivated neurons to  
+%\gl{Should we talk about the
+%fact that it automatically gets rid of dead neurons ?}. 
+This is important
+because oversized networks have a lower inference throughput and higher memory
+footprint.
 
@@
 \textbf{Filter Layers: } They have weights in the range $[0,+\infty]$ and are placed after
-linear and convolutional layers of traditional deep networks \gl{This is how I
-  used it but with the new implementation we can be more creative and put them
-  anywhere, should we say "usually placed" insdead ?}. The \textit{Filter
-  Layer} takes an input of size $\left(B \times C \times D_1 \times \dots
-  \times D_n\right)$, where $B$ is the batch size, $C$ the number of features
-(or channels), and $D$ any additional dimension. This structure makes it
-compatible with fully connected layers with $n=0$ or convolutional layers with
-$n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$, defined
-as follows:
+linear and convolutional layers of traditional deep networks.
+%\gl{This is how I
+%  used it but with the new implementation we can be more creative and put them
+%  anywhere, should we say "usually placed" insdead ?}. 
+The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
+\times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number of
+features (or channels, in the case of convolutional layers), and $D$ any additional dimension. This structure makes
+it compatible with fully connected layers with $n=0$ or convolutional layers
+with $n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$,
+defined as follows:
 
@@
 
-Where $\circ$ is the Hadamard product (pointwise multiplication \gl{Should we
-  keep only one of them to be more concise ?}), and $\theta$ is expanded in all
+Where $\circ$ is the 
+%Hadamard product (
+pointwise multiplication,
+%\gl{Should we
+%  keep only one of them to be more concise ?}), 
+and $\theta$ is expanded in all
 dimensions except the second one to match the input size. It is easy to see
 that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel
-will forever be $0$. When this happens, we say the Filter layer disables the
+will forever be $0$. When this happens, we say the Filter layer deactivates the
 neuron. These disabled neurons/channels can be removed from the network without
-changing its output (we describe how we perform this removal below). We explain
+changing its output. Before explaining how that is achieved, we 
+% (we describe how we perform this removal below). We 
+explain
 next how the weights of the Filter Layer are adjusted during training.
@@
 %$\text{Uniform}(0, 1)$ distribution. 
-we could train it directly and it
-would be equivalent to a normal neural network. However, our goal is to find the
-smallest network with reasonable performance. We achieve that by introducing
-sparsity in the parameters of the \textit{Filter Layers}.
-Indeed, having a negative component in the $\theta$ parameter of the filter layer permamently disable its associated feature \gl{Maybe redundant ?
-we talked about that in the previous paragraph}
-. To obtain this sparsity, we simply redefine the loss function:
+we could train it directly and it would be equivalent to a normal neural
+network. However, our goal is to find the smallest network with reasonable
+performance. We achieve that by introducing sparsity in the parameters of the
+\textit{Filter Layers}, thus forcing the deactivation of neurons.
+%. Indeed, having a negative component in the $\theta$
+%parameter of the filter layer permamently disable its associated feature
+%\gl{Maybe redundant ? we talked about that in the previous paragraph} . 
+To obtain this sparsity, we simply redefine the loss function:
 
@@
 
-This choice come from the Lasso loss ~\cite{Tibshirani1996} and we use it for the same reason:
-it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
-are set to zer0, and since zero entries in $\theta$ correspond to dead neurons,
-lambda effectively control the number of neurons/channels in the entire
-network.
-Next, we explain how to implement ShrinkNets efficiently.
+The additional term $\lambda|\theta|$ introduces sparsity (see Lasso
+loss~\cite{Tibshirani1996}).
+%This choice comes from the Lasso loss ~\cite{Tibshirani1996} and we use it for
+%the same reason: it introduces sparsity. 
+The $\lambda$ parameter adjusts how aggressive the network deactivates neurons,
+with larger values indicating more aggressive deactivation. 
+%The bigger the $\lambda$ the more
+%entries in $\theta$ are set to zero, and 
+Because the entries in $\theta$ with a value of $0$
+correspond to dead neurons, $\lambda$ effectively controls the number of
+neurons/channels in the entire network.  
+Next, we explain how to implement
+ShrinkNets efficiently.
 
-\textbf{Software architecture\footnote{The code is available as Python/PyTorch
-    library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
-      the repository ?}}: }\textit{Filter Vectors} can easily be implemented in
-a few lines of code in many existing deep learning frameworks. However, in
-ShrinkNets, we assume that we start with obviously oversized networks. If
-disabled neurons are not quickly removed, the overhead might cause the training
-process to be significantly slower than classic neural networks. This is why we
-want to support what we call garbage collection: removing the weights in the
-layers that are responsible (or using) features that are disabled.  \par To be
-able to catpure this relationship between layers, we agumented \textit{Pytorch}
-~\cite{paszke2017automatic} (the framework we used as the
-foundation of our implementation) with a graph structure very similar to the
-one available in Keras ~\cite{chollet2015keras}.  In this graph, edges are
-effectively event hubs responsible for propagating \textit{feature removal}
-events to its endpoints. ShrinkNet layers are designed to emit and react to
-these events but also propagate the event further if has an impact at the other
-endpoint of the layer (input or output) \gl{What I mean here is: if the event
-  comes from the output, it might be propagated to the inputs, and the other
-  way around}.  \par This event-based implementation coordinated by edges makes
-it very easy to integrate new layers in the library.  We even provide automatic
-wrapping for layers from \textit{PyTorch} if they have no internal state. For
-more complex ones, we provide utilitaries that
-makes the implementation very concise.
+\textbf{Dynamic Network Resizing}
+It is possible to reduce the overhead of the training process by removing
+neurons as soon as they become deactivated.
+%If
+%disabled neurons are not quickly removed, the overhead might cause the training
+%process to be significantly slower than classic neural networks. 
+For that, we implemented a \emph{neural garbage collection} mechanism which
+prunes deactivated neurons on-the-fly, therefore reducing the processing time
+and memory overhead. To support this feature, it is crucial to understand the
+information flow between neurons and layers in the neural network. We achieve
+this by representing such information flow as a graph, in which edges indicate
+what action each node, i.e., neuron, must take.
 
 \section{Evaluation}
-\subsection{Convergence}
 
-To demonstrate that the approach is viable, we will first show that Shrinking
-Networks converge properly. For this experiment we trained a one hidden layer
+We have implemented ShrinkNets, including the \emph{garbage collection}
+mechanism on top of \textit{PyTorch}~\cite{paszke2017automatic}, and we have
+made the software open source.\footnote{The code is available as Python/PyTorch
+library on \url{http://github.com/mitdbg/fastdeepnets} 
+%\gl{Should we rename the repository ?}
+}. We have then used our implementation to evaluate two crucial aspects of
+ShrinkNets, which we present next.
+
+%This is why we
+%want to support what we call garbage collection: removing the weights in the
+%layers that are responsible (or using) features that are disabled.  \par To be
+%able to catpure this relationship between layers, we augmented \textit{Pytorch}
+%~\cite{paszke2017automatic} (the framework we used as the
+%foundation of our implementation) with a graph structure very similar to the
+%one available in Keras ~\cite{chollet2015keras}.  In this graph, edges are
+%effectively event hubs responsible for propagating \textit{feature removal}
+%events to its endpoints. ShrinkNet layers are designed to emit and react to
+%these events but also propagate the event further if has an impact at the other
+%endpoint of the layer (input or output) \gl{What I mean here is: if the event
+%  comes from the output, it might be propagated to the inputs, and the other
+%  way around}.  \par This event-based implementation coordinated by edges makes
+%it very easy to integrate new layers in the library.  We even provide automatic
+%wrapping for layers from \textit{PyTorch} if they have no internal state. For
+%more complex ones, we provide utilitaries that
+%makes the implementation very concise.
+
+%\textbf{Software architecture
+%\footnote{The code is available as Python/PyTorch library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
+%      the repository ?}
+%}
+%: }\textit{Filter Vectors} can easily be implemented in
+%a few lines of code in many existing deep learning frameworks. However, in
+%ShrinkNets, we assume that we start with obviously oversized networks. 
+%
+
+\subsection{Does ShrinkNet converge?}
+
+%To demonstrate that the approach is viable, we will first show that Shrinking
+%Networks converge properly. For this experiment 
+We trained a one hidden layer
 neural network with one filter layer to control the number of hidden units. We
 initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
-~\cite{Lecun1998} using different regularization factors ($\lambda$). We
-summarized the results in \autoref{convergence_plot}. We can see on this plot
-is that for a given $\lambda$ the number of hidden units seems to always
-converge to some value. It has two implications: it seems that $\lambda$ is, as
-we would think, a proxy of the network size (bigger $\lambda$ imply smaller
-networks). Secondly, it indicates that the spikes we see in the regular spikes
-we see in the loss that occur when neurons are disabled will eventually
-disapear because the number of neurons reach a plateau. \gl{I feel we should
-  give a conclusion for this paragraph but I am not sure what to say}
+~\cite{Lecun1998} using different values for $\lambda$.
+Figure~\autoref{convergence_plot} shows that
+%We
+%summarized the results in \autoref{convergence_plot}. We can see on this plot
+%is that for a given $\lambda$ the number of hidden units seems to always
+%converge to some value. It has two implications: it seems that 
+$\lambda$ works as a proxy for the network size,
+% as
+%we would think, a proxy of the network size 
+with bigger $\lambda$ implying smaller
+networks. More importantly, the figure helps us confirm that despite the regular
+spikes---which are caused by the dynamic disabling of neurons---ShrinkNets
+eventually converge.
+%we see in the
+%loss function that occur when neurons are disabled will eventually disappear
+%because the number of neurons reach a plateau. 
+%\gl{I feel we should give a
+%  conclusion for this paragraph but I am not sure what to say}
+
+\ra{stopped here}
+
 \begin{figure}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{convergence}
+\includegraphics[width=0.9\columnwidth]{convergence}
 \caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
@@
 \begin{center}
-  \includegraphics[width=0.5\textwidth]{hyper_opt}
+  \includegraphics[width=0.9\columnwidth]{hyper_opt}
 \caption{Distributions of the testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}

### 2018-01-05 paper/paper.tex
pass

@@
 
-When designing Neural Networks, finding the appropriate size
+When designing neural networks, one of the key parameters is the network size, i.e., 
 %, number of layers
@@
 %(width and depth)
-is key. It consists of determining the number of layers and neurons per layer
-that lead to the best accuracy.
+the number of layers and neurons per layer.  Choosing these parameters appropriately
+can dramatically affect performance, yet
 %In particular, these hyper parameters have a strong correlation with
@@
 %actually this statement is quite controversial, should we rephrase ?}. 
-Unfortunately, we have no reliable way to find the best parameters. Decades of
-experimentation led to search strategies and heuristics~\cite{Bengio2012a} that prune
-the immense space of possible network sizes and suggest range of values to
-explore. Examples of search strategies are
+there is no reliable way to efficiently set them. Although many search
+ strategies and heuristics~\cite{Bengio2012a} have been proposed, including
 %To select the best candidates, researchers have used strategies such
@@
 meta-gradient descent~\cite{Pedregosa2016},
-gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}. 
+Gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}. 
 %to find good parameters without exhaustively
 %exploring the entire hyper-parameter space. 
-Although these strategies help with
-finding a good set of hyper-parameters, they still require a compute-intensive
-search of the space.
+ these methods generally require a compute-intensive
+search of parameter space.
 
@@
 In this paper we present a method to automatically find an appropriate network
-size, thus
+size,
 %from a single parameter, 
-drastically reducing the hyper-parameter optimization time.
+drastically reducing optimization time.
 %dimensionality. 
@@
 approach we can provide the training data to a network---without sizing it a
-priori---and expect to end up with a network that has learnt to classify images
-with an accuracy similar to a manually engineered network.
+priori---and expect to end up with a network that has learned to classify images
+with an accuracy similar to a the best manually engineered network.
 %\gl{too strong, we do not really have
@@
 %  a network that learnt a tradeoff between size and accuracy}. 
-This approach has two main benefits. First, we do no longer need to choose a
-network size before training. Second, the final network size will be
+Our approach has two main benefits. First, no longer need to choose a
+network size before training. Second, the final network size will tuned to be
 appropriate for the task at hand, and not larger. 
@@
 This is important
-because oversized networks have a lower inference throughput and higher memory
+because over-sized networks have a lower inference throughput and higher memory
 footprint.
 
-Our approach has two main challenges. First, on how to dynamically size the
-network during training. Second, on how to find a loss function that optimizes
+Our approach has two main challenges. First, we need a way to dynamically size the
+network during training. Second, we need a loss function that optimizes
 for the additional task of sizing, without deteriorating the learning
-performance of the main task. We describe next ShrinkNets, which cope with both
-challenges:
+performance of the main task. Our approach, called ShrinkNets, copes with both
+challenges.
 
@@
 
-Our approach consists of starting the training process for the task of interest
-with an explicitly oversized network. Then, as training progresses, we learn
-which neurons are not contributing to learning the main task and remove them
-dynamically, thus shrinking the network size. This method requires two building
-blocks. First, a way of identifying neurons that are not contributing to the
-learning process, and second a way of balancing the network size and the
-generalization capability for the main task. We introduce a new layer, called
-\textsf{Filter}, which takes care of \emph{deactivating} neurons. We also modify
+During training, our approach starts
+with an explicitly over-sized network. As training progresses, we learn
+which neurons are not contributing to learning and remove them
+dynamically, effectively shrinking the network. This method requires two key components: first, we need a way to identify neurons that are not contributing to the
+learning process, and second we need a way to balance the network size and the
+generalization capability for the main task. We introduce a new \textsf{Filter} layer that takes care of \emph{deactivating} neurons. We also modify
 existing loss functions to incorporate a new term that takes care of balancing
-network sizing and generalization capability appropriately. We explain them
-next:
+network size and generalization capability appropriately.
 
@@
 
-\textbf{Filter Layers: } They have weights in the range $[0,+\infty]$ and are placed after
-linear and convolutional layers of traditional deep networks.
+\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are placed after
+linear and convolutional layers.
 %\gl{This is how I
@@
 defined as follows:
-
+\vspace{-1em}
 \begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
-
 Where $\circ$ is the 
@@
 and $\theta$ is expanded in all
-dimensions except the second one to match the input size. It is easy to see
+dimensions except the second one \srm{why not the second one? what is the second one?  C?} to match the input size. It is easy to see
 that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel
 will forever be $0$. When this happens, we say the Filter layer deactivates the
-neuron. These disabled neurons/channels can be removed from the network without
+neuron. \srm{Not easy to see this because you haven't told me that theta only decays over time?} These disabled neurons/channels can be removed from the network without
 changing its output. Before explaining how that is achieved, we 
@@
 explain
-next how the weights of the Filter Layer are adjusted during training.
+next how the weights of the Filter Layer are adjusted during training. \srm{How are filter weights initialized?}
 
@@
 %\subsection{The training procedure}
-\textbf{Training Procedure: } Once Filter layers are placed in a deep network, 
+\textbf{Training Procedure: } Once Filter layers are placed in a network, 
 %To train networks we need start with a substantially oversized network, then we
@@
 %$\text{Uniform}(0, 1)$ distribution. 
-we could train it directly and it would be equivalent to a normal neural
+we could train the network directly using our standard loss function, and we could achieve performance equivalent to a normal neural
 network. However, our goal is to find the smallest network with reasonable
 performance. We achieve that by introducing sparsity in the parameters of the
-\textit{Filter Layers}, thus forcing the deactivation of neurons.
+\textit{Filter Layers}, thus forcing the deactivation of neurons \srm{by decaying the value of theta}
 %. Indeed, having a negative component in the $\theta$
@@
 To obtain this sparsity, we simply redefine the loss function:
-
+\vspace{-.5em}
 \begin{equation}
@@
 The additional term $\lambda|\theta|$ introduces sparsity (see Lasso
-loss~\cite{Tibshirani1996}).
+loss~\cite{Tibshirani1996}). \srm{Say lambda is in [0,1]?}
 %This choice comes from the Lasso loss ~\cite{Tibshirani1996} and we use it for
 %the same reason: it introduces sparsity. 
-The $\lambda$ parameter adjusts how aggressive the network deactivates neurons,
+The $\lambda$ parameter adjusts how aggressively the network deactivates neurons,
 with larger values indicating more aggressive deactivation.
+\srm{Give some intuitive statement about how this loss function causes theta to decay in irrelevant neurons, while preserving the value of important neurons.}
 %The bigger the $\lambda$ the more
@@
 It is possible to reduce the overhead of the training process by removing
-neurons as soon as they become deactivated.
+neurons as soon as they become deactivated by $\theta$ going to 0.
 %If
@@
 %process to be significantly slower than classic neural networks. 
-For that, we implemented a \emph{neural garbage collection} mechanism which
-prunes deactivated neurons on-the-fly, therefore reducing the processing time
+To do this, we implemented a \emph{neural garbage collection} mechanism which
+prunes deactivated neurons on-the-fly,  reducing the processing time
 and memory overhead. To support this feature, it is crucial to understand the
@@
 what action each node, i.e., neuron, must take. 
+\srm{I can't really understand what this means -- need to add a bit more detail.}
 
@@
 
-We have implemented ShrinkNets, including the \emph{garbage collection}
+We  implemented ShrinkNets, including the \emph{garbage collection}
 mechanism on top of \textit{PyTorch}~\cite{paszke2017automatic}, and we have
@@
 %\gl{Should we rename the repository ?}
-}. We have then used our implementation to evaluate two crucial aspects of
+}. We used used our implementation to evaluate two crucial aspects of
 ShrinkNets, which we present next.
@@
 \begin{figure}
+\vspace{-.2in}
 \begin{center}
 \includegraphics[width=0.9\columnwidth]{convergence}
+\vspace{-.2in}
 \caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
+\srm{Move legend inside top of figure, to save space.}
+\vspace{-.2in}
 \end{center}
@@
 
-\subsection{Relevance in the context of hyper-parameter optimization}
+\subsection{Does ShrinkNet find good networks?}
 
-One of our main goal is to help finding neural network architectures that
-perform reasonably well faster than existing techniques. For simplicity, we
-will try to see how ShrinkNets perform when doing random search over a sub set
-of the hyper-parameter space (we will fix everything except the size-related
-parameters). However, we believe that the results generalize to more complex
-methods, most of them might actually benefit a lot from the reduction of the
-dimensionality of the hyper-parameter space.
+One of our main goals is to show that ShrinkNets quickly finds neural network architectures that
+perform well. To show this, we ran a simple experiment where we compare ShrinkNets
+to other network tuning methods,
+ using random search over the
+hyper-parameters that control the network size ($\lambda$ in the case of ShrinkNets). 
+Despite the simple nature of this experiment, 
+we believe that the results generalize to more complex
+search methods, many of of which will actually benefit
+dimensionality of the hyper-parameter space in the ShrinkNets approach.
 
-\par To isolate the effect of ShrinkNets we will consider two very simple
+To isolate the effect of ShrinkNets we will consider two very simple
 architectures: multi-layer perceptrons (with three hidden layers) and the
-\textit{LeNet-5} model ~\cite{Lecun1998}. For this experiment we assume we have no prior
+\textit{LeNet-5} model ~\cite{Lecun1998}.
+For this experiment we assume we have no prior
 information about the size except an upper bound of $50$ channels per
-convolutional layer and $5000$ neuron for fully connected layers.  We try to
-find the appropriate size of the network using classical neural networks and
-ShrinkNets. To make sure that we are as fair as possible and since one might
-argue that ShrinkNets is also regularizing the network in addition to finding
-the size, we will also considered regularized classic networks using the most
-commonly used technique: the $L_2$ penalty ~\cite{Ng2004}.
-\par The experiment consist in sampling parameters randomly for each class of
-network, train them for the same amount of epochs (100 for MLPs and 200 for CNNs). Pick the epoch that performed the best on the validation set and evaluate it
-on the testing set. We repeat the process for 50 models. This evaluation was done
+convolutional layer and $5000$ neurons for fully connected layers.  We try to
+find the appropriate size of the network using classical network-size optimization methods
+ and
+ShrinkNets. For the classical methods we use: i) purely random selection of network size parameters (``Fixed''), as well as hyper-parameter
+regularization over the network size parameters using  $L_2$ penalty ~\cite{Ng2004} 
+(``Fixed-L2'').
+In the experiment, we randomly sample parameters for each class of
+network and  train them for the same number of epochs (100 for MLPs and 200 for CNNs). We picked the epoch that performed the best on the validation set and evaluated it
+on the testing set. We repeat the process for 50 iterations. This evaluation was done
 on \texttt{MNIST} ~\cite{Lecun1998}, \texttt{FashionMNIST} ~\cite{Xiao2017} and \texttt{CIFAR10} ~\cite{Krizhevsky2009}.
-The distribution of the testing accuracy we obtained is summarized on \autoref{hyper_opt_res}.
+The distribution of the testing accuracy we obtained is summarized in \autoref{hyper_opt_res}.
 
-We can see that the distributions for ShrinkNets are consistently better than the
-others for all datasets and both architectures. It shows that by training fewer
-networks, we are likely to obtain on-par or even better models which effectively
-reduces the cost of hyper-parameter optimization. In some cases the best ShrinkNets
-models even outperforms the best model of the other techniques.
+We can see that in all cases the distributions for ShrinkNets have substantially higher medians are are less variable than the other architectures (the best model is not always found by ShrinkNets, but this is likely an artifact of our randomized search process).
+This shows that ShrinkNets can find better networks with fewer training iterations than existing methods.
+\srm{Note something about how we expect this to bear out even with methods other than random search?}
 
 \begin{figure}
+\vspace{-.2in}
 \begin{center}
   \includegraphics[width=0.9\columnwidth]{hyper_opt}
+  \vspace{-.2in}
 \caption{Distributions of the testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
+\vspace{-.2in}
 \end{center}
@@
 
-\par There are many methods in the litterature that try to simplify the neural
+\par There are many methods in the literature that aim to simplify 
 network structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
@@
 leverage sparsity in the connections efficiently (as explained in ~\cite{Han2016}). On the other side, ShrinkNets
-and some others ~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neuron instead of
-connections. This is very usefull because it reduces the size of the matrices,
+and some others ~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead of
+connections. This is very useful because it reduces the size of the matrices,
 producing speed-up on every device. ShrinkNets improves on
 ~\cite{Scardapane2017} because it removes neurons during training, speeding up
-the rest of the process and beats ~\cite{Philipp} on convergence speed and because it
-does not need to change the optimizer. To the best of our knowledge this is
-also the first contribution that tries to learn the number of channels of a
+the rest of the process.  Further it outperforms~\cite{Philipp} on convergence speed and because it does not need to change the optimizer. To the best of our knowledge this is
+also the first work that tries to learn the number of channels in a
 convolutional neural network.
@@
 
-In this paper we presented a novel technique to guess a resonable network size
-based on single parameter $\lambda$ that control the tradeof between loss and
-the size. We demonstrated that it works both on fully connected networks and
-convolutional neural networks.  Even though the firsts results seem promising,
-there are many ways we could improve. In the current implementation we only
-"learn" the number of features (neurons or channels). We could try to augment
-it with dynamic number of layers as seen in ~\cite{meier} to be able to
-determine the entire architecture. \par We saw on Figure \ref{convergence_plot}
+In this paper we presented a novel technique to guess a reasonable network size
+based on single parameter $\lambda$ that control the tradeoff between loss and
+network size. We demonstrated that ShrinkNets works both on fully connected networks and
+convolutional neural networks.  Although the initial results are promising,
+there are many additional avenues to explore. In the current implementation we only
+``learn'' the number of features (neurons or channels). We plan to augment
+this with a dynamic number of layers as seen in ~\cite{meier} to be able to
+determine the entire architecture. Further, as shown in Figure \ref{convergence_plot}
 that the loss temporarily suffers from the removal of neurons. It is likely
 that the loss would be more stable if the number of neurons converged faster or
-neurons disappeared slower. For this reason we plan to explore proximal
+neurons disappeared more slowly. For this reason we plan to explore proximal
 gradient methods to optimize the filter vectors and/or randomize neuron
-removals. \par During our evaluation we picked small datasets mainly to be able
-to train many models and have statistically significant distributions. With
-more computation resources and time, we could see if it generalizes to bigger
-datasets and other architectures like \texttt{ResNet} ~\cite{He2016} (small
-modifications to the existing code base are required to support them)
+removals. Finally, during our evaluation we picked small datasets mainly to be able
+to train many models and have statistically significant distributions. We 
+plan to verify that our approach
+ see if it generalizes to bigger
+datasets and other architectures like \texttt{ResNet} ~\cite{He2016}, which is possible
+with small
+modifications to our existing code base.
 

### 2018-01-05 paper/convergence_experiment_plot.py

@@ -53,7 +53,7 @@ ax_loss.set_xticks(r)
 ax_size.set_xticklabels(["$10^{-%s}$" % x for x in range(1, 6)])
 ax_loss.set_xticklabels(["$10^{-%s}$" % x for x in range(1, 6)])
 plt.tight_layout()
-ax_size.legend(handles=[l1, l2] , labels=['\\texttt{MNIST}', '\\texttt{FashionMNIST}'] ,loc='lower center', bbox_to_anchor=(1.175, 1), ncol=3, columnspacing=0.5)
+ax_size.legend(handles=[l1, l2] , labels=['\\texttt{MNIST}', '\\texttt{FashionMNIST}'], bbox_to_anchor=(1.175, 1), ncol=3, columnspacing=0.5)
 f.set_size_inches(5, 2.05)
 plt.savefig('conv_MNIST_FM_comp.pdf', bbox_inches='tight')
 

### 2018-01-05 paper/paper.tex
finished my pass. left couple comments

@@
 
-One of our main goals is to show that ShrinkNets quickly finds neural network architectures that
-perform well. To show this, we ran a simple experiment where we compare ShrinkNets
-to other network tuning methods,
- using random search over the
-hyper-parameters that control the network size ($\lambda$ in the case of ShrinkNets). 
-Despite the simple nature of this experiment, 
-we believe that the results generalize to more complex
-search methods, many of of which will actually benefit
-dimensionality of the hyper-parameter space in the ShrinkNets approach.
+In this experiment we want to find an appropriate network size for two network
+architectures, a multi-layer perceptron (MLP) and the \textit{LeNet-5}
+model~\cite{Lecun1998}. We have no prior information about the network size, but
+we set an upper bound of $50$ channels per convolutional layer and $5000$
+neurons for fully connected layers. We then use random search to vary the
+parameters that determine the network size, i.e., $\lambda$ in the case of
+ShrinkNets, random selection of depth and witdh in the case of \textsf{Fixed}
+and similar to previous but adding a $L_2$ penalty~\cite{Ng2004}
+(\textsf{Fixed-L2}).  We train all variants on \texttt{MNIST}~\cite{Lecun1998},
+\texttt{FashionMNIST}~\cite{Xiao2017} and
+\texttt{CIFAR10}~\cite{Krizhevsky2009}. We use the same number of epochs, 100
+for MLPs and 200 for \textit{LeNet-5}. We select the epoch that performed the
+best on the validation set and evaluated it on the testing set. We repeat this
+process 50 times and show the distribution of the testing accuracy in
+\autoref{hyper_opt_res}.
 
-To isolate the effect of ShrinkNets we will consider two very simple
-architectures: multi-layer perceptrons (with three hidden layers) and the
-\textit{LeNet-5} model ~\cite{Lecun1998}.
-For this experiment we assume we have no prior
-information about the size except an upper bound of $50$ channels per
-convolutional layer and $5000$ neurons for fully connected layers.  We try to
-find the appropriate size of the network using classical network-size optimization methods
- and
-ShrinkNets. For the classical methods we use: i) purely random selection of network size parameters (``Fixed''), as well as hyper-parameter
-regularization over the network size parameters using  $L_2$ penalty ~\cite{Ng2004} 
-(``Fixed-L2'').
-In the experiment, we randomly sample parameters for each class of
-network and  train them for the same number of epochs (100 for MLPs and 200 for CNNs). We picked the epoch that performed the best on the validation set and evaluated it
-on the testing set. We repeat the process for 50 iterations. This evaluation was done
-on \texttt{MNIST} ~\cite{Lecun1998}, \texttt{FashionMNIST} ~\cite{Xiao2017} and \texttt{CIFAR10} ~\cite{Krizhevsky2009}.
-The distribution of the testing accuracy we obtained is summarized in \autoref{hyper_opt_res}.
+The results in the figure show that ShrinkNets finds better networks with fewer
+training iterations than the other methods, because it achieves higher median 
+and less variable accuracies. Despite the simple nature of this experiment, we
+believe that the results generalize to more complex search methods.
+\srm{Note something about
+how we expect this to bear out even with methods other than random search?}
 
-We can see that in all cases the distributions for ShrinkNets have substantially higher medians are are less variable than the other architectures (the best model is not always found by ShrinkNets, but this is likely an artifact of our randomized search process).
-This shows that ShrinkNets can find better networks with fewer training iterations than existing methods.
-\srm{Note something about how we expect this to bear out even with methods other than random search?}
+%the distributions for ShrinkNets have higher
+%medians and are less variable than the others. ShrinkNets can find better
+%networks with fewer training iterations than the other methods
+%
+%We can see that in all cases the distributions for ShrinkNets have substantially
+%higher medians are are less variable than the other architectures (the best
+%model is not always found by ShrinkNets, but this is likely an artifact of our
+%randomized search process).  This shows that ShrinkNets can find better networks
+%with fewer training iterations than existing methods.
+
+%One of our main goals is to show that ShrinkNets quickly finds neural network
+%architectures that perform well. To show this, we ran a simple experiment where
+%we compare ShrinkNets to other network tuning methods, using random search over
+%the hyper-parameters that control the network size ($\lambda$ in the case of
+%ShrinkNets).  Despite the simple nature of this experiment, we believe that the
+%results generalize to more complex search methods, many of of which will
+%actually benefit dimensionality of the hyper-parameter space in the ShrinkNets
+%approach.
+%
+%To isolate the effect of ShrinkNets we will consider two very simple
+%architectures: multi-layer perceptrons (with three hidden layers) and the
+%\textit{LeNet-5} model ~\cite{Lecun1998}.  For this experiment we assume we have
+%no prior information about the size except an upper bound of $50$ channels per
+%convolutional layer and $5000$ neurons for fully connected layers.  We try to
+%find the appropriate size of the network using classical network-size
+%optimization methods and ShrinkNets. For the classical methods we use: i) purely
+%random selection of network size parameters (``Fixed''), as well as
+%hyper-parameter regularization over the network size parameters using  $L_2$
+%penalty ~\cite{Ng2004} (``Fixed-L2'').  In the experiment, 
+%we randomly sample
+%parameters for each class of network and  train them for the same number of
+%epochs (100 for MLPs and 200 for CNNs). We picked the epoch that performed the
+%best on the validation set and evaluated it on the testing set. We repeat the
+%process for 50 iterations. This evaluation was done on \texttt{MNIST}
+%~\cite{Lecun1998}, \texttt{FashionMNIST} ~\cite{Xiao2017} and \texttt{CIFAR10}
+%~\cite{Krizhevsky2009}. The distribution of the testing accuracy we obtained is
+%summarized in \autoref{hyper_opt_res}.
 
@@
   \vspace{-.2in}
-\caption{Distributions of the testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
+\caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
 \vspace{-.2in}
@@
 
-\par There are many methods in the literature that aim to simplify 
-network structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
-~\cite{Han2015}).  However, most hardware (GPU's, TPUS ~\cite{Jouppi2017}, TensorCores) do not really
-leverage sparsity in the connections efficiently (as explained in ~\cite{Han2016}). On the other side, ShrinkNets
-and some others ~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead of
-connections. This is very useful because it reduces the size of the matrices,
+There are many methods in the literature that aim to simplify network
+structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
+~\cite{Han2015}).  \ra{not sure the following is relevant. Instead, just
+contrast with the approach in this paper} However, most hardware (GPU's, TPUS ~\cite{Jouppi2017},
+TensorCores) do not really leverage sparsity in the connections efficiently (as
+explained in ~\cite{Han2016}). On the other side, ShrinkNets and some others
+~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead
+of connections. This is very useful because it reduces the size of the matrices,
 producing speed-up on every device. ShrinkNets improves on
 ~\cite{Scardapane2017} because it removes neurons during training, speeding up
-the rest of the process.  Further it outperforms~\cite{Philipp} on convergence speed and because it does not need to change the optimizer. To the best of our knowledge this is
-also the first work that tries to learn the number of channels in a
-convolutional neural network.
+the rest of the process. Further it outperforms~\cite{Philipp} on convergence
+speed and because it does not need to change the optimizer. To the best of our
+knowledge this is also the first work that tries to learn the number of channels
+in a convolutional neural network.
 
 \section{Conclusion}
-
-In this paper we presented a novel technique to guess a reasonable network size
-based on single parameter $\lambda$ that control the tradeoff between loss and
-network size. We demonstrated that ShrinkNets works both on fully connected networks and
-convolutional neural networks.  Although the initial results are promising,
-there are many additional avenues to explore. In the current implementation we only
-``learn'' the number of features (neurons or channels). We plan to augment
-this with a dynamic number of layers as seen in ~\cite{meier} to be able to
-determine the entire architecture. Further, as shown in Figure \ref{convergence_plot}
-that the loss temporarily suffers from the removal of neurons. It is likely
-that the loss would be more stable if the number of neurons converged faster or
-neurons disappeared more slowly. For this reason we plan to explore proximal
-gradient methods to optimize the filter vectors and/or randomize neuron
-removals. Finally, during our evaluation we picked small datasets mainly to be able
-to train many models and have statistically significant distributions. We 
-plan to verify that our approach
- see if it generalizes to bigger
-datasets and other architectures like \texttt{ResNet} ~\cite{He2016}, which is possible
-with small
-modifications to our existing code base.
+In this paper we presented a novel technique to guess a
+reasonable network size based on single parameter $\lambda$ that control the
+tradeoff between loss and network size. We demonstrated that ShrinkNets works
+both on fully connected networks and convolutional neural networks.  Although
+the initial results are promising, there are many additional avenues to explore.
+In the current implementation we only ``learn'' the number of features (neurons
+or channels).  We plan to augment this with a dynamic number of layers as seen
+in ~\cite{meier} to be able to determine the entire architecture. Further, as
+shown in Figure \ref{convergence_plot} that the loss temporarily suffers from
+the removal of neurons. It is likely that the loss would be more stable if the
+number of neurons converged faster or neurons disappeared more slowly. For this
+reason we plan to explore proximal gradient methods to optimize the filter
+vectors and/or randomize neuron removals. Finally, during our evaluation we
+picked small datasets mainly to be able to train many models and have
+statistically significant distributions. We plan to verify that our approach see
+if it generalizes to bigger datasets and other architectures like
+\texttt{ResNet} ~\cite{He2016}, which is possible with small modifications to
+our existing code base.
 

### 2018-01-05 paper/convergence_experiment_plot.py
Move legend and fix compilation

@@ -82,7 +82,7 @@ for m, lamb in zip(reversed(markers), reversed(lambdas)):
     file = load_file(
         './experiments_results/conv_MNIST_bs256_lamb%s.dat' % lamb)
     ax_loss.plot(np.arange(0, 100, 1 / len(file) * 100), file['loss'], m + '-', markevery=int(len(file) / 5))
-ax_size.legend(handles=lines , labels=reversed(tex_labels) ,loc='lower center', bbox_to_anchor=(0.5, 1), ncol=3, columnspacing=0.5)
-f.set_size_inches(5, 5)
+ax_loss.legend(handles=lines , labels=reversed(tex_labels) ,loc='lower center', bbox_to_anchor=(0.595, 0.68), ncol=3, columnspacing=0.5)
+f.set_size_inches(5, 4.5)
 plt.show()
 plt.savefig('convergence.pdf', bbox_inches='tight')

### 2018-01-06 paper/paper.tex
Move legend and fix compilation
Attempt to fix some of the comments

@@
 \makeatletter
-\renewcommand\@formatdoi[1]{\ignorespaces}
 \makeatother
@@
 The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
-\times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number of
-features (or channels, in the case of convolutional layers), and $D$ any additional dimension. This structure makes
-it compatible with fully connected layers with $n=0$ or convolutional layers
-with $n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$,
-defined as follows:
-\vspace{-1em}
+  \times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number
+of features (or channels, in the case of convolutional layers), and $D$ any
+additional dimension. This structure makes it compatible with fully connected
+layers with $n=0$ or convolutional layers with $n=2$. Their crucial property is
+a parameter $\theta \in \mathbb{R}^C$, defined as follows: \vspace{-1em}
 \begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
-Where $\circ$ is the 
-%Hadamard product (
-pointwise multiplication,
-%\gl{Should we
-%  keep only one of them to be more concise ?}), 
-and $\theta$ is expanded in all
-dimensions except the second one \srm{why not the second one? what is the second one?  C?} to match the input size. It is easy to see
-that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel
-will forever be $0$. When this happens, we say the Filter layer deactivates the
-neuron. \srm{Not easy to see this because you haven't told me that theta only decays over time?} These disabled neurons/channels can be removed from the network without
-changing its output. Before explaining how that is achieved, we 
-% (we describe how we perform this removal below). We 
-explain
-next how the weights of the Filter Layer are adjusted during training. \srm{How are filter weights initialized?}
+Where $\circ$ is the pointwise multiplication, and $\theta$ is expanded in all
+dimensions to match the input size (except the second one since they are equal by definition). It is easy to see that if for any
+$k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be
+$0$. When this happens, we say the Filter layer deactivates the neuron.
+\srm{Not easy to see this because you haven't told me that theta only decays
+  over time?} \gl{The decay is only caused by the loss, and actually it does not depends on how it became zero, if it is zero for any reason, multiplying by zero will nullfy any value and cancel any gradient going through the layer} These disabled neurons/channels can be removed from the network
+without changing its output. Before explaining how that is achieved, we explain
+next how the weights of the Filter Layer are initialized and adjusted during training.
 
@@
 %\subsection{The training procedure}
-\textbf{Training Procedure: } Once Filter layers are placed in a network, 
+\textbf{Training Procedure: } Once Filter layers are placed in a network and initialized (sampled from the Uniform$[0, 1]$ distribution),
 %To train networks we need start with a substantially oversized network, then we
@@
 performance. We achieve that by introducing sparsity in the parameters of the
-\textit{Filter Layers}, thus forcing the deactivation of neurons \srm{by decaying the value of theta}
+\textit{Filter Layers}, thus forcing the deactivation of neurons \srm{by decaying the value of theta} \gl{$\theta$ only decays (and only for some features), only because of the loss function that we have not defined yet at this moment in the paper}
 %. Indeed, having a negative component in the $\theta$
@@
 The additional term $\lambda|\theta|$ introduces sparsity (see Lasso
-loss~\cite{Tibshirani1996}). \srm{Say lambda is in [0,1]?}
-%This choice comes from the Lasso loss ~\cite{Tibshirani1996} and we use it for
-%the same reason: it introduces sparsity. 
-The $\lambda$ parameter adjusts how aggressively the network deactivates neurons,
-with larger values indicating more aggressive deactivation.
-\srm{Give some intuitive statement about how this loss function causes theta to decay in irrelevant neurons, while preserving the value of important neurons.}
-%The bigger the $\lambda$ the more
-%entries in $\theta$ are set to zero, and 
-Because the entries in $\theta$ with a value of $0$
-correspond to dead neurons, $\lambda$ effectively controls the number of
-neurons/channels in the entire network.  
-Next, we explain how to implement
-ShrinkNets efficiently.
+loss~\cite{Tibshirani1996}). 
+% The $\lambda$ parameter, that can take any
+% positive value, adjusts how aggressively the network deactivates neurons, with
+% larger values indicating more aggressive deactivation.
+Indeed, the second component of the loss, because it increases the gradient in
+respect with $\theta$, pushes its value towards zero. Neurons with little
+impact on the original loss (gradient lower than $\lambda$), will not be able
+to compete against this attraction towards zero. Because the entries in
+$\theta$ with a value of $0$ correspond to dead neurons, $\lambda$ effectively
+controls the number of neurons/channels in the entire network.  Next, we
+explain how to implement ShrinkNets efficiently.
 
@@
 information flow between neurons and layers in the neural network. We achieve
-this by representing such information flow as a graph, in which edges indicate
-what action each node, i.e., neuron, must take. 
-\srm{I can't really understand what this means -- need to add a bit more detail.}
+this by representing such information flow as a graph. Vertices represent layers,
+and edges are event-hubs responsible for propagating information about disabled
+neurons to the relevant layers.
 
@@
 
-\ra{stopped here}
-
 \begin{figure}
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{convergence}
+\includegraphics[width=\columnwidth]{convergence}
 \vspace{-.2in}
 \caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
-\srm{Move legend inside top of figure, to save space.}
 \vspace{-.2in}
@@
 \end{figure}
-
 \subsection{Does ShrinkNet find good networks?}
@@
 believe that the results generalize to more complex search methods.
-\srm{Note something about
-how we expect this to bear out even with methods other than random search?}
 
@@
 \begin{center}
-  \includegraphics[width=0.9\columnwidth]{hyper_opt}
+  \includegraphics[width=\columnwidth]{hyper_opt}
   \vspace{-.2in}
@@
 structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
-~\cite{Han2015}).  \ra{not sure the following is relevant. Instead, just
-contrast with the approach in this paper} However, most hardware (GPU's, TPUS ~\cite{Jouppi2017},
-TensorCores) do not really leverage sparsity in the connections efficiently (as
-explained in ~\cite{Han2016}). On the other side, ShrinkNets and some others
+~\cite{Han2015}). On the other side, ShrinkNets and some others
 ~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead

### 2018-01-06 paper/paper.tex
Update plots and add some explanation for the generalization

@@
 and less variable accuracies. Despite the simple nature of this experiment, we
-believe that the results generalize to more complex search methods.
+believe that the results generalize to more complex search methods; mainly
+because our solution reduce the dimensionality of the space they have to
+explore.
 

### 2018-01-06 paper/convergence_experiment_plot.py

@@ -85,4 +85,4 @@ for m, lamb in zip(reversed(markers), reversed(lambdas)):
 ax_loss.legend(handles=lines , labels=reversed(tex_labels) ,loc='lower center', bbox_to_anchor=(0.595, 0.68), ncol=3, columnspacing=0.5)
 f.set_size_inches(5, 4.5)
 plt.show()
-plt.savefig('convergence.pdf', bbox_inches='tight')
+plt.savefig('convergence.pdf', bbox_inches='tight', pad_inches=0)

### 2018-01-06 paper/hyper_opt_epxeriment_plot.py

@@ -89,17 +89,18 @@ def sub_plot(ax, dataset, first, conv=False, ff=False):
     if first:
         ax.set_ylabel('Accuracy (\\%)')
     if ff:
-        ax.legend(handles=boxes , labels=tex_labels ,loc='lower center', bbox_to_anchor=(1.75, 1.09), ncol=3, columnspacing=0.5)
+        ax.legend(handles=boxes , labels=tex_labels ,loc='lower center', bbox_to_anchor=(1.75, - 0.23), ncol=3, columnspacing=0.5)
 
 f, [axes_fc, axes_conv] = plt.subplots(2, 3, sharex=True)
 plt.subplots_adjust(wspace=0.3, hspace=0.1)
 first = True
-ff = True
+ff = False
 for ax, ds in zip(axes_fc, ['MNIST', 'FashionMNIST', 'CIFAR10']):
     sub_plot(ax, ds, first, False, ff)
     first = False
     ff = False
 first = True
+ff = True
 for ax, ds in zip(axes_conv, ['MNIST', 'FashionMNIST', 'CIFAR10']):
     sub_plot(ax, ds, first, True, ff)
     first = False
@@ -107,5 +108,5 @@ for ax, ds in zip(axes_conv, ['MNIST', 'FashionMNIST', 'CIFAR10']):
 
 f.set_size_inches(5, 5)
 plt.show()
-plt.savefig('hyper_opt.pdf', bbox_inches='tight')
+plt.savefig('hyper_opt.pdf', bbox_inches='tight', pad_inches=0)
 

### 2018-01-06 paper/paper.tex
Fix technical innacuracies

--- 2018-01-06 paper/paper.tex
@@
 meta-gradient descent~\cite{Pedregosa2016},
-Gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}. 
+Gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}, 
 %to find good parameters without exhaustively
 %exploring the entire hyper-parameter space. 
- these methods generally require a compute-intensive
+ they generally require a compute-intensive
 search of parameter space.
@@
 %  a network that learnt a tradeoff between size and accuracy}. 
-Our approach has two main benefits. First, no longer need to choose a
+Our approach has two main benefits. First, we no longer need to choose a
 network size before training. Second, the final network size will tuned to be
@@
 
-\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are placed after
+\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are usually placed after
 linear and convolutional layers.
@@
 layers with $n=0$ or convolutional layers with $n=2$. Their crucial property is
-a parameter $\theta \in \mathbb{R}^C$, defined as follows: \vspace{-1em}
+a parameter $\theta \in \mathbb{R}^C$. The output is defined as follows: \vspace{-1em}
 \begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
 Where $\circ$ is the pointwise multiplication, and $\theta$ is expanded in all
-dimensions to match the input size (except the second one since they are equal by definition). It is easy to see that if for any
-$k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be
-$0$. When this happens, we say the Filter layer deactivates the neuron.
-\srm{Not easy to see this because you haven't told me that theta only decays
-  over time?} \gl{The decay is only caused by the loss, and actually it does not depends on how it became zero, if it is zero for any reason, multiplying by zero will nullfy any value and cancel any gradient going through the layer} These disabled neurons/channels can be removed from the network
+dimensions to match the input size (except the second one since they are equal
+by definition). It is easy to see that if for any $k$, if $\theta_k \leq 0$,
+the $k^{\text{th}}$ input feature/channel is multiplied by zero and have no
+influence on the output. If this happens, we say the Filter layer deactivates
+the neuron. These disabled neurons/channels can be removed from the network
 without changing its output. Before explaining how that is achieved, we explain
-next how the weights of the Filter Layer are initialized and adjusted during training.
+next how the weights of the Filter Layer are initialized and adjusted during
+training.
 
@@
 performance. We achieve that by introducing sparsity in the parameters of the
-\textit{Filter Layers}, thus forcing the deactivation of neurons \srm{by decaying the value of theta} \gl{$\theta$ only decays (and only for some features), only because of the loss function that we have not defined yet at this moment in the paper}
-%. Indeed, having a negative component in the $\theta$
+\textit{Filter Layers}, thus forcing the deactivation of neurons%. Indeed, having a negative component in the $\theta$
 %parameter of the filter layer permamently disable its associated feature
 %\gl{Maybe redundant ? we talked about that in the previous paragraph} . 
-To obtain this sparsity, we simply redefine the loss function:
+. To obtain this sparsity, we simply redefine the loss function:
 \vspace{-.5em}
 \begin{equation}
-  L'(x,y;\theta) = L(x, y) + \lambda|\theta|
+  L'(x,y;\theta) = L(x, y) + \lambda|\max(0, \theta)|
 \end{equation}
 
-The additional term $\lambda|\theta|$ introduces sparsity (see Lasso
+The additional term $\lambda|\max(0, \theta)|$ introduces sparsity (see Lasso
 loss~\cite{Tibshirani1996}). 
@@
 % larger values indicating more aggressive deactivation.
-Indeed, the second component of the loss, because it increases the gradient in
-respect with $\theta$, pushes its value towards zero. Neurons with little
-impact on the original loss (gradient lower than $\lambda$), will not be able
-to compete against this attraction towards zero. Because the entries in
-$\theta$ with a value of $0$ correspond to dead neurons, $\lambda$ effectively
-controls the number of neurons/channels in the entire network.  Next, we
+The second component of the loss, because it increases the gradient with
+respect to $\theta$, pushes its value towards zero. Neurons with little impact
+on the original loss (gradient lower than $\lambda$), will not be able to
+compete against this attraction towards zero. Because the entries in $\theta$
+with a value of $0$ or less correspond to dead neurons, $\lambda$ effectively
+controls the number of neurons/channels in the entire network. We introduced
+the $\max(\dots)$ into the loss to make sure that neurons are permamently disabled
+when performing gradient descent based optimization. Next, we
 explain how to implement ShrinkNets efficiently.
@@
 architectures, a multi-layer perceptron (MLP) and the \textit{LeNet-5}
-model~\cite{Lecun1998}. We have no prior information about the network size, but
-we set an upper bound of $50$ channels per convolutional layer and $5000$
+model~\cite{Lecun1998}. We have no prior information about the network size,
+but we set an upper bound of $50$ channels per convolutional layer and $5000$
 neurons for fully connected layers. We then use random search to vary the
 parameters that determine the network size, i.e., $\lambda$ in the case of
-ShrinkNets, random selection of depth and witdh in the case of \textsf{Fixed}
-and similar to previous but adding a $L_2$ penalty~\cite{Ng2004}
+ShrinkNets, the width of each layer in the case of
+\textsf{Fixed} and similar to previous but adding a $L_2$ penalty~\cite{Ng2004}
 (\textsf{Fixed-L2}).  We train all variants on \texttt{MNIST}~\cite{Lecun1998},
@@
 and less variable accuracies. Despite the simple nature of this experiment, we
-believe that the results generalize to more complex search methods.
+believe that the results generalize to more complex search methods; mainly
+because our solution reduces the dimensionality of the space they have to
+explore.
 
@@
 of connections. This is very useful because it reduces the size of the matrices,
-producing speed-up on every device. ShrinkNets improves on
+producing speed-up even on devices/libraries that only support dense matrices
+. ShrinkNets improves on
 ~\cite{Scardapane2017} because it removes neurons during training, speeding up

### 2018-01-06 paper/hyper_opt_epxeriment_plot.py
Margin adjustments

@@ -106,7 +106,7 @@ for ax, ds in zip(axes_conv, ['MNIST', 'FashionMNIST', 'CIFAR10']):
     first = False
     ff = False
 
-f.set_size_inches(5, 5)
+f.set_size_inches(5, 4.5)
 plt.show()
 plt.savefig('hyper_opt.pdf', bbox_inches='tight', pad_inches=0)
 

### 2018-01-06 paper/paper.tex
Margin adjustments
Title and rephrasing

@@
 \begin{document}
-\title{ShrinkNets}
+\title{Learning Network Size While Training with ShrinkNets}
 
@@
 % larger values indicating more aggressive deactivation.
-The second component of the loss, because it increases the gradient with
-respect to $\theta$, pushes its value towards zero. Neurons with little impact
+ The second component of the loss increases the gradient with respect to $\theta$, thus pushing its value towards zero. Neurons with little impact
 on the original loss (gradient lower than $\lambda$), will not be able to
@@
 \includegraphics[width=\columnwidth]{convergence}
-\vspace{-.2in}
+\vspace{-.25in}
 \caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
@@
   \includegraphics[width=\columnwidth]{hyper_opt}
-  \vspace{-.2in}
+  \vspace{-.25in}
 \caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}

### 2018-01-27 paper/CIFAR100.py
Try to fix CIFAR100

@@ -1,0 +1,215 @@
+import numpy as np
+from models.vgg import VGG
+from torch.autograd import Variable
+from torch.nn import CrossEntropyLoss
+from torch.optim import Adam, SGD
+from torchvision import transforms
+from torchvision.datasets import MNIST, FashionMNIST, CIFAR10, CIFAR100
+from torch.utils.data import DataLoader, TensorDataset, Dataset
+from sklearn.model_selection import train_test_split
+from dynnet.utils import shrinknet_penalty
+from dynnet.filters import SimpleFilter
+from dynnet.graph import Graph
+import torchsample as ts
+import torch
+
+SEED = 0
+CRITERION = CrossEntropyLoss()
+NORMALIZATIONS = {
+    MNIST: [(0.13066047740239478,), (0.30810780876661253,)],
+    FashionMNIST: [(0.2860406021898328,), (0.353024253432129,)],
+    CIFAR10: [(0.49139968, 0.48215845, 0.44653094),
+              (0.24703224003314972, 0.24348513782024384, 0.26158785820007324)],
+    CIFAR100: [(0.50707513, 0.48654887, 0.44091785),
+               (0.26733428, 0.25643846, 0.27615047)]
+}
+SIZES = {
+    MNIST: (1, 28, 28),
+    FashionMNIST: (1, 28, 28),
+    CIFAR10: (3, 32, 32),
+    CIFAR100: (3, 32, 32)
+}
+REGULARIZATIONS = {
+    MNIST: [2, 5],
+    FashionMNIST: [2, 5],
+    CIFAR10: [2, 6],
+    CIFAR100: [2, 6]
+}
+
+DATA_AUGMENTATIONS = {
+    MNIST: [],
+    FashionMNIST: [],
+    CIFAR100: [
+        ts.transforms.RandomFlip(True, False, 0.5),
+        ts.transforms.RandomShear(25),
+        ts.transforms.RandomBrightness(-0.3, 0.4),
+        ts.transforms.RandomRotate(35),
+        ts.transforms.RandomSaturation(-0.8, 1),
+    ],
+    CIFAR10: [
+        ts.transforms.RandomFlip(True, False, 0.5),
+        ts.transforms.RandomShear(25),
+        ts.transforms.RandomBrightness(-0.3, 0.4),
+        ts.transforms.RandomRotate(35),
+        ts.transforms.RandomSaturation(-0.8, 1),
+    ]
+}
+
+class IndexDataset(Dataset):
+    def __init__(self, dataset, indices, transform=None):
[…]

### 2018-01-27 paper/hyper_opt_epxeriment.py
Add CIFAR100 settings

@@ -6,8 +6,8 @@ from torch.nn.functional import relu
 from torch.autograd import Variable
 from torch.optim import Adam
 from torchvision import transforms
-from torchvision.datasets import MNIST, FashionMNIST, CIFAR10
-from dynnet.graph import Graph
+from torchvision.datasets import MNIST, FashionMNIST, CIFAR10, CIFAR100
+from dynnet.graph import Graph, Sequential
 from dynnet.filters import SimpleFilter
 from sklearn.model_selection import train_test_split
 from uuid import uuid4
@@ -23,23 +23,28 @@ NORMALIZATIONS = {
     MNIST: [(0.13066047740239478,), (0.30810780876661253,)],
     FashionMNIST: [(0.2860406021898328,), (0.353024253432129,)],
     CIFAR10: [(0.49139968, 0.48215845, 0.44653094),
-              (0.24703224003314972, 0.24348513782024384, 0.26158785820007324)]
+              (0.24703224003314972, 0.24348513782024384, 0.26158785820007324)],
+    CIFAR100: [(0.50707513, 0.48654887, 0.44091785),
+               (0.26733428, 0.25643846, 0.27615047)]
 }
 SIZES = {
     MNIST: (1, 28, 28),
     FashionMNIST: (1, 28, 28),
-    CIFAR10: (3, 32, 32)
+    CIFAR10: (3, 32, 32),
+    CIFAR100: (3, 32, 32)
 }
 REGULARIZATIONS = {
     MNIST: [2, 5],
     FashionMNIST: [2, 5],
-    CIFAR10: [2, 6]
+    CIFAR10: [2, 6],
+    CIFAR100: [2, 6]
 }
 
 DATASETS = {
     'MNIST': MNIST,
     'FashionMNIST' : FashionMNIST,
-    'CIFAR10': CIFAR10
+    'CIFAR10': CIFAR10,
+    'CIFAR100': CIFAR100
 }
 
 def preload_dataset(dataset, train):
@@ -80,7 +85,7 @@ def init_model(model):
             torch.nn.init.xavier_normal(parameter.data, gain=np.sqrt(2))
     for l in model:
         if isinstance(l, SimpleFilter):
-            l.weight.data.uniform_(0, 1)
+            l.weight.data.uniform_(0, 0)
 
 
 def create_dynamic_model(start_size=5000, size=(1, 28, 28), conv=False):
@@ -149,6 +154,7 @@ def regularized_loss(graph, prediction, labels, lamb):
[…]

### 2018-01-27 paper/ICML/paper.tex

%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{bm}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{stmaryrd}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{amsmath}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\diag}[1]{\text{diag}\left(#1\right)}
\newcommand{\intint}[1]{\left\llbracket#1\right\rrbracket}
\newtheorem{proposition}{Proposition}[section]

% Use the following line for the initial blind version submitted for review:
\usepackage[accepted]{icml2018}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Learning Neural Network size with shrinkNets}

\begin{document}

\twocolumn[
\icmltitle{Learning Network Size while Training with ShrinkNets}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2018
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Guillaume Leclerc}{mit}
\icmlauthor{Raul Castro Fernandez}{mit}
\icmlauthor{Manasi Vartak}{mit}
\icmlauthor{Martin Jaggi}{epfl}
\icmlauthor{Samuel Madden}{mit}
\end{icmlauthorlist}

\icmlaffiliation{mit}{Computer Science and Artificial Intelligence Laboratories, Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}

\icmlaffiliation{epfl}{Swiss Federal Institute of Technology, Lausanne, Switzerland}

\icmlcorrespondingauthor{Guillaume Leclerc}{leclerc@mit.edu}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{} % otherwise use the standard text.

\begin{abstract}
  Let's write the abstract at the end
\end{abstract}

\section{Tentative outline}

\begin{itemize}
  \item We want to figure out what is the proper network size
  \item If we had a oversized network and for each neuron we would have an on/off switch, we could optimize the state of each switch to achieve any size/accuracy tradeof (we can prove that, do we care ?)
  \item Solving such problem is NP-Hard
  \item We could approximate the binary switch by relaxing them and doing L1 loss instead of L0 loss
  \item This is the definition of Shrinknets
  \item group sparsity tries to achieve a similar goal but with a different formulation
  \item How are they related ?
  \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
  \item We conclude that without this constraint our formulation has more degree of freedom
  \item What happen when we drop this constraint
  \item The problem becomes non-convex and without a global minimum
  \item Not having a global minimum is bad, how can we solve that ?
  \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
  \item Now we have a framework to switch on and of neurons
  \item We are still doing useless computation for neurons that will stay off forever, if we pruned them then we would speed up training
  \item Define the strategy to detect "forever dead" neurons
  \item (should we talk about the software architecture ?)
  \item now we evaluate the system
  \item First we show that our system has indeed more freedom than Group sparsity by showing that for any given amount of sparsity it can fit closer than the previous method
  \item On the same problem we show that removing neurons on the fly does not dramatically reduce accuracy (we might not be able to see any difference in performance for a linear/logistic regression though)
  \item We show that works with Bigger networks (multi layers perceptrons and CNNs), describe the training dynamics, discuss the shape we obtain
  \item Show that it is easier to do hyper-parameter optimization on the regularization parameter that the size of each layer. I think a nice experiment would be to plot the evolution of the final size of a two layer network (so going from a lambda to two sizes). And plot the trajectory in the "size space" as we decrease lambda. It would show how the system trades off the budget between the two layer in a nice and visual way
  \item Then we evaluate performance
\end{itemize}

\section{Introduction}

\section{ShrinkNets}

\subsection{Motivation}

\subsection{Notations}

\par In order to avoid any potential ambiguity, in this section we will
describe in details the mathematical notations used in this article. Non-bold
letters represent scalar values, while bold lowercase and upper case
repectively denote vectors and matrices. $\bm{A}^T$ stands for the transpose of
the matrix $\bm{A}$. Subscripts are used to index particular elements of
vectors and matrices. $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
$\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
component of the $i^{th}$ row of $\bm{A}$. All the following definitions assume
$\bm{A}$ to be an $n\times p$ matrix.  For any vetor $\bm{b}$ with $n$
components, we define $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.  For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
\left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$. For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function. The only constraint that we want to enforce is that $a(0) = 0$. We use $\intint{u, v}$ to denote inteveral of integers, $\bm{0}$ is the null vector (size depending on the context). $\#S$ is meant to represent the cardinality of a set $S$. To simplify the notation of function composition we use the following operator: $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
\subsection{Definition}

\begin{equation}
  \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
\end{equation}

\section{Theoretical analysis}

Our goal when designing ShrinkNets was to be able to remove inputs
and outputs of layers. For classic fully connected layers, which are defined
as :

\begin{equation} \label{fully_connected}
  f_{\bm{A}, \bm{b}}(\bm{x})=a(\bm{Ax + b})
\end{equation}

removing an input neuron $j$ is equivalent to have $\left(\bm{A}^T\right)_j = \bm{0}$
and removing an output neuron $i$ is the same as having $\bm{A}_i = \bm{0}$ and $\bm{b}_i = 0$. Solving  optimization problems while trying to set entire groups
of parameters to zero has been already studied and the most popular method
is without doubt the group sparsity regularization [ref]. For any partitionning of the set of parameter defining a model in $p$ groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$ we define it the following way:

\begin{equation}
  \Omega_\lambda^{gp} = \lambda \sum_{i=1}^p \sqrt{\#\bm{\theta_i}} \norm{\bm{\theta_i}}_2 \\
\end{equation}

In the context of a fully-connected layer, the groups are either: columns of $\bm{A}$ if we want to remove inputs, or rows of $\bm{A}$ and the corresponding entry in $\bm{b}$ if we want to remove outputs. For simplicity, we will focus our analysis in the simple one-layer case. In this case filtering outputs does not make a lot of sense, this is why we will only consider the former case. The group sparsity regularization then becomes:

\begin{equation} \label{group_sparsity_regularization}
  \Omega_\lambda^{gp} = \lambda \sum_{j=1}^p \norm{\bm{\left(A^T\right)_j}}_2 \\
\end{equation}

Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
we now embed $\sqrt{n}$ inside $\lambda$.

Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The ShrinkNet problem is:

\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s
\end{equation}

And the Group Sparsity problem is:

\begin{equation}
  \min_{\bm{A}} \norm{\bm{y} - \bm{A}\bm{x}}_2^2 + \Omega_\lambda^{gp}
\end{equation}

We can prove the under the condition: $\forall 1 \leq j \leq p, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}). However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}). Fortunately, by adding an extra term to the ShrinkNet regularization term we can proove that:

\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s + \lambda_2\norm{A}_p^p
\end{equation}

has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we define the \textit{regularized ShrinkNet penalty}:

\begin{equation}
  \Omega_{\lambda, \lambda_2, p}^{rs} = \lambda\norm{\bm{\beta}}_1 + \lambda_2\norm{\bm\theta}_p^p
\end{equation}

In practice we observed that $p=2$ or $p=1$ are good choice, while the latter will also introduce additional sparsity in the parameters.

\section{Speeding up training with pruning}

\section{Evaluation}

\subsection{Multi-Target Linear and Logistic regressions}

\subsection{Neuron Removal strategies}

\subsection{Convergence and training dynamics of Neural networks}

\subsection{Hyper-optimization of ShrinkNets}

\subsection{Transfer Learning with ShrinkNets}

\subsection{Performance}

\section{Related Work}

\section{Future Work}

\section{Conclusion}

\appendix
\section{Appendix}
\subsection{Proofs of propositions}
Unless specified, all the proofs consider the Multi-Target linear regression problem
\begin{proposition}
\label{gps_equivalence}
  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$

  \begin{align*}
    & \min_{\bf{A}} \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
     = &\min_{\bf{A'}, \bm{\beta}} \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1 \\
     & \text{s.t.} \forall j \in \intint{1, p}, \norm{\left(A'^T\right)_j}_2^2 = 1
  \end{align*}
\end{proposition}

\begin{proof}
  In order to prove this statement we will show that for any solution $\bm{A}$ in the first problem, there exists a solution in the second with the exact same value, and vice-versa.
We now assume we have a potential solution $\bm{A}$ for the first problem and we define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$. It is easy to see that the constraint on $\bm{A}'$ is statisfied by construction. Now:
  \begin{align*}
    & \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A'^T\right)_j\beta_j}_2 \\
    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \abs{\beta_j} \cdot 1\\
    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
  \end{align*}
  Assuming we take an $\bm{A}'$ that satisfy the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$. We can apply the same operations in reverse order and obtain an instance of the first problem with the same value. We can now see that the two problems must have the same minimum otherwise we would be able to construct a solution to the other with exact same value.
\end{proof}

\begin{proposition}
\label{unconstrained_non_convex}
\begin{equation*}
     \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2
\end{equation*}
is not convex in $\bm{A}$ and $\bm{\beta}$.
\begin{proof}
  To prove this we will take the simplest instance of the problem: with only scalars. We have $f(a, \beta) = \left(y - a\beta x\right)^2$. For simplicty let's take $y = $ and $x > 0$. If we take two candidates $s_1 = (0, 2)$ and $s_2 = (2, 0)$, we have $f(s_1) = f(s_2) = 0$. However $f(\frac{2}{2}, \frac{2}{2}) = x > \frac{1}{2} f(0, 2) + \frac{1}{2}f(2, 0)$, which break the convexity property. Since we showed that a particular case of the problem is non-convex then necessarly the general cannot be convex.
\end{proof}
\end{proposition}

\begin{proposition}
\label{unconstrained_shrinknet_no_min}
\begin{equation*}
     \min_{\bf{A}, \bm{\beta}} \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
\end{equation*}
has no solution if $\lambda > 0$.
\end{proposition}
\begin{proof}
  Let's assume this problem has a minimum $\bm{A}^*, \bm{\beta}^*$. Let's consider $2\bm{A}^*, \frac{1}{2}\bm{\beta}^*$. Trivially the first component of the sum is identical for the two solutions, however $\lambda\norm{\frac{1}{2}\bm{\beta}} < \lambda\norm{\bm{\beta}}$. Therefore $\bm{A}^*, \bm{\beta}^*$ cannot be the minimum. We conclude that this problem has no solution.
\end{proof}
\begin{proposition}
  \label{shrinknet_regularized_minimum}
For this proposition we will not restrict ourselves to single layer but the composition of an an arbitrary large ($n$) layers as defined individually as $f_{\bm{A}_i, \bm{\beta}_i, \bm{b}_i}(x) = a(\bm{A_i}\diag{\bm{\beta_i}}\bm{x} + \bm{b_i})$. The entire network follows as: $N(\bm{x}) = \left(\bigcirc_{i=1}^n f_{\bm{A_i}, \bm{\beta_i}, \bm{b_i}}\right)(\bm{x})$. For $\lambda > 0$, $\lambda_2 > 0$ and $p > 0$ we have:
  \begin{equation*}
    \min \norm{\bm{y} - N(\bm{x})}_2^2 + \Omega_{\lambda, \lambda_2, p}^{rs}
  \end{equation*}
  has at least $2^k$ global minimum where $k = \sum_{i=1}^n \#\bm{\beta_i}$
\end{proposition}

\begin{proof}
First let's prove that there is at least one minimum to this problem. The two components of the expression are always positive so we know that this problem is bounded by below by $0$. Let's assume this function does not have a minimum. Then there is a sequence of parameters $(S_n)_{n>0}$ such that the function evaluated at that point convereges to the infimum of the problem. Since the function is defined everywhere does not have a minimum then this sequence must diverge. Since the entire sequence deverge the there is at least one individual parameter that diverges. First case, the parameter is a component $k$ of some $\bm{\beta_i}$ for some $i$. Necessarly $\norm{\bm{\beta_i}}_1$ diverge towards $+ \infty$, which is incompatible with the fact that $(S_n)$ converges to the infimum. We can have the exact same argument if the diverging parameter is in $\bm{A_i}$ or $\bm{b_i}$ because $p > 0$. Since there is always a contradiction then our assumption that the function has no global minimum must be false. Therefore, this problem has at least one global minimum.

\par Let's consider one optimal solution of the problem. For each component $k$ of $\bm{\beta_i}$ for some $i$. Negating it and negating the $k^{th}$ column of $\bm{A_i}$ does not change the the first part of the objetive because the two factors cancel each other. The two norms do not change either because by definition the norm is independant of the sign. As a result these two sets of parameter have the same value and are both global minimum. It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$. We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.

\end{proof}
\subsection{Experiment details}
\subsubsection{Multi-Target Linear and Logistic regressions}
\subsubsection{Neuron Removal strategies}
\subsubsection{Convergence and Training Dynamics of Neural networks}
\subsubsection{Hyper-optimization of ShrinkNets}
\subsubsection{Transfer Learning with ShrinkNets}
\subsubsection{Performance}

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite

\bibliography{example_paper}
\bibliographystyle{icml2018}

\end{document}

### 2018-01-27 paper/ICML/linear_regression_experiment.py
Finished evaluation of Linear regression models

@@ -1,0 +1,180 @@
+from multiprocessing import set_start_method
+try:
+    set_start_method('spawn')
+except RuntimeError:
+    pass
+import numpy as np
+from torch.autograd import Variable
+from torch.optim import Adam, Adagrad, SGD
+from scipy.io.arff import loadarff
+from torch.multiprocessing import Pool
+import torch
+
+def tn(o):
+    try:
+        return o.data.cpu().numpy()[0]
+    except:
+        return o
+
+def normalize(tensor):
+    m = tensor.mean(0)
+    tensor -= m
+    s = tensor.std(0)
+    return tensor / s
+
+def load_dataset(ds):
+    file = loadarff('../../datasets/mtr-datasets/%s' % ds)[0]
+    data = np.array([[w for w in y] for y in file])
+    inputs = torch.from_numpy(data[:, :-16]).float().cuda()
+    outputs = torch.from_numpy(data[:, -16:]).float().cuda()
+    return Variable(normalize(inputs)), Variable(normalize(outputs))
+
+def get_sparse_columns(model, threshold=1e-3):
+    weights = model.get_weights()
+    return (weights.abs() < threshold).float().sum(0) == weights.size(0)
+
+def get_sparsity(model):
+    return get_sparse_columns(model).float().mean()
+
+# This class is just a wrapper so that they all have the same
+# interface
+class LinearModel(torch.nn.Module):
+    def __init__(self, in_features, out_features):
+        super(LinearModel, self).__init__()
+        self.linear = torch.nn.Linear(in_features, out_features, bias=True)
+
+    def penalty(self, l1, l2):
+        return 0.0
+
+    def forward(self, x):
+        return self.linear(x)
+
+    def get_weights(self):
+        return self.linear.weight
+
+class GroupSparseModel(torch.nn.Module):
+    def __init__(self, in_features, out_features):
+        super(GroupSparseModel, self).__init__()
+        self.linear = torch.nn.Linear(in_features, out_features, bias=True)
+
+    def penalty(self, l1, l2):
+        return l1 * self.linear.weight.pow(2).sum(0).sqrt().sum()
+
+    def get_weights(self):
+        return self.linear.weight
+
+    def forward(self, x):
[…]

### 2018-01-28 paper/ICML/logistic_regression_experiment.py
Finish experiment 1 (some results are still waiting)

@@ -1,0 +1,130 @@
+from multiprocessing import set_start_method
+try:
+    set_start_method('spawn')
+except RuntimeError:
+    pass
+import numpy as np
+from torch.autograd import Variable
+from torch.optim import Adam, Adagrad, SGD
+from scipy.io.arff import loadarff
+from torch.multiprocessing import Pool
+from linear_regression_experiment import (
+    tn, normalize, get_sparse_columns, get_sparsity,
+    GroupSparseModel, ShrinkModel
+)
+import openml
+import torch
+from sklearn import preprocessing
+
+def load_dataset(id, do_normalize=True, factor=1):
+    dataset = openml.datasets.get_dataset(id)
+    X, y, categorical = dataset.get_data(
+        target=dataset.default_target_attribute,
+        return_categorical_indicator=True)
+    lines_without_nans = (np.isnan(X).sum(1) == 0)
+    X = X[lines_without_nans]
+    y = y[lines_without_nans]
+    if any(categorical):
+        enc = preprocessing.OneHotEncoder(categorical_features=categorical)
+        X = enc.fit_transform(X).todense()
+    inputs = torch.from_numpy(X).float().cuda()
+    outputs = torch.from_numpy(y).long().cuda()
+    if do_normalize:
+        inputs = normalize(inputs)
+    return Variable(inputs * factor), Variable(outputs)
+
+def train(inputs, outputs, model, l1, l2, lr=1e-5, epochs=10000):
+    criterion = torch.nn.CrossEntropyLoss()
+    optimizer = Adagrad(model.parameters(), lr=lr)
+
+    log = []
+    for _ in range(epochs):
+        prediction = model(inputs)
+        acc = tn((prediction.max(1)[1] == outputs).float().mean())
+        original_loss = criterion(prediction, outputs)
+        penalty = model.penalty(l1, l2)
+        error = original_loss + penalty
+        optimizer.zero_grad()
+        error.backward()
+        log.append((tn(original_loss), tn(penalty), tn(get_sparsity(model)), acc))
+        optimizer.step()
+
+    return np.array(log)
+
+def run_experiment(exp):
+    Ctr, inputs, outputs, l1, l2, lr, epochs = exp
[…]

### 2018-01-28 paper/ICML/plot_regressions.py

@@ -1,0 +1,119 @@
+from matplotlib import rc, use
+# use('agg')
+import numpy as np
+import pandas as pd
+import torch
+import matplotlib.pyplot as plt
+from glob import glob
+# for Palatino and other serif fonts use:
+rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+# lambdas = [0.1, 0.01, 0.001, 0.0001, 0.00001]
+# tex_labels = ["$\lambda=10^{-%s}$" % x for x in range(1, 6)]
+# 
+# def load_file(filename):
+#     with open(filename, 'r') as f:
+#         lines = [list(map(float, x.strip().split())) for x in f.readlines()]
+#     frame =  pd.DataFrame(np.array(lines), columns=['loss', 'size'])
+#     window_size = int(len(frame) / 100)
+#     return frame.rolling(window_size, min_periods=0).mean()
+# 
+# files = glob('./experiments_results/*')
+# 
+# comparisons = []
+# for l in lambdas:
+#     f_mnist = load_file('./experiments_results/conv_MNIST_bs256_lamb%s.dat' % l).iloc[-100:].min()
+#     f_fm = load_file('./experiments_results/conv_FashionMNIST_bs256_lamb%s.dat' % l).iloc[-100:].min()
+#     comparisons.append([
+#         f_mnist['size'], f_mnist['loss'], f_fm['size'], f_fm['loss']
+#     ])
+# comparisons = np.array(comparisons)
+# 
+# r = np.array(list(range(0, comparisons.shape[0])))
+# bw = 0.25
+# 
+# f, (ax_size, ax_loss) = plt.subplots(1, 2, sharex=True)
+# l1, = ax_size.plot(r, comparisons[:, 0], '-x')
+# l2, = ax_size.plot(r, comparisons[:, 2], '-o')
+# ax_loss.plot(r, comparisons[:, 1], '-x')
+# ax_loss.plot(r, comparisons[:, 3], '-o')
+# ax_loss.set_xlim(0, 4)
+# ax_size.set_xlim(0, 4)
+# ax_loss.set_yscale('log')
+# ax_size.set_xlabel('$\lambda$')
+# ax_loss.set_xlabel('$\lambda$')
+# ax_size.set_ylabel('Hidden Units')
+# ax_loss.set_ylabel('Cross-Entropy Loss')
[…]

### 2018-01-28 paper/ICML/plot_regressions.py
Add first evaluation to paper
- And start second

@@ -1,5 +1,5 @@
 from matplotlib import rc, use
-# use('agg')
+use('agg')
 import numpy as np
 import pandas as pd
 import torch
@@ -100,7 +100,7 @@ def plot_file(ax, fn, max_val, right=False):
     gs, s = load_file(fn)
     ax.plot(gs[:, 2], gs[:, 0] / max_val, 'x-', label="Group Sparsity")
     ax.plot(s[:, 2], s[:, 0] / max_val, '.-', label="ShrinkNet")
-    ax.set_ylim((0, 1.1))
+    ax.set_ylim((-0.1, 1.1))
     if right:
         ax.yaxis.set_ticklabels([])
     ax.yaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
@@ -115,5 +115,6 @@ plot_file(axs_logistic[1], './experiments_results/logistic_reg_1447.pkl', np.log
 axs_linear[0].legend()
 f.set_size_inches((5, 5))
 
-f.text(0.52, 0.04, 'Ratio of features dropped', ha='center')
-f.text(0.04, 0.5, 'Normalized error', va='center', rotation='vertical')
+f.text(0.52, 0.04, 'Sparsity', ha='center')
+f.text(0.02, 0.5, 'Normalized loss', va='center', rotation='vertical')
+plt.savefig('regressions.pdf', bbox_inches='tight', pad_inches=0)

### 2018-01-28 paper/ICML/plot_regressions.py
Add latest results

@@ -111,9 +111,9 @@ plt.subplots_adjust(wspace=0.05, hspace=0.05)
 plot_file(axs_linear[0], './experiments_results/linear_reg_scm1d.arff.pkl', 1)
 plot_file(axs_linear[1], './experiments_results/linear_reg_oes97.arff.pkl', 1, True)
 plot_file(axs_logistic[0], './experiments_results/logistic_reg_1041.pkl', np.log(10))
-plot_file(axs_logistic[1], './experiments_results/logistic_reg_1447.pkl', np.log(6), True)
+plot_file(axs_logistic[1], './experiments_results/logistic_reg_1477.pkl', np.log(6), True)
 axs_linear[0].legend()
 f.set_size_inches((5, 5))
 
 f.text(0.52, 0.04, 'Ratio of features dropped', ha='center')
-f.text(0.04, 0.5, 'Normalized error', va='center', rotation='vertical')
+f.text(0, 0.5, 'Normalized error', va='center', rotation='vertical')

### 2018-01-28 paper/ICML/paper.tex

@@
 % Use the following line for the initial blind version submitted for review:
-\usepackage[accepted]{icml2018}
+\usepackage{icml2018}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Learning Neural Network size with shrinkNets}
+\icmltitlerunning{Learning Neural Network size with ShrinkNets}
 
@@
 
-We can prove the under the condition: $\forall 1 \leq j \leq p, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}).
+We can prove the under the condition: $\forall j\in \intint{1, p}, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}).
 However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}).
@@
 
-\subsection{Multi-Target Linear and Logistic regressions}
+\subsection{Multi-Target Linear and Multi-Class Logistic regressions}
+
+We will start evaluating ShrinkNets with the simplest problems possible: linear
+and logistic regression. As we showed, Group sparsity share similarities with
+our method, this is why we will use it as baseline. We decided to focus on
+multi-target linear regression because in the single target case, groups in the
+Group Sparsity problem would have a size of one ($\bm{A}$ would be a vector in this
+case).
+
+The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
+[ref] for linear regressions and we will use \texttt{gina\_prior2} [ref] and
+the \textit{Gas Sensor Array Drift Dataset} [ref] (that we shorten in
+\texttt{gsadd}) for logistic regressions.
+
+For each dataset we fit with different regularization parameters and measure
+the error and sparsity obtained after convergence. In this context we define sparsity as the ratio of columns that have all their weight under $10^{-3}$ in absolute value. Parameters were choosed in
+order to obtain the widest sparsity spectrum. Loss is normalized depending on the problem to be in the $[0, 1]$ range. We summarized the results in
+\cref{sparsity_accuracy}.
+From our experiments it is clear that ShrinkNets can fit the data closer than Group Sparsity for the same amount of sparsity.
+The fact that we are able to reach very low loss demonstrate that even if our objective function is non convex, in practice it works as good or better as convex alternatives.
+Details about these datasets and the parameters used
+are available in \cref{linear_datasets}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.97\columnwidth]{regressions}
+\vspace*{-5mm}
+\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
+From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
+
+\end{center}
+\vspace*{-4mm}
+\end{figure}
 
 \subsection{Neuron Removal strategies}
+
+In our previous experiment, we showed that the ShrinkNet loss was
+reasonable in practice, we are now interested in the impact on
+early pruning. The two most important questions to answer are:
+What are the impact on convergence speed (i.e. the number of iterations) ?
+and: What is the difference in loss with and without early pruning ?
 
@@
 \subsection{Hyper-optimization of ShrinkNets}
-
-\subsection{Transfer Learning with ShrinkNets}
 
@@
 \section{Appendix}
-\subsection{Proofs of propositions}
+\subsection{Proofs}
 Unless specified, all the proofs consider the Multi-Target linear regression problem
@@
 \subsubsection{Multi-Target Linear and Logistic regressions}
+\label{linear_datasets}
 \subsubsection{Neuron Removal strategies}
@@
 \subsubsection{Hyper-optimization of ShrinkNets}
-\subsubsection{Transfer Learning with ShrinkNets}
 \subsubsection{Performance}
@@
 % references without citing it in the main text, use \nocite
+\nocite{OpenML2013}
 
-\bibliography{example_paper}
+\bibliography{custom}
 \bibliographystyle{icml2018}

### 2018-01-29 paper/ICML/neuron_removal_experiment.py
Add first results for experiment 2

@@ -1,0 +1,91 @@
+import torch
+import numpy as np
+from torch.optim import Adagrad
+from torch.autograd import Variable
+from torch.multiprocessing import Pool
+from linear_regression_experiment import (
+    ShrinkModel, load_dataset, tn, get_sparsity, SHRINK_PARAMS
+)
+
+THRESHOLD = 0.5
+FACTOR = 3
+
+def train(inputs, outputs, model, l1, l2, lr=1e-5, epochs=10000, gamma=0.9, remove=False, randomized=False):
+    criterion = torch.nn.MSELoss()
+    optimizer = Adagrad(model.parameters(), lr=lr)
+
+    # Everyone starts the same way
+    for p in model.parameters():
+        # p.data.fill_(1.0)
+        pass
+
+    log = []
+    sum_beta = 0
+
+    if gamma is not None:
+        mask = model.beta.data.new(model.beta.size()).fill_(1).byte()
+        exp_avg = model.beta.data.new(model.beta.size()).fill_(1.0)
+        exp_std= model.beta.data.new(model.beta.size()).fill_(0)
+    if randomized:
+        noise = inputs.data.new(inputs.data.size())
+
+    for _ in range(FACTOR * epochs):
+        sum_beta += tn(mask.float().sum())
+        if randomized:
+            noise.uniform_(0, THRESHOLD)
+            current_inputs = inputs * Variable((noise > exp_std).float())
+        else:
+            current_inputs = inputs
+        original_loss = criterion(model(current_inputs), outputs)
+        penalty = model.penalty(l1, l2)
+        error = original_loss + penalty
+        optimizer.zero_grad()
+        error.backward()
+        log.append((tn(original_loss),
+                    tn(penalty),
+                    tn(get_sparsity(model))))
+        optimizer.step()
+        if gamma is not None:
+            bs = model.beta.data.sign()
+            diff = bs - exp_avg
+            exp_std.mul_(gamma).addcmul_(1 - gamma, diff, diff)
+            exp_avg.mul_(gamma).add_(1 - gamma, bs)
+            mask.mul_(exp_std <= THRESHOLD)
+            if remove:
+                model.beta.data.mul_(mask.float())
+    return tuple(log[-1]) + (tn(mask.float().sum()), sum_beta)
+
+def run_experiment(exp):
+    model = exp[0](exp[1].size(1), exp[2].size(1)).cuda()
+    return train(*((exp[1], exp[2] , model,) +exp[3:]))
+
+
[…]

### 2018-01-29 paper/ICML/plot_neuron_removal.py

@@ -1,0 +1,95 @@
+from matplotlib import rc, use
+# use('agg')
+import numpy as np
+import pandas as pd
+import torch
+import matplotlib.pyplot as plt
+from glob import glob
+# for Palatino and other serif fonts use:
+rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+# def last(experiments):
+#     return np.stack([x[-1] for x in experiments])
+# 
+# def load_file(filename):
+#     with open(filename, 'rb') as f:
+#         [gs_params, gs_logs, s_params, s_logs] = torch.load(f)
+#     return last(gs_logs), last(s_logs)
+# 
+# def plot_file(ax, fn, max_val, right=False):
+#     gs, s = load_file(fn)
+#     ax.plot(gs[:, 2], gs[:, 0] / max_val, 'x-', label="Group Sparsity")
+#     ax.plot(s[:, 2], s[:, 0] / max_val, '.-', label="ShrinkNet")
+#     ax.set_ylim((-0.1, 1.1))
+#     if right:
+#         ax.yaxis.set_ticklabels([])
+#     ax.yaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
+#     ax.xaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
+# 
+# f, (axs_linear, axs_logistic) = plt.subplots(2, 2, sharex=True)
+# plt.subplots_adjust(wspace=0.05, hspace=0.05)
+# plot_file(axs_linear[0], './experiments_results/linear_reg_scm1d.arff.pkl', 1)
+# plot_file(axs_linear[1], './experiments_results/linear_reg_oes97.arff.pkl', 1, True)
+# plot_file(axs_logistic[0], './experiments_results/logistic_reg_1041.pkl', np.log(10))
+# plot_file(axs_logistic[1], './experiments_results/logistic_reg_1477.pkl', np.log(6), True)
+# axs_linear[0].legend()
+# f.set_size_inches((5, 5))
+# 
+# f.text(0.52, 0.04, 'Sparsity', ha='center')
+# f.text(0.02, 0.5, 'Normalized loss', va='center', rotation='vertical')
+# plt.savefig('regressions.pdf', bbox_inches='tight', pad_inches=0)
+
+def load_file(ds, lamb):
+    fn = './experiments_results/neuron_removal_reg_%s.arff_l_%s.pkl' % (ds, lamb)
+    with open(fn, 'rb') as f:
[…]

### 2018-01-29 paper/ICML/paper.tex
First attempt implementing the Smooth Filter

@@
 \begin{icmlauthorlist}
-\icmlauthor{Guillaume Leclerc}{mit}
+\icmlauthor{Guillaume Leclerc}{mit,epfl}
 \icmlauthor{Raul Castro Fernandez}{mit}
@@
 \begin{center}
-\includegraphics[height=0.97\columnwidth]{regressions}
+\includegraphics[width=\columnwidth]{regressions}
 \vspace*{-5mm}
@@
 reasonable in practice, we are now interested in the impact on
-early pruning. The two most important questions to answer are:
-What are the impact on convergence speed (i.e. the number of iterations) ?
-and: What is the difference in loss with and without early pruning ?
+early pruning. The method we suggest for early prunning uses a
+parameter $\gamma$ that control the aggressiveness of neuron removal
+so we will try to evaluate its impact on the final loss achieved by
+the model and the cost required to train the model. Our cost model
+is simple and hardware independant, we sum the number of input neurons
+at each epoch. In theory the cost in time should be asymptotically
+linear to this metric. To have a baseline we also train the same model
+but without neuron removal. Keep in mind that this is just in order to
+have some reference. Indeed, if we were to remove the neurons with small
+weights it would deteriorate the loss (and picking the threshould would
+be completely arbitrary). Therefore the baseline is evaluated with all neurons.
+One could consider it as a "theoretical lower bound" of the best achievable loss.
+
+We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$).
+We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}.
+In order to reduce the noise in the result, each experiment was performed $30$ times and we display the range arround $\pm$ $1$ standard deviation.
+
+\textbf{TODO: Interpret the results}
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{neuron_removal}
+\vspace*{-5mm}
+\caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$.
+First column is the difference in the final loss in function of the removal factor.
+We plot theoretical baseline as a reference.
+Right column is a proxy of the total cost for training the model (i.e.
+the sum of input neurons at each epoch).
+Each row is a dataset/$\lambda$ combination.
+From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}
+
+\end{center}
+\vspace*{-4mm}
+\end{figure}
 

### 2018-01-29 dynnet/filters.py

@@ -1,15 +1,24 @@
 """This module implements different algorithms for feature selection"""
 
 from typing import Any, Union
-from torch import ones, nonzero, LongTensor, ByteTensor, rand
+from torch import ones, nonzero, LongTensor, ByteTensor, rand, randn
 from torch.nn import Parameter
 from torch.nn.functional import relu
 
 from dynnet.interfaces import DynamicModule, GarbageCollectionLog
 from dynnet.operations import IndexSelectOperation
 
+class Filter(DynamicModule):
 
-class SimpleFilter(DynamicModule):
+    def forward(self, x):
+        raise NotImplementedError("This is an abstract class")
+
+    def get_weights(self):
+        raise NotImplementedError("This is an abstract class")
+
+
+
+class SimpleFilter(Filter):
 
     def __init__(self, starting_value: Union[float, str] = 'random', **kwargs):
         input_features = kwargs['input_features']
@@ -23,8 +32,14 @@ class SimpleFilter(DynamicModule):
             # we do not want dead neurons from the beginning so (0, 1] is
             # a better range for the random numbers
             self.weight = Parameter(1 - rand(features.feature_count))
+        elif starting_value == 'normal':
+            self.weight = Parameter(randn(features.feature_count))
         else:
+            print(starting_value)
             self.weight = Parameter(ones(features.feature_count) * starting_value)
+
+    def get_weight(self):
+        return relu(self.weight)
 
     def forward(self, x):
         # Size checks
@@ -33,11 +48,11 @@ class SimpleFilter(DynamicModule):
         # This is the only implementation that keeps the output
         # contiguous in memory (and therefore does not involve reordering
         # it later
-        weight = self.weight.unsqueeze(0)
+        weight = self.get_weight().unsqueeze(0)
         for _ in range(len(self.output_features.additional_dims)):
             weight = weight.unsqueeze(2)
         weight = weight.expand(x.size())
-        x = x * relu(weight)
+        x = x * weight
         return x
 
     def remove_input_features(self, remaining_features: LongTensor,
@@ -71,3 +86,51 @@ class SimpleFilter(DynamicModule):
 
     def __repr__(self):
         return "SimpleFilter(%s)" % self.output_features.feature_count
+
+class SmoothFilter(SimpleFilter):
+
+    def __init__(self, starting_value: Union[float, str] = 'random',
+                 gamma=0.99, threshold=0.5 **kwargs):
[…]

### 2018-01-29 paper/ICML/plot_neuron_removal.py

@@ -1,5 +1,5 @@
 from matplotlib import rc, use
-# use('agg')
+use('agg')
 import numpy as np
 import pandas as pd
 import torch
@@ -87,9 +87,14 @@ def plot(ax_left, ax_right, det, ran, bl):
     ax_left.xaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
 
 def plot_configs(configs):
-    f, lines = plt.subplots(len(configs), 2, sharex=True)
+    fig, lines = plt.subplots(len(configs), 2, sharex=True)
     plt.subplots_adjust(wspace=0.05, hspace=0.05)
     for line, config in zip(lines, configs):
         f = load_file(*config)
         plot(*(tuple(line) + tuple(f)))
-    lines[-1][0].legend(ncol=2, loc='lower right')
+    lines[0][0].legend(bbox_to_anchor=(1.9, 1.3), ncol=2, loc='upper right')
+    fig.set_size_inches((5, 5))
+    fig.text(0.515, 0.04, '$\gamma$', ha='center')
+
+plot_configs([('scm1d', 0.1), ('oes97', 0.1)])
+plt.savefig('neuron_removal.pdf', bbox_inches='tight', pad_inches=0)

### 2018-01-30 paper/ICML/plot_neuron_removal.py
Update paper with results for the second evaluation

@@ -93,8 +93,8 @@ def plot_configs(configs):
         f = load_file(*config)
         plot(*(tuple(line) + tuple(f)))
     lines[0][0].legend(bbox_to_anchor=(1.9, 1.3), ncol=2, loc='upper right')
-    fig.set_size_inches((5, 5))
+    fig.set_size_inches((5, 10))
     fig.text(0.515, 0.04, '$\gamma$', ha='center')
 
-plot_configs([('scm1d', 0.1), ('oes97', 0.1)])
+plot_configs([('scm1d', 0.1), ('scm1d', 0.001), ('oes97', 0.1), ('oes97', 0.0036)])
 plt.savefig('neuron_removal.pdf', bbox_inches='tight', pad_inches=0)

### 2018-02-01 paper/ICML/dataset_settings.py
Add experiment results for CIFAR10-VGG16

@@ -1,0 +1,95 @@
+from torch.nn import CrossEntropyLoss
+import re
+from paper.ICML.models.FullyConnected import FullyConnected
+from paper.ICML.models.VGG import VGG
+from copy import deepcopy
+from datasets import MNIST, FashionMNIST, CIFAR10
+from torchvision import transforms
+import torchsample as ts
+
+LOG_DISTRIBUTIONS = re.compile("(" + ")|(".join([
+    'lambda',
+    'weight_decay',
+    'learning_rate',
+    'batch_size',
+    'size_layer_[1-9]+',
+    'classifier_layer_[1-9]+'
+]) + ")")
+
+INTEGERS = re.compile("(" + ")|(".join([
+    'batch_size',
+    'size_layer_[1-9]+',
+    'classifier_layer_[1-9]+'
+    'layers'
+]) + ")")
+
+SETTINGS = {
+    'MNIST_FC_DYNAMIC': {
+        'mode': 'classification',
+        'model': FullyConnected,
+        'dataset': MNIST,
+        'val_batch_size': 1000,
+        'normalization': [(0.13066047740239478,),
+                          (0.30810780876661253,)],
+        'data_augmentations': [],
+        'params': {
+            'lambda': (1e-2, 1e-6),
+            'input_features': [(1, 28, 28)],
+            'output_features': [10],
+            'layers': (1, 5),
+            'learning_rate': (0.1, 1e-6),
+            'batch_size': (8, 512),
+            'dropout': [0, 0.1, 0.2, 0.5],
+            'batch_norm': [True, False],
+            'weight_decay': (1e-2, 1e-5),
+            'dynamic': [True],
+            'gamma': [0.99],
+            'size_layer_1': [5000],
+            'size_layer_2': [5000],
+            'size_layer_3': [5000],
+            'size_layer_4': [5000],
+            'size_layer_5': [5000],
+        },
+    },
+    'CIFAR10_VGG_DYNAMIC': {
+        'mode': 'classification',
+        'model': VGG,
+        'dataset': CIFAR10,
+        'val_batch_size': 1000,
+        'normalization': [(0.4914, 0.4822, 0.4465),
+                          (0.2023, 0.1994, 0.2010)],
+        'data_augmentations': [
+            transforms.ToPILImage(),
+            transforms.RandomCrop(32, padding=4),
[…]

### 2018-02-01 paper/ICML/datasets.py

@@ -1,0 +1,36 @@
+from torchvision import transforms
+from torchvision.datasets import (
+    MNIST as MNISTLoader,
+    FashionMNIST as FashionMNISTLoader,
+    CIFAR10 as CIFAR10Loader,
+    CIFAR100 as CIFAR100Loader
+)
+
+def MNIST(train=True, transform=[]):
+    total_transform = transforms.Compose([transforms.ToTensor()] + transform)
+    return MNISTLoader('../../datasets', download=True, train=train,
+                       transform=total_transform)
+
+def FashionMNIST(train=True, transform=[]):
+    total_transform = transforms.Compose([transforms.ToTensor()] + transform)
+    return FashionMNISTLoader('../../datasets',
+                       download=True,
+                       train=train,
+                       transform=total_transform
+                       )
+
+def CIFAR10(train=True, transform=[]):
+    total_transform = transforms.Compose([transforms.ToTensor()] + transform)
+    return CIFAR10Loader('../../datasets',
+                       download=True,
+                       train=train,
+                       transform=total_transform
+                       )
+
+def CIFAR100(train=True, transform=[]):
+    total_transform = transforms.Compose([transforms.ToTensor()] + transform)
+    return CIFAR100Loader('../../datasets',
+                       download=True,
+                       train=train,
+                       transform=total_transform
+                       )

### 2018-02-01 paper/ICML/models/FullyConnected.py

@@ -1,0 +1,43 @@
+import torch
+from dynnet.graph import Sequential
+from dynnet.layers import Input, Linear, BatchNorm, Flatten, CapNorm
+from dynnet.filters import SmoothFilter
+
+class FullyConnected(torch.nn.Module):
+
+    def __init__(self, params):
+        super(FullyConnected, self).__init__()
+        layer_count = params['layers']
+        dropout = params['dropout']
+        batch_norm = params['batch_norm']
+        dynamic = params['dynamic']
+        input_features = params['input_features']
+        output_features = params['output_features']
+        gamma = params['gamma']
+        graph = Sequential()
+        graph.add(Input, *input_features)
+        graph.add(Flatten)
+
+        if dynamic:
+            Bn = CapNorm
+        else:
+            Bn = BatchNorm
+
+        assert layer_count > 0, "Need at least one layer"
+        for i in range(layer_count):
+            graph.add(Linear, out_features=params['size_layer_%s' % (i + 1)])
+            if batch_norm:
+                graph.add(Bn)
+            if dropout > 0:
+                graph.add(torch.nn.Dropout, p=dropout)
+            if dynamic:
+                graph.add(SmoothFilter, starting_value='uniform', gamma=gamma)
+            graph.add(torch.nn.ReLU, inplace=True)
+        graph.add(Linear, out_features=output_features)
+        self.graph = graph
+
+    def forward(self, x):
+        return self.graph(x)
+
+    def garbage_collect(self):
+        return self.graph.garbage_collect()

### 2018-02-01 paper/ICML/models/VGG.py

@@ -1,0 +1,72 @@
+import torch
+import torch.nn as nn
+from torch.nn import ReLU
+from torch.autograd import Variable
+from dynnet.layers import Input, Linear, BatchNorm, Flatten, CapNorm, Conv2d
+from dynnet.filters import SmoothFilter
+from dynnet.graph import Sequential
+
+cfg = {
+    'VGG11': [64, 'M', 128, 'M', 256, 256, 'M', 512, 512, 'M', 512, 512, 'M'],
+    'VGG13': [64, 64, 'M', 128, 128, 'M', 256, 256, 'M', 512, 512, 'M', 512, 512, 'M'],
+    'VGG16': [64, 64, 'M', 128, 128, 'M', 256, 256, 256, 'M', 512, 512, 512, 'M', 512, 512, 512, 'M'],
+    'VGG19': [64, 64, 'M', 128, 128, 'M', 256, 256, 256, 256, 'M', 512, 512, 512, 512, 'M', 512, 512, 512, 512, 'M'],
+}
+
+
+class VGG(nn.Module):
+    def __init__(self, params):
+        dynamic = params['dynamic']
+        batch_norm = params['batch_norm']
+        super(VGG, self).__init__()
+        if dynamic:
+            Bn = BatchNorm
+        else:
+            Bn = BatchNorm
+
+        graph = Sequential()
+        self.graph = graph
+        graph.add(Input, *params['input_features'])
+
+        config = cfg[params['name']]
+
+        for descriptor in config:
+            if descriptor == 'M':
+                graph.add(nn.MaxPool2d, kernel_size=2, stride=2)
+            else:
+                descriptor = int(descriptor * params['factor'])
+                graph.add(Conv2d, out_channels=descriptor,
+                          kernel_size=3, padding=1)
+                if batch_norm:
+                    graph.add(Bn)
+                if dynamic:
+                    graph.add(SmoothFilter, starting_value='uniform',
+                              gamma=params['gamma'])
+                graph.add(ReLU, inplace=True)
+        graph.add(Flatten)
+        for i in range(2):
+            graph.add(Linear, out_features=params['classifier_layer_%s' % (i + 1)])
+            graph.add(SmoothFilter, starting_value='uniform',
+                      gamma=params['gamma'])
+            graph.add(ReLU, inplace=True)
+        graph.add(Linear, out_features=params['output_features'])
+
+    def forward(self, x):
+        return self.graph(x)
+
+    def _make_layers(self, cfg):
+        layers = []
[…]

### 2018-02-01 paper/ICML/neural_network_train.py

@@ -1,0 +1,219 @@
+import torch
+import numpy as np
+from copy import deepcopy, copy
+from random import choice
+from dataset_settings import SETTINGS as DATASETS, LOG_DISTRIBUTIONS, INTEGERS
+from torchvision import transforms
+from torch.utils.data import Dataset, DataLoader, TensorDataset
+from tools import IndexDataset, preload_dataset, compute_size
+from torch.autograd import Variable
+from dynnet.utils import shrinknet_penalty, update_statistics
+from utils.measures import TrainingStats
+from utils.misc import tn
+from multiprocessing import cpu_count
+from torch.optim import Adam, SGD, Adamax
+from torch.optim.lr_scheduler import ReduceLROnPlateau
+
+def clean_params(params):
+    result = {}
+    for key, value in params.items():
+        if INTEGERS.match(key) is not None:
+            value = int(value)
+        result[key] = value
+    return result
+
+def sample_params(params, full_config=True):
+    if full_config:
+        full_params = copy(params)
+        params = params['params']
+    result = {}
+    for key, value in params.items():
+        if isinstance(value, list):
+            result[key] = choice(value)
+        elif isinstance(value, tuple):
+            assert len(value) == 2, 'only allow ranges'
+            value = np.array(value)
+            is_log = LOG_DISTRIBUTIONS.match(key) is not None
+            if is_log:
+                value = np.log(value)
+            sampled = np.random.uniform(*value)
+            if is_log:
+                sampled = np.exp(sampled)
+            result[key] = sampled
+    result = clean_params(result)
+    if full_config:
+       full_params['params'] = result
+       return full_params
+    return result
+
+def prepare_loaders(config, split=0.8):
+    data_augmentations = config['data_augmentations']
+    dataset = config['dataset']
+    normalization_params = config['normalization']
+    basic_transforms = []
+    data_augmentations_transforms = []
+    if data_augmentations:
+        data_augmentations_transforms.extend(data_augmentations)
+    if normalization_params:
+        basic_transforms.append(transforms.Normalize(*normalization_params))
+        data_augmentations_transforms.append(transforms.Normalize(*normalization_params))
+
+
+    full_train_dataset_simple = dataset(train=True, transform=basic_transforms)
+    full_train_dataset_augmented = dataset(train=True, transform=data_augmentations_transforms)
+    testing_dataset = dataset(train=False, transform=basic_transforms)
+
[…]

### 2018-02-01 paper/ICML/neuron_removal_experiment.py

@@ -24,7 +24,7 @@ def train(inputs, outputs, model, l1, l2, lr=1e-5, epochs=10000, gamma=0.9, remo
 
     if gamma is not None:
         mask = model.beta.data.new(model.beta.size()).fill_(1).byte()
-        exp_avg = model.beta.data.new(model.beta.size()).fill_(1.0)
+        exp_avg = model.beta.data.new(model.beta.size()).fill_(0)
         exp_std= model.beta.data.new(model.beta.size()).fill_(0)
     if randomized:
         noise = inputs.data.new(inputs.data.size())

### 2018-02-01 paper/ICML/plot_sample_conv_train.py

@@ -1,0 +1,78 @@
+from matplotlib import rc, use
+# use('agg')
+import numpy as np
+import pandas as pd
+import torch
+import matplotlib.pyplot as plt
+from glob import glob
+# for Palatino and other serif fonts use:
+rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+# def last(experiments):
+#     return np.stack([x[-1] for x in experiments])
+# 
+# def load_file(filename):
+#     with open(filename, 'rb') as f:
+#         [gs_params, gs_logs, s_params, s_logs] = torch.load(f)
+#     return last(gs_logs), last(s_logs)
+# 
+# def plot_file(ax, fn, max_val, right=False):
+#     gs, s = load_file(fn)
+#     ax.plot(gs[:, 2], gs[:, 0] / max_val, 'x-', label="Group Sparsity")
+#     ax.plot(s[:, 2], s[:, 0] / max_val, '.-', label="ShrinkNet")
+#     ax.set_ylim((-0.1, 1.1))
+#     if right:
+#         ax.yaxis.set_ticklabels([])
+#     ax.yaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
+#     ax.xaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
+# 
+# f, (axs_linear, axs_logistic) = plt.subplots(2, 2, sharex=True)
+# plt.subplots_adjust(wspace=0.05, hspace=0.05)
+# plot_file(axs_linear[0], './experiments_results/linear_reg_scm1d.arff.pkl', 1)
+# plot_file(axs_linear[1], './experiments_results/linear_reg_oes97.arff.pkl', 1, True)
+# plot_file(axs_logistic[0], './experiments_results/logistic_reg_1041.pkl', np.log(10))
+# plot_file(axs_logistic[1], './experiments_results/logistic_reg_1477.pkl', np.log(6), True)
+# axs_linear[0].legend()
+# f.set_size_inches((5, 5))
+# 
+# f.text(0.52, 0.04, 'Sparsity', ha='center')
+# f.text(0.02, 0.5, 'Normalized loss', va='center', rotation='vertical')
+# plt.savefig('regressions.pdf', bbox_inches='tight', pad_inches=0)
+
+def read_file(mode, id):
+    fn = './experiments_results/simple_%s_CIFAR10_%s.pkl' % (mode, id)
+    with open(fn, 'rb') as f:
[…]

### 2018-02-01 paper/ICML/tools.py

@@ -1,0 +1,33 @@
+from torch.utils.data import Dataset, DataLoader, TensorDataset
+from dynnet.filters import Filter
+
+class IndexDataset(Dataset):
+    def __init__(self, dataset, indices, transform=None):
+        super(IndexDataset, self).__init__()
+        self.dataset = dataset
+        self.indices = indices
+        self.transform = transform
+
+    def __len__(self):
+        return len(self.indices)
+
+    def __getitem__(self, ix):
+        result = self.dataset[self.indices[ix]]
+        if self.transform is not None:
+            result = (self.transform(result[0]), result[1])
+        return result
+
+def preload_dataset(ds, batch_size):
+    dummy_dl = DataLoader(ds, batch_size=10000000, shuffle=False)
+    inputs, labels = next(iter(dummy_dl))
+    return DataLoader(TensorDataset(*[
+        x.cuda() for x in (inputs, labels)]),
+        batch_size=batch_size, shuffle=False)
+
+def compute_size(model):
+    layers = []
+    for module in model.modules():
+        if isinstance(module, Filter):
+            layers.append(int(module.get_alive_features().float().sum()))
+    return layers
+

### 2018-02-01 dynnet/filters.py
Update batchnorm and other layers

@@ -1,7 +1,9 @@
 """This module implements different algorithms for feature selection"""
 
 from typing import Any, Union
-from torch import ones, nonzero, LongTensor, ByteTensor, rand, randn
+from torch import (
+    ones, nonzero, LongTensor, ByteTensor, rand, randn, zeros
+)
 from torch.nn import Parameter
 from torch.nn.functional import relu
 
@@ -10,12 +12,8 @@ from dynnet.operations import IndexSelectOperation
 
 class Filter(DynamicModule):
 
-    def forward(self, x):
-        raise NotImplementedError("This is an abstract class")
-
     def get_weights(self):
         raise NotImplementedError("This is an abstract class")
-
 
 
 class SimpleFilter(Filter):
@@ -34,11 +32,13 @@ class SimpleFilter(Filter):
             self.weight = Parameter(1 - rand(features.feature_count))
         elif starting_value == 'normal':
             self.weight = Parameter(randn(features.feature_count))
+        elif starting_value == 'uniform':
+            self.weight = Parameter(rand(features.feature_count) * 2 - 1)
         else:
             print(starting_value)
             self.weight = Parameter(ones(features.feature_count) * starting_value)
 
-    def get_weight(self):
+    def get_weights(self):
         return relu(self.weight)
 
     def forward(self, x):
@@ -48,7 +48,7 @@ class SimpleFilter(Filter):
         # This is the only implementation that keeps the output
         # contiguous in memory (and therefore does not involve reordering
         # it later
-        weight = self.get_weight().unsqueeze(0)
+        weight = self.get_weights().unsqueeze(0)
         for _ in range(len(self.output_features.additional_dims)):
             weight = weight.unsqueeze(2)
         weight = weight.expand(x.size())
@@ -90,11 +90,13 @@ class SimpleFilter(Filter):
 class SmoothFilter(SimpleFilter):
 
     def __init__(self, starting_value: Union[float, str] = 'random',
-                 gamma=0.99, threshold=0.5 **kwargs):
+                 gamma=0.99, threshold=0.5, **kwargs):
+        self.gamma = gamma
+        self.threshold = threshold
         super(SmoothFilter, self).__init__(starting_value, **kwargs)
-        self.register_buffer('exp_avg', torch.zeros(self.weight.size()))
-        self.register_buffer('exp_std', torch.zeros(self.weight.size()))
[…]

### 2018-02-01 dynnet/graph.py

@@ -183,6 +183,7 @@ class Sequential(Graph):
 
     def add(self, factory: Callable[[], Module],
             *args, **kwargs) -> DynamicModule:
+        print("adding", factory)
         parent = []
         if len(self) > 0:
             parent = [self[-1]]

### 2018-02-01 dynnet/interfaces.py

@@ -226,7 +226,7 @@ class FeatureBag():
         assert context in self.module_awareness, (
             "The module requesting the feature removal is not a listener")
         # We do not care about the torch format here
-        remaining_offsets = remaining_offsets.numpy()
+        remaining_offsets = remaining_offsets.cpu().numpy()
 
         # Compute the features from the offsets in context
         remaining_features = self.offsets_to_features(context,

### 2018-02-01 dynnet/layers.py

@@ -6,6 +6,8 @@ from torch.autograd import Variable
 from torch.nn import (
     Linear as SimpleLinear,
     BatchNorm1d as SimpleBatchNorm1d,
+    BatchNorm2d as SimpleBatchNorm2d,
+    BatchNorm3d as SimpleBatchNorm3d,
     Conv2d as SimpleConv2d
 )
 
@@ -230,15 +232,25 @@ class Linear(BaseDynamicLayer):
                                      *args, **kwargs)
 
 
-class BatchNorm1d(BaseDynamicLayer):
+class BatchNorm(BaseDynamicLayer):
     """We will reuse the docstring from pytorch"""
+
+    def get_factory(self):
+        raise NotImplementedError('This is a base class')
 
     def __init__(self, *args, **kwargs):
         input_features = kwargs['input_features']
         assert len(input_features) == 1, (
-            "BatchNorm1d only supports 1 parent")
+            "BatchNorm only supports 1 parent")
+        dim = len(input_features[0].additional_dims)
+        if dim == 0:
+            factory = SimpleBatchNorm1d
+        elif dim == 1:
+            factory = SimpleBatchNorm2d
+        elif dim == 2:
+            factory = SimpleBatchNorm3d
 
-        super(BatchNorm1d, self).__init__(factory=SimpleBatchNorm1d,
+        super(BatchNorm, self).__init__(factory=factory,
                                           in_feature_arg_name="num_features",
                                           out_feature_arg_name="num_features",
                                           in_feature_dim=0,
@@ -257,7 +269,7 @@ class BatchNorm1d(BaseDynamicLayer):
 
     def remove_output_features(self, remaining_features: LongTensor,
                                log: GarbageCollectionLog) -> None:
-        super(BatchNorm1d, self).remove_output_features(remaining_features,
+        super(BatchNorm, self).remove_output_features(remaining_features,
                                                         log)
         operation = IndexSelectOperation(remaining_features, 0)
         # The operations on the buffer do not need te be logged, they
@@ -269,6 +281,38 @@ class BatchNorm1d(BaseDynamicLayer):
         self.implementation.num_features = (
             self.output_features.feature_count)
 
+class CapNorm(BatchNorm):
+
+    def __init__(self, *args, **kwargs):
+        input_features = kwargs['input_features']
+        assert len(input_features) == 1, (
+            "BatchNorm only supports 1 parent")
[…]

### 2018-02-01 dynnet/utils.py

@@ -3,10 +3,9 @@
 from typing import List, Union
 
 import numpy as np
-from torch import from_numpy, LongTensor, cat
+from torch import from_numpy, LongTensor, cat, abs
 from torch.nn import Module
 from torch.autograd import Variable
-from torch.nn.functional import relu
 import dynnet
 
 
@@ -164,8 +163,8 @@ def shrinknet_penalty(model: Module) -> Variable:
     """
     filter_weights = []
     for layer in model.modules():
-        if isinstance(layer, dynnet.filters.SimpleFilter):
-            filter_weights.append(layer.weight)
+        if isinstance(layer, dynnet.filters.Filter):
+            filter_weights.append(layer.get_weights())
     if not filter_weights:
         return 0
     # It might look it is subobtimal to do it this way and we should
@@ -176,4 +175,9 @@ def shrinknet_penalty(model: Module) -> Variable:
     #   Having a lot of sum (one for every filter layer) would generate a very
     #   deep computation graph, Here we have a constant number of pytorch
     #   operations
-    return relu(cat(filter_weights)).sum()
+    return abs(cat(filter_weights)).sum()
+
+def update_statistics(model: Module) -> None:
+    for module in model.modules():
+        if hasattr(module, 'update_statistics'):
+            module.update_statistics()

### 2018-02-01 paper/ICML/neural_network_train.py
Add shape plot

@@ -129,17 +129,6 @@ def init_model(model):
             module.running_var.fill_(0.9)
 
 def train(config, epochs=400):
-    config['params']['dropout'] = 0
-    config['params']['batch_norm'] = True
-    config['params']['dynamic'] = True
-    config['params']['weight_decay'] = 0.000001
-    config['params']['layers'] = 2
-    config['params']['lambda'] = 0.0001
-    config['params']['factor'] = 2
-    config['params']['batch_size'] = 150
-    config['params']['learning_rate'] = 1e-2
-    print(config)
-
 
     stats = TrainingStats()
     is_classification = config['mode'] == 'classification'
@@ -203,7 +192,7 @@ def train_simple_CIFAR10_dynamic():
             torch.save((config, stats), f)
 
 def train_simple_CIFAR10_static():
-    for i in range(1, 10):
+    for i in range(10, 20):
         config = deepcopy(sample_params(DATASETS['CIFAR10_VGG_DYNAMIC']))
         config['params']['batch_norm'] = True
         config['params']['dynamic'] = False
@@ -216,4 +205,4 @@ def train_simple_CIFAR10_static():
         with open('./experiments_results/simple_static_CIFAR10_%s.pkl' %i, 'wb') as f:
             torch.save((config, stats), f)
 
-train_simple_CIFAR10_dynamic()
+train_simple_CIFAR10_static()

### 2018-02-01 paper/ICML/plot_sample_conv_train.py

@@ -5,9 +5,11 @@ import pandas as pd
 import torch
 import matplotlib.pyplot as plt
 from glob import glob
+from paper.ICML.models.VGG import cfg
 # for Palatino and other serif fonts use:
 rc('font',**{'family':'serif','serif':['Palatino']})
 rc('text', usetex=True)
+vgg_configs = {k: [x for x in v if x != 'M'] for (k, v) in cfg.items()}
 
 # def last(experiments):
 #     return np.stack([x[-1] for x in experiments])
@@ -45,6 +47,8 @@ def read_file(mode, id):
     with open(fn, 'rb') as f:
         params, logs = torch.load(f)
         logs = logs.logs
+    # Mistake while writing
+    logs.measure.replace('test_', 'test_acc', inplace=True)
     return params, logs
 
 def extrat_timeline(logs, key):
@@ -76,3 +80,40 @@ def plot_timings(logs):
     print(sums)
     ax4.bar(list(range(0, 4)), sums, color=['C0', 'C1', 'C2', 'C3'])
     ax4.set_yscale('log')
+
+def get_best_entry(logs):
+    vac = logs[logs.measure == 'val_acc']
+    return logs[logs.epoch == vac.ix[vac['value'].argmax()].epoch]
+
+def plot_shape(logs, segments=10, vgg='VGG16', factor=2):
+    cf = vgg_configs[vgg]
+    best = get_best_entry(logs)
+    best_epoch = int(best.epoch.iloc[0])
+    parts = np.linspace(0, best_epoch, segments).astype(int)
+    last_value = None
+    for epoch in parts:
+        if epoch == 0:
+            values = np.array(cf) * factor
+        else:
+            at_that_time = logs[logs.epoch == epoch]
+            at_that_time = at_that_time[at_that_time['measure'].str.startswith('size')]
+            values = at_that_time.value.as_matrix()[:-2]
+        last_value = values
+        plt.fill_between(range(len(values)), 0*values, values, color='C0', alpha=0.1)
+    plt.xlabel('layer')
+    plt.ylabel('size')
+    plt.plot(range(len(last_value)), last_value, color='C0', label='Converted Shrinknet size')
+    plt.plot(range(len(last_value)), cf, color='C1', label='Original VGG16 size')
+    ax = plt.gca()
+    ax.yaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
+    ax.xaxis.grid(b=True, which='major', alpha=0.4, linestyle='--')
[…]

### 2018-02-01 paper/ICML/plot_sample_conv_train.py
Make plot to pdf

@@ -1,5 +1,5 @@
 from matplotlib import rc, use
-# use('agg')
+use('agg')
 import numpy as np
 import pandas as pd
 import torch
@@ -76,3 +76,7 @@ def plot_timings(logs):
     print(sums)
     ax4.bar(list(range(0, 4)), sums, color=['C0', 'C1', 'C2', 'C3'])
     ax4.set_yscale('log')
+    f.set_size_inches((20, 5))
+    plt.savefig('dynamic_timings.pdf', bbox_inches='tight', pad_inches=0)
+
+plot_timings(read_file('dynamic', 0)[1])

### 2018-02-03 paper/ICML/plot_sample_conv_train.py
Add new plotting functions

@@ -3,6 +3,7 @@ from matplotlib import rc, use
 import numpy as np
 import pandas as pd
 import torch
+from glob import glob
 import matplotlib.pyplot as plt
 from glob import glob
 from paper.ICML.models.VGG import cfg
@@ -42,14 +43,17 @@ vgg_configs = {k: [x for x in v if x != 'M'] for (k, v) in cfg.items()}
 # f.text(0.02, 0.5, 'Normalized loss', va='center', rotation='vertical')
 # plt.savefig('regressions.pdf', bbox_inches='tight', pad_inches=0)
 
-def read_file(mode, id):
-    fn = './experiments_results/simple_%s_CIFAR10_%s.pkl' % (mode, id)
+def process_file(fn):
     with open(fn, 'rb') as f:
         params, logs = torch.load(f)
         logs = logs.logs
     # Mistake while writing
     logs.measure.replace('test_', 'test_acc', inplace=True)
     return params, logs
+
+def read_file(mode, id):
+    fn = './experiments_results/simple_%s_CIFAR10_%s.pkl' % (mode, id)
+    return process_file(fn)
 
 def extrat_timeline(logs, key):
     return logs[logs.measure==key]
@@ -117,3 +121,41 @@ def compare_static_dynamic():
         results.append(cur)
     return results
 
+def cost(seq):
+    prev = 3
+    total = 0
+    for e in seq:
+        total += prev * e * 9
+        prev = e
+    return total
+
+def get_final_size(logs,):
+    best = get_best_entry(logs)
+    epoch = int(best.epoch.iloc[0])
+    at_that_time = logs[logs.epoch == epoch]
+    at_that_time = at_that_time[at_that_time['measure'].str.startswith('size')]
+    values = at_that_time.value.as_matrix()[:-2]
+    return cost(values)
+
+def get_all_files(mode):
+    pattern = './experiments_results/simple_%s_CIFAR10_*.pkl' % (mode)
+    files = glob(pattern)
+    return [process_file(x) for x in files]
+
+
+def get_compression(vgg='VGG16'):
+    compressions = []
+    cf = vgg_configs[vgg]
+    original_cost = cost(cf)
+    result = []
+    for _, logs in get_all_files('dynamic'):
+        b = get_best_entry(logs)
+        result.append(cost(cf) / get_final_size(logs))
+    return np.array(result)
+
+def get_final_measure(mode, measure='test_acc'):
+    best_results = [get_best_entry(x[1]) for x in get_all_files(mode)]
[…]

### 2018-02-03 paper/ICML/dataset_settings.py
Update MNIST settings

@@ -19,7 +19,7 @@ LOG_DISTRIBUTIONS = re.compile("(" + ")|(".join([
 INTEGERS = re.compile("(" + ")|(".join([
     'batch_size',
     'size_layer_[1-9]+',
-    'classifier_layer_[1-9]+'
+    'classifier_layer_[1-9]+',
     'layers'
 ]) + ")")
 
@@ -37,11 +37,11 @@ SETTINGS = {
             'input_features': [(1, 28, 28)],
             'output_features': [10],
             'layers': (1, 5),
-            'learning_rate': (0.1, 1e-6),
+            'learning_rate': (1e-2, 1e-5),
             'batch_size': (8, 512),
             'dropout': [0, 0.1, 0.2, 0.5],
-            'batch_norm': [True, False],
-            'weight_decay': (1e-2, 1e-5),
+            'batch_norm': [True],
+            'weight_decay': (1e-2, 1e-8),
             'dynamic': [True],
             'gamma': [0.99],
             'size_layer_1': [5000],
@@ -66,18 +66,18 @@ SETTINGS = {
             ts.transforms.RandomRotate(10),
         ],
         'params': {
-            'lambda': (1e-2, 1e-6),
+            'lambda': (1e-2, 1e-5),
             'name': ['VGG16'],
             'input_features': [(3, 32, 32)],
             'output_features': [10],
-            'learning_rate': (0.1, 1e-6),
+            'learning_rate': (1e-2, 1e-6),
             'batch_size': (8, 512),
-            'weight_decay': (1e-2, 1e-5),
-            'factor': [1],
+            'weight_decay': (1e-2, 1e-8),
+            'factor': [2],
             'classifier_layer_1': [5000],
             'classifier_layer_2': [5000],
-            'gamma': [0.9],
-            'batch_norm': [False],
+            'gamma': [0.9, 0.99, 0],
+            'batch_norm': [True],
             'dynamic': [True],
         },
     }
@@ -90,6 +90,8 @@ for i in range(1, 6):
     )
 SETTINGS['MNIST_FC_STATIC']['params']['dynamic'] = [False]
 
-# SETTINGS['FashionMNIST_FC_DYNAMIC'] = deepcopy(SETTINGS['MNIST_FC_DYNAMIC'])
[…]

### 2018-02-03 paper/ICML/neural_network_train.py

@@ -1,7 +1,9 @@
 import torch
 import numpy as np
+import os
 from copy import deepcopy, copy
 from random import choice
+from uuid import uuid4
 from dataset_settings import SETTINGS as DATASETS, LOG_DISTRIBUTIONS, INTEGERS
 from torchvision import transforms
 from torch.utils.data import Dataset, DataLoader, TensorDataset
@@ -13,6 +15,7 @@ from utils.misc import tn
 from multiprocessing import cpu_count
 from torch.optim import Adam, SGD, Adamax
 from torch.optim.lr_scheduler import ReduceLROnPlateau
+import sys
 
 def clean_params(params):
     result = {}
@@ -136,7 +139,8 @@ def train(config, epochs=400):
     init_model(model)
     dl_train, dl_val, dl_test = prepare_loaders(config)
     weight_decay = config['params']['weight_decay']
-    optimizer =  Adam(model.parameters(), weight_decay=weight_decay)
+    lr = config['params']['learning_rate']
+    optimizer =  Adam(model.parameters(), weight_decay=weight_decay, lr=lr)
 
     if is_classification:
         direction = 'max'
@@ -158,6 +162,7 @@ def train(config, epochs=400):
                 with stats.time('optimizer_update'):
                     log.update_optimizer(optimizer)
                 sizes = compute_size(model)
+                print(sizes)
                 for i, value, in enumerate(sizes):
                     stats.log('size_%s' % (i + 1), value)
             with stats.time('inference_val'):
@@ -168,31 +173,25 @@ def train(config, epochs=400):
                 test_loss, test_acc = forward(model, dl_test, config)
                 stats.log('test_loss', test_loss)
                 stats.log('test_acc', test_acc)
+            print(train_acc, test_acc)
             stats.log('learning_rate', optimizer.param_groups[0]['lr'])
             scheduler.step(val_acc)
             if optimizer.param_groups[0]['lr'] < 1e-6:
                 break
     except:
-        pass
-
+        raise
     return stats, model
 
 def train_simple_CIFAR10_dynamic():
-    for i in range(1, 10):
-        config = deepcopy(sample_params(DATASETS['CIFAR10_VGG_DYNAMIC']))
-        config['params']['batch_norm'] = True
-        config['params']['dynamic'] = True
-        config['params']['weight_decay'] = 0.000001
-        config['params']['lambda'] = 0.0001
[…]

### 2018-02-05 paper/ICML/paper.tex
restructed paper files

--- 2018-01-27 paper/ICML/paper.tex
@@
 
-\section{Introduction}
+\section{Outline2}
+\begin{itemize}
+  \item Introduction
+  \item Related Work
+  \item Our Approach
+  \item Experiments
+  \item Discussion
+  \item Conclusion
+\end{itemize}
 
-\section{ShrinkNets}
-
-\subsection{Motivation}
-
-\subsection{Notations}
-
-\par In order to avoid any potential ambiguity, in this section we will
-describe in details the mathematical notations used in this article. Non-bold
-letters represent scalar values, while bold lowercase and upper case
-repectively denote vectors and matrices. $\bm{A}^T$ stands for the transpose of
-the matrix $\bm{A}$. Subscripts are used to index particular elements of
-vectors and matrices. $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
-$\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
-the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
-component of the $i^{th}$ row of $\bm{A}$. All the following definitions assume
-$\bm{A}$ to be an $n\times p$ matrix.  For any vetor $\bm{b}$ with $n$
-components, we define $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
-1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.  For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
-\left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$.
-For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function.
-The only constraint that we want to enforce is that $a(0) = 0$.
-We use $\intint{u, v}$ to denote inteveral of integers, $\bm{0}$ is the null vector (size depending on the context).
-$\#S$ is meant to represent the cardinality of a set $S$.
-To simplify the notation of function composition we use the following operator: $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
-\subsection{Definition}
-
-\begin{equation}
-  \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
-\end{equation}
-
-\section{Theoretical analysis}
-
-Our goal when designing ShrinkNets was to be able to remove inputs
-and outputs of layers. For classic fully connected layers, which are defined
-as :
-
-\begin{equation} \label{fully_connected}
-  f_{\bm{A}, \bm{b}}(\bm{x})=a(\bm{Ax + b})
-\end{equation}
-
-removing an input neuron $j$ is equivalent to have $\left(\bm{A}^T\right)_j = \bm{0}$
-and removing an output neuron $i$ is the same as having $\bm{A}_i = \bm{0}$ and $\bm{b}_i = 0$. Solving  optimization problems while trying to set entire groups
-of parameters to zero has been already studied and the most popular method
-is without doubt the group sparsity regularization [ref].
-For any partitionning of the set of parameter defining a model in $p$ groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$ we define it the following way:
-
-\begin{equation}
-  \Omega_\lambda^{gp} = \lambda \sum_{i=1}^p \sqrt{\#\bm{\theta_i}} \norm{\bm{\theta_i}}_2 \\
-\end{equation}
-
-In the context of a fully-connected layer, the groups are either: columns of $\bm{A}$ if we want to remove inputs, or rows of $\bm{A}$ and the corresponding entry in $\bm{b}$ if we want to remove outputs.
-For simplicity, we will focus our analysis in the simple one-layer case.
-In this case filtering outputs does not make a lot of sense, this is why we will only consider the former case.
-The group sparsity regularization then becomes:
-
-\begin{equation} \label{group_sparsity_regularization}
-  \Omega_\lambda^{gp} = \lambda \sum_{j=1}^p \norm{\bm{\left(A^T\right)_j}}_2 \\
-\end{equation}
-
-Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
-we now embed $\sqrt{n}$ inside $\lambda$.
-
-Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The ShrinkNet problem is:
-
-\begin{equation}
-  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s
-\end{equation}
-
-And the Group Sparsity problem is:
-
-\begin{equation}
-  \min_{\bm{A}} \norm{\bm{y} - \bm{A}\bm{x}}_2^2 + \Omega_\lambda^{gp}
-\end{equation}
-
-We can prove the under the condition: $\forall 1 \leq j \leq p, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}).
-However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}).
-Fortunately, by adding an extra term to the ShrinkNet regularization term we can proove that:
-
-\begin{equation}
-  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s + \lambda_2\norm{A}_p^p
-\end{equation}
-
-has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we define the \textit{regularized ShrinkNet penalty}:
-
-\begin{equation}
-  \Omega_{\lambda, \lambda_2, p}^{rs} = \lambda\norm{\bm{\beta}}_1 + \lambda_2\norm{\bm\theta}_p^p
-\end{equation}
-
-In practice we observed that $p=2$ or $p=1$ are good choice, while the latter will also introduce additional sparsity in the parameters.
-
-\section{Speeding up training with pruning}
-
-\section{Evaluation}
-
-\subsection{Multi-Target Linear and Logistic regressions}
-
-\subsection{Neuron Removal strategies}
-
-\subsection{Convergence and training dynamics of Neural networks}
-
-\subsection{Hyper-optimization of ShrinkNets}
-
-\subsection{Transfer Learning with ShrinkNets}
-
-\subsection{Performance}
-
-\section{Related Work}
-
-\section{Future Work}
-
-\section{Conclusion}
+\input{introduction}
+\input{approach}
+\input{theory}
+\input{evaluation}
+\input{related_work}
+\input{discussion}
+\input{conclusion}
 
 \appendix
-\section{Appendix}
-\subsection{Proofs of propositions}
-Unless specified, all the proofs consider the Multi-Target linear regression problem
-\begin{proposition}
-\label{gps_equivalence}
-  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$
-
-  \begin{align*}
-    & \min_{\bf{A}} \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
-     = &\min_{\bf{A'}, \bm{\beta}} \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1 \\
-     & \text{s.t.} \forall j \in \intint{1, p}, \norm{\left(A'^T\right)_j}_2^2 = 1
-  \end{align*}
-\end{proposition}
-
-\begin{proof}
-  In order to prove this statement we will show that for any solution $\bm{A}$ in the first problem, there exists a solution in the second with the exact same value, and vice-versa.
-We now assume we have a potential solution $\bm{A}$ for the first problem and we define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$.
-It is easy to see that the constraint on $\bm{A}'$ is statisfied by construction.
-Now:
-  \begin{align*}
-    & \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
-    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A'^T\right)_j\beta_j}_2 \\
-    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \abs{\beta_j} \cdot 1\\
-    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
-  \end{align*}
-  Assuming we take an $\bm{A}'$ that satisfy the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
-We can apply the same operations in reverse order and obtain an instance of the first problem with the same value.
-We can now see that the two problems must have the same minimum otherwise we would be able to construct a solution to the other with exact same value.
-\end{proof}
-
-\begin{proposition}
-\label{unconstrained_non_convex}
-\begin{equation*}
-     \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2
-\end{equation*}
-is not convex in $\bm{A}$ and $\bm{\beta}$.
-\begin{proof}
-  To prove this we will take the simplest instance of the problem: with only scalars.
-We have $f(a, \beta) = \left(y - a\beta x\right)^2$.
-For simplicty let's take $y = $ and $x > 0$.
-If we take two candidates $s_1 = (0, 2)$ and $s_2 = (2, 0)$, we have $f(s_1) = f(s_2) = 0$.
-However $f(\frac{2}{2}, \frac{2}{2}) = x > \frac{1}{2} f(0, 2) + \frac{1}{2}f(2, 0)$, which break the convexity property.
-Since we showed that a particular case of the problem is non-convex then necessarly the general cannot be convex.
-\end{proof}
-\end{proposition}
-
-\begin{proposition}
-\label{unconstrained_shrinknet_no_min}
-\begin{equation*}
-     \min_{\bf{A}, \bm{\beta}} \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
-\end{equation*}
-has no solution if $\lambda > 0$.
-\end{proposition}
-\begin{proof}
-  Let's assume this problem has a minimum $\bm{A}^*, \bm{\beta}^*$.
-Let's consider $2\bm{A}^*, \frac{1}{2}\bm{\beta}^*$.
-Trivially the first component of the sum is identical for the two solutions, however $\lambda\norm{\frac{1}{2}\bm{\beta}} < \lambda\norm{\bm{\beta}}$.
-Therefore $\bm{A}^*, \bm{\beta}^*$ cannot be the minimum.
-We conclude that this problem has no solution.
-\end{proof}
-\begin{proposition}
-  \label{shrinknet_regularized_minimum}
-For this proposition we will not restrict ourselves to single layer but the composition of an an arbitrary large ($n$) layers as defined individually as $f_{\bm{A}_i, \bm{\beta}_i, \bm{b}_i}(x) = a(\bm{A_i}\diag{\bm{\beta_i}}\bm{x} + \bm{b_i})$.
-The entire network follows as: $N(\bm{x}) = \left(\bigcirc_{i=1}^n f_{\bm{A_i}, \bm{\beta_i}, \bm{b_i}}\right)(\bm{x})$.
-For $\lambda > 0$, $\lambda_2 > 0$ and $p > 0$ we have:
-  \begin{equation*}
-    \min \norm{\bm{y} - N(\bm{x})}_2^2 + \Omega_{\lambda, \lambda_2, p}^{rs}
-  \end{equation*}
-  has at least $2^k$ global minimum where $k = \sum_{i=1}^n \#\bm{\beta_i}$
-\end{proposition}
-
-\begin{proof}
-First let's prove that there is at least one minimum to this problem.
-The two components of the expression are always positive so we know that this problem is bounded by below by $0$.
-Let's assume this function does not have a minimum.
-Then there is a sequence of parameters $(S_n)_{n>0}$ such that the function evaluated at that point convereges to the infimum of the problem.
-Since the function is defined everywhere does not have a minimum then this sequence must diverge.
-Since the entire sequence deverge the there is at least one individual parameter that diverges.
-First case, the parameter is a component $k$ of some $\bm{\beta_i}$ for some $i$.
-Necessarly $\norm{\bm{\beta_i}}_1$ diverge towards $+ \infty$, which is incompatible with the fact that $(S_n)$ converges to the infimum.
-We can have the exact same argument if the diverging parameter is in $\bm{A_i}$ or $\bm{b_i}$ because $p > 0$.
-Since there is always a contradiction then our assumption that the function has no global minimum must be false.
-Therefore, this problem has at least one global minimum.
-
-\par Let's consider one optimal solution of the problem.
-For each component $k$ of $\bm{\beta_i}$ for some $i$.
-Negating it and negating the $k^{th}$ column of $\bm{A_i}$ does not change the the first part of the objetive because the two factors cancel each other.
-The two norms do not change either because by definition the norm is independant of the sign.
-As a result these two sets of parameter have the same value and are both global minimum.
-It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$.
-We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.
-
-\end{proof}
-\subsection{Experiment details}
-\subsubsection{Multi-Target Linear and Logistic regressions}
-\subsubsection{Neuron Removal strategies}
-\subsubsection{Convergence and Training Dynamics of Neural networks}
-\subsubsection{Hyper-optimization of ShrinkNets}
-\subsubsection{Transfer Learning with ShrinkNets}
-\subsubsection{Performance}
+\input{appendix}
 

### 2018-02-05 paper/ICML/evaluation.tex

\section{Evaluation}

\subsection{Multi-Target Linear and Multi-Class Logistic regressions}

We will start evaluating ShrinkNets with the simplest problems possible: linear
and logistic regression. As we showed, Group sparsity share similarities with
our method, this is why we will use it as baseline. We decided to focus on
multi-target linear regression because in the single target case, groups in the
Group Sparsity problem would have a size of one ($\bm{A}$ would be a vector in this
case).

The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
[ref] for linear regressions and we will use \texttt{gina\_prior2} [ref] and
the \textit{Gas Sensor Array Drift Dataset} [ref] (that we shorten in
\texttt{gsadd}) for logistic regressions.

For each dataset we fit with different regularization parameters and measure
the error and sparsity obtained after convergence. In this context we define sparsity as the ratio of columns that have all their weight under $10^{-3}$ in absolute value. Parameters were choosed in
order to obtain the widest sparsity spectrum. Loss is normalized depending on the problem to be in the $[0, 1]$ range. We summarized the results in
\cref{sparsity_accuracy}. From our experiments it is clear that ShrinkNets can fit the data closer than Group Sparsity for the same amount of sparsity. The fact that we are able to reach very low loss demonstrate that even if our objective function is non convex, in practice it works as good or better as convex alternatives. Details about these datasets and the parameters used
are available in \cref{linear_datasets}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{regressions}
\vspace*{-5mm}
\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression. From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}

\end{center}
\vspace*{-4mm}
\end{figure}

\subsection{Neuron Removal strategies}

In our previous experiment, we showed that the ShrinkNet loss was
reasonable in practice, we are now interested in the impact on
early pruning. The method we suggest for early prunning uses a
parameter $\gamma$ that control the aggressiveness of neuron removal
so we will try to evaluate its impact on the final loss achieved by
the model and the cost required to train the model. Our cost model
is simple and hardware independant, we sum the number of input neurons
at each epoch. In theory the cost in time should be asymptotically
linear to this metric. To have a baseline we also train the same model
but without neuron removal. Keep in mind that this is just in order to
have some reference. Indeed, if we were to remove the neurons with small
weights it would deteriorate the loss (and picking the threshould would
be completely arbitrary). Therefore the baseline is evaluated with all neurons.
One could consider it as a "theoretical lower bound" of the best achievable loss.

We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$). We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}. In order to reduce the noise in the result, each experiment was performed $30$ times and we display the range arround $\pm$ $1$ standard deviation.

\textbf{TODO: Interpret the results}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{neuron_removal}
\vspace*{-5mm}
\caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$. First column is the difference in the final loss in function of the removal factor. We plot theoretical baseline as a reference. Right column is a proxy of the total cost for training the model (i.e. the sum of input neurons at each epoch). Each row is a dataset/$\lambda$ combination. From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}

\end{center}
\vspace*{-4mm}
\end{figure}

\subsection{Convergence and training dynamics of Neural networks}

\subsection{Hyper-optimization of ShrinkNets}

\subsection{Performance}

\section{Speeding up training with pruning}

### 2018-02-05 paper/ICML/introduction.tex

\section{Introduction}

\subsection{ShrinkNets}

\subsection{Motivation}

### 2018-02-05 paper/ICML/theory.tex

\section{Theoretical analysis}

\subsection{Notations}

\par In order to avoid any potential ambiguity, in this section we will
describe in details the mathematical notations used in this article. Non-bold
letters represent scalar values, while bold lowercase and upper case
repectively denote vectors and matrices. $\bm{A}^T$ stands for the transpose of
the matrix $\bm{A}$. Subscripts are used to index particular elements of
vectors and matrices. $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
$\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
component of the $i^{th}$ row of $\bm{A}$. All the following definitions assume
$\bm{A}$ to be an $n\times p$ matrix.  For any vetor $\bm{b}$ with $n$
components, we define $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.  For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
\left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$. For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function. The only constraint that we want to enforce is that $a(0) = 0$. We use $\intint{u, v}$ to denote inteveral of integers, $\bm{0}$ is the null vector (size depending on the context). $\#S$ is meant to represent the cardinality of a set $S$. To simplify the notation of function composition we use the following operator: $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
\subsection{Definition}

\begin{equation}
  \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
\end{equation}

Our goal when designing ShrinkNets was to be able to remove inputs
and outputs of layers. For classic fully connected layers, which are defined
as :

\begin{equation} \label{fully_connected}
  f_{\bm{A}, \bm{b}}(\bm{x})=a(\bm{Ax + b})
\end{equation}

removing an input neuron $j$ is equivalent to have $\left(\bm{A}^T\right)_j = \bm{0}$
and removing an output neuron $i$ is the same as having $\bm{A}_i = \bm{0}$ and $\bm{b}_i = 0$. Solving  optimization problems while trying to set entire groups
of parameters to zero has been already studied and the most popular method
is without doubt the group sparsity regularization [ref]. For any partitionning of the set of parameter defining a model in $p$ groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$ we define it the following way:

\begin{equation}
  \Omega_\lambda^{gp} = \lambda \sum_{i=1}^p \sqrt{\#\bm{\theta_i}} \norm{\bm{\theta_i}}_2 \\
\end{equation}

In the context of a fully-connected layer, the groups are either: columns of $\bm{A}$ if we want to remove inputs, or rows of $\bm{A}$ and the corresponding entry in $\bm{b}$ if we want to remove outputs. For simplicity, we will focus our analysis in the simple one-layer case. In this case filtering outputs does not make a lot of sense, this is why we will only consider the former case. The group sparsity regularization then becomes:

\begin{equation} \label{group_sparsity_regularization}
  \Omega_\lambda^{gp} = \lambda \sum_{j=1}^p \norm{\bm{\left(A^T\right)_j}}_2 \\
\end{equation}

Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
we now embed $\sqrt{n}$ inside $\lambda$.

Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The ShrinkNet problem is:

\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s
\end{equation}

And the Group Sparsity problem is:

\begin{equation}
  \min_{\bm{A}} \norm{\bm{y} - \bm{A}\bm{x}}_2^2 + \Omega_\lambda^{gp}
\end{equation}

We can prove the under the condition: $\forall j\in \intint{1, p}, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}). However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}). Fortunately, by adding an extra term to the ShrinkNet regularization term we can proove that:

\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s + \lambda_2\norm{A}_p^p
\end{equation}

has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we define the \textit{regularized ShrinkNet penalty}:

\begin{equation}
  \Omega_{\lambda, \lambda_2, p}^{rs} = \lambda\norm{\bm{\beta}}_1 + \lambda_2\norm{\bm\theta}_p^p
\end{equation}

In practice we observed that $p=2$ or $p=1$ are good choice, while the latter will also introduce additional sparsity in the parameters.

### 2018-02-05 paper/ICML/paper.tex
First pass on outline, filling in sections

@@
 \usepackage{icml2018}
-
+\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
+\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
+\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
+\newcommand{\mpv}[1]{\textcolor{green}{{\bf MV:} #1}}
 % If accepted, instead use the following line for the camera-ready submission:
@@
 
-\begin{itemize}
-  \item We want to figure out what is the proper network size
-  \item If we had a oversized network and for each neuron we would have an on/off switch, we could optimize the state of each switch to achieve any size/accuracy tradeof (we can prove that, do we care ?)
-  \item Solving such problem is NP-Hard
-  \item We could approximate the binary switch by relaxing them and doing L1 loss instead of L0 loss
-  \item This is the definition of Shrinknets
-  \item group sparsity tries to achieve a similar goal but with a different formulation
-  \item How are they related ?
-  \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
-  \item We conclude that without this constraint our formulation has more degree of freedom
-  \item What happen when we drop this constraint
-  \item The problem becomes non-convex and without a global minimum
-  \item Not having a global minimum is bad, how can we solve that ?
-  \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
-  \item Now we have a framework to switch on and of neurons
-  \item We are still doing useless computation for neurons that will stay off forever, if we pruned them then we would speed up training
-  \item Define the strategy to detect "forever dead" neurons
-  \item (should we talk about the software architecture ?)
-  \item now we evaluate the system
-  \item First we show that our system has indeed more freedom than Group sparsity by showing that for any given amount of sparsity it can fit closer than the previous method
-  \item On the same problem we show that removing neurons on the fly does not dramatically reduce accuracy (we might not be able to see any difference in performance for a linear/logistic regression though)
-  \item We show that works with Bigger networks (multi layers perceptrons and CNNs), describe the training dynamics, discuss the shape we obtain
-  \item Show that it is easier to do hyper-parameter optimization on the regularization parameter that the size of each layer.
+% \begin{itemize}
+  % \item We want to figure out what is the proper network size
+  % \item If we had a oversized network and for each neuron we would have an on/off switch, we could optimize the state of each switch to achieve any size/accuracy tradeof (we can prove that, do we care ?)
+  % \item Solving such problem is NP-Hard
+  % \item We could approximate the binary switch by relaxing them and doing L1 loss instead of L0 loss
+  % \item This is the definition of Shrinknets
+  % \item group sparsity tries to achieve a similar goal but with a different formulation
+  % \item How are they related ?
+  % \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
+  % \item We conclude that without this constraint our formulation has more degree of freedom
+  % \item What happen when we drop this constraint
+  % \item The problem becomes non-convex and without a global minimum
+  % \item Not having a global minimum is bad, how can we solve that ?
+  % \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
+  % \item Now we have a framework to switch on and of neurons
+  % \item We are still doing useless computation for neurons that will stay off forever, if we pruned them then we would speed up training
+  % \item Define the strategy to detect "forever dead" neurons
+  % \item (should we talk about the software architecture ?)
+  % \item now we evaluate the system
+  % \item First we show that our system has indeed more freedom than Group sparsity by showing that for any given amount of sparsity it can fit closer than the previous method
+  % \item On the same problem we show that removing neurons on the fly does not dramatically reduce accuracy (we might not be able to see any difference in performance for a linear/logistic regression though)
+  % \item We show that works with Bigger networks (multi layers perceptrons and CNNs), describe the training dynamics, discuss the shape we obtain
+  % \item Show that it is easier to do hyper-parameter optimization on the regularization parameter that the size of each layer.
 I think a nice experiment would be to plot the evolution of the final size of a two layer network (so going from a lambda to two sizes).
@@
 It would show how the system trades off the budget between the two layer in a nice and visual way
-  \item Then we evaluate performance
-\end{itemize}
+  % \item Then we evaluate performance
+% \end{itemize}
 
-\section{Outline2}
+% \section{Outline2}
 \begin{itemize}
   \item Introduction
+  \begin{itemize}
+    \item Finding an appropriately sized network is challenging
+    \item ML practitioners spend a large amount of time tuning the size of layers
+    in a network in order to get the best possible accuracy.
+    \item Many techniques have been proposed for hyperparam opt but these
+    are computationally expensive and take long to train
+    \item We propose ShrinkNets, an approach to tune the size of the network 
+    as it is being trained without incurring the significant costs of 
+    hyperparameter optimization. 
+    \item Thus, our contribution are: ...
+  \end{itemize}
+  \item Our Approach
+  \begin{itemize}
+    \item Assign an on/off switch to each neuron. But this is np-hard, so we
+    consider a relaxation
+    \item Formulation
+    \item Relationship to sparsity
+    \item Strategies to kill neurons (relation to theory above?)
+    \item Implementation details
+  \end{itemize}
   \item Related Work
-  \item Our Approach
+  \begin{itemize}
+    \item Hyperparameter optimization: random, bayesian opt, bandit methods
+    \item distillation techniques
+    \item post-training compression techniques
+    \item group sparsity, non-parametric neural networks
+    \item training dynamics paper: first overfitting and then randomization?
+  \end{itemize}
   \item Experiments
+  \begin{itemize}
+    \item Accuracy obtained by Shrinknets
+    \item Time taken to reach that accuracy compared with other hyperopt methods
+    \item Characterize method wrt params
+    \item Other experiments  
+  \end{itemize}
   \item Discussion
+  \begin{itemize}
+    \item Where does the method shine?
+    \item Side-effects of method: smaller networks, time to train
+    \item Potential extensions/limitations
+  \end{itemize}
   \item Conclusion

### 2018-02-05 paper/ICML/related_work.tex
First pass on outline, filling in sections

--- 2018-02-05 paper/ICML/paper.tex
@@
-%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
-
-\documentclass{article}
-
-% Recommended, but optional, packages for figures and better typesetting:
-\usepackage{microtype}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{cleveref}
-\usepackage{bm}
-\usepackage{amsthm}
-\usepackage{amsfonts}
-\usepackage{subfigure}
-\usepackage{stmaryrd}
-\usepackage{booktabs} % for professional tables
-
-% hyperref makes hyperlinks in the resulting PDF.
-% If your build breaks (sometimes temporarily if a hyperlink spans a page)
-% please comment out the following usepackage line and replace
-% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
-\usepackage{amsmath}
-
-% Attempt to make hyperref and algorithmic work together better:
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\newcommand{\abs}[1]{\left|#1\right|}
-\newcommand{\diag}[1]{\text{diag}\left(#1\right)}
-\newcommand{\intint}[1]{\left\llbracket#1\right\rrbracket}
-\newtheorem{proposition}{Proposition}[section]
-
-% Use the following line for the initial blind version submitted for review:
-\usepackage{icml2018}
-
-% If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2018}
-
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Learning Neural Network size with ShrinkNets}
-
-\begin{document}
-
-\twocolumn[
-\icmltitle{Learning Network Size while Training with ShrinkNets}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2018
-% package.
-
-% List of affiliations: The first argument should be a (short)
-% identifier you will use later to specify author affiliations
-% Academic affiliations should list Department, University, City, Region, Country
-% Industry affiliations should list Company, City, Region, Country
-
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
-\icmlsetsymbol{equal}{*}
-
-\begin{icmlauthorlist}
-\icmlauthor{Guillaume Leclerc}{mit,epfl}
-\icmlauthor{Raul Castro Fernandez}{mit}
-\icmlauthor{Manasi Vartak}{mit}
-\icmlauthor{Martin Jaggi}{epfl}
-\icmlauthor{Samuel Madden}{mit}
-\end{icmlauthorlist}
-
-\icmlaffiliation{mit}{Computer Science and Artificial Intelligence Laboratories, Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}
-
-\icmlaffiliation{epfl}{Swiss Federal Institute of Technology, Lausanne, Switzerland}
-
-\icmlcorrespondingauthor{Guillaume Leclerc}{leclerc@mit.edu}
-
-% You may provide any keywords that you
-% find helpful for describing your paper; these are used to populate
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Machine Learning, ICML}
-
-\vskip 0.3in
-]
-
-% this must go after the closing bracket ] following \twocolumn[ ...
-
-% This command actually creates the footnote in the first column
-% listing the affiliations and the copyright notice.
-% The command takes one argument, which is text to display at the start of the footnote.
-% The \icmlEqualContribution command is standard text for equal contribution.
-% Remove it (just {}) if you do not need this facility.
-
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{} % otherwise use the standard text.
-
-\begin{abstract}
-  Let's write the abstract at the end
-\end{abstract}
-
-\section{Tentative outline}
+\section{Related Work}
 
 \begin{itemize}
-  \item We want to figure out what is the proper network size
-  \item If we had a oversized network and for each neuron we would have an on/off switch, we could optimize the state of each switch to achieve any size/accuracy tradeof (we can prove that, do we care ?)
-  \item Solving such problem is NP-Hard
-  \item We could approximate the binary switch by relaxing them and doing L1 loss instead of L0 loss
-  \item This is the definition of Shrinknets
-  \item group sparsity tries to achieve a similar goal but with a different formulation
-  \item How are they related ?
-  \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
-  \item We conclude that without this constraint our formulation has more degree of freedom
-  \item What happen when we drop this constraint
-  \item The problem becomes non-convex and without a global minimum
-  \item Not having a global minimum is bad, how can we solve that ?
-  \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
-  \item Now we have a framework to switch on and of neurons
-  \item We are still doing useless computation for neurons that will stay off forever, if we pruned them then we would speed up training
-  \item Define the strategy to detect "forever dead" neurons
-  \item (should we talk about the software architecture ?)
-  \item now we evaluate the system
-  \item First we show that our system has indeed more freedom than Group sparsity by showing that for any given amount of sparsity it can fit closer than the previous method
-  \item On the same problem we show that removing neurons on the fly does not dramatically reduce accuracy (we might not be able to see any difference in performance for a linear/logistic regression though)
-  \item We show that works with Bigger networks (multi layers perceptrons and CNNs), describe the training dynamics, discuss the shape we obtain
-  \item Show that it is easier to do hyper-parameter optimization on the regularization parameter that the size of each layer.
-I think a nice experiment would be to plot the evolution of the final size of a two layer network (so going from a lambda to two sizes).
-And plot the trajectory in the "size space" as we decrease lambda.
-It would show how the system trades off the budget between the two layer in a nice and visual way
-  \item Then we evaluate performance
+    \item Hyperparameter optimization: random, bayesian opt, bandit methods
+    \item distillation techniques
+    \item post-training compression techniques
+    \item group sparsity, non-parametric neural networks
+    \item training dynamics paper: first overfitting and then randomization?
   \end{itemize}
-
-\section{Outline2}
-\begin{itemize}
-  \item Introduction
-  \item Related Work
-  \item Our Approach
-  \item Experiments
-  \item Discussion
-  \item Conclusion
-\end{itemize}
-
-\input{introduction}
-\input{approach}
-\input{theory}
-\input{evaluation}
-\input{related_work}
-\input{discussion}
-\input{conclusion}
-
-\appendix
-\input{appendix}
-
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-\nocite{OpenML2013}
-
-\bibliography{custom}
-\bibliographystyle{icml2018}
-
-\end{document}

### 2018-02-05 paper/ICML/theory.tex

@@
 \section{Theoretical analysis}
+
+\begin{itemize}
+  \item Comparison to group sparsity
+  \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
+  \item We conclude that without this constraint our formulation has more degree of freedom
+  \item What happen when we drop this constraint
+  \item The problem becomes non-convex and without a global minimum
+  \item Not having a global minimum is bad, how can we solve that ?
+  \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
+\end{itemize}
 

### 2018-02-05 paper/ICML/related_work.tex
related work added

@@
 \end{itemize}
+
+Given the importance of network structure, many techniques have been proposed to
+find the best network structure for a given learning task.
+These techniques broadly fall into four categories: hyperparameter optimization
+strategies, post-training model compression for inference as well as model 
+simplification, techniques to resize models during training, and 
+automated architecture search methods.
+
+The most popular techniques for hyperparameter optimization include simple 
+methods such as random search~\cite{Bergstra2012} which have been shown to work
+suprisingly well compared to more complex methods such as those based on
+Bayesian optimization~\cite{Snoek12}.
+Techniques such as~\cite{Snoek12} model generalization performance via 
+Gaussian Processes~\cite{GaussianProcesses} and select hyperparameter 
+combinations that come from uncertain areas of the hyperparameter space.
+Recently, methods based on bandit algorithms (e.g. ~\cite{li2016hyperband, 
+jamieson2016}) have also become a popular way to tune hyperparameters.
+As noted before, all of the above techniques require many tens to hundreds of
+models to be trained, making this process computationally inefficient and slow.
+
+In contrast with hyperparameter tuning methods, some methods such as 
+DeepCompression~\cite{han2015deepcompression} seek to compress the network to 
+make inference more efficient.
+This is accomplished by pruning connections and quantizing weights.
+On similar lines, multiple techniques such as~\cite{romero2014fitnets, 
+hinton2015distilling} have been proposed for distilling a network into a 
+simpler network or a different model.
+Unlike our technique which works during training, these techiques are used after
+training and it would be interesting to apply them to ShrinkNets as well.
+
+The techniques closed to our work are those based on group sparsity such as 
+\mpv{Guillaume: fill in}.
+
+Finally, there has also been recent work in automatically learning model
+architecture through the use of genetic algorithms and reinforcement learning 
+techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}.
+These techniques are focused more on learning higher-level architectures (e.g.
+building blocks for neural network architectures) as opposed to learning 
+network size.

### 2018-02-05 paper/ICML/dataset_settings.py
Prepare cover dataset for the other machines

@@ -3,7 +3,7 @@ import re
 from paper.ICML.models.FullyConnected import FullyConnected
 from paper.ICML.models.VGG import VGG
 from copy import deepcopy
-from datasets import MNIST, FashionMNIST, CIFAR10
+from paper.ICML.datasets import MNIST, FashionMNIST, CIFAR10, covertype
 from torchvision import transforms
 import torchsample as ts
 
@@ -51,6 +51,32 @@ SETTINGS = {
             'size_layer_5': [5000],
         },
     },
+    'COVER_FC_DYNAMIC': {
+        'mode': 'classification',
+        'model': FullyConnected,
+        'dataset': covertype,
+        'val_batch_size': 10000,
+        'normalization': None,
+        'data_augmentations': [],
+        'params': {
+            'lambda': (1e-2, 1e-6),
+            'input_features': [(98,)],
+            'output_features': [7],
+            'layers': (1, 5),
+            'learning_rate': (1e-2, 1e-4),
+            'batch_size': (300, 3000),
+            'dropout': [0, 0, 0, 0.1, 0.2, 0.5],
+            'batch_norm': [True, False],
+            'weight_decay': (1e-2, 1e-8),
+            'dynamic': [True],
+            'gamma': [0.99, 0.9, 0],
+            'size_layer_1': [5000],
+            'size_layer_2': [5000],
+            'size_layer_3': [5000],
+            'size_layer_4': [5000],
+            'size_layer_5': [5000],
+        },
+    },
     'CIFAR10_VGG_DYNAMIC': {
         'mode': 'classification',
         'model': VGG,
@@ -66,12 +92,12 @@ SETTINGS = {
             ts.transforms.RandomRotate(10),
         ],
         'params': {
-            'lambda': (1e-2, 1e-5),
+            'lambda': (1e-2, 1e-7),
             'name': ['VGG16'],
             'input_features': [(3, 32, 32)],
             'output_features': [10],
-            'learning_rate': (1e-2, 1e-6),
-            'batch_size': (8, 512),
+            'learning_rate': (1e-2, 1e-4),
+            'batch_size': (32, 512),
             'weight_decay': (1e-2, 1e-8),
             'factor': [2],
[…]

### 2018-02-05 paper/ICML/datasets.py

@@ -1,10 +1,34 @@
+import torch
+import numpy as np
 from torchvision import transforms
+from sklearn import preprocessing
+from torch.utils.data import TensorDataset
 from torchvision.datasets import (
     MNIST as MNISTLoader,
     FashionMNIST as FashionMNISTLoader,
     CIFAR10 as CIFAR10Loader,
     CIFAR100 as CIFAR100Loader
 )
+from sklearn.model_selection import train_test_split
+from linear_regression_experiment import normalize
+import openml
+
+
+def load_dataset(id, do_normalize=True, factor=1):
+    dataset = openml.datasets.get_dataset(id)
+    X, y, categorical = dataset.get_data(
+        target=dataset.default_target_attribute,
+        return_categorical_indicator=True)
+    lines_without_nans = (np.isnan(X).sum(1) == 0)
+    X = X[lines_without_nans]
+    y = y[lines_without_nans]
+    if do_normalize:
+        X = normalize(X)
+    if any(categorical):
+        enc = preprocessing.OneHotEncoder(categorical_features=categorical)
+        X = enc.fit_transform(X).todense()
+    return X, y
+
 
 def MNIST(train=True, transform=[]):
     total_transform = transforms.Compose([transforms.ToTensor()] + transform)
@@ -34,3 +58,12 @@ def CIFAR100(train=True, transform=[]):
                        train=train,
                        transform=total_transform
                        )
+
+def covertype(train=True, test_split=0.1, seed=0, normalized=True, transform=[]):
+    X, y = load_dataset(1596)
+    X_train, X_test, y_train, y_test = train_test_split(
+        X, y, test_size=test_split, random_state=seed)
+    if train:
+        return TensorDataset(torch.from_numpy(X_train).float(), torch.from_numpy(y_train).long())
+    else:
+        return TensorDataset(torch.from_numpy(X_test).float(), torch.from_numpy(y_test).long())

### 2018-02-05 paper/ICML/models/VGG.py

@@ -46,8 +46,9 @@ class VGG(nn.Module):
         graph.add(Flatten)
         for i in range(2):
             graph.add(Linear, out_features=params['classifier_layer_%s' % (i + 1)])
-            graph.add(SmoothFilter, starting_value='uniform',
-                      gamma=params['gamma'])
+            if dynamic:
+                graph.add(SmoothFilter, starting_value='uniform',
+                          gamma=params['gamma'])
             graph.add(ReLU, inplace=True)
         graph.add(Linear, out_features=params['output_features'])
 

### 2018-02-05 paper/ICML/neural_network_train.py

@@ -1,6 +1,7 @@
 import torch
 import numpy as np
 import os
+from collections import Counter
 from copy import deepcopy, copy
 from random import choice
 from uuid import uuid4
@@ -15,6 +16,7 @@ from utils.misc import tn
 from multiprocessing import cpu_count
 from torch.optim import Adam, SGD, Adamax
 from torch.optim.lr_scheduler import ReduceLROnPlateau
+from dynnet.filters import SimpleFilter
 import sys
 
 def clean_params(params):
@@ -75,6 +77,14 @@ def prepare_loaders(config, split=0.8):
     training_dataset = IndexDataset(full_train_dataset_augmented, train_indices)
     validation_dataset = IndexDataset(full_train_dataset_simple, validation_indices)
 
+
+    weights = [0] * config['params']['output_features']
+
+    for _, labels in DataLoader(training_dataset, batch_size=100000, num_workers=cpu_count()):
+        for label in labels.cpu().numpy():
+            weights[label] +=1
+    class_weights = torch.from_numpy(1 / np.array(weights) / len(weights) * len(training_dataset)).float().cuda()
+
     if data_augmentations:
         training_dataloader = DataLoader(training_dataset,
                                          batch_size=config['params']['batch_size'],
@@ -88,19 +98,19 @@ def prepare_loaders(config, split=0.8):
                                             config['val_batch_size'])
     testing_dataloader = preload_dataset(testing_dataset,
                                          config['val_batch_size'])
-    return training_dataloader, validation_dataloader, testing_dataloader
+    return training_dataloader, validation_dataloader, testing_dataloader, class_weights
 
-def forward(model, dataloader, config, optimizer=None):
+def forward(model, dataloader, config, class_weights, optimizer=None):
     accs = []
     losses = []
     is_classification = config['mode'] == 'classification'
     if is_classification:
-        criterion = torch.nn.CrossEntropyLoss()
+            criterion = torch.nn.CrossEntropyLoss(weight=class_weights)
     else:
         criterion = torch.nn.MSELoss()
     lamb = config['params']['lambda']
 
-    for inputs, labels in dataloader:
+    for i, (inputs, labels) in enumerate(dataloader):
         inputs = Variable(inputs.cuda(async=True), volatile=(optimizer is None))
         labels = Variable(labels.cuda(async=True), volatile=(optimizer is None))
         prediction = model(inputs)
@@ -131,16 +141,33 @@ def init_model(model):
             module.running_mean.fill_(0)
[…]

### 2018-02-05 paper/ICML/plot_random_search.py

@@ -1,0 +1,90 @@
+import torch
+import pandas as pd
+import numpy as np
+from glob import glob
+from paper.ICML.models.VGG import cfg
+from algorithms.expectation_random_permutation import max_expectation
+
+def load_files(prefix, mode):
+    files = glob('./experiments_results/random_search/%s_%s/*' % (prefix, mode))
+    result = []
+    for file_name in files:
+        try:
+            with open(file_name, 'rb') as f:
+                result.append(torch.load(f))
+        except:
+            pass
+    return result
+
+def get_best_entry(logs):
+    vac = logs[logs.measure == 'val_acc']
+    return logs[logs.epoch == vac.ix[vac['value'].argmax()].epoch]
+
+def get_final_measure(log, measure='test_acc'):
+    x = get_best_entry(log)
+    if measure == 'time':
+        return float(x.max().time)
+    else:
+        return float(x[x.measure == measure].value)
+
+def generate_stats(infos):
+    logs = infos[2].logs
+    params = infos[1]['params']
+    return [
+        get_final_measure(logs, 'test_acc'),
+        compute_size(infos),
+        get_final_measure(logs, 'val_acc'),
+        get_final_measure(logs, 'train_acc'),
+        get_final_measure(logs, 'time'),
+        params['lambda'],
+        params['batch_size'],
+        params['learning_rate'],
+        params['gamma'],
+        params['factor'],
+        params['weight_decay']
+    ]
+
+def compute_cost(seq, cl1, cl2):
+    prev = 3
+    total = 0
+    for e in seq:
+        total += prev * e * 9
+        prev = e
+    total += 1024 * cl1
+    total += cl1 * cl2
+    total += 10 * cl2
+    return total
+
+def compute_size(infos, model='VGG16'):
+    i = 0
+    logs = infos[2].logs
+    sizes = []
+    channel_count = 3
+    cost = 0
+    try:
+        while True:
+            i += 1
+            sizes.append(get_final_measure(logs, 'size_%s' % i))
+    except:
+        pass
+    if sizes:
+        cl1 = sizes[-2]
+        cl2 = sizes[-1]
+        sizes = sizes[:-2]
+    else:
+        original_sizes = [x for x in cfg[model] if x is not 'M']
+        sizes = infos[1]['params']['factor'] * np.array(original_sizes)
[…]

### 2018-02-05 paper/ICML/approach.tex

--- 2018-01-06 paper/paper.tex
@@
-\documentclass[sigconf]{acmart}
-\sloppy
-\usepackage{graphicx}
-\usepackage{color}
-\settopmatter{printacmref=false} % Removes citation information below abstract
-\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
-\pagestyle{plain} % removes running headers
-\makeatletter
-\makeatother
-\settopmatter{printacmref=false}
+\section{Our Approach}
 
-\usepackage{booktabs} % For formal tables
-\setcopyright{none}
+\begin{itemize}
+  \item Assign an on/off switch to each neuron. But this is np-hard, so we
+  consider a relaxation
+  \item Formulation
+  \item Relationship to group sparsity
+  \item Strategies to kill neurons (relation to theory above?)
+  \item Implementation details
+\end{itemize}
 
-\newcommand{\MITAffiliation}{
-\affiliation{%
-  \institution{Massachussets Institute of Technology}
-  \streetaddress{32 Vassar Street}
-  \city{Cambridge}
-  \state{Massachussets}
-  \country{USA}
-  \postcode{02139}
-}}
-
- \newcommand{\EPFLAffiliation}{
-\affiliation{%
-  \institution{Swiss Federal Institute of Technology in Lausanne (EPFL)}
-  \streetaddress{Route Cantonale}
-  \city{Lausanne}
-  \country{Switzerland}
-  \postcode{02139}
-}}
-
-\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
-\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
-\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
-\begin{document}
-\title{Learning Network Size While Training with ShrinkNets}
-
-\author{Guillaume Leclerc, Raul Castro Fernandez, Samuel Madden}
-\affiliation{%
-  \institution{Massachussets Institute of Technology}
-}
-\email{[leclerc, raulcf, madden]@mit.edu}
-
-%\author{Guillaume Leclerc}
-%\authornote{Visiting Student}
-%\MITAffiliation
-%\email{leclerc@mit.edu}
-%
-%\author{Raul Castro Fernandez}
-%\MITAffiliation
-%\email{raulcf@csail.mit.edu}
-%
-%\author{Samuel Madden}
-%\MITAffiliation
-%\email{madden@csail.mit.edu}
-
-% The default list of authors is too long for headers.
-\renewcommand{\shortauthors}{G. Leclerc et al.}
-
-%\begin{abstract}
-%  Write the abstract at the end !
-%\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-When designing neural networks, one of the key parameters is the network size, i.e., 
-%, number of layers
-%and number of neuros per layer, 
-%(width and depth)
-the number of layers and neurons per layer.  Choosing these parameters appropriately
-can dramatically affect performance, yet
-%In particular, these hyper parameters have a strong correlation with
-%over/underfitting \srm{give reference} \gl{I did some litterature review and
-%actually this statement is quite controversial, should we rephrase ?}. 
-there is no reliable way to efficiently set them. Although many search
- strategies and heuristics~\cite{Bengio2012a} have been proposed, including
-%To select the best candidates, researchers have used strategies such
-%as 
-random search,
-%\gl{Should we also move the references here if we remove the
-%pargraph from the related work ?}, 
-meta-gradient descent~\cite{Pedregosa2016},
-Gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}, 
-%to find good parameters without exhaustively
-%exploring the entire hyper-parameter space. 
- they generally require a compute-intensive
-search of parameter space.
-
-%However, we are still bound to use costly and sometimes complex methods to
-%find reasonable values for these hyper-parameters.
-
-In this paper we present a method to automatically find an appropriate network
-size,
-%from a single parameter, 
-drastically reducing optimization time.
-%dimensionality. 
-The key idea is to
-\emph{learn} the right network size at the same time that the network is
-learning the main task. For example, for an image classification task, with our
-approach we can provide the training data to a network---without sizing it a
-priori---and expect to end up with a network that has learned to classify images
-with an accuracy similar to a the best manually engineered network.
-%\gl{too strong, we do not really have
-%  any guarantee on the generalization, how about changing it to: to end up with
-%  a network that learnt a tradeoff between size and accuracy}. 
-Our approach has two main benefits. First, we no longer need to choose a
-network size before training. Second, the final network size will tuned to be
-appropriate for the task at hand, and not larger. 
-%Because the sizing occurs
-%dynamically, while the
-%network is training, we remove the useless neurons 
-%implement a new mechanism that removes
-%the deactivated neurons to  
-%\gl{Should we talk about the
-%fact that it automatically gets rid of dead neurons ?}. 
-This is important
-because over-sized networks have a lower inference throughput and higher memory
-footprint.
-
-Our approach has two main challenges. First, we need a way to dynamically size the
-network during training. Second, we need a loss function that optimizes
-for the additional task of sizing, without deteriorating the learning
-performance of the main task. Our approach, called ShrinkNets, copes with both
-challenges.
-
-% \subsection{Main Contributions}
-% 
-% The main contribution of this article are:
-% \begin{itemize}
-%   \item The Filter layer, a neural network layer which puropose is to allow feature selection
-%   \item To the best of our knowledge, the first attempts to dynamically change the number of channels in deep convolutional neural networks
-%   \item A deep learning library built on top of PyTorch that allow partictionners to train shrinking networks (Feed-Forward and Convolutional)
-% \end{itemize}
-%
-
-\section{ShrinkNets}
+Our approach has two main challenges. First, we need a way to
+dynamically size the network during training. Second, we need a
+loss function that optimizes for the additional task of sizing, without
+deteriorating the learning performance of the main task. Our
+approach, called ShrinkNets, copes with both challenges.
 
@@
 learning process, and second we need a way to balance the network size and the
-generalization capability for the main task. We introduce a new \textsf{Filter} layer that takes care of \emph{deactivating} neurons. We also modify
+generalization capability for the main task. We introduce a new \textsf{Filter} 
+\mpv{Choose a different name if possible bc this can be confused w/convolutional
+filters. Maybe Shrinkage layer?} 
+layer that takes care of \emph{deactivating} neurons. We also modify
 existing loss functions to incorporate a new term that takes care of balancing
@@
 
-%\subsection{Motivation}
-%
-%\srm{This makes what we have done sound like an incremental change over prior
-%work.  Instead, move this description to prior work and say why its not a good
-%approach there, then describe what we do as a new method.  }
-%
-%The method described in [ref] grows and shrinks the network over time. Though
-%this seems to be an attractive property to have, during our experiments and
-%according to their results, models are very slow to train and sometimes
-%converge to suboptimal solutions. Their method also requires a new optimizer
-%\textit{AdaRad}.  Our goal was to provide a solution that can easily be
-%integrated in existing machine learning systems and provide similar convergence
-%speed and accuracy. Therefore, designing a new layer that only allow shrinking
-%seemed to be best approach.
-%
-
-%\subsection{Definition}
-
 \textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are usually placed after
 linear and convolutional layers.
-%\gl{This is how I
-%  used it but with the new implementation we can be more creative and put them
-%  anywhere, should we say "usually placed" insdead ?}. 
 The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
@@
 
-%We can use this property to devise a training procedure.
-
-%To train networks we need start with a substantially oversized network, then we
-%insert \textit{Filter Layers}  (usually after every linear or convolutional
-%layer except the last one) and we sample their weight from the
-%$\text{Uniform}(0, 1)$ distribution.
-
-%The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
-%\times \dots \times D_n\right)$ so it is compatible with fully connected layers
-%with $n=0$ or convolutional layers with $n=2$. This layer has a parameter
-%$\theta \in \mathbb{R}^C$ and is defined the following way. \srm{Need to define
-%B, C, D}.  
-%
-%\begin{equation} 
-%Filter(I;\theta) = I \circ \max(0, \theta)
-%\end{equation}
-%
-%Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
-%is expanded in all dimensions except the second one to match the input size. It
-%is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
-%feature/channel will forever be $0$. We can use this property to devise a
-%training procedure.  
-%
-%\srm{Give an English description of what this formalism
-%achieves -- what does the filter layer do, why is it significant.}
-
-%\subsection{The training procedure}
 \textbf{Training Procedure: } Once Filter layers are placed in a network and initialized (sampled from the Uniform$[0, 1]$ distribution),
@@
 
-\textbf{Dynamic Network Resizing}
+\subsection{Strategies to Remove Neurons}
+
+\textbf{Implementation}
 It is possible to reduce the overhead of the training process by removing
@@
 neurons to the relevant layers.
-
-\section{Evaluation}
-
-We  implemented ShrinkNets, including the \emph{garbage collection}
-mechanism on top of \textit{PyTorch}~\cite{paszke2017automatic}, and we have
-made the software open source.\footnote{The code is available as Python/PyTorch
-library on \url{http://github.com/mitdbg/fastdeepnets}
-%\gl{Should we rename the repository ?}
-}. We used used our implementation to evaluate two crucial aspects of
-ShrinkNets, which we present next.
-
-%This is why we
-%want to support what we call garbage collection: removing the weights in the
-%layers that are responsible (or using) features that are disabled.  \par To be
-%able to catpure this relationship between layers, we augmented \textit{Pytorch}
-%~\cite{paszke2017automatic} (the framework we used as the
-%foundation of our implementation) with a graph structure very similar to the
-%one available in Keras ~\cite{chollet2015keras}.  In this graph, edges are
-%effectively event hubs responsible for propagating \textit{feature removal}
-%events to its endpoints. ShrinkNet layers are designed to emit and react to
-%these events but also propagate the event further if has an impact at the other
-%endpoint of the layer (input or output) \gl{What I mean here is: if the event
-%  comes from the output, it might be propagated to the inputs, and the other
-%  way around}.  \par This event-based implementation coordinated by edges makes
-%it very easy to integrate new layers in the library.  We even provide automatic
-%wrapping for layers from \textit{PyTorch} if they have no internal state. For
-%more complex ones, we provide utilitaries that
-%makes the implementation very concise.
-
-%\textbf{Software architecture
-%\footnote{The code is available as Python/PyTorch library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
-%      the repository ?}
-%}
-%: }\textit{Filter Vectors} can easily be implemented in
-%a few lines of code in many existing deep learning frameworks. However, in
-%ShrinkNets, we assume that we start with obviously oversized networks. 
-%
-
-\subsection{Does ShrinkNet converge?}
-
-%To demonstrate that the approach is viable, we will first show that Shrinking
-%Networks converge properly. For this experiment 
-We trained a one hidden layer
-neural network with one filter layer to control the number of hidden units. We
-initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
-~\cite{Lecun1998} using different values for $\lambda$.
-Figure~\autoref{convergence_plot} shows that
-%We
-%summarized the results in \autoref{convergence_plot}. We can see on this plot
-%is that for a given $\lambda$ the number of hidden units seems to always
-%converge to some value. It has two implications: it seems that 
-$\lambda$ works as a proxy for the network size,
-% as
-%we would think, a proxy of the network size 
-with bigger $\lambda$ implying smaller
-networks. More importantly, the figure helps us confirm that despite the regular
-spikes---which are caused by the dynamic disabling of neurons---ShrinkNets
-eventually converge.
-%we see in the
-%loss function that occur when neurons are disabled will eventually disappear
-%because the number of neurons reach a plateau. 
-%\gl{I feel we should give a
-%  conclusion for this paragraph but I am not sure what to say}
-
-\begin{figure}
-\vspace{-.2in}
-\begin{center}
-\includegraphics[width=\columnwidth]{convergence}
-\vspace{-.25in}
-\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
-\vspace{-.2in}
-\end{center}
-\end{figure}
-\subsection{Does ShrinkNet find good networks?}
-
-In this experiment we want to find an appropriate network size for two network
-architectures, a multi-layer perceptron (MLP) and the \textit{LeNet-5}
-model~\cite{Lecun1998}. We have no prior information about the network size,
-but we set an upper bound of $50$ channels per convolutional layer and $5000$
-neurons for fully connected layers. We then use random search to vary the
-parameters that determine the network size, i.e., $\lambda$ in the case of
-ShrinkNets, the width of each layer in the case of
-\textsf{Fixed} and similar to previous but adding a $L_2$ penalty~\cite{Ng2004}
-(\textsf{Fixed-L2}).  We train all variants on \texttt{MNIST}~\cite{Lecun1998},
-\texttt{FashionMNIST}~\cite{Xiao2017} and
-\texttt{CIFAR10}~\cite{Krizhevsky2009}. We use the same number of epochs, 100
-for MLPs and 200 for \textit{LeNet-5}. We select the epoch that performed the
-best on the validation set and evaluated it on the testing set. We repeat this
-process 50 times and show the distribution of the testing accuracy in
-\autoref{hyper_opt_res}.
-
-The results in the figure show that ShrinkNets finds better networks with fewer
-training iterations than the other methods, because it achieves higher median 
-and less variable accuracies. Despite the simple nature of this experiment, we
-believe that the results generalize to more complex search methods; mainly
-because our solution reduces the dimensionality of the space they have to
-explore.
-
-%the distributions for ShrinkNets have higher
-%medians and are less variable than the others. ShrinkNets can find better
-%networks with fewer training iterations than the other methods
-%
-%We can see that in all cases the distributions for ShrinkNets have substantially
-%higher medians are are less variable than the other architectures (the best
-%model is not always found by ShrinkNets, but this is likely an artifact of our
-%randomized search process).  This shows that ShrinkNets can find better networks
-%with fewer training iterations than existing methods.
-
-%One of our main goals is to show that ShrinkNets quickly finds neural network
-%architectures that perform well. To show this, we ran a simple experiment where
-%we compare ShrinkNets to other network tuning methods, using random search over
-%the hyper-parameters that control the network size ($\lambda$ in the case of
-%ShrinkNets).  Despite the simple nature of this experiment, we believe that the
-%results generalize to more complex search methods, many of of which will
-%actually benefit dimensionality of the hyper-parameter space in the ShrinkNets
-%approach.
-%
-%To isolate the effect of ShrinkNets we will consider two very simple
-%architectures: multi-layer perceptrons (with three hidden layers) and the
-%\textit{LeNet-5} model ~\cite{Lecun1998}.  For this experiment we assume we have
-%no prior information about the size except an upper bound of $50$ channels per
-%convolutional layer and $5000$ neurons for fully connected layers.  We try to
-%find the appropriate size of the network using classical network-size
-%optimization methods and ShrinkNets. For the classical methods we use: i) purely
-%random selection of network size parameters (``Fixed''), as well as
-%hyper-parameter regularization over the network size parameters using  $L_2$
-%penalty ~\cite{Ng2004} (``Fixed-L2'').  In the experiment, 
-%we randomly sample
-%parameters for each class of network and  train them for the same number of
-%epochs (100 for MLPs and 200 for CNNs). We picked the epoch that performed the
-%best on the validation set and evaluated it on the testing set. We repeat the
-%process for 50 iterations. This evaluation was done on \texttt{MNIST}
-%~\cite{Lecun1998}, \texttt{FashionMNIST} ~\cite{Xiao2017} and \texttt{CIFAR10}
-%~\cite{Krizhevsky2009}. The distribution of the testing accuracy we obtained is
-%summarized in \autoref{hyper_opt_res}.
-
-\begin{figure}
-\vspace{-.2in}
-\begin{center}
-  \includegraphics[width=\columnwidth]{hyper_opt}
-  \vspace{-.25in}
-\caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
-\vspace{-.2in}
-\end{center}
-\end{figure}
-
-\section{Related Work}
-
-There are many methods in the literature that aim to simplify network
-structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
-~\cite{Han2015}). On the other side, ShrinkNets and some others
-~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead
-of connections. This is very useful because it reduces the size of the matrices,
-producing speed-up even on devices/libraries that only support dense matrices
-. ShrinkNets improves on
-~\cite{Scardapane2017} because it removes neurons during training, speeding up
-the rest of the process. Further it outperforms~\cite{Philipp} on convergence
-speed and because it does not need to change the optimizer. To the best of our
-knowledge this is also the first work that tries to learn the number of channels
-in a convolutional neural network.
-
-\section{Conclusion}
-In this paper we presented a novel technique to guess a
-reasonable network size based on single parameter $\lambda$ that control the
-tradeoff between loss and network size. We demonstrated that ShrinkNets works
-both on fully connected networks and convolutional neural networks.  Although
-the initial results are promising, there are many additional avenues to explore.
-In the current implementation we only ``learn'' the number of features (neurons
-or channels).  We plan to augment this with a dynamic number of layers as seen
-in ~\cite{meier} to be able to determine the entire architecture. Further, as
-shown in Figure \ref{convergence_plot} that the loss temporarily suffers from
-the removal of neurons. It is likely that the loss would be more stable if the
-number of neurons converged faster or neurons disappeared more slowly. For this
-reason we plan to explore proximal gradient methods to optimize the filter
-vectors and/or randomize neuron removals. Finally, during our evaluation we
-picked small datasets mainly to be able to train many models and have
-statistically significant distributions. We plan to verify that our approach see
-if it generalizes to bigger datasets and other architectures like
-\texttt{ResNet} ~\cite{He2016}, which is possible with small modifications to
-our existing code base.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{bib,custom}
-
-\end{document}

### 2018-02-05 paper/ICML/discussion.tex

--- 2018-02-05 paper/ICML/paper.tex
@@
-%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
-
-\documentclass{article}
-
-% Recommended, but optional, packages for figures and better typesetting:
-\usepackage{microtype}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{cleveref}
-\usepackage{bm}
-\usepackage{amsthm}
-\usepackage{amsfonts}
-\usepackage{subfigure}
-\usepackage{stmaryrd}
-\usepackage{booktabs} % for professional tables
-
-% hyperref makes hyperlinks in the resulting PDF.
-% If your build breaks (sometimes temporarily if a hyperlink spans a page)
-% please comment out the following usepackage line and replace
-% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
-\usepackage{amsmath}
-
-% Attempt to make hyperref and algorithmic work together better:
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\newcommand{\abs}[1]{\left|#1\right|}
-\newcommand{\diag}[1]{\text{diag}\left(#1\right)}
-\newcommand{\intint}[1]{\left\llbracket#1\right\rrbracket}
-\newtheorem{proposition}{Proposition}[section]
-
-% Use the following line for the initial blind version submitted for review:
-\usepackage{icml2018}
-
-% If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2018}
-
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Learning Neural Network size with ShrinkNets}
-
-\begin{document}
-
-\twocolumn[
-\icmltitle{Learning Network Size while Training with ShrinkNets}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2018
-% package.
-
-% List of affiliations: The first argument should be a (short)
-% identifier you will use later to specify author affiliations
-% Academic affiliations should list Department, University, City, Region, Country
-% Industry affiliations should list Company, City, Region, Country
-
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
-\icmlsetsymbol{equal}{*}
-
-\begin{icmlauthorlist}
-\icmlauthor{Guillaume Leclerc}{mit,epfl}
-\icmlauthor{Raul Castro Fernandez}{mit}
-\icmlauthor{Manasi Vartak}{mit}
-\icmlauthor{Martin Jaggi}{epfl}
-\icmlauthor{Samuel Madden}{mit}
-\end{icmlauthorlist}
-
-\icmlaffiliation{mit}{Computer Science and Artificial Intelligence Laboratories, Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}
-
-\icmlaffiliation{epfl}{Swiss Federal Institute of Technology, Lausanne, Switzerland}
-
-\icmlcorrespondingauthor{Guillaume Leclerc}{leclerc@mit.edu}
-
-% You may provide any keywords that you
-% find helpful for describing your paper; these are used to populate
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Machine Learning, ICML}
-
-\vskip 0.3in
-]
-
-% this must go after the closing bracket ] following \twocolumn[ ...
-
-% This command actually creates the footnote in the first column
-% listing the affiliations and the copyright notice.
-% The command takes one argument, which is text to display at the start of the footnote.
-% The \icmlEqualContribution command is standard text for equal contribution.
-% Remove it (just {}) if you do not need this facility.
-
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{} % otherwise use the standard text.
-
-\begin{abstract}
-  Let's write the abstract at the end
-\end{abstract}
-
-\section{Tentative outline}
+\section{Discussion}
 
 \begin{itemize}
-  \item We want to figure out what is the proper network size
-  \item If we had a oversized network and for each neuron we would have an on/off switch, we could optimize the state of each switch to achieve any size/accuracy tradeof (we can prove that, do we care ?)
-  \item Solving such problem is NP-Hard
-  \item We could approximate the binary switch by relaxing them and doing L1 loss instead of L0 loss
-  \item This is the definition of Shrinknets
-  \item group sparsity tries to achieve a similar goal but with a different formulation
-  \item How are they related ?
-  \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
-  \item We conclude that without this constraint our formulation has more degree of freedom
-  \item What happen when we drop this constraint
-  \item The problem becomes non-convex and without a global minimum
-  \item Not having a global minimum is bad, how can we solve that ?
-  \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
-  \item Now we have a framework to switch on and of neurons
-  \item We are still doing useless computation for neurons that will stay off forever, if we pruned them then we would speed up training
-  \item Define the strategy to detect "forever dead" neurons
-  \item (should we talk about the software architecture ?)
-  \item now we evaluate the system
-  \item First we show that our system has indeed more freedom than Group sparsity by showing that for any given amount of sparsity it can fit closer than the previous method
-  \item On the same problem we show that removing neurons on the fly does not dramatically reduce accuracy (we might not be able to see any difference in performance for a linear/logistic regression though)
-  \item We show that works with Bigger networks (multi layers perceptrons and CNNs), describe the training dynamics, discuss the shape we obtain
-  \item Show that it is easier to do hyper-parameter optimization on the regularization parameter that the size of each layer.
-I think a nice experiment would be to plot the evolution of the final size of a two layer network (so going from a lambda to two sizes).
-And plot the trajectory in the "size space" as we decrease lambda.
-It would show how the system trades off the budget between the two layer in a nice and visual way
-  \item Then we evaluate performance
+  \item Where does the method shine?
+  \item Side-effects of method: smaller networks, time to train
+  \item Potential extensions/limitations
 \end{itemize}
-
-\section{Outline2}
-\begin{itemize}
-  \item Introduction
-  \item Related Work
-  \item Our Approach
-  \item Experiments
-  \item Discussion
-  \item Conclusion
-\end{itemize}
-
-\input{introduction}
-\input{approach}
-\input{theory}
-\input{evaluation}
-\input{related_work}
-\input{discussion}
-\input{conclusion}
-
-\appendix
-\input{appendix}
-
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-\nocite{OpenML2013}
-
-\bibliography{custom}
-\bibliographystyle{icml2018}
-
-\end{document}

### 2018-02-05 paper/ICML/evaluation.tex

@@
 \section{Evaluation}
+
+\begin{itemize}
+  \item Accuracy obtained by Shrinknets
+  \item Time taken to reach that accuracy compared with other hyperopt methods
+  \item Characterize method wrt params (lambda, starting network size), training dynamics
+  \item Other experiments: compression achieved by network, shape of network
+  obtained
+  \item Extra: Shrinknets have more freedom than group sparsity,  
+\end{itemize}
 

### 2018-02-05 paper/ICML/introduction.tex

@@
 
-\subsection{ShrinkNets}
+One of the key determinants of network accuracy is the shape of the network, 
+i.e., the number of layers, number of neurons per layer, and connections between
+layers.
+An under-sized network is likely to have low accuracy because of insufficient 
+capacity while an over-sized network is difficult to train due to additional 
+parameters and is computationally inefficient during trainging as well as
+inference.
+% A sub-optimal network shape can lead to low accuracy .
+%Although the hyperparameters related wo network size can dramatically affect
+% performance, there is no reliable way to efficiently set them.
+Consequently, many techniques have been proposed to determine the optimal size of
+a neural network.
+This problem is also referred to as {\it hyperparameter optimization}.
+The most popular techniques include hyperparameter optimization strategies 
+ranging from random search~\cite{paper-on-random-is-good-enough}, 
+what-is-this-paper~\cite{Bengio2012a}, 
+meta-gradient descent~\cite{Pedregosa2016},
+Gaussian processes~\cite{Bergstra2011a} etc.
+All of these techniques without exception require a compute-intensive search of 
+parameter space and often the training of many tens or hundreds of models.
+As a result, tuning models via hyperparameter optimization takes many times 
+longer than the training of a single model and also requires more compute power
+for the training of every model with different model shape.
 
-\subsection{Motivation}
+In this paper we present a novel method to automatically find an appropriate
+network size, drastically reducing optimization time. 
+The key idea is to learn the right network size at the same time that
+the network is learning the main task.
+Our strategy, called \textbf{ShrinkNets}, is blah blah \mpv{Short blurb about the technique}
+% For example, for an image classification task, with our approach we can 
+% provide the training data to a network—without sizing it a priori—and expect 
+% to end up with a network that has learned to classify images with an accuracy
+% similar to a the best manually engineered network. 
+Our approach has two main benefits. 
+First and foremost, we no longer need to choose a network size before training.
+We can merely set an initial size for the network and then the algorithm will
+determine the best network that is smaller or equal in size to the inital size.
+Second, our technique trains a single model as opposed to the hundreds trained
+during hyperparameter optimization, as a result, we can find the best model 
+faster as well as with less computational overhead.
+
+Thus, our contributions are as follows: 
+(a) we propose a novel technique based on dynamically switching neurons on/off 
+to learn network size as the network is being trained. 
+(b) we show that our technique is a relaxation\mpv{?} of group sparsity and 
+prove \mpv{fill in}. 
+(c) we demonstrate the efficacy of our technique on CNNs and FCNs where 
+ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
+training time compared to competing hyperparameter optimization methods.
+(d) we also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
+of neurons.

### 2018-02-06 paper/ICML/neural_network_train.py
Save the models now

@@ -236,11 +236,15 @@ def random_train(mode):
     config = deepcopy(sample_params(sampling_settings))
     print(mode)
     print(config)
-    filename = './experiments_results/random_search/%s/%s.pkl' % (mode, uuid4())
-    os.makedirs(os.path.dirname(filename), exist_ok=True)
+    filename_stats = './experiments_results/random_search/%s/%s.pkl' % (mode, uuid4())
+    filename_model = './experiments_results/random_search/%s/%s.model' % (mode, uuid4())
+    os.makedirs(os.path.dirname(filename_stats), exist_ok=True)
+    os.makedirs(os.path.dirname(filename_model), exist_ok=True)
     stats, model = train(config)
-    with open(filename, 'wb') as f:
+    with open(filename_stats, 'wb') as f:
         torch.save((sampling_settings, config, stats), f)
+    with open(filename_model, 'wb') as f:
+        torch.save(model.cpu(), f)
 
 if __name__ == '__main__':
     random_train(sys.argv[-1])

### 2018-02-07 paper/ICML/dataset_settings.py
Make cover experiment closer to GSNN paper

@@ -62,14 +62,14 @@ SETTINGS = {
             'lambda': (1, 1e-5),
             'input_features': [(98,)],
             'output_features': [7],
-            'layers': [4],
+            'layers': [3],
             'learning_rate': (1e-2, 1e-4),
-            'batch_size': (300, 3000),
+            'batch_size': [1000],
             'dropout': [0, 0, 0, 0.1, 0.2, 0.5],
             'batch_norm': [True, False],
             'weight_decay': (1e-1, 1e-7),
             'dynamic': [True],
-            'gamma': [0.9],
+            'gamma': [0.9, 0],
             'size_layer_1': [5000],
             'size_layer_2': [5000],
             'size_layer_3': [5000],

### 2018-02-07 paper/ICML/dataset_settings.py
Remove batch norm and dropout
- The GSNN paper does not use it

@@ -65,8 +65,8 @@ SETTINGS = {
             'layers': [3],
             'learning_rate': (1e-2, 1e-4),
             'batch_size': [1000],
-            'dropout': [0, 0, 0, 0.1, 0.2, 0.5],
-            'batch_norm': [True, False],
+            'dropout': [0],
+            'batch_norm': [False],
             'weight_decay': (1e-1, 1e-7),
             'dynamic': [True],
             'gamma': [0.9, 0],

### 2018-02-07 paper/ICML/dataset_settings.py
Update lambda for COVER dataset
- 1 is way too much

@@ -59,7 +59,7 @@ SETTINGS = {
         'normalization': None,
         'data_augmentations': [],
         'params': {
-            'lambda': (1, 1e-5),
+            'lambda': (0.1, 1e-6),
             'input_features': [(98,)],
             'output_features': [7],
             'layers': [3],

### 2018-02-08 paper/ICML/evaluate_performance.py
Fix issue with the static FC networks in benchmakrs

@@ -17,8 +17,12 @@ def load_model(filename, dataset='cover'):
     if dataset == 'cover':
         cfg = deepcopy(data[1])
         for i in range(cfg['params']['layers']):
-            cs = float(best_entry[best_entry.measure == 'size_%s' % (i + 1)].value)
-            cfg['params']['size_layer_%s' % (i + 1)] = int(cs)
+            try:
+                cs = float(best_entry[best_entry.measure == 'size_%s' % (i + 1)].value)
+                cfg['params']['size_layer_%s' % (i + 1)] = int(cs)
+            except:
+                pass # Keep the original size
+
     cfg['params']['dynamic'] = False # remove filters
     model = model(cfg['params'])
     return cfg, model
@@ -60,5 +64,5 @@ def get_all_models(dataset, mode):
         torch.save(result, f)
 
 if __name__ == '__main__':
-    get_all_models('COVER_FC', 'DYNAMIC')
+    # get_all_models('COVER_FC', 'DYNAMIC')
     get_all_models('COVER_FC', 'STATIC')

### 2018-02-08 paper/SysML/paper.tex

--- 2018-01-06 paper/paper.tex
@@
 \affiliation{%
-  \institution{Massachussets Institute of Technology}
+  \institution{Massachusetts Institute of Technology}
 }
@@
 \section{Introduction}
+Alternative intro sketch:
+As neural networks become commodity in many applications from improving camera quality on mobile phones \cite{googleapple} over language translation \cite{languagetranslation} to text auto-complete \cite{autocomplete}, inference performance and model size become equally important to the quality of the prediction.
+Surprisingly, today those three concerns, quality, performance and model size, are largely handled separately with suboptimal results. 
+That is, models are trained with a fixed architecture (e.g., considering a certain size and performance budget), but then during the training the network architecture is considered fixed and does not further improve.
+In contrast, recently proposed techniques to make neural nets smaller after they have been trained, such as XX \cite{xx} and YY \cite{yy}, do not focus on the inference performance. 
+In fact, besides universal applicable techniques such as quantitazation \cite{quant} and compiling neural networks to binary code to avoid unneccassary overhead, most existing techniques to make neural nets smaller actually harm performance as they often transform dense into sparse matrix multiplications, which is inherently slower to execute on modern hardware \cite{something}.
+%I am still not super happy with the flow. Will work on it more.
 
+In this paper we present a new method to automatically tune the network size while training the model to drastically improve the inference performance with comparable quality to much larger networks  
+The key idea is to
+\emph{learn} the right network size at the same time that the network is
+learning the main task.
+For example, for an image classification task, with our approach we can provide the training data to a network---without sizing it a priori---and expect to end up with a network that has learned to classify images with an accuracy similar to much larger network architectures.
+Our approach has two main benefits. 
+First, in contrast to existing neural network compression techniques, such as brain damage, it results in small dense models, which helps to improve inference performances
+Second, and most surprisingly, the resulting models are often not only much smaller but also have better accuracy than much larger models.
+
+Old intro:
 When designing neural networks, one of the key parameters is the network size, i.e., 
@@
 %\gl{Should we rename the repository ?}
-}. We used used our implementation to evaluate two crucial aspects of
+}. We used our implementation to evaluate two crucial aspects of
 ShrinkNets, which we present next.

### 2018-02-08 paper/ICML/evaluate_performance.py
Add experiment results for CIFAR
- Also repare benchmarking for CIFAR

@@ -9,33 +9,67 @@ from glob import glob
 # Enable performance optimizations
 torch.backends.cudnn.benchmark = True
 
-def load_model(filename, dataset='cover'):
+configs = {
+    'COVER_FC': {
+        'warmup': 10,
+        'rep': 500,
+    },
+    'CIFAR10_VGG': {
+        'warmup': 1,
+        'rep': 10,
+        'large_batches': 64,
+    }
+}
+
+def load_model(filename, dataset):
     with open(filename, 'rb') as f:
         data = torch.load(f)
     best_entry =  get_best_entry(data[2].logs)
     model = data[1]['model']
-    if dataset == 'cover':
-        cfg = deepcopy(data[1])
+    cfg = deepcopy(data[1])
+    if dataset == 'COVER_FC':
         for i in range(cfg['params']['layers']):
             try:
                 cs = float(best_entry[best_entry.measure == 'size_%s' % (i + 1)].value)
                 cfg['params']['size_layer_%s' % (i + 1)] = int(cs)
             except:
                 pass # Keep the original size
+    elif dataset == 'CIFAR10_VGG':
+        sizes = []
+        i = 0
+        while True:
+            try:
+                cs = int(best_entry[best_entry.measure == 'size_%s' % (i + 1)].value)
+                sizes.append(cs)
+                i += 1
+            except:
+                break
+        classifier_sizes = sizes[-2:]
+        vgg_sizes = sizes[:-2]
+        for i, s in enumerate(vgg_sizes):
+            cfg['params']['size_%s' % (i + 1)] = s
+
+        cfg['params']['classifier_layer_1'] = classifier_sizes[0]
+        cfg['params']['classifier_layer_2'] = classifier_sizes[1]
+        del cfg['params']['factor']
+
+
 
     cfg['params']['dynamic'] = False # remove filters
     model = model(cfg['params'])
     return cfg, model
 
-def evaluate_model(cfg, model, hardware, batch_size):
+def evaluate_model(cfg, model, hardware, size, dataset):
+    batch_size = 1 if size == 'small' else configs[dataset]['large_batches']
     size = cfg['params']['input_features']
+    off = configs[dataset]['warmup']
+    rep = configs[dataset]['rep']
     data = Variable(torch.rand(*((batch_size,) + size)))
     if hardware == 'gpu':
[…]

### 2018-02-08 paper/ICML/models/VGG.py

@@ -30,11 +30,16 @@ class VGG(nn.Module):
 
         config = cfg[params['name']]
 
+        layer_id = 0
         for descriptor in config:
             if descriptor == 'M':
                 graph.add(nn.MaxPool2d, kernel_size=2, stride=2)
             else:
-                descriptor = int(descriptor * params['factor'])
+                try:
+                    descriptor = int(descriptor * params['factor'])
+                except:
+                    descriptor = params['size_%s' % (layer_id + 1)]
+                    layer_id += 1
                 graph.add(Conv2d, out_channels=descriptor,
                           kernel_size=3, padding=1)
                 if batch_norm:

### 2018-02-08 paper/ICML/evaluate_performance.py
Add support for evaluation of STATIC VGG

@@ -49,9 +49,12 @@ def load_model(filename, dataset):
         for i, s in enumerate(vgg_sizes):
             cfg['params']['size_%s' % (i + 1)] = s
 
-        cfg['params']['classifier_layer_1'] = classifier_sizes[0]
-        cfg['params']['classifier_layer_2'] = classifier_sizes[1]
-        del cfg['params']['factor']
+        try:
+            cfg['params']['classifier_layer_1'] = classifier_sizes[0]
+            cfg['params']['classifier_layer_2'] = classifier_sizes[1]
+            del cfg['params']['factor']
+        except:
+            pass # Keep the original values
 
 
 
@@ -100,4 +103,5 @@ def get_all_models(dataset, mode):
 if __name__ == '__main__':
     # get_all_models('COVER_FC', 'DYNAMIC')
     # get_all_models('COVER_FC', 'STATIC')
-    get_all_models('CIFAR10_VGG', 'DYNAMIC')
+    # get_all_models('CIFAR10_VGG', 'DYNAMIC')
+    get_all_models('CIFAR10_VGG', 'STATIC')

### 2018-02-08 paper/ICML/plot_random_search.py
Fix size calculation

@@ -5,14 +5,24 @@ from glob import glob
 from paper.ICML.models.VGG import cfg
 from algorithms.expectation_random_permutation import max_expectation
 
+def is_pareto_efficient(costs):
+     is_efficient = np.ones(costs.shape[0], dtype= bool)
+     for i, c in enumerate(costs):
+         if is_efficient[i]:
+             is_efficient[is_efficient] = np.any(costs[is_efficient]<=c, axis=1)
+     return is_efficient
+
+
 def load_files(prefix, mode):
-    files = glob('./experiments_results/random_search/%s_%s/*' % (prefix, mode))
+    files = glob('./experiments_results/random_search/%s_%s/*.pkl' % (prefix, mode))
+    print(len(files))
     result = []
     for file_name in files:
         try:
             with open(file_name, 'rb') as f:
                 result.append(torch.load(f))
-        except:
+        except Exception as e:
+            print('error', file_name)
             pass
     return result
 
@@ -22,6 +32,8 @@ def get_best_entry(logs):
 
 def get_final_measure(log, measure='test_acc'):
     x = get_best_entry(log)
+    if measure == 'epoch':
+        return int(x.epoch.iloc[0])
     if measure == 'time':
         return float(x.max().time)
     else:
@@ -30,19 +42,28 @@ def get_final_measure(log, measure='test_acc'):
 def generate_stats(infos):
     logs = infos[2].logs
     params = infos[1]['params']
-    return [
+    result = [
         get_final_measure(logs, 'test_acc'),
         compute_size(infos),
         get_final_measure(logs, 'val_acc'),
         get_final_measure(logs, 'train_acc'),
         get_final_measure(logs, 'time'),
+        get_final_measure(logs, 'epoch'),
         params['lambda'],
         params['batch_size'],
         params['learning_rate'],
         params['gamma'],
-        params['factor'],
-        params['weight_decay']
+        params['weight_decay'],
     ]
+    try:
+        result.append(params['factor'])
+    except:
+        pass
+    try:
+        result.append(params['layers'])
+    except:
+        pass
+    return result
 
 def compute_cost(seq, cl1, cl2):
     prev = 3
@@ -55,36 +76,67 @@ def compute_cost(seq, cl1, cl2):
     total += 10 * cl2
     return total
 
[…]

### 2018-02-08 paper/ICML/evaluate_performance.py
More sensible configs for evaluation

@@ -11,13 +11,28 @@ torch.backends.cudnn.benchmark = True
 
 configs = {
     'COVER_FC': {
-        'warmup': 10,
-        'rep': 500,
+        'cpu': {
+            'warmup': 50,
+            'rep': 500,
+            'large_batches': 512,
+        },
+        'gpu': {
+            'warmup': 1,
+            'rep': 100,
+            'large_batches': 4096,
+        }
     },
     'CIFAR10_VGG': {
-        'warmup': 1,
-        'rep': 10,
-        'large_batches': 64,
+        'cpu': {
+            'warmup': 1,
+            'rep': 10,
+            'large_batches': 64,
+        },
+        'gpu': {
+            'warmup': 1,
+            'rep': 100,
+            'large_batches': 1024,
+        }
     }
 }
 
@@ -63,10 +78,11 @@ def load_model(filename, dataset):
     return cfg, model
 
 def evaluate_model(cfg, model, hardware, size, dataset):
-    batch_size = 1 if size == 'small' else configs[dataset]['large_batches']
+    cd = configs[dataset][hardware]
+    batch_size = 1 if size == 'small' else cd['large_batches']
     size = cfg['params']['input_features']
-    off = configs[dataset]['warmup']
-    rep = configs[dataset]['rep']
+    off = cd['warmup']
+    rep = cd['rep']
     data = Variable(torch.rand(*((batch_size,) + size)))
     if hardware == 'gpu':
         model = model.cuda()
@@ -102,6 +118,6 @@ def get_all_models(dataset, mode):
 
 if __name__ == '__main__':
     # get_all_models('COVER_FC', 'DYNAMIC')
-    # get_all_models('COVER_FC', 'STATIC')
+    get_all_models('COVER_FC', 'STATIC')
     # get_all_models('CIFAR10_VGG', 'DYNAMIC')
     get_all_models('CIFAR10_VGG', 'STATIC')

### 2018-02-08 paper/ICML/evaluate_performance.py
First version of the final plots

@@ -3,7 +3,7 @@ import numpy as np
 from torch.autograd import Variable
 from copy import deepcopy
 from time import perf_counter
-from paper.ICML.plot_random_search import get_best_entry
+import paper
 from glob import glob
 
 # Enable performance optimizations
@@ -39,7 +39,7 @@ configs = {
 def load_model(filename, dataset):
     with open(filename, 'rb') as f:
         data = torch.load(f)
-    best_entry =  get_best_entry(data[2].logs)
+    best_entry =  paper.ICML.plot_random_search.get_best_entry(data[2].logs)
     model = data[1]['model']
     cfg = deepcopy(data[1])
     if dataset == 'COVER_FC':

### 2018-02-08 paper/ICML/plot_random_search.py

@@ -1,9 +1,42 @@
+from matplotlib import rc, use
+use('agg')
+rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
 import torch
+import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 from glob import glob
 from paper.ICML.models.VGG import cfg
 from algorithms.expectation_random_permutation import max_expectation
+configs = {
+    'COVER_FC': {
+        'ymin': 0.5,
+        'cpu': {
+            'warmup': 50,
+            'rep': 500,
+            'large_batches': 512,
+        },
+        'gpu': {
+            'warmup': 1,
+            'rep': 100,
+            'large_batches': 4096,
+        }
+    },
+    'CIFAR10_VGG': {
+        'ymin': 0.4,
+        'cpu': {
+            'warmup': 1,
+            'rep': 10,
+            'large_batches': 64,
+        },
+        'gpu': {
+            'warmup': 1,
+            'rep': 100,
+            'large_batches': 1024,
+        }
+    }
+}
 
 def is_pareto_efficient(costs):
      is_efficient = np.ones(costs.shape[0], dtype= bool)
@@ -14,16 +47,21 @@ def is_pareto_efficient(costs):
 
 
 def load_files(prefix, mode):
+    with open('./experiments_results/%s_%s_benchmark.pkl' % (prefix, mode), 'rb') as f:
+        benchmark = torch.load(f)
+        benchmark = {k[0]: k[1:] for k in benchmark}
     files = glob('./experiments_results/random_search/%s_%s/*.pkl' % (prefix, mode))
-    print(len(files))
     result = []
+    errors = 0
     for file_name in files:
+        id = file_name.split('/')[-1].replace('.pkl', '')
         try:
             with open(file_name, 'rb') as f:
-                result.append(torch.load(f))
-        except Exception as e:
-            print('error', file_name)
+                result.append(torch.load(f) + (benchmark[id],))
+        except:
+            errors += 1
             pass
+    print(errors)
     return result
 
 def get_best_entry(logs):
@@ -54,6 +92,7 @@ def generate_stats(infos):
[…]

### 2018-02-08 paper/ICML/introduction.tex
edits to intro

--- 2018-02-05 paper/ICML/introduction.tex
@@
+%!TEX root=paper.tex
+
 \section{Introduction}
 
-\subsection{ShrinkNets}
+One of the key defactors that affects neural net perforamnce is  is the {\it shape} of the network, 
+i.e., the number of layers, the number of neurons per layer, and the connections between
+layers.
+An {\it under-sized} network, with too few neurons or layers,
+ is likely to have low accuracy because of insufficient 
+capacity while an {\it over-sized} network is slow to train due to additional 
+parameters and is computationally inefficient at both training and inference time.
+% A sub-optimal network shape can lead to low accuracy .
+%Although the hyperparameters related wo network size can dramatically affect
+% performance, there is no reliable way to efficiently set them.
+Consequently, many {\it hyperparameter optimization} techniques have been proposed to determine the optimal size of
+a neural network; these include random search~\cite{paper-on-random-is-good-enough}, 
+what-is-this-paper~\cite{Bengio2012a}, 
+meta-gradient descent~\cite{Pedregosa2016},
+Gaussian processes~\cite{Bergstra2011a}, and many others.
+\srm{Are we really sure that no other techniques optimize the network size during training like we do?  Don't we also require 
+iterating over lambda?  Is this really the key contribution of our work, that it reduces model search time?  Isn't the key point that
+we find smaller, better models?}
+These existing techniques all require a compute-intensive search of 
+model space,  often training of tens or hundreds of models.
+As a result, tuning these techniques require times 
+longer (or many times more computational power) 
+than the time take for a single training run.
 
-\subsection{Motivation}
+In this paper we present a novel method to automatically find an appropriate
+network size, which drastically reduces optimization time. \srm{In comparison to previous search models?}
+The key idea is to learn the network size while optimizing the primary objective function.
+Our strategy, called \textbf{ShrinkNets}, is blah blah \mpv{Short blurb about the technique}
+% For example, for an image classification task, with our approach we can 
+% provide the training data to a network—without sizing it a priori—and expect 
+% to end up with a network that has learned to classify images with an accuracy
+% similar to a the best manually engineered network. 
+Our approach has two main benefits. 
+First, we no longer need to choose a network size before training.
+We simply set an initial size for the network and then the algorithm will
+determine the best network that is smaller or equal in size to the inital size.
+Second, this optimization is done during a {\it single} training run, as opposed to the large number of training runs
+required by existing hyperparameter optimization 
+techniques.  As a result, we can find the best model 
+faster as well as with less computational overhead.
+
+In summary, our contributions are as follows: 
+\begin{itemize}
+\item we propose a novel technique based on dynamically swiching on and off neurons, 
+which allows us to optimize the network size as the network is trained. 
+\item we show that our technique is a relaxation\mpv{?} of group sparsity and 
+prove \mpv{fill in}. 
+\item \srm{Some claim about model size vs performance}
+\item we demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
+showing that 
+ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
+training time compared to existing hyperparameter optimization methods.
+\item we also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
+of neurons.
+\item \srm{Some claim about inference time?}
+\item \srm{Some claim about compatibility with existing compression techniques?}
+\end{itemize}

### 2018-02-08 paper/ICML/introduction.tex
edits

@@
 In summary, our contributions are as follows: 
-\begin{itemize}
-\item we propose a novel technique based on dynamically swiching on and off neurons, 
+\begin{compactenum}
+\item We propose a novel technique based on dynamically swiching on and off neurons, 
 which allows us to optimize the network size as the network is trained. 
-\item we show that our technique is a relaxation\mpv{?} of group sparsity and 
+\item We show that our technique is a relaxation\mpv{?} of group sparsity and 
 prove \mpv{fill in}. 
 \item \srm{Some claim about model size vs performance}
-\item we demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
+\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
 showing that 
@@
 training time compared to existing hyperparameter optimization methods.
-\item we also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
+\item We also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
 of neurons.
@@
 \item \srm{Some claim about compatibility with existing compression techniques?}
-\end{itemize}
+\end{compactenum}

### 2018-02-08 paper/ICML/introduction.tex
Update introduction.tex
Alternative intro

@@
 \section{Introduction}
+{\bf Alternative intro sketch:}
+As neural networks become commodity in many applications from improving camera quality on mobile phones \cite{googleapple} over language translation \cite{languagetranslation} to text auto-complete \cite{autocomplete}, inference performance and model size become equally important to the quality of the prediction.
+Surprisingly, today those three concerns, quality, performance and model size, are largely handled separately with suboptimal results. 
+That is, models are trained with a fixed architecture (e.g., considering a certain size and performance budget), but then during the training the network architecture is considered fixed and does not further improve.
+This is especially problematic for complex networks architectures such as CNNs where the search space of potentially network architectures is so big, that it is unfeasible to try all possible combinations.
 
+In contrast, recently proposed techniques to make neural nets smaller \cite{something1,something2} allow to start from a network architecture which is known to be perform well, but do not focus on the inference performance and often have a negative impact on the model quality.
+In fact, besides universal applicable techniques such as quantitazation \cite{quant} and compiling neural networks to binary code to avoid unneccassary overhead, most existing techniques to make neural nets smaller actually harm performance as they often transform dense into sparse matrix multiplications, which is inherently slower to execute on modern hardware \cite{something}.
+%I am still not super happy with the flow. Will work on it more.
+
+In this paper we present a new method to automatically tune the network size while training the model to drastically improve the inference performance with comparable quality to much larger networks  
+The key idea is to \emph{learn} the right network size at the same time that the network is learning the main task. 
+For example, for an image classification task we can start with a well-known model architecture and shrink it while training the model  to end up with a much smaller network that has learned to classify images with an accuracy similar to larger network architectures.
+Our approach has two main benefits. 
+First, in contrast to existing neural network compression techniques, such as brain damage, it results in small dense models, which helps to improve inference performances
+Second, we avoid the exhaustive and expensive model search to find a smaller network architecture with good accuracy.
+
+{\bf Old introduction:}
 One of the key defactors that affects neural net perforamnce is  is the {\it shape} of the network, 

### 2018-02-08 paper/ICML/approach.tex
First pass on section 2

@@
 
-\begin{itemize}
-  \item Assign an on/off switch to each neuron. But this is np-hard, so we
-  consider a relaxation
-  \item Formulation
-  \item Relationship to group sparsity
-  \item Strategies to kill neurons (relation to theory above?)
-  \item Implementation details
-\end{itemize}
+from the universality theorem, we know that we can find a network that ca
+arbitrarly fit a function. Therefore, for a given error tolreance there exists
+an optimal size to solve a given problem.
 
-Our approach has two main challenges. First, we need a way to
-dynamically size the network during training. Second, we need a
-loss function that optimizes for the additional task of sizing, without
-deteriorating the learning performance of the main task. Our
-approach, called ShrinkNets, copes with both challenges.
+If we have an oversized network then there exist a pruned version that can still
+achieve our goal. The main idea is to consider an on/off switch for each neuron,
+and we want to find an assignement for this switches that achieve a certain
+size/accuracy tradeof. We model these on/off switches by multiplying each input
+(or output) of each layer by a number $0$ or $1$. $0$ will deactivate the
+neuron, $1$ will let the signal go through. We want to minimize the number of on
+switches to reduce the model size as much as we can. This can be modeled solved
+by jointly minimizing the objective of the network and a factor of the L0 norm
+of the vector containing all the on/off switches.
 
-During training, our approach starts
-with an explicitly over-sized network. As training progresses, we learn
-which neurons are not contributing to learning and remove them
-dynamically, effectively shrinking the network. This method requires two key components: first, we need a way to identify neurons that are not contributing to the
-learning process, and second we need a way to balance the network size and the
-generalization capability for the main task. We introduce a new \textsf{Filter} 
-\mpv{Choose a different name if possible bc this can be confused w/convolutional
-filters. Maybe Shrinkage layer?} 
-layer that takes care of \emph{deactivating} neurons. We also modify
-existing loss functions to incorporate a new term that takes care of balancing
-network size and generalization capability appropriately.
+Finding an optimal binary assignement is an NP-Hard problem (\textbf{Should we
+prove this ? I think it should be fairly doable reducing it to 3-SAT
+considering the structure of neural networks}). We decide to relax this
+problem because this is what people usually do with NP-Hard problem. Our
+relaxation is we allow $\bm{\theta}$ to be a real number instead of a boolean We
+also use L1 instead of L1. This way we obtain a non-convex, but at least
+differentiable (almost everywhere).
 
-\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are usually placed after
+This approach assumes that we start with an upper bound on the model size. This
+obviously translates in a computational overhead. Our insight is that some
+usless neurons (we have multiple definitions below) can be removed early without
+impacting the final solution. It has two practical implications: It mitigate the
+issue we describe but it also allows other neurons to adapt as soon as one of
+their peer is killed. Existing technique usually remove them after convergence
+and require an extra fine-tuning process to compensate for the removal.
+
+The key components of the system are: The filter vectors that simulate the
+continuous on/off switches, a regularization that tries to kill neurons, the
+neuron removal strategy that detects neurons that should probably be removed,
+and the garbage collection that effectively remove dead neurons from the model,
+and the simplifaction procedure that remove the filter vector for fast
+inference.
+
+We will describe these components in the upcoming sections.
+
+\subsection{Notations}
+
+\par In order to avoid any potential ambiguity, in this section we will
+describe in details the mathematical notations used in this article. Non-bold
+letters represent scalar values, while bold lowercase and upper case
+repectively denote vectors and matrices. $\bm{A}^T$ stands for the transpose of
+the matrix $\bm{A}$. Subscripts are used to index particular elements of
+vectors and matrices. $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
+$\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
+the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
+component of the $i^{th}$ row of $\bm{A}$. All the following definitions assume
+$\bm{A}$ to be an $n\times p$ matrix.  For any vetor $\bm{b}$ with $n$
+components, we define $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
+1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.  For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
+\left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$.
+For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function.
+The only constraint that we want to enforce is that $a(0) = 0$.
+We use $\intint{u, v}$ to denote inteveral of integers, $\bm{0}$ is the null vector (size depending on the context).
+$\#S$ is meant to represent the cardinality of a set $S$.
+To simplify the notation of function composition we use the following operator: $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
+
+\subsection{The Switch Layer}
+
+\textbf{Do you like the name of the layer ?}
+
+Switch layers have weights in the range $[-\infty,+\infty]$ and are usually placed after
 linear and convolutional layers.
-The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
+The \textit{Switch Layer} takes an input of size $\left(B \times C \times D_1
   \times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number
@@
 a parameter $\theta \in \mathbb{R}^C$. The output is defined as follows: \vspace{-1em}
-\begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
-Where $\circ$ is the pointwise multiplication, and $\theta$ is expanded in all
+\begin{equation} Switch(\bm{I};\bm{\theta}) = \diag{\bm{\theta}} \bm{I}  \end{equation}
+Where $\theta$ is expanded in all
 dimensions to match the input size (except the second one since they are equal
@@
 the $k^{\text{th}}$ input feature/channel is multiplied by zero and have no
-influence on the output. If this happens, we say the Filter layer deactivates
+influence on the output. If this happens, we say the Switch layer deactivates
 the neuron. These disabled neurons/channels can be removed from the network
 without changing its output. Before explaining how that is achieved, we explain
-next how the weights of the Filter Layer are initialized and adjusted during
+next how the weights of the Switch Layer are initialized and adjusted during
 training.
 
-\textbf{Training Procedure: } Once Filter layers are placed in a network and initialized (sampled from the Uniform$[0, 1]$ distribution),
+\subsection{Training Procedure} Once Switch layers are placed in a network and
+initialized (sampled from the $\mathcal{N}(0, 1)$ distribution),
 %To train networks we need start with a substantially oversized network, then we
-%insert \textit{Filter Layers}  (usually after every linear or convolutional
+%insert \textit{Switch Layers}  (usually after every linear or convolutional
 %layer except the last one) and we sample their weight from the
@@
 performance. We achieve that by introducing sparsity in the parameters of the
-\textit{Filter Layers}, thus forcing the deactivation of neurons%. Indeed, having a negative component in the $\theta$
+\textit{Switch Layers}, thus forcing the deactivation of neurons%. Indeed, having a negative component in the $\theta$
 %parameter of the filter layer permamently disable its associated feature
@@
 . To obtain this sparsity, we simply redefine the loss function:
-\vspace{-.5em}
 \begin{equation}
-  L'(x,y;\theta) = L(x, y) + \lambda|\max(0, \theta)|
+  L'(\bm{x},\bm{y};\bm{W}, \bm{\theta}) = L(\bm{x}, \bm{y}; \bm{W}) +
+  \lambda\norm{\theta}_1 + \lambda_2\norm{\bm{W}}_p
 \end{equation}
@@
 with a value of $0$ or less correspond to dead neurons, $\lambda$ effectively
-controls the number of neurons/channels in the entire network. We introduced
-the $\max(\dots)$ into the loss to make sure that neurons are permamently disabled
-when performing gradient descent based optimization. Next, we
-explain how to implement ShrinkNets efficiently.
+controls the number of neurons/channels in the entire network. Without the last
+term our problem sounds very similar to the Group Sparsity regularization which
+is well known in the area of linear and logistic regressions. In the next
+section we will try to undercover the relationship between these two problems,
+explain why we need this additional regularization term and what should be the
+value of $p$.
 
-\subsection{Strategies to Remove Neurons}
+\input{theory}
 
-\textbf{Implementation}
+\subsection{Speeding up training}
+
+In order to have a practical implementation of ShrinkNets it is absolutely
+necessary to prune useless neurons as quick as possible. In order to try more
+different strategies we split this task in two subproblems: detecting
+potentially non-crucial neurons and setting their corresponding entry in the
+switch layer to exactly 0, and neural garbage collection that
+
+\subsubsection{Neuron killing}
+\textbf{Threshold strategy} \\ We kill neurons based on a threshold (in absolute
+value), this is the method used by deep compression. It is bad because it is
+scale dependant and is not robust to noise in the gradients (explain that)
+\textbf{Sign change strategy} \\ We look at when the sign change. This is also
+sensitive to noise but has the advantage
+\textbf{Sign variance strategy}
+
+In our library we implemented a variant of the second strategy and the last one.
+
+\subsubsection{Neural garbage collection}
+
 It is possible to reduce the overhead of the training process by removing
@@
 and edges are event-hubs responsible for propagating information about disabled
-neurons to the relevant layers.
+neurons to the relevant layers. As soon as a layer receive an event, it updates
+his parameters to reflect the new size. Each operation is stored in a log that
+is used later to update other component of the system. For example some
+optimizers like Adam [Ref] store state about each parameter, their state needs
+to be updated the exact same way and at the exact same time as layers in order
+to obtain apropriate parameter updates.
+
+\subsection{Speeding up Inference}
+
+The sole puropose of \textit{Switch Layer} are to detect which neurons should be
+killed and which should be left. When the training is over we will never remove
+more neurons. Therefore, they loose all their interest at inference time. To
+improve size and inference time we propose the following method to get rid of
+them without changing the output of the model (modulo floating point errors).
+The basic idea is to start from every \textit{Switch Layer} and try to find the
+nearset linear operator (child or parent) and multiply its weights by the values
+in the switch layer. For example we can merge Filter layers with surrounding
+Convolutional layer, Linear layer or even BatchNormalization [ref] if they are
+before the \textit{Switch Layer}. However we need to be extremely careful not to
+cross a non-linearity otherwise it would change the output of network.

### 2018-02-08 paper/ICML/evaluation.tex
First version of the final plots
Start evaluation section and add a few lines to sec 2

--- 2018-02-05 paper/ICML/evaluation.tex
@@
 \section{Evaluation}
+
+\subsection{Core evaluation (CHANGE\_MY\_NAME)}
+
+To show the versatility of our aproach we evaluate both on two very different
+scenario
+
+\subsubsection{\texttt{CIFAR10} dataset}
+
+\gl{Cite and describe the dataset}
+
+To solve this task we use the \texttt{VGG16} model [ref]. It is constituted of
+alternating convolutional layers and \textit{MaxPool} layers interleaved by
+\textit{BatchNorm} [ref] and \textit{ReLU} [ref] layers. The two last layers are
+Fully connected layers separated by just a \textit{ReLU} activation function.
+
+To turn it into a ShrinkNet we introduce \textit{Switch Layers} after each
+\textit{BatchNorm} and each Fully connected (except the last one).
+
+ShrinkNets assume that the starting size of the network is an upper bound on the
+optimal size. We though that picking two times the recommended size for each
+layer (that was designed for ImageNet[ref]), is a generous upper bound. For the
+classification layers we use $5000$ neurons as an upper bound where the ImageNet
+version uses $4096$ \gl{This is on the top of my head, need to be double checked}.
+
+We assume no prior knowledge on the optimal batch size, learning rate,
+$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
+from a range of reasonable values (\gl{should we make them explicit ?}).
+For each of the models we trained, we pick the epoch with the best validation
+accuracy and report the corresponding testing accuracy. For each model, we also
+measure the total size, in number of floating point parameters, excluding the
+\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
+get rid of them when training is done.
+
+We want to compare against classical (\textit{Static}) networks. The number of
+parameters that control the size is large: 13 for the size of convolutional
+layers and $2$ for the fully connected ones. Without Shrinknets to help and fuse
+all these parameters in a single $\lambda$ it is infeasible to sample reasonably
+well a search space of that size. This is why we have to rely on the very well
+known heuristic that the original VGG architecture (and many CNNs) \gl{try to
+  find the paper that introduces this heuristic}. For \textit{Static Networks}
+we sample the size between $0.1$ and $2$ times the size optimized for ImageNet.
+We report the same numbers as we did for \textit{ShrinkNets} and we compare the
+two distributions of models we obtain on the first plot of \cref{figure_CIFAR10}.
+
+\subsubsection{\texttt{COVERTYPE} dataset}
+
+We followed the same procedure 
+\gl{Cite and describe the dataset}
+
+We try to fit
+
+\subsection{Benefits of smaller sizes}
+
+We showed in the previous section that \textit{ShrinkNets} were able to find
+more or at least as efficient as \textit{Static Networks}. In this experiment we
+want to determine the perf
 
@@
 
-We will start evaluating ShrinkNets with the simplest problems possible: linear
-and logistic regression. As we showed, Group sparsity share similarities with
-our method, this is why we will use it as baseline. We decided to focus on
-multi-target linear regression because in the single target case, groups in the
-Group Sparsity problem would have a size of one ($\bm{A}$ would be a vector in this
-case).
+As we showed, Group sparsity share similarities with our method, and we claim
+that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
+to compare the two aproaches.  We decided to focus on multi-target linear
+regression because in the single target case, groups in the Group Sparsity
+problem would have a size of one ($\bm{A}$ would be a vector in this case).
 
@@
 For each dataset we fit with different regularization parameters and measure
-the error and sparsity obtained after convergence. In this context we define sparsity as the ratio of columns that have all their weight under $10^{-3}$ in absolute value. Parameters were choosed in
-order to obtain the widest sparsity spectrum. Loss is normalized depending on the problem to be in the $[0, 1]$ range. We summarized the results in
-\cref{sparsity_accuracy}.
-From our experiments it is clear that ShrinkNets can fit the data closer than Group Sparsity for the same amount of sparsity.
-The fact that we are able to reach very low loss demonstrate that even if our objective function is non convex, in practice it works as good or better as convex alternatives.
-Details about these datasets and the parameters used
-are available in \cref{linear_datasets}.
+the error and sparsity obtained after convergence. In this context we define
+sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
+absolute value. Regularization parameters were choosed in order to obtain the
+widest sparsity spectrum. Loss is normalized depending on the problem to be in
+the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
+our experiments it is clear that ShrinkNets can fit the data closer than Group
+Sparsity for the same amount of sparsity. The fact that we are able to reach
+very low loss demonstrate that even if our objective function is non convex, in
+practice it works as good or better as convex alternatives. Details about these
+datasets and the parameters used are available in \cref{linear_datasets}.
 
@@
 
-\subsection{Convergence and training dynamics of Neural networks}
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary}
+\vspace*{-5mm}
+\caption{\label{figure_CIFAR10} Summary of the result of random
+search over the hyper-parameters the \texttt{CIFAR10} dataset}
+\end{center}
+\vspace*{-4mm}
+\end{figure}
 
-\subsection{Hyper-optimization of ShrinkNets}
-
-\subsection{Performance}
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{COVER_FC_summary}
+\vspace*{-5mm}
+\caption{COVER}
+\end{center}
+\vspace*{-4mm}
+\end{figure}
 

### 2018-02-09 paper/ICML/evaluation.tex
First part of the draft of the evaluation

@@
 
-\subsection{Core evaluation (CHANGE\_MY\_NAME)}
+The goal of our evaluation is to show two main properties of
+\textit{ShrinkNets}: they are exploring the space of possible sizes in a "smart"
+way, and that as a result we obtain the smaller or equal size than
+\textit{Static Networks}. We will then evaluate the performance benefits implied
+by these gains in size.
 
-To show the versatility of our aproach we evaluate both on two very different
-scenario
+\subsection{Datasets and Setup}
 
-\subsubsection{\texttt{CIFAR10} dataset}
+\subsubsection{\texttt{CIFAR10}}
 
-\gl{Cite and describe the dataset}
+Previous attempt at solving this problem focus on simple datasets and simple
+architectures (limited to Fully connected). We believe that self-resizing
+network really matter for problems where the architecture you need to solve them
+involve so many layers that it is impractical to explore the space of possible
+sizes. We considered ImageNet but the time required to train models is so long
+that it would have not been possible to train enough and get statistically
+significant results. This is why we picked \texttt{CIFAR10} [ref]. It is an
+image classification dataset containing $60000$ color images $(3 \times 32
+\times 32)$, belonging to $10$ different classes.
 
@@
 from a range of reasonable values (\gl{should we make them explicit ?}).
+Training is done using our library, based on \texttt{PyTorch} [ref], that
+support dynamically resized layers. We train the network using gradient descent
+and \textit{Adam} optimizer [ref]. We start with the learning rate sampled
+randomly and every $5$ epochs of non improvement in validation accuracy we
+divide the learning rate by $10$. We stop training after $400$ epochs or when
+the learning rate is under $10^{-7}$ whichever comes first. \gl{Should I also
+  give the details about the removal strategy we used and the $\gamma$ and
+  threshold I used ? because this is clearly getting boring}
 For each of the models we trained, we pick the epoch with the best validation
@@
 
-We followed the same procedure 
-\gl{Cite and describe the dataset}
+Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. \gl{TODO
+  rephrase the description taken from the UCI website} We picked
+this one for couple of reasons. First it is simply enough that we can reach good
+accuracy with small models. This important because we want to show that
+\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
+are sampling the entire space of possible sizes. The second reason is that [ref]
+are also doing their evaluation on this dataset, which allow us to compare the
+results obtained by the two methods.
 
-We try to fit
+The only difference in terms of setup are minimal. We use the same architecture
+as [ref], i.e. three layers Fully Connected neural network with  no
+\textit{Dropout} [ref] nor \textit{BatchNorm} [ref]. \gl{Should we say here that we
+  don't expect Dropout to work here ? I could write an entire paragraph about it
+  if needed}. In this case for the \textit{Static Networks}, we sample
+independently sizes of the three different layers to explore all possible
+architectures.
+
+\gl{Todo for me: explain how I select the best epoch to get rid of the outliers}
+
+\subsection{Intepretation of the result of random search}
+
+\gl{TODO draw conclusions from the plots}:
+\begin{itemize}
+  \item Pareto frontier better or as good, even when we sample the entire search
+    space
+  \item Static NEts are much more spread in terms of size for a given accuracy
+    while shrinknets are smarter and always lie close to the frontier (I am
+    changing the way I select the best epoch so the outliers in the COVER
+    dataset will go away in the next version of the plot)
+  \item We reach as good or better accuracies than normal networks
+\end{itemize}
 
@@
 more or at least as efficient as \textit{Static Networks}. In this experiment we
-want to determine the perf
+want to determine benefits of the smaller size we get.
+
+For some applications, the absolute best accuracy is not something desirable if
+it implies having enormous models. This observation motivates our methodology:
+for a given target accuracy that you want your model to achieve, we pick the
+smallest that satisfy the constraint. For both \textit{ShrinkNets} and
+\textit{Static Networks} we measure multiple metrics and compute the ratio
+between the two. The metrics are interested in are: the final model size (in
+number of parameters) and inference speed on CPU and GPU for small batch sizes
+($1$ input) and large batch sizes (depend on the dataset and hardware).
 

### 2018-02-09 paper/ICML/introduction.tex
sam pass

--- 2018-02-08 paper/ICML/introduction.tex
@@
 
-One of the key defactors that affects neural net perforamnce is  is the {\it shape} of the network, 
-i.e., the number of layers, the number of neurons per layer, and the connections between
-layers.
-An {\it under-sized} network, with too few neurons or layers,
- is likely to have low accuracy because of insufficient 
-capacity while an {\it over-sized} network is slow to train due to additional 
-parameters and is computationally inefficient at both training and inference time.
-% A sub-optimal network shape can lead to low accuracy .
-%Although the hyperparameters related wo network size can dramatically affect
-% performance, there is no reliable way to efficiently set them.
-Consequently, many {\it hyperparameter optimization} techniques have been proposed to determine the optimal size of
-a neural network; these include random search~\cite{paper-on-random-is-good-enough}, 
-what-is-this-paper~\cite{Bengio2012a}, 
-meta-gradient descent~\cite{Pedregosa2016},
-Gaussian processes~\cite{Bergstra2011a}, and many others.
-\srm{Are we really sure that no other techniques optimize the network size during training like we do?  Don't we also require 
-iterating over lambda?  Is this really the key contribution of our work, that it reduces model search time?  Isn't the key point that
-we find smaller, better models?}
-These existing techniques all require a compute-intensive search of 
-model space,  often training of tens or hundreds of models.
-As a result, tuning these techniques require times 
-longer (or many times more computational power) 
-than the time take for a single training run.
+As neural networks become increasingly widely deployed in a variety of
+applications  -- ranging from improving camera quality on mobile phones
+\cite{googleapple} to language translation \cite{languagetranslation} to text
+auto-completion \cite{autocomplete} -- and on diverse hardware architectures
+-- from laptops to phones to embedded sensors --  inference performance and
+model size are becoming equally as important as  traditional measures of
+prediction quality. However, these three aspect of model performance --
+quality, performance and size -- are largely optimized separately today, often
+with suboptimal results.
 
-In this paper we present a novel method to automatically find an appropriate
-network size, which drastically reduces optimization time. \srm{In comparison to previous search models?}
-The key idea is to learn the network size while optimizing the primary objective function.
-Our strategy, called \textbf{ShrinkNets}, is blah blah \mpv{Short blurb about the technique}
-% For example, for an image classification task, with our approach we can 
-% provide the training data to a network—without sizing it a priori—and expect 
-% to end up with a network that has learned to classify images with an accuracy
-% similar to a the best manually engineered network. 
-Our approach has two main benefits. 
-First, we no longer need to choose a network size before training.
-We simply set an initial size for the network and then the algorithm will
-determine the best network that is smaller or equal in size to the inital size.
-Second, this optimization is done during a {\it single} training run, as opposed to the large number of training runs
-required by existing hyperparameter optimization 
-techniques.  As a result, we can find the best model 
-faster as well as with less computational overhead.
+Of course, the problem of finding compressed or small networks is not new.
+Existing techniques typically aim make a pre-trained neural network smaller
+\cite{something1,something2} by taking one of two approaches:  either by
+applying quantitazation \cite{quant} or code compilation~\cite{something}
+techniques that can be applied blindly to any network, or they analyze the
+structure of the network and systematically prune
+connections~\cite{han2015deepcompression,brain-damage} or neurons~\cite{XXX}
+based on some loss function.  Although these techniques can substantially
+reduce model size, they have several drawbacks.  First, they often negatively
+impact model quality.  Second, they can (surprisingly) negatively impact
+inference time as they transform dense matrix operations into sparse ones,
+which can be substantially slower to execute on modern hardware
+\cite{something}, especially GPUs which do not efficiently support sparse
+linear algebra.  Third, these techniques generally start by optimizing
+particular architecture for prediction performance, and then, as a post-
+processing step, apply compression  to generate a smaller model that meets the
+resource constraints of the   deployment setting.  Because the network
+architecture is essentially fixed during compression,   model architectures
+that work better in small settings may be missed -- this is especially true in
+large networks like many- layered CNNs,  where it is infeasible to try explore
+even a small fraction of possible network configurations.
+
+%I am still not super happy with the flow. Will work on it more.
+
+In contrast, in this paper we present a new method to simultaneously optimize
+both network size and model performance. The key idea is to learn the right
+network size at the same time that we optimize for prediction performance. Our
+approach, called {\it ShrinkNets}, starts with an {\it oversized} network, and
+dynamically shrinks it by eliminating neurons during training time.  Our
+approach has two main benefits.  First, we explore the architecture of models
+that are both small and perform well, rather than starting with a high-
+performance model and making it small.  This allows us to efficiently generate
+a family of smaller and accurate models without an exhaustive and expensive
+hyperparameter search over the number of neurons in each layer. Second, in
+contrast to existing neural network compression techniques~\cite{brain-
+damage,han2015deepcompression}, our approach results in models that are both
+not only small, but where the  layers are dense, which means that inference
+time is also improved, e.g., on GPUs.
+
+% {\bf Old introduction:}
+% One of the key defactors that affects neural net perforamnce is  is the {\it shape} of the network, 
+% i.e., the number of layers, the number of neurons per layer, and the connections between
+% layers.
+% An {\it under-sized} network, with too few neurons or layers,
+%  is likely to have low accuracy because of insufficient 
+% capacity while an {\it over-sized} network is slow to train due to additional 
+% parameters and is computationally inefficient at both training and inference time.
+% % A sub-optimal network shape can lead to low accuracy .
+% %Although the hyperparameters related wo network size can dramatically affect
+% % performance, there is no reliable way to efficiently set them.
+% Consequently, many {\it hyperparameter optimization} techniques have been proposed to determine the optimal size of
+% a neural network; these include random search~\cite{paper-on-random-is-good-enough}, 
+% what-is-this-paper~\cite{Bengio2012a}, 
+% meta-gradient descent~\cite{Pedregosa2016},
+% Gaussian processes~\cite{Bergstra2011a}, and many others.
+% \srm{Are we really sure that no other techniques optimize the network size during training like we do?  Don't we also require 
+% iterating over lambda?  Is this really the key contribution of our work, that it reduces model search time?  Isn't the key point that
+% we find smaller, better models?}
+% These existing techniques all require a compute-intensive search of 
+% model space,  often training of tens or hundreds of models.
+% As a result, tuning these techniques require times 
+% longer (or many times more computational power) 
+% than the time take for a single training run.
+
+% In this paper we present a novel method to automatically find an appropriate
+% network size, which drastically reduces optimization time. \srm{In comparison to previous search models?}
+% The key idea is to learn the network size while optimizing the primary objective function.
+% Our strategy, called \textbf{ShrinkNets}, is blah blah \mpv{Short blurb about the technique}
+% % For example, for an image classification task, with our approach we can 
+% % provide the training data to a network—without sizing it a priori—and expect 
+% % to end up with a network that has learned to classify images with an accuracy
+% % similar to a the best manually engineered network. 
+% Our approach has two main benefits. 
+% First, we no longer need to choose a network size before training.
+% We simply set an initial size for the network and then the algorithm will
+% determine the best network that is smaller or equal in size to the inital size.
+% Second, this optimization is done during a {\it single} training run, as opposed to the large number of training runs
+% required by existing hyperparameter optimization 
+% techniques.  As a result, we can find the best model 
+% faster as well as with less computational overhead.
 
@@
 \begin{compactenum}
-\item We propose a novel technique based on dynamically swiching on and off neurons, 
+\item We propose a novel technique based on dynamically switching on and off neurons, 
 which allows us to optimize the network size as the network is trained. 
@@
 of neurons.
-\item \srm{Some claim about inference time?}
+\item \srn{Something about dense networks and then benefit over optimal brain damage}
+\item \srm{Some claim about inference time}
 \item \srm{Some claim about compatibility with existing compression techniques?}

### 2018-02-09 paper/ICML/evaluation.tex
Continue work on eval section

@@
 number of parameters) and inference speed on CPU and GPU for small batch sizes
-($1$ input) and large batch sizes (depend on the dataset and hardware).
+($1$ input) and large batch sizes (depend on the dataset and hardware). Results
+are shown on \cref{figure_CIFAR10} and \cref{figure_COVER} after the
+distribution of sizes and accuracy. We limit our plot to the ($80-100\%$
+accuracy range because we consider that models with lower accuracy have less
+practical use).
+
+Regarding size, the key observation we can make is that size improvenets are
+significant for
 
@@
 
-\textbf{TODO: Interpret the results}
 \begin{figure}
@@
 \vspace*{-5mm}
-\caption{COVER}
+\caption{\label{figure_COVER} Summary of the result of random
+search over the hyper-parameters the \texttt{COVERTYPE} dataset}
 \end{center}
@@
 
-\section{Speeding up training with pruning}
+\section{Architectures obtained after convergence}
+
+We sucessfully demonstrated that the architecture \textit{Shrinknets} converge
+to make sense both in term of size and performance. And for a given accuracy the
+size needed is significantly smaller than when we use the classic heursitc we
+commonly use to size convolutional neural networks. It might be an indication
+that this strategy is suboptimal and might need to be adjusted. During our
+experimentations on simpler datasets like \texttt{MNIST} and
+\texttt{FashionMNIST} we observed that even if they have the same number of
+classes, input features, and output distribution. For a fixed $\lambda$
+\textit{ShrinkNets} converged to considerably bigger networks in the case of
+\texttt{FashionMNIST}.
+take a look closer to the architectures \textit{ShrinkNets} converge to

### 2018-02-09 paper/ICML/appendix.tex

\section{Appendix}
\subsection{Proofs}
Unless specified, all the proofs consider the Multi-Target linear regression problem
\begin{proposition}
\label{gps_equivalence}
  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$

  \begin{align*}
    & \min_{\bf{A}} \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
     = &\min_{\bf{A'}, \bm{\beta}} \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1 \\
     & \text{s.t.} \forall j \in \intint{1, p}, \norm{\left(A'^T\right)_j}_2^2 = 1
  \end{align*}
\end{proposition}

\begin{proof}
  In order to prove this statement we will show that for any solution $\bm{A}$ in the first problem, there exists a solution in the second with the exact same value, and vice-versa.
We now assume we have a potential solution $\bm{A}$ for the first problem and we define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$. It is easy to see that the constraint on $\bm{A}'$ is statisfied by construction. Now:
  \begin{align*}
    & \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A'^T\right)_j\beta_j}_2 \\
    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \abs{\beta_j} \cdot 1\\
    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
  \end{align*}
  Assuming we take an $\bm{A}'$ that satisfy the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$. We can apply the same operations in reverse order and obtain an instance of the first problem with the same value. We can now see that the two problems must have the same minimum otherwise we would be able to construct a solution to the other with exact same value.
\end{proof}

\begin{proposition}
\label{unconstrained_non_convex}
\begin{equation*}
     \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2
\end{equation*}
is not convex in $\bm{A}$ and $\bm{\beta}$.
\begin{proof}
  To prove this we will take the simplest instance of the problem: with only scalars. We have $f(a, \beta) = \left(y - a\beta x\right)^2$. For simplicty let's take $y = $ and $x > 0$. If we take two candidates $s_1 = (0, 2)$ and $s_2 = (2, 0)$, we have $f(s_1) = f(s_2) = 0$. However $f(\frac{2}{2}, \frac{2}{2}) = x > \frac{1}{2} f(0, 2) + \frac{1}{2}f(2, 0)$, which break the convexity property. Since we showed that a particular case of the problem is non-convex then necessarly the general cannot be convex.
\end{proof}
\end{proposition}

\begin{proposition}
\label{unconstrained_shrinknet_no_min}
\begin{equation*}
     \min_{\bf{A}, \bm{\beta}} \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
\end{equation*}
has no solution if $\lambda > 0$.
\end{proposition}
\begin{proof}
  Let's assume this problem has a minimum $\bm{A}^*, \bm{\beta}^*$. Let's consider $2\bm{A}^*, \frac{1}{2}\bm{\beta}^*$. Trivially the first component of the sum is identical for the two solutions, however $\lambda\norm{\frac{1}{2}\bm{\beta}} < \lambda\norm{\bm{\beta}}$. Therefore $\bm{A}^*, \bm{\beta}^*$ cannot be the minimum. We conclude that this problem has no solution.
\end{proof}
\begin{proposition}
  \label{shrinknet_regularized_minimum}
For this proposition we will not restrict ourselves to single layer but the composition of an an arbitrary large ($n$) layers as defined individually as $f_{\bm{A}_i, \bm{\beta}_i, \bm{b}_i}(x) = a(\bm{A_i}\diag{\bm{\beta_i}}\bm{x} + \bm{b_i})$. The entire network follows as: $N(\bm{x}) = \left(\bigcirc_{i=1}^n f_{\bm{A_i}, \bm{\beta_i}, \bm{b_i}}\right)(\bm{x})$. For $\lambda > 0$, $\lambda_2 > 0$ and $p > 0$ we have:
  \begin{equation*}
    \min \norm{\bm{y} - N(\bm{x})}_2^2 + \Omega_{\lambda, \lambda_2, p}^{rs}
  \end{equation*}
  has at least $2^k$ global minimum where $k = \sum_{i=1}^n \#\bm{\beta_i}$
\end{proposition}

\begin{proof}
First let's prove that there is at least one minimum to this problem. The two components of the expression are always positive so we know that this problem is bounded by below by $0$. Let's assume this function does not have a minimum. Then there is a sequence of parameters $(S_n)_{n>0}$ such that the function evaluated at that point convereges to the infimum of the problem. Since the function is defined everywhere does not have a minimum then this sequence must diverge. Since the entire sequence deverge the there is at least one individual parameter that diverges. First case, the parameter is a component $k$ of some $\bm{\beta_i}$ for some $i$. Necessarly $\norm{\bm{\beta_i}}_1$ diverge towards $+ \infty$, which is incompatible with the fact that $(S_n)$ converges to the infimum. We can have the exact same argument if the diverging parameter is in $\bm{A_i}$ or $\bm{b_i}$ because $p > 0$. Since there is always a contradiction then our assumption that the function has no global minimum must be false. Therefore, this problem has at least one global minimum.

\par Let's consider one optimal solution of the problem. For each component $k$ of $\bm{\beta_i}$ for some $i$. Negating it and negating the $k^{th}$ column of $\bm{A_i}$ does not change the the first part of the objetive because the two factors cancel each other. The two norms do not change either because by definition the norm is independant of the sign. As a result these two sets of parameter have the same value and are both global minimum. It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$. We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.

\end{proof}
\subsection{Experiment details}
\subsubsection{Multi-Target Linear and Logistic regressions}
\label{linear_datasets}
\subsubsection{Neuron Removal strategies}
\subsubsection{Convergence and Training Dynamics of Neural networks}
\subsubsection{Hyper-optimization of ShrinkNets}
\subsubsection{Performance}

### 2018-02-09 paper/ICML/approach.tex

@@
 \subsubsection{Neuron killing}
-\textbf{Threshold strategy} \\ We kill neurons based on a threshold (in absolute
+\textbf{Threshold strategy}:  We kill neurons based on a threshold (in absolute
 value), this is the method used by deep compression. It is bad because it is
 scale dependant and is not robust to noise in the gradients (explain that)
-\textbf{Sign change strategy} \\ We look at when the sign change. This is also
+\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
 sensitive to noise but has the advantage
-\textbf{Sign variance strategy}
+\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold.
+\gl{Maybe we should add some intuition on why it makes sense}.
+\gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}
 

### 2018-02-09 paper/ICML/theory.tex

--- 2018-02-05 paper/ICML/theory.tex
@@
-\section{Theoretical analysis}
+\subsection{Relation to Group Sparsity}
 
-\subsection{Notations}
-
-\par In order to avoid any potential ambiguity, in this section we will
-describe in details the mathematical notations used in this article. Non-bold
-letters represent scalar values, while bold lowercase and upper case
-repectively denote vectors and matrices. $\bm{A}^T$ stands for the transpose of
-the matrix $\bm{A}$. Subscripts are used to index particular elements of
-vectors and matrices. $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
-$\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
-the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
-component of the $i^{th}$ row of $\bm{A}$. All the following definitions assume
-$\bm{A}$ to be an $n\times p$ matrix.  For any vetor $\bm{b}$ with $n$
-components, we define $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
-1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.  For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
-\left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$.
-For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function.
-The only constraint that we want to enforce is that $a(0) = 0$.
-We use $\intint{u, v}$ to denote inteveral of integers, $\bm{0}$ is the null vector (size depending on the context).
-$\#S$ is meant to represent the cardinality of a set $S$.
-To simplify the notation of function composition we use the following operator: $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
-\subsection{Definition}
-
-\begin{equation}
-  \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
-\end{equation}
+% \begin{equation}
+%   \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
+% \end{equation}
 
@@
 Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
-we now embed $\sqrt{n}$ inside $\lambda$.
+we embedded $\sqrt{n}$ inside $\lambda$.
 
-Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The ShrinkNet problem is:
+Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The original ShrinkNet problem is:
 
 \begin{equation}
-  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s
+  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
 \end{equation}
@@
 
-has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we define the \textit{regularized ShrinkNet penalty}:
+has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we defined the \textit{regularized ShrinkNet penalty} earlier this way:
 

### 2018-02-09 paper/ICML/approach.tex

--- 2018-02-05 paper/ICML/approach.tex
@@
 
-\begin{itemize}
-  \item Assign an on/off switch to each neuron. But this is np-hard, so we
-  consider a relaxation
-  \item Formulation
-  \item Relationship to group sparsity
-  \item Strategies to kill neurons (relation to theory above?)
-  \item Implementation details
-\end{itemize}
+% from the universality theorem, we know that we can find a network that ca
+% arbitrarly fit a function. Therefore, for a given error tolreance there exists
+% an optimal size to solve a given problem.
 
-Our approach has two main challenges. First, we need a way to
-dynamically size the network during training. Second, we need a
-loss function that optimizes for the additional task of sizing, without
-deteriorating the learning performance of the main task. Our
-approach, called ShrinkNets, copes with both challenges.
+Our approach is based on the insight that given enough capacity (and time), an 
+optimization routine can find a network that can fit an arbitrary function.
+Therefore, by starting with an oversize network and applying on/off switches to
+each of the neurons in it, we can identify a {\it pruned} version of the network
+that can achieve similar accuracy to the oversized network.
 
-During training, our approach starts
-with an explicitly over-sized network. As training progresses, we learn
-which neurons are not contributing to learning and remove them
-dynamically, effectively shrinking the network. This method requires two key components: first, we need a way to identify neurons that are not contributing to the
-learning process, and second we need a way to balance the network size and the
-generalization capability for the main task. We introduce a new \textsf{Filter} 
-\mpv{Choose a different name if possible bc this can be confused w/convolutional
-filters. Maybe Shrinkage layer?} 
-layer that takes care of \emph{deactivating} neurons. We also modify
-existing loss functions to incorporate a new term that takes care of balancing
-network size and generalization capability appropriately.
+% If we have an oversized network then there exist a pruned version that can still
+% achieve our goal. The main idea is to consider an on/off switch for each neuron,
+% and we want to find an assignement for this switches that achieve a certain
+% size/accuracy tradeof. 
+We model these on/off switches by multiplying each input
+(or output) of each layer by a number $0$ or $1$. 
+$0$ will deactivate the
+neuron, $1$ will let the signal go through. 
+We want to minimize the number of on
+switches to reduce the model size as much as we can. 
+This can be modeled solved
+by jointly minimizing the objective of the network and a factor of the L0 norm
+of the vector containing all the on/off switches.
 
-\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are usually placed after
-linear and convolutional layers.
-The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
-  \times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number
-of features (or channels, in the case of convolutional layers), and $D$ any
-additional dimension. This structure makes it compatible with fully connected
-layers with $n=0$ or convolutional layers with $n=2$. Their crucial property is
-a parameter $\theta \in \mathbb{R}^C$. The output is defined as follows: \vspace{-1em}
-\begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
-Where $\circ$ is the pointwise multiplication, and $\theta$ is expanded in all
-dimensions to match the input size (except the second one since they are equal
-by definition). It is easy to see that if for any $k$, if $\theta_k \leq 0$,
-the $k^{\text{th}}$ input feature/channel is multiplied by zero and have no
-influence on the output. If this happens, we say the Filter layer deactivates
-the neuron. These disabled neurons/channels can be removed from the network
-without changing its output. Before explaining how that is achieved, we explain
-next how the weights of the Filter Layer are initialized and adjusted during
-training.
+Finding an optimal binary assignement is an NP-Hard problem. 
+% (\textbf{Should we
+% prove this ? I think it should be fairly doable reducing it to 3-SAT
+% considering the structure of neural networks. No.})
+We relax this problem
+% problem because this is what people usually do with NP-Hard problem. Our
+% relaxation is we allow 
+by allowing $\bm{\theta}$ to be a real number instead of a 0/1 value, thus
+constraining the L1 norm as opposed to the L0 norm.
+% , effectively
+% t We
+% also use L1 instead of L1. This way we obtain a non-convex, but at least
+% differentiable (almost everywhere).
 
-\textbf{Training Procedure: } Once Filter layers are placed in a network and initialized (sampled from the Uniform$[0, 1]$ distribution),
+This approach assumes that we start with an upper bound on the model size. This
+obviously translates in a computational overhead. Our insight is that some
+usless neurons (we have multiple definitions below) can be removed early without
+impacting the final solution. It has two practical implications: It mitigate the
+issue we describe but it also allows other neurons to adapt as soon as one of
+their peer is killed. Existing technique usually remove them after convergence
+and require an extra fine-tuning process to compensate for the removal.
+
+% The key components of the system are: The filter vectors that simulate the
+% continuous on/off switches, a regularization that tries to kill neurons, the
+% neuron removal strategy that detects neurons that should probably be removed,
+% and the garbage collection that effectively remove dead neurons from the model,
+% and the simplifaction procedure that remove the filter vector for fast
+% inference.
+
+% We will describe these components in the upcoming sections.
+
+% \subsection{Notations}
+
+% \par In order to avoid any potential ambiguity, in this section we will
+% describe in details the mathematical notations used in this article. 
+% Non-bold
+% letters represent scalar values, while bold lowercase and upper case
+% repectively denote vectors and matrices. 
+% $\bm{A}^T$ stands for the transpose of
+% the matrix $\bm{A}$. 
+% Subscripts are used to index particular elements of
+% vectors and matrices. 
+% $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
+% $\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
+% the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
+% component of the $i^{th}$ row of $\bm{A}$. 
+% All the following definitions assume
+% $\bm{A}$ to be an $n\times p$ matrix.
+
+% For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
+% \left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$. 
+% For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function.
+% The only constraint that we want to enforce is that $a(0) = 0$. 
+% We use $\intint{u, v}$ to denote inteveral of integers, 
+% $\bm{0}$ is the null vector (size depending on the context). 
+% $\#S$ is meant to represent the cardinality of a set $S$. 
+% To simplify the notation of function composition we use the following operator: 
+% $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from 
+% $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
+
+We implement our strategy of dynamically deactivating neurons by means of a 
+specialized neural network layer called the \textbf{Switch Layer}.
+We first describe the key concepts and theory backing the switch layer and then
+provide a brief summary of our implementation of switch layers.
+
+\subsection{The Switch Layer}
+
+% \textbf{Do you like the name of the layer ? Yes!}
+
+Let $L$ be a layer in a neural network that takes an input tensor $\bm{x}$ and 
+produces an output tensor $y$ of shape $\left(c \times d_1 \times \dots \times 
+d_n\right)$ where $c$ is the number of neurons in that layer.
+For instance, for fully connected layers, $n$=0 and the output is single 
+dimensional of size $c$ (ignoring batch size for now) while for a 2-D 
+convolutional layer, $n$=2 and $c$ is the number of output channels or feature 
+maps.
+% maps
+% For instance, for fully connected layers, $n$=0 and the output is single 
+% dimensional of size $c$ (ignoring batch size for now) while for a 2-D 
+% convolutional layer, $n$=2 and $c$ is the number of output channels or feature 
+% maps.
+%  and furthermore, let the output
+% of layer $l$ be a tensor of shape $\left(C \times D_1 \times \dots \times 
+% D_n\right)$ where $C$ is the number of neurons in $l$.
+% In the case of a fully connected layer, $C$ is the dimensionality of the output
+% of the layer whereas in the case of a convolutional layer, $C$ is the number of
+% feature maps and $\left(D_1 \times \dots \times D_n\right)$ is the size of those feature
+% maps.
+
+Suppose we wish to tune the size of $L$ by applying a switch layer.
+A switch layer $S$ applied to the output of $L$ can be parametrized by a 
+vector $\theta \in \mathbb{R}^c$ such that the result of applying $S$ to $L(\bm{x})$
+is a tensor also of size $\left(c \times d_1 \times \dots \times d_n\right)$
+such that: 
+\begin{equation} 
+S_{\theta}(L(\bm{x}))_{i,...} = \bm{\theta}_iL(\bm{x})_{i, ...}
+\end{equation}
+% where $\diag{\bm{\theta}}$ is a $c\times c$ matrix such that: $\forall
+% 1 \leq i \leq c$, $\diag{\bm{\theta}}_{i, i} = \bm{\theta}_i$ and $0$ otherwise. 
+Effectively, once passed through the switch layer, each output channel $i$ 
+produced by $L$ is scaled by the corresponding $\theta_i$.
+If for any $k$, if $\theta_i = 0$, the $i^{\text{th}}$ channel is multiplied by 
+zero and wont contribute to any computations after the switch layer.
+If this happens, we say the Switch layer has {\it deactivated} or killed the 
+neuron of layer $L$ corresponding to channel $i$. 
+% Switch layers have weights in the range $[-\infty,+\infty]$ and are usually 
+% placed after linear and convolutional layers.
+% The \textit{Switch Layer} takes an input of size $\left(B \times C \times D_1
+%   \times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number
+% of features (or channels, in the case of convolutional layers), and $D$ any
+% additional dimension. 
+% This structure makes it compatible with fully connected
+% layers with $n=0$ or convolutional layers with $n=2$. 
+% Their crucial property is
+% a parameter $\theta \in \mathbb{R}^C$. 
+% The output is defined as follows: \vspace{-1em}
+% \begin{equation} 
+% Switch(\bm{I};\bm{\theta}) = \diag{\bm{\theta}} \bm{I}  
+% \end{equation}
+% where $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
+% 1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.
+
+% Where $\theta$ is expanded in all
+% dimensions to match the input size (except the second one since they are equal
+% by definition).
+
+% These disabled neurons/channels can be removed from the network
+% without changing its output. 
+% Before explaining how that is achieved, we explain
+% next how the weights of the Switch Layer are initialized and adjusted during
+% training.
+
+\subsection{Training Procedure}
+
+To tune the size of a network, we place Switch Layers after each layer whose size
+we wish to tune; these are typically the fully connected and convolutional layers
+in a network.
+Since the switch layers are adept at deactivating neurons, we start with an
+oversized network (i.e. network with more capacity than required) and then use
+switch layers to deactivate or kill off neurons that are unnecessary.
+
+Formally, we can express this procedure in terms of a sparsity constraint that pushes
+values in the $\theta$ vector to 0.
+Given a neural network parameterized by weights $\bm{W}$ and switch layer 
+parameters $\bm{\theta}$, we optimize the following ShrinkNet loss that 
+augments the regular training loss with a 
+regularization term for the switch parameters and another on the network weights.
+\begin{equation}
+  L_{SN}(\bm{x},\bm{y};\bm{W}, \bm{\theta}) = L(\bm{x}, \bm{y}; \bm{W}) +
+  \lambda\norm{\theta}_1 + \lambda_2\norm{\bm{W}}_p
+\end{equation}
+
 %To train networks we need start with a substantially oversized network, then we
-%insert \textit{Filter Layers}  (usually after every linear or convolutional
+%insert \textit{Switch Layers}  (usually after every linear or convolutional
 %layer except the last one) and we sample their weight from the
 %$\text{Uniform}(0, 1)$ distribution. 
-we could train the network directly using our standard loss function, and we could achieve performance equivalent to a normal neural
-network. However, our goal is to find the smallest network with reasonable
-performance. We achieve that by introducing sparsity in the parameters of the
-\textit{Filter Layers}, thus forcing the deactivation of neurons%. Indeed, having a negative component in the $\theta$
+% we could train the network directly using our standard loss function, and we could achieve performance equivalent to a normal neural
+% network. However, our goal is to find the smallest network with reasonable
+% performance. We achieve that by introducing sparsity in the parameters of the
+% \textit{Switch Layers}, thus forcing the deactivation of neurons
+%. Indeed, having a negative component in the $\theta$
 %parameter of the filter layer permamently disable its associated feature
 %\gl{Maybe redundant ? we talked about that in the previous paragraph} . 
-. To obtain this sparsity, we simply redefine the loss function:
-\vspace{-.5em}
-\begin{equation}
-  L'(x,y;\theta) = L(x, y) + \lambda|\max(0, \theta)|
-\end{equation}
+% To obtain this sparsity, we simply redefine the loss function:
+% \begin{equation}
+%   L'(\bm{x},\bm{y};\bm{W}, \bm{\theta}) = L(\bm{x}, \bm{y}; \bm{W}) +
+%   \lambda\norm{\theta}_1 + \lambda_2\norm{\bm{W}}_p
+% \end{equation}
 
-The additional term $\lambda|\max(0, \theta)|$ introduces sparsity (see Lasso
-loss~\cite{Tibshirani1996}). 
+% The additional term $\lambda|\max(0, \theta)|$ introduces sparsity (see Lasso
+% loss~\cite{Tibshirani1996}). 
 % The $\lambda$ parameter, that can take any
@@
 % larger values indicating more aggressive deactivation.
- The second component of the loss increases the gradient with respect to $\theta$, thus pushing its value towards zero. Neurons with little impact
-on the original loss (gradient lower than $\lambda$), will not be able to
-compete against this attraction towards zero. Because the entries in $\theta$
-with a value of $0$ or less correspond to dead neurons, $\lambda$ effectively
-controls the number of neurons/channels in the entire network. We introduced
-the $\max(\dots)$ into the loss to make sure that neurons are permamently disabled
-when performing gradient descent based optimization. Next, we
-explain how to implement ShrinkNets efficiently.
+%  The second component of the loss increases the gradient with respect to $\theta$, thus pushing its value towards zero. Neurons with little impact
+% on the original loss (gradient lower than $\lambda$), will not be able to
+% compete against this attraction towards zero. Because the entries in $\theta$
+% with a value of $0$ or less correspond to dead neurons, $\lambda$ effectively
+% controls the number of neurons/channels in the entire network. Without the last
+% term our problem sounds very similar to the Group Sparsity regularization which
+% is well known in the area of linear and logistic regressions. In the next
+% section we will try to undercover the relationship between these two problems,
+% explain why we need this additional regularization term and what should be the
+% value of $p$.
 
-\subsection{Strategies to Remove Neurons}
+\input{theory}
 
-\textbf{Implementation}
-It is possible to reduce the overhead of the training process by removing
-neurons as soon as they become deactivated by $\theta$ going to 0.
+\subsubsection{Neuron killing}
+Once Switch layers are placed in a network and
+initialized (sampled from the $\mathcal{N}(0, 1)$ distribution),
+
+\textbf{Threshold strategy}:  We kill neurons based on a threshold (in absolute
+value), this is the method used by deep compression. It is bad because it is
+scale dependant and is not robust to noise in the gradients (explain that)
+\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
+sensitive to noise but has the advantage
+\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold.
+\gl{Maybe we should add some intuition on why it makes sense}.
+\gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}
+
+\subsection{Implementation}
+
+We have implemented \textbf{Switch Layers} and the associated training procedure
+as a library in pytorch~\cite{github}.
+The layer can be freely mixed with other popular layers such as convolutional
+layers, batchnorm layers, fully connected layers etc.
+There are two key challenges that must be overcome while implementing 
+\textbf{Switch Layers}.
+First, since ShrinkNets kill off a large fraction of neurons, we must remove the
+overhead of carrying around dead neurons.
+And second, we must update the various network layers and training machinery (e.g.
+optimizer state) to reflect the deactivation of neurons.
+We address these challenges by augmenting every layer with additional information
+about neuron status and implementing a \emph{neural garbage collection} 
+mechanism which prunes deactivated neurons on-the-fly and updates the state of 
+the training machinery.
+% We do so by augmenting every layer with additional information such as what
+% neurons have been deactivated.
+% The layer then updates its size accordingly and this change is then propagated
+% to other parts of the training machinery including the optimizer which must
+% know the sizes of parameters.
+
+A second implementation challenge we address with ShrinkNets is the potentially
+higher inference time.
+This increase in inference time is both due to the extra computation introduced 
+by switch layers and because our switch layers are not currently optimized for 
+CUDA.
+Therefore, for now, our library provides a post-training routine to ``fold''
+switch layers into existing, optimized layers.
+Specifically, for every switch layer, we check if the parent or child of this 
+layer is a linearly scalable layer (e.g. convolutional layer, fully connected layer,
+batchnormalization layer) and if so, we fold the switch layer into this 
+neighboring layer by multiplying through by the switch weights.
+In the unlikely case that a switch layer is sandwiched between two non-linearly
+scalable layers, we leave the switch layer as is.
+
+% \subsection{Speeding up training}
+
+% In order to have a practical implementation of ShrinkNets it is absolutely
+% necessary to prune useless neurons as quick as possible. In order to try more
+% different strategies we split this task in two subproblems: detecting
+% potentially non-crucial neurons and setting their corresponding entry in the
+% switch layer to exactly 0, and neural garbage collection that
+
+% In our library we implemented a variant of the second strategy and the last one.
+
+% \subsubsection{Neural garbage collection}
+
+% It is possible to reduce the overhead of the training process by removing
+% neurons as soon as they become deactivated by $\theta$ going to 0.
 %If
@@
 %process to be significantly slower than classic neural networks. 
-To do this, we implemented a \emph{neural garbage collection} mechanism which
-prunes deactivated neurons on-the-fly,  reducing the processing time
-and memory overhead. To support this feature, it is crucial to understand the
-information flow between neurons and layers in the neural network. We achieve
-this by representing such information flow as a graph. Vertices represent layers,
-and edges are event-hubs responsible for propagating information about disabled
-neurons to the relevant layers.
+% To do this, we implemented a \emph{neural garbage collection} mechanism which
+% prunes deactivated neurons on-the-fly,  reducing the processing time
+% and memory overhead. 
+% To support this feature, it is crucial to understand the
+% information flow between neurons and layers in the neural network. 
+% We achieve
+% this by representing such information flow as a graph. 
+% Vertices represent layers,
+% and edges are event-hubs responsible for propagating information about disabled
+% neurons to the relevant layers. 
+% As soon as a layer receive an event, it updates
+% his parameters to reflect the new size. 
+% Each operation is stored in a log that
+% is used later to update other component of the system. 
+% For example some
+% optimizers like Adam [Ref] store state about each parameter, their state needs
+% to be updated the exact same way and at the exact same time as layers in order
+% to obtain apropriate parameter updates.
+
+% \subsubsection{Speeding up Inference}
+% \mpv{This may be moved to discussion or ``other considerations'' or impl details.}
+
+% our post-processing code searches the 
+% network graph to identify a parent or child layer the linear layer closest (child or parent) to every 
+% switch layer and multiplies the weights of that layer by the corresponding
+% switch layer weights.
+
+% Our proposed \textit{Switch Layer} are relevant only during training, and can be
+% removed from the network architecture during inference if they can be ``folded''
+% into the nearest linear layer.
+% Specifically, we provide a post-processing routine that will, for each switch 
+% layer, search the network graph
+
+% The sole puropose of \textit{Switch Layer} are to detect which neurons should be
+% killed and which should be left. When the training is over we will never remove
+% more neurons. Therefore, they loose all their interest at inference time. 
+% To
+% improve size and inference time we propose the following method to get rid of
+% them without changing the output of the model (modulo floating point errors).
+% The basic idea is to start from every \textit{Switch Layer} and try to find the
+% nearset linear operator (child or parent) and multiply its weights by the values
+% in the switch layer. For example we can merge Filter layers with surrounding
+% Convolutional layer, Linear layer or even BatchNormalization [ref] if they are
+% before the \textit{Switch Layer}. However we need to be extremely careful not to
+% cross a non-linearity otherwise it would change the output of network.

### 2018-02-09 paper/ICML/approach.tex
split section 2 into 2; re-structured section 2; Pass over 2.0 and 2.1; checkpoing---will continue from 2.1 in the morning

@@
-\section{Our Approach}
+\section{The ShrinkNets Approach}
 
-% from the universality theorem, we know that we can find a network that ca
-% arbitrarly fit a function. Therefore, for a given error tolreance there exists
-% an optimal size to solve a given problem.
+In this section we present the \emph{Switch layer}, a core concept of our
+ShrinkNets approach that allows to learn the network size as part of the
+training process. Then, we explain how to adapt the training procedure to
+support the new layer. We begin with a high-level overview of our method.
 
-Our approach is based on the insight that given enough capacity (and time), an 
-optimization routine can find a network that can fit an arbitrary function.
-Therefore, by starting with an oversize network and applying on/off switches to
-each of the neurons in it, we can identify a {\it pruned} version of the network
-that can achieve similar accuracy to the oversized network.
+\subsection{Overview}
 
+At a high-level, the ShrinkNets approach consists of two interconnected stages.
+The first stage is concerned with identifying neurons that are not contributing
+to increasing the prediction accuracy of the network and deacivate them. The
+second stage is concerned with actually removing the neurons from the network
+and shrinking its size, therefore leading to faster inference times. We give an
+overview of both processes next:
+
+\noindent\textbf{Deactivating Neurons On-The-Fly: }During the first stage,
+ShrinkNets applies an on/off switch to every neuron of an initially oversized
+network. We model the on/off switches by multiplying each input (or output) of
+each layer by a parameter $\bm{\theta}$, with values $0$ or $1$. A value of $0$
+will deactivate the neuron, while $1$ will let the signal go through. These
+switches are part of a new layer, which we call \textbf{Switch layer} which can
+be applied to fully connected as well as convolutional layers.
+
+We want to minimize the number of on switches to reduce the model size as much
+as we can, while preserving prediction accuracy. This can be achieved by jointly
+minimizing the objective of the network and a factor of the L0 norm of the
+vector containing all the on/off switches. Because finding an optimal binary
+assignement is an NP-Hard problem, we allow $\bm{\theta}$ to be a real number
+instead of a 0/1 value, thus constraining the L1 norm as opposed to the L0 norm.
+
+\noindent\textbf{Neuron Removal: } During this stage, the neurons that are
+deactivated by the Switch layers are actually removed from the network,
+effectively shrinking the network size. This is what leads to faster inference
+times, as we demonstrate in our evaluation. We choose to remove neurons at
+training time because we have observed that allows the active neurons to adapt
+to the new network architecture. Existing techniques focus on neuron removal
+after training, and require an extra fine-tuning process to compensate for the
+removal.
+
+In the remainder of this section we describe in detail the Switch layer as well
+as how to adapt the training process for ShrinkNets.
+
+%This approach assumes that we start with an upper bound on the model size. This
+%obviously translates in a computational overhead. Our insight is that some
+%usless neurons (we have multiple definitions below) can be removed early without
+%impacting the final solution. It has two practical implications: It mitigate the
+%issue we describe but it also allows other neurons to adapt as soon as one of
+%their peer is killed. Existing technique usually remove them after convergence
+%and require an extra fine-tuning process to compensate for the removal.
+
+%We implement our strategy of dynamically deactivating neurons by means of a 
+%specialized neural network layer called the \textbf{Switch Layer}.
+%We first describe the key concepts and theory backing the switch layer and then
+%provide a brief summary of our implementation of switch layers.
+
+%Our approach is based on the insight that given enough capacity (and time), an 
+%optimization routine can find a network that can fit an arbitrary function.
+%Therefore, by starting with an oversize network and applying on/off switches to
+%each of the neurons in it, we can identify a {\it pruned} version of the network
+%that can achieve similar accuracy to the oversized network.
+%
+%
 % If we have an oversized network then there exist a pruned version that can still
@@
 % size/accuracy tradeof.
-We model these on/off switches by multiplying each input
-(or output) of each layer by a number $0$ or $1$. 
-$0$ will deactivate the
-neuron, $1$ will let the signal go through. 
-We want to minimize the number of on
-switches to reduce the model size as much as we can. 
-This can be modeled solved
-by jointly minimizing the objective of the network and a factor of the L0 norm
-of the vector containing all the on/off switches.
-
-Finding an optimal binary assignement is an NP-Hard problem. 
-% (\textbf{Should we
-% prove this ? I think it should be fairly doable reducing it to 3-SAT
-% considering the structure of neural networks. No.})
-We relax this problem
-% problem because this is what people usually do with NP-Hard problem. Our
-% relaxation is we allow 
-by allowing $\bm{\theta}$ to be a real number instead of a 0/1 value, thus
-constraining the L1 norm as opposed to the L0 norm.
-% , effectively
-% t We
-% also use L1 instead of L1. This way we obtain a non-convex, but at least
-% differentiable (almost everywhere).
-
-This approach assumes that we start with an upper bound on the model size. This
-obviously translates in a computational overhead. Our insight is that some
-usless neurons (we have multiple definitions below) can be removed early without
-impacting the final solution. It has two practical implications: It mitigate the
-issue we describe but it also allows other neurons to adapt as soon as one of
-their peer is killed. Existing technique usually remove them after convergence
-and require an extra fine-tuning process to compensate for the removal.
 
@@
 
-We implement our strategy of dynamically deactivating neurons by means of a 
-specialized neural network layer called the \textbf{Switch Layer}.
-We first describe the key concepts and theory backing the switch layer and then
-provide a brief summary of our implementation of switch layers.
-
 \subsection{The Switch Layer}
-
-% \textbf{Do you like the name of the layer ? Yes!}
 
@@
 produces an output tensor $y$ of shape $\left(c \times d_1 \times \dots \times
-d_n\right)$ where $c$ is the number of neurons in that layer.
-For instance, for fully connected layers, $n$=0 and the output is single 
-dimensional of size $c$ (ignoring batch size for now) while for a 2-D 
-convolutional layer, $n$=2 and $c$ is the number of output channels or feature 
-maps.
+d_n\right)$ where $c$ is the number of neurons in that layer.  For instance, for
+fully connected layers, $n$=0 and the output is single dimensional of size $c$
+(ignoring batch size for now) while for a 2-D convolutional layer, $n$=2 and $c$
+is the number of output channels or feature maps.
+
 % maps
@@
 
-\subsection{Training Procedure}
+\subsection{Training ShrinkNets}
 
@@
 \input{theory}
-
-\subsubsection{Neuron killing}
-Once Switch layers are placed in a network and
-initialized (sampled from the $\mathcal{N}(0, 1)$ distribution),
-
-\textbf{Threshold strategy}:  We kill neurons based on a threshold (in absolute
-value), this is the method used by deep compression. It is bad because it is
-scale dependant and is not robust to noise in the gradients (explain that)
-\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
-sensitive to noise but has the advantage
-\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold.
-\gl{Maybe we should add some intuition on why it makes sense}.
-\gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}
-
-\subsection{Implementation}
-
-We have implemented \textbf{Switch Layers} and the associated training procedure
-as a library in pytorch~\cite{github}.
-The layer can be freely mixed with other popular layers such as convolutional
-layers, batchnorm layers, fully connected layers etc.
-There are two key challenges that must be overcome while implementing 
-\textbf{Switch Layers}.
-First, since ShrinkNets kill off a large fraction of neurons, we must remove the
-overhead of carrying around dead neurons.
-And second, we must update the various network layers and training machinery (e.g.
-optimizer state) to reflect the deactivation of neurons.
-We address these challenges by augmenting every layer with additional information
-about neuron status and implementing a \emph{neural garbage collection} 
-mechanism which prunes deactivated neurons on-the-fly and updates the state of 
-the training machinery.
-% We do so by augmenting every layer with additional information such as what
-% neurons have been deactivated.
-% The layer then updates its size accordingly and this change is then propagated
-% to other parts of the training machinery including the optimizer which must
-% know the sizes of parameters.
-
-A second implementation challenge we address with ShrinkNets is the potentially
-higher inference time.
-This increase in inference time is both due to the extra computation introduced 
-by switch layers and because our switch layers are not currently optimized for 
-CUDA.
-Therefore, for now, our library provides a post-training routine to ``fold''
-switch layers into existing, optimized layers.
-Specifically, for every switch layer, we check if the parent or child of this 
-layer is a linearly scalable layer (e.g. convolutional layer, fully connected layer,
-batchnormalization layer) and if so, we fold the switch layer into this 
-neighboring layer by multiplying through by the switch weights.
-In the unlikely case that a switch layer is sandwiched between two non-linearly
-scalable layers, we leave the switch layer as is.
-
-% \subsection{Speeding up training}
-
-% In order to have a practical implementation of ShrinkNets it is absolutely
-% necessary to prune useless neurons as quick as possible. In order to try more
-% different strategies we split this task in two subproblems: detecting
-% potentially non-crucial neurons and setting their corresponding entry in the
-% switch layer to exactly 0, and neural garbage collection that
-
-% In our library we implemented a variant of the second strategy and the last one.
-
-% \subsubsection{Neural garbage collection}
-
-% It is possible to reduce the overhead of the training process by removing
-% neurons as soon as they become deactivated by $\theta$ going to 0.
-%If
-%disabled neurons are not quickly removed, the overhead might cause the training
-%process to be significantly slower than classic neural networks. 
-% To do this, we implemented a \emph{neural garbage collection} mechanism which
-% prunes deactivated neurons on-the-fly,  reducing the processing time
-% and memory overhead. 
-% To support this feature, it is crucial to understand the
-% information flow between neurons and layers in the neural network. 
-% We achieve
-% this by representing such information flow as a graph. 
-% Vertices represent layers,
-% and edges are event-hubs responsible for propagating information about disabled
-% neurons to the relevant layers. 
-% As soon as a layer receive an event, it updates
-% his parameters to reflect the new size. 
-% Each operation is stored in a log that
-% is used later to update other component of the system. 
-% For example some
-% optimizers like Adam [Ref] store state about each parameter, their state needs
-% to be updated the exact same way and at the exact same time as layers in order
-% to obtain apropriate parameter updates.
-
-% \subsubsection{Speeding up Inference}
-% \mpv{This may be moved to discussion or ``other considerations'' or impl details.}
-
-% our post-processing code searches the 
-% network graph to identify a parent or child layer the linear layer closest (child or parent) to every 
-% switch layer and multiplies the weights of that layer by the corresponding
-% switch layer weights.
-
-% Our proposed \textit{Switch Layer} are relevant only during training, and can be
-% removed from the network architecture during inference if they can be ``folded''
-% into the nearest linear layer.
-% Specifically, we provide a post-processing routine that will, for each switch 
-% layer, search the network graph
-
-% The sole puropose of \textit{Switch Layer} are to detect which neurons should be
-% killed and which should be left. When the training is over we will never remove
-% more neurons. Therefore, they loose all their interest at inference time. 
-% To
-% improve size and inference time we propose the following method to get rid of
-% them without changing the output of the model (modulo floating point errors).
-% The basic idea is to start from every \textit{Switch Layer} and try to find the
-% nearset linear operator (child or parent) and multiply its weights by the values
-% in the switch layer. For example we can merge Filter layers with surrounding
-% Convolutional layer, Linear layer or even BatchNormalization [ref] if they are
-% before the \textit{Switch Layer}. However we need to be extremely careful not to
-% cross a non-linearity otherwise it would change the output of network.

### 2018-02-09 paper/ICML/impl.tex
split section 2 into 2; re-structured section 2; Pass over 2.0 and 2.1; checkpoing---will continue from 2.1 in the morning

\section{ShrinkNets in Practice}

\subsubsection{Neuron killing}
Once Switch layers are placed in a network and
initialized (sampled from the $\mathcal{N}(0, 1)$ distribution),

\textbf{Threshold strategy}:  We kill neurons based on a threshold (in absolute
value), this is the method used by deep compression. It is bad because it is
scale dependant and is not robust to noise in the gradients (explain that)
\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
sensitive to noise but has the advantage
\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold. \gl{Maybe we should add some intuition on why it makes sense}. \gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}

\subsection{Implementation}

We have implemented \textbf{Switch Layers} and the associated training procedure
as a library in pytorch~\cite{github}.
The layer can be freely mixed with other popular layers such as convolutional
layers, batchnorm layers, fully connected layers etc.
There are two key challenges that must be overcome while implementing 
\textbf{Switch Layers}.
First, since ShrinkNets kill off a large fraction of neurons, we must remove the
overhead of carrying around dead neurons.
And second, we must update the various network layers and training machinery (e.g.
optimizer state) to reflect the deactivation of neurons.
We address these challenges by augmenting every layer with additional information
about neuron status and implementing a \emph{neural garbage collection} 
mechanism which prunes deactivated neurons on-the-fly and updates the state of 
the training machinery.
% We do so by augmenting every layer with additional information such as what
% neurons have been deactivated.
% The layer then updates its size accordingly and this change is then propagated
% to other parts of the training machinery including the optimizer which must
% know the sizes of parameters.

A second implementation challenge we address with ShrinkNets is the potentially
higher inference time.
This increase in inference time is both due to the extra computation introduced 
by switch layers and because our switch layers are not currently optimized for 
CUDA.
Therefore, for now, our library provides a post-training routine to ``fold''
switch layers into existing, optimized layers.
Specifically, for every switch layer, we check if the parent or child of this 
layer is a linearly scalable layer (e.g. convolutional layer, fully connected layer,
batchnormalization layer) and if so, we fold the switch layer into this 
neighboring layer by multiplying through by the switch weights.
In the unlikely case that a switch layer is sandwiched between two non-linearly
scalable layers, we leave the switch layer as is.

% \subsection{Speeding up training}

% In order to have a practical implementation of ShrinkNets it is absolutely
% necessary to prune useless neurons as quick as possible. In order to try more
% different strategies we split this task in two subproblems: detecting
% potentially non-crucial neurons and setting their corresponding entry in the
% switch layer to exactly 0, and neural garbage collection that

% In our library we implemented a variant of the second strategy and the last one.

% \subsubsection{Neural garbage collection}

% It is possible to reduce the overhead of the training process by removing
% neurons as soon as they become deactivated by $\theta$ going to 0.
%If
%disabled neurons are not quickly removed, the overhead might cause the training
%process to be significantly slower than classic neural networks. 
% To do this, we implemented a \emph{neural garbage collection} mechanism which
% prunes deactivated neurons on-the-fly,  reducing the processing time
% and memory overhead. 
% To support this feature, it is crucial to understand the
% information flow between neurons and layers in the neural network. 
% We achieve
% this by representing such information flow as a graph. 
% Vertices represent layers,
% and edges are event-hubs responsible for propagating information about disabled
% neurons to the relevant layers. 
% As soon as a layer receive an event, it updates
% his parameters to reflect the new size. 
% Each operation is stored in a log that
% is used later to update other component of the system. 
% For example some
% optimizers like Adam [Ref] store state about each parameter, their state needs
% to be updated the exact same way and at the exact same time as layers in order
% to obtain apropriate parameter updates.

% \subsubsection{Speeding up Inference}
% \mpv{This may be moved to discussion or ``other considerations'' or impl details.}

% our post-processing code searches the 
% network graph to identify a parent or child layer the linear layer closest (child or parent) to every 
% switch layer and multiplies the weights of that layer by the corresponding
% switch layer weights.

% Our proposed \textit{Switch Layer} are relevant only during training, and can be
% removed from the network architecture during inference if they can be ``folded''
% into the nearest linear layer.
% Specifically, we provide a post-processing routine that will, for each switch 
% layer, search the network graph

% The sole puropose of \textit{Switch Layer} are to detect which neurons should be
% killed and which should be left. When the training is over we will never remove
% more neurons. Therefore, they loose all their interest at inference time. 
% To
% improve size and inference time we propose the following method to get rid of
% them without changing the output of the model (modulo floating point errors).
% The basic idea is to start from every \textit{Switch Layer} and try to find the
% nearset linear operator (child or parent) and multiply its weights by the values
% in the switch layer. For example we can merge Filter layers with surrounding
% Convolutional layer, Linear layer or even BatchNormalization [ref] if they are
% before the \textit{Switch Layer}. However we need to be extremely careful not to
% cross a non-linearity otherwise it would change the output of network.

### 2018-02-09 paper/ICML/paper.tex
edits
First pass on section 2
split section 2 into 2; re-structured section 2; Pass over 2.0 and 2.1; checkpoing---will continue from 2.1 in the morning

@@
 \usepackage{bm}
+\usepackage{xcolor}
 \usepackage{amsthm}
@@
 \usepackage{booktabs} % for professional tables
-
+\usepackage{paralist}
 % hyperref makes hyperlinks in the resulting PDF.
@@
 
-\section{Tentative outline}
-
+%\section{Tentative outline}
+%
 % \begin{itemize}
@@
 % \section{Outline2}
-\begin{itemize}
-  \item Introduction
-  \begin{itemize}
-    \item Finding an appropriately sized network is challenging
-    \item ML practitioners spend a large amount of time tuning the size of layers
-    in a network in order to get the best possible accuracy.
-    \item Many techniques have been proposed for hyperparam opt but these
-    are computationally expensive and take long to train
-    \item We propose ShrinkNets, an approach to tune the size of the network 
-    as it is being trained without incurring the significant costs of 
-    hyperparameter optimization. 
-    \item Thus, our contribution are: ...
-  \end{itemize}
-  \item Our Approach
-  \begin{itemize}
-    \item Assign an on/off switch to each neuron. But this is np-hard, so we
-    consider a relaxation
-    \item Formulation
-    \item Relationship to sparsity
-    \item Strategies to kill neurons (relation to theory above?)
-    \item Implementation details
-  \end{itemize}
-  \item Related Work
-  \begin{itemize}
-    \item Hyperparameter optimization: random, bayesian opt, bandit methods
-    \item distillation techniques
-    \item post-training compression techniques
-    \item group sparsity, non-parametric neural networks
-    \item training dynamics paper: first overfitting and then randomization?
-  \end{itemize}
-  \item Experiments
-  \begin{itemize}
-    \item Accuracy obtained by Shrinknets
-    \item Time taken to reach that accuracy compared with other hyperopt methods
-    \item Characterize method wrt params
-    \item Other experiments  
-  \end{itemize}
-  \item Discussion
-  \begin{itemize}
-    \item Where does the method shine?
-    \item Side-effects of method: smaller networks, time to train
-    \item Potential extensions/limitations
-  \end{itemize}
-  \item Conclusion
-\end{itemize}
+%\begin{itemize}
+%  \item Introduction
+%  \begin{itemize}
+%    \item Finding an appropriately sized network is challenging
+%    \item ML practitioners spend a large amount of time tuning the size of layers
+%    in a network in order to get the best possible accuracy.
+%    \item Many techniques have been proposed for hyperparam opt but these
+%    are computationally expensive and take long to train
+%    \item We propose ShrinkNets, an approach to tune the size of the network 
+%    as it is being trained without incurring the significant costs of 
+%    hyperparameter optimization. 
+%    \item Thus, our contribution are: ...
+%  \end{itemize}
+%  \item Our Approach
+%  \begin{itemize}
+%    \item Assign an on/off switch to each neuron. But this is np-hard, so we
+%    consider a relaxation
+%    \item Formulation
+%    \item Relationship to sparsity
+%    \item Strategies to kill neurons (relation to theory above?)
+%    \item Implementation details
+%  \end{itemize}
+%  \item Related Work
+%  \begin{itemize}
+%    \item Hyperparameter optimization: random, bayesian opt, bandit methods
+%    \item distillation techniques
+%    \item post-training compression techniques
+%    \item group sparsity, non-parametric neural networks
+%    \item training dynamics paper: first overfitting and then randomization?
+%  \end{itemize}
+%  \item Experiments
+%  \begin{itemize}
+%    \item Accuracy obtained by Shrinknets
+%    \item Time taken to reach that accuracy compared with other hyperopt methods
+%    \item Characterize method wrt params
+%    \item Other experiments
+%  \end{itemize}
+%  \item Discussion
+%  \begin{itemize}
+%    \item Where does the method shine?
+%    \item Side-effects of method: smaller networks, time to train
+%    \item Potential extensions/limitations
+%  \end{itemize}
+%  \item Conclusion
+%\end{itemize}
 
@@
 \input{approach}
-\input{theory}
+\input{impl}
 \input{evaluation}

### 2018-02-09 paper/ICML/evaluation.tex

@@
 For each of the models we trained, we pick the epoch with the best validation
-accuracy and report the corresponding testing accuracy. For each model, we also
-measure the total size, in number of floating point parameters, excluding the
-\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
-get rid of them when training is done.
+accuracy and report the corresponding testing accuracy. Because of the nature of
+our method, it can happen that for network that are aggressively compressed, the
+best validation accuracy is obtained early in the training, before the size has
+converged. To be sure that accuracy measured corresponds to the final shape and
+not the starting shape, we only consider the second half of the training when
+picking the best epoch. For each model, we also measure the total size, in
+number of floating point parameters, excluding the \textit{Switch Layers}
+because as we saw in section \gl{REFERENCE\_ME}, we can get rid of them when
+training is done.
 
@@
 
-Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. \gl{TODO
-  rephrase the description taken from the UCI website} We picked
-this one for couple of reasons. First it is simply enough that we can reach good
-accuracy with small models. This important because we want to show that
+Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. This dataset
+contains $581012$ description of geographical area (elevation, inclination,
+etc...) and the goal is to predict the type of forest growing there. We picked
+this one for couple of reasons. First it is simple that we can reach good
+accuracy with only a few layers. This important because we want to show that
 \textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
 are sampling the entire space of possible sizes. The second reason is that [ref]
-are also doing their evaluation on this dataset, which allow us to compare the
+also perform their evaluation on this dataset, which allow us to compare the
 results obtained by the two methods.
@@
 
-\gl{Todo for me: explain how I select the best epoch to get rid of the outliers}
+\subsection{Results of the random search procedure}
 
-\subsection{Intepretation of the result of random search}
-
-\gl{TODO draw conclusions from the plots}:
-\begin{itemize}
-  \item Pareto frontier better or as good, even when we sample the entire search
-    space
-  \item Static NEts are much more spread in terms of size for a given accuracy
-    while shrinknets are smarter and always lie close to the frontier (I am
-    changing the way I select the best epoch so the outliers in the COVER
-    dataset will go away in the next version of the plot)
-  \item We reach as good or better accuracies than normal networks
-\end{itemize}
+On the plot, the Pareto front for the two training methods clearly indicates
+that not only \textit{ShrinkNets} find models that are as accurate as
+\textit{Static Networks}, but they are more efficient in terms of size. Even
+when we sample the entire size space (in the \texttt{COVERTYPE} case),
+\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
+it has two implications. First it reinforces, our observation in [ref] that
+showed that the models do not suffer from the non-convexity introduced by the
+multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
+that the parametrization from a $\lambda$ (real value) to the size of the
+size of the network (vector) is optimal or close to optimal. Indeed, if it was
+not the case then eventually a randomly sampled size would have beaten
+\textit{ShrinkNets} models. \gl{Too strong ?}
 
@@
 Regarding size, the key observation we can make is that size improvenets are
-significant for
+significant for the \texttt{CIFAR10}. In the range of accuracies we are
+interested in, improvements in size go from 4x to 40x. On the \texttt{COVERTYPE}
+dataset even if the compression ratio is always above 1, it hardly exceeds 3x,
+except for very high accuracy where \textit{ShrinkNets} obtained some
+particularly good solutions.
 
-\subsection{Multi-Target Linear and Multi-Class Logistic regressions}
-
-As we showed, Group sparsity share similarities with our method, and we claim
-that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
-to compare the two aproaches.  We decided to focus on multi-target linear
-regression because in the single target case, groups in the Group Sparsity
-problem would have a size of one ($\bm{A}$ would be a vector in this case).
-
-The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
-[ref] for linear regressions and we will use \texttt{gina\_prior2} [ref] and
-the \textit{Gas Sensor Array Drift Dataset} [ref] (that we shorten in
-\texttt{gsadd}) for logistic regressions.
-
-For each dataset we fit with different regularization parameters and measure
-the error and sparsity obtained after convergence. In this context we define
-sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
-absolute value. Regularization parameters were choosed in order to obtain the
-widest sparsity spectrum. Loss is normalized depending on the problem to be in
-the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
-our experiments it is clear that ShrinkNets can fit the data closer than Group
-Sparsity for the same amount of sparsity. The fact that we are able to reach
-very low loss demonstrate that even if our objective function is non convex, in
-practice it works as good or better as convex alternatives. Details about these
-datasets and the parameters used are available in \cref{linear_datasets}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{regressions}
-\vspace*{-5mm}
-\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
-From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
-
-\end{center}
-\vspace*{-4mm}
-\end{figure}
-
-\subsection{Neuron Removal strategies}
-
-In our previous experiment, we showed that the ShrinkNet loss was
-reasonable in practice, we are now interested in the impact on
-early pruning. The method we suggest for early prunning uses a
-parameter $\gamma$ that control the aggressiveness of neuron removal
-so we will try to evaluate its impact on the final loss achieved by
-the model and the cost required to train the model. Our cost model
-is simple and hardware independant, we sum the number of input neurons
-at each epoch. In theory the cost in time should be asymptotically
-linear to this metric. To have a baseline we also train the same model
-but without neuron removal. Keep in mind that this is just in order to
-have some reference. Indeed, if we were to remove the neurons with small
-weights it would deteriorate the loss (and picking the threshould would
-be completely arbitrary). Therefore the baseline is evaluated with all neurons.
-One could consider it as a "theoretical lower bound" of the best achievable loss.
-
-We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$).
-We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}.
-In order to reduce the noise in the result, each experiment was performed $30$ times and we display the range arround $\pm$ $1$ standard deviation.
+We observe that unlike local sparsity compression based method, our method
+translates directly improvement in size to higher bandwidth at inference time.
+In situations where inference is already incredibly fast (\texttt{COVERTYPE}
+with a batch size of $1$ and \texttt{CIFAR10} with a batch size of $1$ on GPU),
+improvements are dominted by noise. However, on machine learning frameworks
+more focused on latency it should be possible to measure them.
 
@@
 
-\section{Architectures obtained after convergence}
+\subsection{Architectures obtained after convergence}
 
@@
 \textit{ShrinkNets} converged to considerably bigger networks in the case of
-\texttt{FashionMNIST}.
-take a look closer to the architectures \textit{ShrinkNets} converge to
+\texttt{FashionMNIST}. This evidence shows that final architecture not only
+depends on the output distribution or shape of the data but actually reflects
+the dataset (we know that FASHIONMNIST is harder then MNIST)
+
+We provide two examples of architectures learned by \textit{ShrinkNet}. One
+for the best test available test accuracy and a slightly underperforming but
+significantly (40x smaller that it's equivalent \textit{Static Network}). For
+these two architectures we show the size at different time during training to
+give a sense how the convergence happen.
+
+\gl{Add the two plots}
+
+\subsection{Multi-Target Linear and Multi-Class Logistic regressions [To be
+  moved in the theoretical part]}
+
+As we showed, Group sparsity share similarities with our method, and we claim
+that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
+to compare the two aproaches.  We decided to focus on multi-target linear
+regression because in the single target case, groups in the Group Sparsity
+problem would have a size of one ($\bm{A}$ would be a vector in this case).
+
+The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
+[ref] for linear regressions and we will use \texttt{gina\_prior2} [ref] and
+the \textit{Gas Sensor Array Drift Dataset} [ref] (that we shorten in
+\texttt{gsadd}) for logistic regressions.
+
+For each dataset we fit with different regularization parameters and measure
+the error and sparsity obtained after convergence. In this context we define
+sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
+absolute value. Regularization parameters were choosed in order to obtain the
+widest sparsity spectrum. Loss is normalized depending on the problem to be in
+the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
+our experiments it is clear that ShrinkNets can fit the data closer than Group
+Sparsity for the same amount of sparsity. The fact that we are able to reach
+very low loss demonstrate that even if our objective function is non convex, in
+practice it works as good or better as convex alternatives. Details about these
+datasets and the parameters used are available in \cref{linear_datasets}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{regressions}
+\vspace*{-5mm}
+\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
+From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
+
+\end{center}
+\vspace*{-4mm}
+\end{figure}
+
+\subsection{Neuron Removal strategies [TO be removed]}
+
+In our previous experiment, we showed that the ShrinkNet loss was
+reasonable in practice, we are now interested in the impact on
+early pruning. The method we suggest for early prunning uses a
+parameter $\gamma$ that control the aggressiveness of neuron removal
+so we will try to evaluate its impact on the final loss achieved by
+the model and the cost required to train the model. Our cost model
+is simple and hardware independant, we sum the number of input neurons
+at each epoch. In theory the cost in time should be asymptotically
+linear to this metric. To have a baseline we also train the same model
+but without neuron removal. Keep in mind that this is just in order to
+have some reference. Indeed, if we were to remove the neurons with small
+weights it would deteriorate the loss (and picking the threshould would
+be completely arbitrary). Therefore the baseline is evaluated with all neurons.
+One could consider it as a "theoretical lower bound" of the best achievable loss.
+
+We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$).
+We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}.
+In order to reduce the noise in the result, each experiment was performed $30$ times and we display the range arround $\pm$ $1$ standard deviation.

### 2018-02-09 paper/ICML/appendix.tex
Resolve most of the bibliography

@@
 \end{proof}
-\subsection{Experiment details}
-\subsubsection{Multi-Target Linear and Logistic regressions}
-\label{linear_datasets}
-\subsubsection{Neuron Removal strategies}
-\subsubsection{Convergence and Training Dynamics of Neural networks}
-\subsubsection{Hyper-optimization of ShrinkNets}
-\subsubsection{Performance}
+\subsection{Additional Experiment}
+As we showed, Group sparsity share similarities with our method, and we claim
+that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
+to compare the two aproaches.  We decided to focus on multi-target linear
+regression because in the single target case, groups in the Group Sparsity
+problem would have a size of one ($\bm{A}$ would be a vector in this case).
+
+The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
+\cite{Spyromitros-Xioufis2016} for linear regressions and we will use \texttt{gina\_prior2} \cite{4371065} and
+the \textit{Gas Sensor Array Drift Dataset} \cite{VERGARA2012320} (that we shorten in
+\texttt{gsadd}) for logistic regressions.
+
+For each dataset we fit with different regularization parameters and measure
+the error and sparsity obtained after convergence. In this context we define
+sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
+absolute value. Regularization parameters were choosed in order to obtain the
+widest sparsity spectrum. Loss is normalized depending on the problem to be in
+the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
+our experiments it is clear that ShrinkNets can fit the data closer than Group
+Sparsity for the same amount of sparsity. The fact that we are able to reach
+very low loss demonstrate that even if our objective function is non convex, in
+practice it works as good or better as convex alternatives.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{regressions}
+\vspace*{-5mm}
+\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
+From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
+
+\end{center}
+\vspace*{-4mm}
+\end{figure}

### 2018-02-09 paper/ICML/approach.tex
Resolve most of the bibliography

--- 2018-02-09 paper/ICML/approach.tex
@@
 We have implemented \textbf{Switch Layers} and the associated training procedure
-as a library in pytorch~\cite{github}.
+as a library in pytorch~\cite{paszke2017automatic}. \gl{This is not a github citation but this is what they ask to cite}
 The layer can be freely mixed with other popular layers such as convolutional

### 2018-02-09 paper/ICML/evaluation.tex
Resolve most of the bibliography

@@
 that it would have not been possible to train enough and get statistically
-significant results. This is why we picked \texttt{CIFAR10} [ref]. It is an
+significant results. This is why we picked \texttt{CIFAR10} \cite{Krizhevsky2009}. It is an
 image classification dataset containing $60000$ color images $(3 \times 32
@@
 
-To solve this task we use the \texttt{VGG16} model [ref]. It is constituted of
+To solve this task we use the \texttt{VGG16} model \cite{Srivastava2014}. It is constituted of
 alternating convolutional layers and \textit{MaxPool} layers interleaved by
@@
 from a range of reasonable values (\gl{should we make them explicit ?}).
-Training is done using our library, based on \texttt{PyTorch} [ref], that
+Training is done using our library, based on \texttt{PyTorch} \cite{paszke2017automatic}, that
 support dynamically resized layers. We train the network using gradient descent
-and \textit{Adam} optimizer [ref]. We start with the learning rate sampled
-randomly and every $5$ epochs of non improvement in validation accuracy we
-divide the learning rate by $10$. We stop training after $400$ epochs or when
-the learning rate is under $10^{-7}$ whichever comes first. \gl{Should I also
-  give the details about the removal strategy we used and the $\gamma$ and
-  threshold I used ? because this is clearly getting boring}
-For each of the models we trained, we pick the epoch with the best validation
-accuracy and report the corresponding testing accuracy. Because of the nature of
-our method, it can happen that for network that are aggressively compressed, the
-best validation accuracy is obtained early in the training, before the size has
-converged. To be sure that accuracy measured corresponds to the final shape and
-not the starting shape, we only consider the second half of the training when
-picking the best epoch. For each model, we also measure the total size, in
-number of floating point parameters, excluding the \textit{Switch Layers}
-because as we saw in section \gl{REFERENCE\_ME}, we can get rid of them when
-training is done.
+and \textit{Adam} optimizer \cite{DBLP:journals/corr/KingmaB14}. We start with
+the learning rate sampled randomly and every $5$ epochs of non improvement in
+validation accuracy we divide the learning rate by $10$. We stop training after
+$400$ epochs or when the learning rate is under $10^{-7}$ whichever comes
+first. \gl{Should I also give the details about the removal strategy we used
+  and the $\gamma$ and threshold I used ? because this is clearly getting
+  boring} For each of the models we trained, we pick the epoch with the best
+validation accuracy and report the corresponding testing accuracy. Because of
+the nature of our method, it can happen that for network that are aggressively
+compressed, the best validation accuracy is obtained early in the training,
+before the size has converged. To be sure that accuracy measured corresponds to
+the final shape and not the starting shape, we only consider the second half of
+the training when picking the best epoch. For each model, we also measure the
+total size, in number of floating point parameters, excluding the
+\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
+get rid of them when training is done.
 
@@
 
-Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. This dataset
+Our second dataset we will evaluate on is \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509}. This dataset
 contains $581012$ description of geographical area (elevation, inclination,
@@
 The only difference in terms of setup are minimal. We use the same architecture
-as [ref], i.e. three layers Fully Connected neural network with  no
-\textit{Dropout} [ref] nor \textit{BatchNorm} [ref]. \gl{Should we say here that we
+as \cite{Scardapane2017}, i.e. three layers Fully Connected neural network with  no
+\textit{Dropout} \cite{Srivastava2014} nor \textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15}. \gl{Should we say here that we
   don't expect Dropout to work here ? I could write an entire paragraph about it
@@
 that this strategy is suboptimal and might need to be adjusted. During our
-experimentations on simpler datasets like \texttt{MNIST} and
-\texttt{FashionMNIST} we observed that even if they have the same number of
+experimentations on simpler datasets like \texttt{MNIST} \cite{Lecun1998} and
+\texttt{FashionMNIST} \cite{Xiao2017} we observed that even if they have the same number of
 classes, input features, and output distribution. For a fixed $\lambda$
@@
   moved in the theoretical part]}
-
-As we showed, Group sparsity share similarities with our method, and we claim
-that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
-to compare the two aproaches.  We decided to focus on multi-target linear
-regression because in the single target case, groups in the Group Sparsity
-problem would have a size of one ($\bm{A}$ would be a vector in this case).
-
-The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
-[ref] for linear regressions and we will use \texttt{gina\_prior2} [ref] and
-the \textit{Gas Sensor Array Drift Dataset} [ref] (that we shorten in
-\texttt{gsadd}) for logistic regressions.
-
-For each dataset we fit with different regularization parameters and measure
-the error and sparsity obtained after convergence. In this context we define
-sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
-absolute value. Regularization parameters were choosed in order to obtain the
-widest sparsity spectrum. Loss is normalized depending on the problem to be in
-the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
-our experiments it is clear that ShrinkNets can fit the data closer than Group
-Sparsity for the same amount of sparsity. The fact that we are able to reach
-very low loss demonstrate that even if our objective function is non convex, in
-practice it works as good or better as convex alternatives. Details about these
-datasets and the parameters used are available in \cref{linear_datasets}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{regressions}
-\vspace*{-5mm}
-\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
-From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
-
-\end{center}
-\vspace*{-4mm}
-\end{figure}
 

### 2018-02-09 paper/ICML/related_work.tex
Resolve most of the bibliography

@@
 The most popular techniques for hyperparameter optimization include simple 
-methods such as random search~\cite{Bergstra2012} which have been shown to work
+methods such as random search~\cite{BergstraJAMESBERGSTRA2012} which have been shown to work
 suprisingly well compared to more complex methods such as those based on

### 2018-02-09 paper/ICML/appendix.tex
Resolve even more references

@@
 \end{proof}
-\subsection{Additional Experiment}
+\subsection{Multi-Target Linear and Multi-Class Logistic regressions experiments}
 As we showed, Group sparsity share similarities with our method, and we claim

### 2018-02-09 paper/ICML/evaluation.tex
Resolve even more references

@@
 involve so many layers that it is impractical to explore the space of possible
-sizes. We considered ImageNet but the time required to train models is so long
+sizes. We considered ImageNet \cite{ILSVRC15} but the time required to train models is so long
 that it would have not been possible to train enough and get statistically
@@
 
-To solve this task we use the \texttt{VGG16} model \cite{Srivastava2014}. It is constituted of
-alternating convolutional layers and \textit{MaxPool} layers interleaved by
-\textit{BatchNorm} [ref] and \textit{ReLU} [ref] layers. The two last layers are
-Fully connected layers separated by just a \textit{ReLU} activation function.
+To solve this task we use the \texttt{VGG16} model \cite{Srivastava2014}. It is
+constituted of alternating convolutional layers and \textit{MaxPool} layers
+interleaved by \textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15} and
+\textit{ReLU} \cite{Nair2010}  layers. The two last layers are Fully connected
+layers separated by just a \textit{ReLU} activation function.
 
@@
 optimal size. We though that picking two times the recommended size for each
-layer (that was designed for ImageNet[ref]), is a generous upper bound. For the
+layer (that was designed for ImageNet), is a generous upper bound. For the
 classification layers we use $5000$ neurons as an upper bound where the ImageNet
@@
 total size, in number of floating point parameters, excluding the
-\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
+\textit{Switch Layers} because as we saw in \cref{neuron_killing}, we can
 get rid of them when training is done.
@@
 as \cite{Scardapane2017}, i.e. three layers Fully Connected neural network with  no
-\textit{Dropout} \cite{Srivastava2014} nor \textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15}. \gl{Should we say here that we
+\textit{Dropout} \cite{Srivastava2014} nor \textit{BatchNorm}. \gl{Should we say here that we
   don't expect Dropout to work here ? I could write an entire paragraph about it
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{neuron_removal}
-\vspace*{-5mm}
-\caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$.
+% \begin{figure}
+% \begin{center}
+% \includegraphics[width=\columnwidth]{neuron_removal}
+% \vspace*{-5mm}
+% \caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$.
 First column is the difference in the final loss in function of the removal factor.
@@
 From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}
-
-\end{center}
-\vspace*{-4mm}
-\end{figure}
+% 
+% \end{center}
+% \vspace*{-4mm}
+% \end{figure}
 
@@
 We sucessfully demonstrated that the architecture \textit{Shrinknets} converge
-to make sense both in term of size and performance. And for a given accuracy the
-size needed is significantly smaller than when we use the classic heursitc we
-commonly use to size convolutional neural networks. It might be an indication
-that this strategy is suboptimal and might need to be adjusted. During our
-experimentations on simpler datasets like \texttt{MNIST} \cite{Lecun1998} and
-\texttt{FashionMNIST} \cite{Xiao2017} we observed that even if they have the same number of
-classes, input features, and output distribution. For a fixed $\lambda$
-\textit{ShrinkNets} converged to considerably bigger networks in the case of
-\texttt{FashionMNIST}. This evidence shows that final architecture not only
-depends on the output distribution or shape of the data but actually reflects
-the dataset (we know that FASHIONMNIST is harder then MNIST)
+to make sense both in term of size and performance. And for a given accuracy
+the size needed is significantly smaller than when we use the classic heursitc
+we commonly use to size convolutional neural networks. It might be an
+indication that this strategy is suboptimal and might need to be adjusted.
+During our experimentations on simpler datasets like \texttt{MNIST}
+\cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017} we observed that
+even if they have the same number of classes, input features, and output
+distribution. For a fixed $\lambda$ \textit{ShrinkNets} converged to
+considerably bigger networks in the case of \texttt{FashionMNIST}. This
+evidence shows that final architecture not only depends on the output
+distribution or shape of the data but actually reflects the dataset, indeed we
+know that \texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.
 
@@
 
-\subsection{Multi-Target Linear and Multi-Class Logistic regressions [To be
-  moved in the theoretical part]}
-
-\subsection{Neuron Removal strategies [TO be removed]}
-
-In our previous experiment, we showed that the ShrinkNet loss was
-reasonable in practice, we are now interested in the impact on
-early pruning. The method we suggest for early prunning uses a
-parameter $\gamma$ that control the aggressiveness of neuron removal
-so we will try to evaluate its impact on the final loss achieved by
-the model and the cost required to train the model. Our cost model
-is simple and hardware independant, we sum the number of input neurons
-at each epoch. In theory the cost in time should be asymptotically
-linear to this metric. To have a baseline we also train the same model
-but without neuron removal. Keep in mind that this is just in order to
-have some reference. Indeed, if we were to remove the neurons with small
-weights it would deteriorate the loss (and picking the threshould would
-be completely arbitrary). Therefore the baseline is evaluated with all neurons.
-One could consider it as a "theoretical lower bound" of the best achievable loss.
-
-We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$).
+% \subsection{Neuron Removal strategies [TO be removed]}
+% 
+% In our previous experiment, we showed that the ShrinkNet loss was
+% reasonable in practice, we are now interested in the impact on
+% early pruning. The method we suggest for early prunning uses a
+% parameter $\gamma$ that control the aggressiveness of neuron removal
+% so we will try to evaluate its impact on the final loss achieved by
+% the model and the cost required to train the model. Our cost model
+% is simple and hardware independant, we sum the number of input neurons
+% at each epoch. In theory the cost in time should be asymptotically
+% linear to this metric. To have a baseline we also train the same model
+% but without neuron removal. Keep in mind that this is just in order to
+% have some reference. Indeed, if we were to remove the neurons with small
+% weights it would deteriorate the loss (and picking the threshould would
+% be completely arbitrary). Therefore the baseline is evaluated with all neurons.
+% One could consider it as a "theoretical lower bound" of the best achievable loss.
+% 
+% 
+% We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$).
 We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}.

### 2018-02-09 paper/ICML/impl.tex
Resolve even more references

@@
 
-\subsubsection{Neuron killing}
+\subsection{Neuron killing}
+\label{neuron_killing}
 Once Switch layers are placed in a network and
@@
 value), this is the method used by deep compression. It is bad because it is
-scale dependant and is not robust to noise in the gradients (explain that)
-\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
-sensitive to noise but has the advantage
-\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold.
-\gl{Maybe we should add some intuition on why it makes sense}.
-\gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}
+scale dependant and is not robust to noise in the gradients (explain that) \\
+
+\textbf{Sign change strategy}:  When using this strategy we consider a neuron
+dead when it changes its sign. This strategy works well in practice but is
+sensible to noise. If we sample a gradient that is not representative of the
+dataset when performing gradient descent then we might wrongly kill a neuron. \\
+
+\textbf{Sign variance strategy}: We measure the exponnential moving variance of
+the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider
+it dead when it goes over a predefined threshold. Thus, this strategy introduce
+two extra parameters, one that controls the behavior of the innertia of the
+variance, and the other is the threshold.
+
+According to our experiments on linear and logistic regressions the
+two last strategies reduce the number of parameter update performed during
+training by at least an order of magnitude with only minimal impact on the final
+error obtained by the model.
 
@@
 We have implemented \textbf{Switch Layers} and the associated training procedure
-as a library in pytorch~\cite{github}.
+as a library in pytorch~\cite{paszke2017automatic}.
 The layer can be freely mixed with other popular layers such as convolutional

### 2018-02-09 paper/ICML/introduction.tex
Resolve even more references

@@
 structure of the network and systematically prune
-connections~\cite{han2015deepcompression,brain-damage} or neurons~\cite{XXX}
+connections~\cite{han2015deepcompression,Cun} or neurons~\cite{XXX}
 based on some loss function.  Although these techniques can substantially
@@
 hyperparameter search over the number of neurons in each layer. Second, in
-contrast to existing neural network compression techniques~\cite{brain-
-damage,han2015deepcompression}, our approach results in models that are both
+contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are both
 not only small, but where the  layers are dense, which means that inference
@@
 of neurons.
-\item \srn{Something about dense networks and then benefit over optimal brain damage}
+\item \srm{Something about dense networks and then benefit over optimal brain damage}
 \item \srm{Some claim about inference time}

### 2018-02-09 paper/ICML/related_work.tex
Resolve even more references

@@
   \item group sparsity, non-parametric neural networks
-  \item training dynamics paper: first overfitting and then randomization?
+  \item training dynamics paper: first overfitting and then randomization?, \gl{Here is the ref, if you can introduce it in the flow \cite{Shwartz-Ziv2017}}
 \end{itemize}
 
-Given the importance of network structure, many techniques have been proposed to
-find the best network structure for a given learning task.
-These techniques broadly fall into four categories: hyperparameter optimization
-strategies, post-training model compression for inference as well as model 
-simplification, techniques to resize models during training, and 
-automated architecture search methods.
+Given the importance of network structure, many techniques have been proposed
+to find the best network structure for a given learning task.  These techniques
+broadly fall into four categories: hyperparameter optimization strategies,
+post-training model compression for inference as well as model simplification,
+techniques to resize models during training, and automated architecture search
+methods.
 
 The most popular techniques for hyperparameter optimization include simple
-methods such as random search~\cite{BergstraJAMESBERGSTRA2012} which have been shown to work
-suprisingly well compared to more complex methods such as those based on
-Bayesian optimization~\cite{Snoek12}.
-Techniques such as~\cite{Snoek12} model generalization performance via 
-Gaussian Processes~\cite{GaussianProcesses} and select hyperparameter 
-combinations that come from uncertain areas of the hyperparameter space.
-Recently, methods based on bandit algorithms (e.g. ~\cite{li2016hyperband, 
-jamieson2016}) have also become a popular way to tune hyperparameters.
-As noted before, all of the above techniques require many tens to hundreds of
-models to be trained, making this process computationally inefficient and slow.
+methods such as random search~\cite{BergstraJAMESBERGSTRA2012} which have been
+shown to work suprisingly well compared to more complex methods such as those
+based on Bayesian optimization~\cite{Snoek12}.  Techniques such
+as~\cite{Snoek12} model generalization performance via Gaussian
+Processes~\cite{GaussianProcesses} and select hyperparameter combinations that
+come from uncertain areas of the hyperparameter space.  Recently, methods based
+on bandit algorithms (e.g. ~\cite{li2016hyperband, jamieson2016}) have also
+become a popular way to tune hyperparameters.  As noted before, all of the
+above techniques require many tens to hundreds of models to be trained, making
+this process computationally inefficient and slow.
 
@@
 DeepCompression~\cite{han2015deepcompression} seek to compress the network to
-make inference more efficient.
-This is accomplished by pruning connections and quantizing weights.
-On similar lines, multiple techniques such as~\cite{romero2014fitnets, 
-hinton2015distilling} have been proposed for distilling a network into a 
-simpler network or a different model.
-Unlike our technique which works during training, these techiques are used after
-training and it would be interesting to apply them to ShrinkNets as well.
+make inference more efficient.  This is accomplished by pruning connections and
+quantizing weights.  On similar lines, multiple techniques such
+as~\cite{romero2014fitnets, hinton2015distilling} have been proposed for
+distilling a network into a simpler network or a different model.  Unlike our
+technique which works during training, these techiques are used after training
+and it would be interesting to apply them to ShrinkNets as well.
+\cite{Abadi2016b} share the common goal of removing entire blocks of parameter to maintain dense matrices, however their method only applies to convolutional layers.
 
 The techniques closed to our work are those based on group sparsity such as
-\mpv{Guillaume: fill in}.
+~\cite{Scardapane2017}, and those like ~\cite{Philipp} who grow and shrink
+dynamically the size of the network during training.
 
@@
 architecture through the use of genetic algorithms and reinforcement learning
-techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}.
-These techniques are focused more on learning higher-level architectures (e.g.
+techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}.  These
+techniques are focused more on learning higher-level architectures (e.g.
 building blocks for neural network architectures) as opposed to learning

### 2018-02-09 paper/ICML/discussion.tex
Improve plots and multiple small changes

@@
 
+\gl{Did not have time to write it but added some pointers}
+
 \begin{itemize}
-  \item Where does the method shine?
-  \item Side-effects of method: smaller networks, time to train
-  \item Potential extensions/limitations
+  \item Where does the method shine:  We shine where there are too many layers
+    To explore the network size and we have to rely on heuristics. It shines by
+    it simplicity compared to other methods \gl{Do we want to talk about the
+      number of lines of codes ?}. Prunning while we train, from the compression
+    results seem to be benificial to prune while training to achieve very good
+    compression.
+  \item Side-effects of method: smaller networks, time to train. There is not
+    significant difference in training time, mostly because the filter layer is
+    not optimized. However we can say the convergence speed is improved. For
+    example
+  \item Potential extensions/limitations: We could add a filter that learn the
+    size of convolutions for convolution layers. Supporting Residual Network
+    would allow us to support more architecture. We could also try to mix try to
+    learn the number of layers such is described in~\cite{meier}
 \end{itemize}

### 2018-02-09 paper/ICML/evaluation.tex
Add convergence plot

@@
 for the best test available test accuracy and a slightly underperforming but
-significantly (40x smaller that it's equivalent \textit{Static Network}). For
+significantly smaller that it's equivalent \textit{Static Network}. For
 these two architectures we show the size at different time during training to
@@
 
-\gl{Add the two plots}
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{size_evolution}
+\vspace*{-5mm} \caption{\label{network_size_evolution} Evolution of the size of
+  each layer over time (lighter: beginning, darker: end). On top a very large
+  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
+  accuracy
+} \end{center}
+\vspace*{-4mm}
+\end{figure}
 

### 2018-02-09 paper/ICML/evaluation.tex
Make a statement less strong

@@
 that the parametrization from a $\lambda$ (real value) to the size of the
-size of the network (vector) is optimal or close to optimal. Indeed, if it was
+size of the network (vector) close to optimal. Indeed, if it was
 not the case then eventually a randomly sampled size would have beaten

### 2018-02-09 paper/ICML/approach.tex
edits

--- 2018-02-09 paper/ICML/approach.tex
@@
+%!TEX root=paper.tex
+
 \section{The ShrinkNets Approach}
 
-In this section we present the \emph{Switch layer}, a core concept of our
-ShrinkNets approach that allows to learn the network size as part of the
-training process. Then, we explain how to adapt the training procedure to
-support the new layer. We begin with a high-level overview of our method.
+In this section describe the
+ShrinkNets approach, which allows us to learn the network size as part of the
+training process. The key idea is the addition of 
+\emph{switch layers} added after each layer in the network;  these 
+layers allow us to disable certain neurons during training.
+ Once we've introducd the basic method, we
+ explain how to adapt the training procedure to
+support this new layer. %We begin with a high-level overview of our method.
 
@@
 At a high-level, the ShrinkNets approach consists of two interconnected stages.
-The first stage is concerned with identifying neurons that are not contributing
+The first stage identifies neurons that do not contribute
 to increasing the prediction accuracy of the network and deacivate them. The

### 2018-02-09 paper/ICML/introduction.tex
Improve plots and multiple small changes
edits

@@
 -- from laptops to phones to embedded sensors --  inference performance and
-model size are becoming equally as important as  traditional measures of
+model size are becoming as important in learning as metrics measures of
 prediction quality. However, these three aspect of model performance --
@@
 \cite{something1,something2} by taking one of two approaches:  either by
-applying quantitazation \cite{quant} or code compilation~\cite{something}
-techniques that can be applied blindly to any network, or they analyze the
-structure of the network and systematically prune
+applying quantization \cite{quant} or code compilation~\cite{something}
+techniques that can be applied blindly to any network, or by analyzing the
+structure of the network and systematically pruning
 connections~\cite{han2015deepcompression,Cun} or neurons~\cite{XXX}
@@
 \cite{something}, especially GPUs which do not efficiently support sparse
-linear algebra.  Third, these techniques generally start by optimizing
+linear algebra.  Third, these techniques generally start by optimizing a
 particular architecture for prediction performance, and then, as a post-
-processing step, apply compression  to generate a smaller model that meets the
+processing step, applying compression  to generate a smaller model that meets the
 resource constraints of the deployment setting.  Because the network
-architecture is essentially fixed during compression,   model architectures
+architecture is essentially fixed during this post-processing,   model architectures
 that work better in small settings may be missed -- this is especially true in
-large networks like many- layered CNNs,  where it is infeasible to try explore
+large networks like many-layered CNNs,  where it is infeasible to try explore
 even a small fraction of possible network configurations.
@@
 hyperparameter search over the number of neurons in each layer. Second, in
-contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are both
+contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are
 not only small, but where the  layers are dense, which means that inference
@@
 which allows us to optimize the network size as the network is trained. 
-\item We show that our technique is a relaxation\mpv{?} of group sparsity and 
-prove \mpv{fill in}. 
+\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
 \item \srm{Some claim about model size vs performance}
@@
 ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
-training time compared to existing hyperparameter optimization methods.
-\item We also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
-of neurons.
+training time compared to existing hyperparameter optimization methods. \srm{Mention the specific 
+model/dataset where this is true.}
+\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
+of neurons. \srm{This claim should be something about how much smaller a network with say 99\%
+accuracy is one some real dataset}
 \item \srm{Something about dense networks and then benefit over optimal brain damage}

### 2018-02-09 paper/ICML/evaluation.tex

@@
+%!TEX root=paper.tex
 \section{Evaluation}
@@
 
-Our second dataset we will evaluate on is \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509}. This dataset
+The second dataset we use for evaluation the \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset. This dataset
 contains $581012$ description of geographical area (elevation, inclination,
 etc...) and the goal is to predict the type of forest growing there. We picked
-this one for couple of reasons. First it is simple that we can reach good
+this dataset for several reasons. First it is simple, such that we can reach good
 accuracy with only a few layers. This important because we want to show that
 \textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
-are sampling the entire space of possible sizes. The second reason is that [ref]
+are sampling the entire space of possible network sizes. The second reason is that Scardapane et al~\cite{Scardapane2017}
 also perform their evaluation on this dataset, which allow us to compare the
-results obtained by the two methods.
+results obtained by the two methods. \srm{what two methods?}
 
@@
 \caption{\label{figure_COVER} Summary of the result of random
-search over the hyper-parameters the \texttt{COVERTYPE} dataset}
+search over the hyper-parameters the \texttt{COVERTYPE} dataset
+\srm{label the x axes on the bottom plots}
+}
 \end{center}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \begin{center}
@@
   network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
-  accuracy
+  accuracy. 
 } \end{center}

### 2018-02-09 paper/ICML/approach.tex
pass on s2; checkpoint

@@
 
-In this section describe the
-ShrinkNets approach, which allows us to learn the network size as part of the
-training process. The key idea is the addition of 
-\emph{switch layers} added after each layer in the network;  these 
-layers allow us to disable certain neurons during training.
- Once we've introducd the basic method, we
- explain how to adapt the training procedure to
-support this new layer. %We begin with a high-level overview of our method.
+In this section we describe the ShrinkNets approach, which allows us to learn
+the network size as part of the training process. The key idea is the addition
+of \emph{switch layers} added after each layer in the network;  these layers
+allow us to disable certain neurons during training.  Once we've introducd the
+basic method, we explain how to adapt the training procedure to support this new
+layer.
 
@@
 At a high-level, the ShrinkNets approach consists of two interconnected stages.
-The first stage identifies neurons that do not contribute
-to increasing the prediction accuracy of the network and deacivate them. The
-second stage is concerned with actually removing the neurons from the network
-and shrinking its size, therefore leading to faster inference times. We give an
-overview of both processes next:
+The first stage identifies neurons that do not contribute to increasing the
+prediction accuracy of the network and deacivates them. The second stage is
+concerned with actually removing the neurons from the network and shrinking its
+size, therefore leading to faster inference times. We give an overview of both
+stages next:
 
@@
 will deactivate the neuron, while $1$ will let the signal go through. These
-switches are part of a new layer, which we call \textbf{Switch layer} which can
+switches are part of a new layer, called \textbf{switch layer}, which can
 be applied to fully connected as well as convolutional layers.
@@
 \noindent\textbf{Neuron Removal: } During this stage, the neurons that are
-deactivated by the Switch layers are actually removed from the network,
+deactivated by the switch layers are actually removed from the network,
 effectively shrinking the network size. This is what leads to faster inference
@@
 
-In the remainder of this section we describe in detail the Switch layer as well
+In the remainder of this section we describe in detail the switch layer as well
 as how to adapt the training process for ShrinkNets.
-
-%This approach assumes that we start with an upper bound on the model size. This
-%obviously translates in a computational overhead. Our insight is that some
-%usless neurons (we have multiple definitions below) can be removed early without
-%impacting the final solution. It has two practical implications: It mitigate the
-%issue we describe but it also allows other neurons to adapt as soon as one of
-%their peer is killed. Existing technique usually remove them after convergence
-%and require an extra fine-tuning process to compensate for the removal.
-
-%We implement our strategy of dynamically deactivating neurons by means of a 
-%specialized neural network layer called the \textbf{Switch Layer}.
-%We first describe the key concepts and theory backing the switch layer and then
-%provide a brief summary of our implementation of switch layers.
-
-%Our approach is based on the insight that given enough capacity (and time), an 
-%optimization routine can find a network that can fit an arbitrary function.
-%Therefore, by starting with an oversize network and applying on/off switches to
-%each of the neurons in it, we can identify a {\it pruned} version of the network
-%that can achieve similar accuracy to the oversized network.
-%
-%
-% If we have an oversized network then there exist a pruned version that can still
-% achieve our goal. The main idea is to consider an on/off switch for each neuron,
-% and we want to find an assignement for this switches that achieve a certain
-% size/accuracy tradeof.
-
-% The key components of the system are: The filter vectors that simulate the
-% continuous on/off switches, a regularization that tries to kill neurons, the
-% neuron removal strategy that detects neurons that should probably be removed,
-% and the garbage collection that effectively remove dead neurons from the model,
-% and the simplifaction procedure that remove the filter vector for fast
-% inference.
-
-% We will describe these components in the upcoming sections.
-
-% \subsection{Notations}
-
-% \par In order to avoid any potential ambiguity, in this section we will
-% describe in details the mathematical notations used in this article. 
-% Non-bold
-% letters represent scalar values, while bold lowercase and upper case
-% repectively denote vectors and matrices. 
-% $\bm{A}^T$ stands for the transpose of
-% the matrix $\bm{A}$. 
-% Subscripts are used to index particular elements of
-% vectors and matrices. 
-% $\bm{x}_i$, $\bm{A}_i$, $\left(\bm{A}^T\right)_j$ and
-% $\bm{A}_{i,j}$ respectively correspond to the $i^{th}$ component of $\bm{x}$,
-% the $i^{th}$ row of $\bm{A}$, the $j^{th}$ column of $\bm{A}$ and the $j^{th}$
-% component of the $i^{th}$ row of $\bm{A}$. 
-% All the following definitions assume
-% $\bm{A}$ to be an $n\times p$ matrix.
-
-% For any $l \in \left[0, +\infty\right]$ we define the norm: $\norm{\bm{A}}_l =
-% \left(\sum_{i=1}^n \sum_{j=1}^p \abs{\bm{A}_{i, j}}^l\right)^{\frac{1}{p}}$. 
-% For the rest of this paper and unless stated otherwise, $\bm{y}$ will represent the output of a network, $\bm{x}$ the input, $\bm{b}$ a bias, $\lambda$ regularization factors, $\Omega$ regularization methods, $\bm{\theta}$ general model parameters and $a$ will stand for any element-wise activation function.
-% The only constraint that we want to enforce is that $a(0) = 0$. 
-% We use $\intint{u, v}$ to denote inteveral of integers, 
-% $\bm{0}$ is the null vector (size depending on the context). 
-% $\#S$ is meant to represent the cardinality of a set $S$. 
-% To simplify the notation of function composition we use the following operator: 
-% $g(f(\bm{x})) = (f \circ g)(\bm{x})$ and for a long sequence of functions from 
-% $f_1$ to $f_n$ we use: $f_n(...f_1(\bm{x})) = \left(\bigcirc_{k = 1}^n f_k\right)(\bm{x})$.
 
@@
 
-% maps
-% For instance, for fully connected layers, $n$=0 and the output is single 
-% dimensional of size $c$ (ignoring batch size for now) while for a 2-D 
-% convolutional layer, $n$=2 and $c$ is the number of output channels or feature 
-% maps.
-%  and furthermore, let the output
-% of layer $l$ be a tensor of shape $\left(C \times D_1 \times \dots \times 
-% D_n\right)$ where $C$ is the number of neurons in $l$.
-% In the case of a fully connected layer, $C$ is the dimensionality of the output
-% of the layer whereas in the case of a convolutional layer, $C$ is the number of
-% feature maps and $\left(D_1 \times \dots \times D_n\right)$ is the size of those feature
-% maps.
+We want to tune the size of $L$ by applying a switch layer, $S$. The switch
+layer is parametrized by a vector $\theta \in \mathbb{R}^c$ such that the result
+of applying $S$ to $L(\bm{x})$ is a tensor also of size $\left(c \times d_1
+\times \dots \times d_n\right)$ such that:
 
-Suppose we wish to tune the size of $L$ by applying a switch layer.
-A switch layer $S$ applied to the output of $L$ can be parametrized by a 
-vector $\theta \in \mathbb{R}^c$ such that the result of applying $S$ to $L(\bm{x})$
-is a tensor also of size $\left(c \times d_1 \times \dots \times d_n\right)$
-such that: 
+%Suppose we wish to tune the size of $L$ by applying a switch layer.
+%A switch layer $S$ applied to the output of $L$ can be parametrized by a 
+%vector
+
 \begin{equation} 
@@
 \end{equation}
-% where $\diag{\bm{\theta}}$ is a $c\times c$ matrix such that: $\forall
-% 1 \leq i \leq c$, $\diag{\bm{\theta}}_{i, i} = \bm{\theta}_i$ and $0$ otherwise. 
+
 Effectively, once passed through the switch layer, each output channel $i$
-produced by $L$ is scaled by the corresponding $\theta_i$.
-If for any $k$, if $\theta_i = 0$, the $i^{\text{th}}$ channel is multiplied by 
-zero and wont contribute to any computations after the switch layer.
-If this happens, we say the Switch layer has {\it deactivated} or killed the 
-neuron of layer $L$ corresponding to channel $i$. 
-% Switch layers have weights in the range $[-\infty,+\infty]$ and are usually 
-% placed after linear and convolutional layers.
-% The \textit{Switch Layer} takes an input of size $\left(B \times C \times D_1
-%   \times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number
-% of features (or channels, in the case of convolutional layers), and $D$ any
-% additional dimension. 
-% This structure makes it compatible with fully connected
-% layers with $n=0$ or convolutional layers with $n=2$. 
-% Their crucial property is
-% a parameter $\theta \in \mathbb{R}^C$. 
-% The output is defined as follows: \vspace{-1em}
-% \begin{equation} 
-% Switch(\bm{I};\bm{\theta}) = \diag{\bm{\theta}} \bm{I}  
-% \end{equation}
-% where $\diag{\bm{b}}$ a $n\times n$ matrix such that: $\forall
-% 1 \leq i \leq n$, $\diag{\bm{b}}_{i, i} = \bm{b}_i$ and $0$ otherwise.
+produced by $L$ is scaled by the corresponding $\theta_i$. Note that when
+$\theta_i = 0$, the $i^{\text{th}}$ channel is multiplied by zero and will not
+contribute to any computations after the switch layer. If this happens, we say
+the switch layer has {\it deactivated} the neuron of layer $L$ corresponding to
+channel $i$.
 
-% Where $\theta$ is expanded in all
-% dimensions to match the input size (except the second one since they are equal
-% by definition).
-
-% These disabled neurons/channels can be removed from the network
-% without changing its output. 
-% Before explaining how that is achieved, we explain
-% next how the weights of the Switch Layer are initialized and adjusted during
-% training.
+We place switch layers after each layer whose size we wish to tune; these are
+typically fully connected and convolutional layers. We discuss next how to train
+ShrinkNets.
 
@@
 
-To tune the size of a network, we place Switch Layers after each layer whose size
-we wish to tune; these are typically the fully connected and convolutional layers
-in a network.
-Since the switch layers are adept at deactivating neurons, we start with an
-oversized network (i.e. network with more capacity than required) and then use
-switch layers to deactivate or kill off neurons that are unnecessary.
+%To tune the size of a network, we place Switch Layers after each layer whose size
+%we wish to tune; these are typically the fully connected and convolutional layers
+%in a network.
+%Since the switch layers are adept at deactivating neurons, we start with an
+%oversized network (i.e. network with more capacity than required) and then use
+%switch layers to deactivate or kill off neurons that are unnecessary.
 
-Formally, we can express this procedure in terms of a sparsity constraint that pushes
-values in the $\theta$ vector to 0.
-Given a neural network parameterized by weights $\bm{W}$ and switch layer 
-parameters $\bm{\theta}$, we optimize the following ShrinkNet loss that 
-augments the regular training loss with a 
-regularization term for the switch parameters and another on the network weights.
+%Formally, 
+For training, we need to account for the effect of the swith layers in the loss
+function. The effect of switch layers can be expressed in terms of a sparsity constraint
+that pushes values in the $\theta$ vector to 0. Then, given a neural network
+parameterized by weights $\bm{W}$ and switch layer parameters $\bm{\theta}$, we
+optimize the following ShrinkNet loss:
+
 \begin{equation}
@@
 \end{equation}
+
+i.e., the expression augments the regular training loss with a regularization
+term for the switch parameters and another on the network weights.
+
+We next analyze why such loss function works to train ShrinkNets and its
+connection to group sparsity:
 

### 2018-02-09 paper/ICML/theory.tex
split section 2 into 2; re-structured section 2; Pass over 2.0 and 2.1; checkpoing---will continue from 2.1 in the morning
pass on s2; checkpoint

@@
-\subsection{Relation to Group Sparsity}
-
-% \begin{equation}
-%   \Omega_\lambda^s = \lambda \norm{\bm{\beta}}_1
-% \end{equation}
-
-Our goal when designing ShrinkNets was to be able to remove inputs
-and outputs of layers. For classic fully connected layers, which are defined
-as :
+%\subsection{Relation to Group Sparsity}
+\noindent\textbf{Relation to Group Sparsity (LASSO): } ShrinkNets removes neurons,
+i.e., inputs and outputs of layers. For a fully connected layer defined as:
 
@@
 
-removing an input neuron $j$ is equivalent to have $\left(\bm{A}^T\right)_j = \bm{0}$
-and removing an output neuron $i$ is the same as having $\bm{A}_i = \bm{0}$ and $\bm{b}_i = 0$. Solving  optimization problems while trying to set entire groups
-of parameters to zero has been already studied and the most popular method
-is without doubt the group sparsity regularization [ref].
-For any partitionning of the set of parameter defining a model in $p$ groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$ we define it the following way:
+Removing an input neuron $j$ is equivalent to have $\left(\bm{A}^T\right)_j =
+\bm{0}$. Removing an output neuron $i$ is the same as having $\bm{A}_i = \bm{0}$
+and $\bm{b}_i = 0$. Solving optimization problems while trying to set entire
+group of parameters to zero is the goal of group sparsity regularization
+\cite{}. For any partitioning of the set of parameter defining a model in $p$
+groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$ we define it the following
+way:
 
@@
 
-In the context of a fully-connected layer, the groups are either: columns of $\bm{A}$ if we want to remove inputs, or rows of $\bm{A}$ and the corresponding entry in $\bm{b}$ if we want to remove outputs.
-For simplicity, we will focus our analysis in the simple one-layer case.
-In this case filtering outputs does not make a lot of sense, this is why we will only consider the former case.
-The group sparsity regularization then becomes:
+In fully-connected layers, the groups are either: columns of
+$\bm{A}$ if we want to remove inputs, or rows of $\bm{A}$ and the corresponding
+entry in $\bm{b}$ if we want to remove outputs. For simplicity, we focus
+our analysis in the simple one-layer case. In this case, filtering outputs does
+not make sense, this is why we will only consider the former case. The
+group sparsity regularization then becomes:
 
@@
 
-Because $\forall i, \#\bm{\theta}_i = n$, To make the notation simpler,
-we embedded $\sqrt{n}$ inside $\lambda$.
+Because $\forall i, \#\bm{\theta}_i = n$, \ra{is \# the general way of expressing
+cardinality? why not |x|?}to make the notation simpler, we
+embedded $\sqrt{n}$ inside $\lambda$.
 
-Since group sparsity and ShrinkNets try to achieve the same goal we will try to understand their similarities and differences. First let's recall the two problems. The original ShrinkNet problem is:
+Group sparsity and ShrinkNets try to achieve the same goal. We discuss next how
+they are related to each other. First let's recall the two problems. The
+original ShrinkNet problem is:
 
@@
 
-We can prove the under the condition: $\forall j\in \intint{1, p}, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}).
-However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}).
-Fortunately, by adding an extra term to the ShrinkNet regularization term we can proove that:
+We can prove that under the condition: $\forall j\in \intint{1, p},
+\norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
+(\cref{gps_equivalence}). However if we relax this constraint then shrinknet
+becomes non-convex and has no global minimum
+(\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}). Fortunately,
+by adding an extra term to the ShrinkNet regularization term we can proove that:
 
@@
 
-has many global minimum (\cref{shrinknet_regularized_minimum}) for all $p>0$. This is the reason we defined the \textit{regularized ShrinkNet penalty} earlier this way:
+has global minimums for all $p>0$ (\cref{shrinknet_regularized_minimum}).
+This is the reason we defined the \textit{regularized ShrinkNet penalty} earlier
+this way:\ra{the notation is slightly different, better to make it consistent}
 
@@
 
-In practice we observed that $p=2$ or $p=1$ are good choice, while the latter will also introduce additional sparsity in the parameters.
+In practice we observed that $p=2$ or $p=1$ are good choice, while the latter
+will also introduce additional sparsity in the parameters.

### 2018-02-09 paper/ICML/evaluation.tex

@@
 
-The goal of our evaluation is to show two main properties of
-\textit{ShrinkNets}: they are exploring the space of possible sizes in a "smart"
-way, and that as a result we obtain the smaller or equal size than
-\textit{Static Networks}. We will then evaluate the performance benefits implied
-by these gains in size.
+The goal of our evaluation is to explore:
+\begin{itemize}
+	\item
+Whether, by varying $\lambda$, \textit{ShrinkNets} can efficiently explore (in terms of number of training runs)  the spectrum of high-accuracy models from small to large, on both CNNs and fully connected networks.
+Our results show that, for each network size, we obtain models that perform as well or better than
+\textit{Static Networks}, trained via traditional hyperparameter optimization.
 
-\subsection{Datasets and Setup}
+\item Whether, because these  smaller networks are dense, they result in improved inference times on both CPUs and GPUs.
+
+\item Whether the ShrinkNets approach results in network architectures that are substantially different than the best network architecutres (in terms of relative number of neurons per layered) identified in the literature.
+
+\item \srm{something else?}
+\end{itemize}
+
+\subsection{Performance vs. Traditional Methods}
+
+We evaluate ShrinkNets on two datasets:  \texttt{CIFAR10} and \texttt{COVERTYPE}.  In this section, we report how we employed ShrinkNets on these datasets and compare our results to 
+training without ShrinkNets.
 
@@
 
-Previous attempt at solving this problem focus on simple datasets and simple
-architectures (limited to Fully connected). We believe that self-resizing
-network really matter for problems where the architecture you need to solve them
-involve so many layers that it is impractical to explore the space of possible
-sizes. We considered ImageNet \cite{ILSVRC15} but the time required to train models is so long
-that it would have not been possible to train enough and get statistically
-significant results. This is why we picked \texttt{CIFAR10} \cite{Krizhevsky2009}. It is an
+Previous research~\cite{Scardapane2017} that attempts to optimize network size during training
+ focused on simple datasets and simple (i.e., fully connected)
+architectures. We believe that self-resizing
+network are most important for problems where the architecture 
+involves many layers, such that that it is impractical to explore the space of all possible
+layer-size configurations. For that reason, we picked \texttt{CIFAR10} \cite{Krizhevsky2009}. It is an
 image classification dataset containing $60000$ color images $(3 \times 32
-\times 32)$, belonging to $10$ different classes.
+\times 32)$, belonging to $10$ different classes, running on  the \texttt{VGG16} network \cite{Srivastava2014}. VGG16
+consists of alternating convolutional layers and \textit{MaxPool} layers
+interleaved by \textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15} and
+\textit{ReLU} \cite{Nair2010}  layers. The two last layers are fully connected
+layers separated by a \textit{ReLU} activation function.
 
-To solve this task we use the \texttt{VGG16} model \cite{Srivastava2014}. It is
-constituted of alternating convolutional layers and \textit{MaxPool} layers
-interleaved by \textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15} and
-\textit{ReLU} \cite{Nair2010}  layers. The two last layers are Fully connected
-layers separated by just a \textit{ReLU} activation function.
+\srm{keep this?}
+ Although ShrinkNets supports larger networks and datasets as well (i.e., ImageNet \cite{ILSVRC15}),  the time required to such train models and get statistically significant result was prohibitive -- especially when comparing against classical hyperparameter search over network architecture.
 
-To turn it into a ShrinkNet we introduce \textit{Switch Layers} after each
-\textit{BatchNorm} and each Fully connected (except the last one).
-
-ShrinkNets assume that the starting size of the network is an upper bound on the
-optimal size. We though that picking two times the recommended size for each
-layer (that was designed for ImageNet), is a generous upper bound. For the
-classification layers we use $5000$ neurons as an upper bound where the ImageNet
-version uses $4096$ \gl{This is on the top of my head, need to be double checked}.
+We applied ShrinkNets to the VGG16 network by adding \textit{Switch Layers} after each
+\textit{BatchNorm} layer and each fully connected layer (except the last).
+Recall that ShrinkNets assume that the starting size of the network is an upper bound on the
+optimal size. For this reason, we simply started with a network with double the recommended size for each
+layer as an upper bound (this is larger than what ImageNet, for example uses). Thus, for the
+classification layers we use $5000$ neurons as a starting limit (ImageNet
+ uses $4096$ \gl{This is on the top of my head, need to be double checked}).
 
 We assume no prior knowledge on the optimal batch size, learning rate,
-$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
-from a range of reasonable values (\gl{should we make them explicit ?}).
-Training is done using our library, based on \texttt{PyTorch} \cite{paszke2017automatic}, that
-support dynamically resized layers. We train the network using gradient descent
-and \textit{Adam} optimizer \cite{DBLP:journals/corr/KingmaB14}. We start with
-the learning rate sampled randomly and every $5$ epochs of non improvement in
+$\lambda$ or weight decay ($\lambda_2$). Instead, we trained a number of models,
+ randomly and independently selecting the values of these parameters 
+from a range of reasonable values (\gl{should we make them explicit ?} \srm{yes}).
+We trained using our modified \texttt{PyTorch} \cite{paszke2017automatic} library that
+supports dynamically resized layers (our code is available at \srm{add anonymized link}). Training is done using gradient descent and the
+ \textit{Adam} optimizer \cite{DBLP:journals/corr/KingmaB14}. Specifically, 
+ we start with
+the learning rate sampled randomly; for every $5$ epochs of non-improvement in
 validation accuracy we divide the learning rate by $10$. We stop training after
-$400$ epochs or when the learning rate is under $10^{-7}$ whichever comes
+$400$ epochs or when the learning rate is under $10^{-7}$, whichever comes
 first.  \gl{Should I also give the details about the removal strategy we used
   and the $\gamma$ and threshold I used ? because this is clearly getting
-  boring} For each of the models we trained, we pick the epoch with the best
+  boring} \srm{probably not necessary} 
+  For each of the models we trained, we pick the epoch with the best
 validation accuracy and report the corresponding testing accuracy. Because of
-the nature of our method, it can happen that for network that are aggressively
-compressed, the best validation accuracy is obtained early in the training,
+the nature of our method, it can happen that for networks that are aggressively
+compressed, the best validation accuracy is obtained early in  training,
 before the size has converged. To be sure that accuracy measured corresponds to
@@
 the training when picking the best epoch. For each model, we also measure the
-total size, in number of floating point parameters, excluding the
-\textit{Switch Layers} because as we saw in \cref{neuron_killing}, we can
-get rid of them when training is done.
+total size, in terms of number of floating point parameters, excluding the
+\textit{Switch Layers} because as described in \cref{neuron_killing}, these are eliminated
+after training.
 
-We want to compare against classical (\textit{Static}) networks. The number of
-parameters that control the size is large: 13 for the size of convolutional
-layers and $2$ for the fully connected ones. Without Shrinknets to help and fuse
-all these parameters in a single $\lambda$ it is infeasible to sample reasonably
-well a search space of that size. This is why we have to rely on the very well
-known heuristic that the original VGG architecture (and many CNNs) \gl{try to
-  find the paper that introduces this heuristic}. For \textit{Static Networks}
-we sample the size between $0.1$ and $2$ times the size optimized for ImageNet.
+We compare against classical (\textit{Static}) networks. In such networks, the number of
+parameters that control the size is large: 13 parameters for the convolutional
+layers and $2$ for the fully connected layers. ShrinkNets effectively fuse
+all these parameters in a single $\lambda$, but in conventional architectures
+where all of these parameters are free, it is infeasible to obtain a reasonable
+sample of a search space of this size. For this reason, we rely on the conventional
+ heuristic that the original VGG architecture (and many CNNs) \gl{try to
+  find the paper that introduces this heuristic} user, where \srm{describe what the heuristic is -- doubling of neurons up to apoint?} For \textit{Static Networks}
+we sample the size between $0.1$ and $2$ times the size \srm{size of what?} optimized for ImageNet. \srm{Why are we using ImageNet and not CIFAR10 as the comparison point?}
 We report the same numbers as we did for \textit{ShrinkNets} and we compare the
-two distributions of models we obtain on the first plot of \cref{figure_CIFAR10}.
+two distributions.  
+\srm{I worry that this method of selecting network sizes for Static will of course constrain it to larger sizes and worse perforamance.
+What if we just randomly sample networks?
+Would it look terrible?}
+
+The results are shown in the top figure of \cref{figure_CIFAR10}.
+Here, the blue dots show the models produced by ShrinkNets, and the orange dots show the models produced for the static networks.
+For each model, we plot its accuracy and model size.
+The lines show the Pareto frontier of models in each of the two optimization settings.
+From the figure, it's apparent that ShrinkNets much more effectively explores the trade-off between model size and accuracy.
+ \srm{Would be good to show Lambda values on the figure somehow.  }
+ \srm{I thought we were going to summarize with distributional plots instead of Pareto frontiers?}
+ \srm{Summarize more quantitatively -- best model performance, model performance drop off for a factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim in the intro, i.e.,
+ ``Note that the best performing ShrinkNets models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets model is x times smaller.
+In addition, if we give up just 1\% error, ShrinkNets finds a model that is z times smaller.'' (If we do this, would be good to highlight these points in the figure somehow)}
 
@@
 
-The second dataset we use for evaluation the \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset. This dataset
-contains $581012$ description of geographical area (elevation, inclination,
-etc...) and the goal is to predict the type of forest growing there. We picked
+The second dataset we use for evaluation is the \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset. This dataset
+contains $581012$ descriptions of geographical area (elevation, inclination,
+etc...) and the goal is to predict the type of forest growing in each area. We picked
 this dataset for several reasons. First it is simple, such that we can reach good
-accuracy with only a few layers. This important because we want to show that
+accuracy with only a few fully-connected layers. This important because we want to show that
 \textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
@@
 also perform their evaluation on this dataset, which allow us to compare the
-results obtained by the two methods. \srm{what two methods?}
+results obtained by our method with the method in ~\cite{Scardapane2017}.
 
-The only difference in terms of setup are minimal. We use the same architecture
-as \cite{Scardapane2017}, i.e. three layers Fully Connected neural network with  no
-\textit{Dropout} \cite{Srivastava2014} nor \textit{BatchNorm}. \gl{Should we say here that we
+The experimental setup on this dataset is similar to {\tt CIFAR10}. We use the same architecture
+as \cite{Scardapane2017}, i.e., three fully-connected layers network with  no
+\textit{Dropout} \cite{Srivastava2014} or \textit{BatchNorm}. \gl{Should we say here that we
   don't expect Dropout to work here ? I could write an entire paragraph about it
-  if needed}. In this case for the \textit{Static Networks}, we sample
-independently sizes of the three different layers to explore all possible
+  if needed}. In this case, for the \textit{Static Networks}, we 
+independently samples the sizes of the three different layers to explore all possible
 architectures.
 
-\subsection{Results of the random search procedure}
+The results are shown in the top figure of \cref{figure_COVER}, with the two optimization methods plotted as before.
+Here, {\it Static} method finds models that perform well at a variety of sizes, because it is able to explore the entire parameter space.
+This is as expected;  the fact that ShrinkNets performs as well as the Static indicates that ShrinkNets is doing an effective job of exploring the parameter space using just the single $\lambda$ parameter.
+ \srm{Summarize more quantitatively -- best model performance, model performance drop off for a factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim in the intro, i.e.,
+ ``Here, the best performing ShrinkNets models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets model is x times smaller.
+Further, note that ShrinkNets finds a model with 9x.x\% accuracy that is y times than the best performing model.
+ Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a model that is z times smaller.'' (If we do this, would be good to highlight these points in the figure somehow)}
 
-On the plot, the Pareto front for the two training methods clearly indicates
-that not only \textit{ShrinkNets} find models that are as accurate as
-\textit{Static Networks}, but they are more efficient in terms of size. Even
+\subsubsection{Discussion}
+
+\srm{we may not need to keep this unless we can think of something more to say}
+
+The Pareto frontier in the two figures shows that 
+that  \textit{ShrinkNets} is able find models that both as accurate and smaller than
+\textit{Static Networks}.
 when we sample the entire size space (in the \texttt{COVERTYPE} case),
 \textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
-it has two implications. First it reinforces, our observation in [ref] that
+This has two implications. First it reinforces our observation \srm{our observation?} in [ref] that
 showed that the models do not suffer from the non-convexity introduced by the
@@
 not the case then eventually a randomly sampled size would have beaten
-\textit{ShrinkNets} models. \gl{Too strong ?}
+\textit{ShrinkNets} models. \gl{Too strong ?} \srm{I think this is too strong -- we have no evidence this is true, do we?}
 
@@
 
-We showed in the previous section that \textit{ShrinkNets} were able to find
-more or at least as efficient as \textit{Static Networks}. In this experiment we
+We showed in the previous experiments that the \textit{ShrinkNets} approach is able to find
+networks with accuracy equal to or better than \textit{Static Networks}. In this experiment we
 want to determine benefits of the smaller size we get.
@@
 
-Regarding size, the key observation we can make is that size improvenets are
+Regarding size, the key observation we can make is that size improvements are
 significant for the \texttt{CIFAR10}. In the range of accuracies we are
@@
 with a batch size of $1$ and \texttt{CIFAR10} with a batch size of $1$ on GPU),
-improvements are dominted by noise. However, on machine learning frameworks
+improvements are dominated by noise. However, on machine learning frameworks
 more focused on latency it should be possible to measure them.
@@
 
-\begin{figure}
+\begin{figure*}[t]\centering
+\begin{minipage}{2.7in}
 \begin{center}
@@
 \vspace*{-4mm}
-\end{figure}
-
-\begin{figure}
+\end{minipage}
+\begin{minipage}{2.7in}
 \begin{center}
@@
 \vspace*{-4mm}
-\end{figure}
+\end{minipage}
+\end{figure*}
 
@@
 
-We sucessfully demonstrated that the architecture \textit{Shrinknets} converge
-to make sense both in term of size and performance. And for a given accuracy
-the size needed is significantly smaller than when we use the classic heursitc
-we commonly use to size convolutional neural networks. It might be an
-indication that this strategy is suboptimal and might need to be adjusted.
-During our experimentations on simpler datasets like \texttt{MNIST}
-\cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017} we observed that
-even if they have the same number of classes, input features, and output
-distribution. For a fixed $\lambda$ \textit{ShrinkNets} converged to
+The previous experiments showed that \textit{ShrinkNets} finds architectures
+the effectively explore the frontier of model size and accuracy. Further, for
+a  given accuracy,
+the size needed is significantly smaller than when we use the \srm{name it} heuristic
+ commonly used to size convolutional neural networks. This suggests that this
+ conventional heuristic may not in fact be optimal, especially when looking for 
+ smaller models. 
+Empirically we observed this to often be the case.  For example, 
+during our experimentations on the \texttt{MNIST}
+\cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017} datasets (not reported here due to space constraints), we observed that
+even though these datasets have the same number of classes, input features, and output
+distributions,  for a fixed $\lambda$ \textit{ShrinkNets} converged to
 considerably bigger networks in the case of \texttt{FashionMNIST}. This
-evidence shows that final architecture not only depends on the output
-distribution or shape of the data but actually reflects the dataset, indeed we
-know that \texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.
+evidence shows that optimal architecture not only depends on the output
+distribution or shape of the data but actually reflects the dataset.  This makes sense,
+as  \texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.
 
-We provide two examples of architectures learned by \textit{ShrinkNet}. One
-for the best test available test accuracy and a slightly underperforming but
-significantly smaller that it's equivalent \textit{Static Network}. For
-these two architectures we show the size at different time during training to
-give a sense how the convergence happen.
+To illustrate this point on a larger dataset, 
+we show two examples of architectures learned by \textit{ShrinkNets} in Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the best
+ test accuracy, with \srm{identical performance to the best static network?}; 
+ the bottom shows a network that slightly under-performs the best in terms of accuracy but is
+significantly smaller that the best equivalent \textit{Static Network} \srm{how much smaller?}.
+In the plot, the dashed line shows the number of neurons in each layer of the original VGG net, and the shaded regions show the size of the ShrinkNet as it converges (with the darkest region representing the fully converged network).
+Observe that the final network that is trained looks quite different in the two cases, with the optimal performing network appearing similar to the original VGG net, whereas the shrunken network allocates many fewer neurons to the middle layers, and then additional neurons to the final fewer layers.
 
-\begin{figure}[t]
+\begin{figure}[htb]
 \begin{center}
-\includegraphics[width=\columnwidth]{size_evolution}
-\vspace*{-5mm} \caption{\label{network_size_evolution} Evolution of the size of
+\includegraphics[width=.7\columnwidth]{size_evolution}
+\vspace*{-5mm} 
+\caption{ Evolution of the size of
   each layer over time (lighter: beginning, darker: end). On top a very large
@@
   accuracy. 
-} \end{center}
+} 
+\label{fig:network_size_evolution}
+\end{center}
 \vspace*{-4mm}

### 2018-02-09 paper/ICML/related_work.tex

@@
+%!TEX root=paper.tex
 \section{Related Work}
@@
 \begin{itemize}
-  \item Hyperparameter optimization: random, bayesian opt, bandit methods
-  \item distillation techniques
-  \item post-training compression techniques
-  \item group sparsity, non-parametric neural networks
+  \item Other techniques for choosing network size (e.g., hyperparmeter optimization) -- manual effort vs optimal techniques -- people actually don't treat network size as a hyperparameter;  we do!
+Also brute force techniques~\cite{nvidia-paper-xxx}
+  \item distillation techniques -- train a big net, then train a smaller net from it 
+  \item post-training compression techniques -- brain damage , 
+  \item group sparsity e.g., \cite{Scardapane2017} and non-parametric neural networks -- 
   \item training dynamics paper: first overfitting and then randomization?, \gl{Here is the ref, if you can introduce it in the flow \cite{Shwartz-Ziv2017}}

### 2018-02-09 paper/ICML/appendix.tex
Improve proofs

@@
 \subsection{Proofs}
-Unless specified, all the proofs consider the Multi-Target linear regression problem
+Unless stated explicitely, all the propositions consider the Multi-Target linear regression problem.
 \begin{proposition}
@@
      = &\min_{\bf{A'}, \bm{\beta}} \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1 \\
-     & \text{s.t.} \forall j \in \intint{1, p}, \norm{\left(A'^T\right)_j}_2^2 = 1
+     & \text{s.t.} \forall j, 1 \leq j \leq p, \norm{\left(A'^T\right)_j}_2^2 = 1
   \end{align*}
@@
 \begin{proof}
+  we will split this proof in two different sections. the first one will
+  demonstrate that there is at least one global minimum. and the second
+  will show how to construct $2^k$ distinct solutions from a single global
+  minimum.
   In order to prove this statement we will show that for any solution $\bm{A}$ in the first problem, there exists a solution in the second with the exact same value, and vice-versa.
-We now assume we have a potential solution $\bm{A}$ for the first problem and we define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$.
+  \\ \textbf{Part 1:} We assume we have a potential solution $\bm{A}$ for the first problem and we define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$.
 It is easy to see that the constraint on $\bm{A}'$ is statisfied by construction.
@@
   \end{align*}
-  Assuming we take an $\bm{A}'$ that satisfy the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
+  Which concludes the first part.
+  \\ \textbf{Part 2:} Assuming we take an $\bm{A}'$ that satisfy the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
 We can apply the same operations in reverse order and obtain an instance of the first problem with the same value.
-We can now see that the two problems must have the same minimum otherwise we would be able to construct a solution to the other with exact same value.
+  \\ \textbf{Conclusion} There is no way these two problems have different minima,
+  because we are able to construct a solution to a problem from the solution
+  of the other while preserving the value of the objective.
 \end{proof}
@@
 \begin{proof}
-  To prove this we will take the simplest instance of the problem: with only scalars.
+  To prove this we will take the simplest instance of the problem: where everything is a scalar.
 We have $f(a, \beta) = \left(y - a\beta x\right)^2$.
-For simplicty let's take $y = $ and $x > 0$.
-If we take two candidates $s_1 = (0, 2)$ and $s_2 = (2, 0)$, we have $f(s_1) = f(s_2) = 0$.
+For simplicty let's take $y = 0$ and $x > 0$.
+If we consider two candidates $s_1 = (0, 2)$ and $s_2 = (2, 0)$, we have $f(s_1) = f(s_2) = 0$.
 However $f(\frac{2}{2}, \frac{2}{2}) = x > \frac{1}{2} f(0, 2) + \frac{1}{2}f(2, 0)$, which break the convexity property.
-Since we showed that a particular case of the problem is non-convex then necessarly the general cannot be convex.
+Since we showed that a particular case of the problem is non-convex then necessarly the general case cannot be convex.
 \end{proof}
@@
 \begin{proof}
-First let's prove that there is at least one minimum to this problem.
+  We will split this proof in two parts. First we will show that there is at least
+  one global minimum, then we will show how to construct $2^n - 1$ other distinct
+  solutions with the same objective.
+\\ \textbf{Part 1:}
 The two components of the expression are always positive so we know that this problem is bounded by below by $0$.
-Let's assume this function does not have a minimum.
-Then there is a sequence of parameters $(S_n)_{n>0}$ such that the function evaluated at that point convereges to the infimum of the problem.
-Since the function is defined everywhere does not have a minimum then this sequence must diverge.
-Since the entire sequence deverge the there is at least one individual parameter that diverges.
-First case, the parameter is a component $k$ of some $\bm{\beta_i}$ for some $i$.
-Necessarly $\norm{\bm{\beta_i}}_1$ diverge towards $+ \infty$, which is incompatible with the fact that $(S_n)$ converges to the infimum.
-We can have the exact same argument if the diverging parameter is in $\bm{A_i}$ or $\bm{b_i}$ because $p > 0$.
-Since there is always a contradiction then our assumption that the function has no global minimum must be false.
-Therefore, this problem has at least one global minimum.
-
-\par Let's consider one optimal solution of the problem.
+$\Omega_{\lambda, \lambda_2, p}^{rs}$ is trivially coercive.
+Since we have a sum of terms, all bounded by below by $0$ and one of them is coercive, then the entire function admit at least one global minimum.
+\\ \textbf{Part 2:} Let's consider one global minimum.
 For each component $k$ of $\bm{\beta_i}$ for some $i$.
-Negating it and negating the $k^{th}$ column of $\bm{A_i}$ does not change the the first part of the objetive because the two factors cancel each other.
+Negating it and negating the $k^{th}$ column of $\bm{A_i}$ do not change the the first part of the objetive because the two factors cancel each other.
 The two norms do not change either because by definition the norm is independant of the sign.
-As a result these two sets of parameter have the same value and are both global minimum.
+As a result these two sets of parameter have the same value and by extension also global minimuma.
 It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$.

### 2018-02-09 paper/ICML/evaluation.tex

@@
 
+\ra{add here the impl. thingy from s3, so we give the context of how we use
+shrinknets}
+
 \subsection{Performance vs. Traditional Methods}
@@
 
-Previous research~\cite{Scardapane2017} that attempts to optimize network size during training
+\ra{this is related work}Previous research~\cite{Scardapane2017} that attempts to optimize network size during training
  focused on simple datasets and simple (i.e., fully connected)
@@
 involves many layers, such that that it is impractical to explore the space of all possible
-layer-size configurations. For that reason, we picked \texttt{CIFAR10} \cite{Krizhevsky2009}. It is an
+layer-size configurations.\ra{until here} For that reason, we picked \texttt{CIFAR10} \cite{Krizhevsky2009}. It is an
 image classification dataset containing $60000$ color images $(3 \times 32

### 2018-02-09 paper/ICML/impl.tex

--- 2018-02-09 paper/ICML/impl.tex
@@
 
-\subsubsection{Neuron killing}
-Once Switch layers are placed in a network and
-initialized (sampled from the $\mathcal{N}(0, 1)$ distribution),
+In this section we discuss practical aspects of ShrinkNets.
 
-\textbf{Threshold strategy}:  We kill neurons based on a threshold (in absolute
-value), this is the method used by deep compression. It is bad because it is
-scale dependant and is not robust to noise in the gradients (explain that)
-\\ \textbf{Sign change strategy}:  We look at when the sign change. This is also
-sensitive to noise but has the advantage
-\textbf{Sign variance strategy}: We measure the variance of the sign ($-1, 1$) of each component in the \textit{Switch Layer}, and consider it dead when it goes over a predefined threshold.
-\gl{Maybe we should add some intuition on why it makes sense}.
-\gl{We should probably explain the impact of $\gamma$ and report numbers from the expertiment that show that it does not hurt too much to kill neurons, we have the data in this experiment in the evaluation that we probably want to remove later.}
+%The previous section described the switch layers, which deactivate neurons
+%on-the-fly. To benefit from ShrinkNets in practice, we must overcome two
+%challenges. First, to effectively reduce the network size we must remove the
+%deactivated neurons. Since removed neurons will no longer contribute to
+%improving prediction accuracy, we must be confident when removing them. Second,
+%for inference, we must remove the switch layers from the network. We describe
+%our solution for both challenges in this section.
 
-\subsection{Implementation}
+\subsection{On-The-Fly Neuron Removal}
+\label{neuron_killing}
 
-We have implemented \textbf{Switch Layers} and the associated training procedure
-as a library in pytorch~\cite{github}.
-The layer can be freely mixed with other popular layers such as convolutional
-layers, batchnorm layers, fully connected layers etc.
-There are two key challenges that must be overcome while implementing 
-\textbf{Switch Layers}.
-First, since ShrinkNets kill off a large fraction of neurons, we must remove the
-overhead of carrying around dead neurons.
-And second, we must update the various network layers and training machinery (e.g.
-optimizer state) to reflect the deactivation of neurons.
-We address these challenges by augmenting every layer with additional information
-about neuron status and implementing a \emph{neural garbage collection} 
-mechanism which prunes deactivated neurons on-the-fly and updates the state of 
-the training machinery.
-% We do so by augmenting every layer with additional information such as what
-% neurons have been deactivated.
-% The layer then updates its size accordingly and this change is then propagated
-% to other parts of the training machinery including the optimizer which must
-% know the sizes of parameters.
+Switch layers are initialized with weights sampled from $\mathcal{N}(0,1)$, and
+their values change as part of the training process so as to swith \emph{on} or
+{off} neurons. When neurons are deactivated by switch layers, we want to remove
+them to shrink the network size. Because after removing a neuron it will no
+longer contribute to improving prediction accuracy, we must devise strategies
+that remove neurons while being robust to changing values. We observe three
+strategies:
 
-A second implementation challenge we address with ShrinkNets is the potentially
-higher inference time.
-This increase in inference time is both due to the extra computation introduced 
-by switch layers and because our switch layers are not currently optimized for 
-CUDA.
-Therefore, for now, our library provides a post-training routine to ``fold''
-switch layers into existing, optimized layers.
-Specifically, for every switch layer, we check if the parent or child of this 
-layer is a linearly scalable layer (e.g. convolutional layer, fully connected layer,
-batchnormalization layer) and if so, we fold the switch layer into this 
-neighboring layer by multiplying through by the switch weights.
-In the unlikely case that a switch layer is sandwiched between two non-linearly
-scalable layers, we leave the switch layer as is.
+\textbf{Threshold strategy}: Under this strategy neurons are removed based on a
+fixed threshold expressed in terms of its absolute value. This is the method
+used by deep compression \cite{}. We found this method is not robust to noise in
+the gradients---which occurs commonly when training networks with stochastic
+gradient descent---because the threshold depends on the scale of each weight.
 
-% \subsection{Speeding up training}
+\textbf{Sign change strategy}: Under this strategy neurons are removed when the
+weight value changes its sign. This strategy works well in practice but it is
+also sensible to gradient noise. \ra{explain what's the consequence of that} If
+we sample a gradient that is not representative of the dataset when performing
+gradient descent then we might wrongly kill a neuron.\ra{last sentence is
+unclear}
 
-% In order to have a practical implementation of ShrinkNets it is absolutely
-% necessary to prune useless neurons as quick as possible. In order to try more
-% different strategies we split this task in two subproblems: detecting
-% potentially non-crucial neurons and setting their corresponding entry in the
-% switch layer to exactly 0, and neural garbage collection that
+\textbf{Sign variance strategy}: We measure the exponential moving variance of
+the sign ($-1, 1$) of each parameter in the \textit{switch layer}. When the
+value of the exponential moving variances goes over a predefined threshold, we
+consider the parameter is deactivating the neuron, and therefore we remove it.
+This strategy introduces two extra parameters, one to control the behavior of
+the inertia of the variance, and the threshold, but we have found it is the
+best performing in practice.
 
-% In our library we implemented a variant of the second strategy and the last one.
+The last two strategies perform the best in practice; they reduce the network
+parameters by an order of magnitude with only a minimal impact on the final
+error obtained by the model.
 
-% \subsubsection{Neural garbage collection}
+%According to our experiments on linear and logistic regressions the
+%two last strategies reduce the number of parameter update performed during
+%training by at least an order of magnitude with only minimal impact on the final
+%error obtained by the model.
 
-% It is possible to reduce the overhead of the training process by removing
-% neurons as soon as they become deactivated by $\theta$ going to 0.
-%If
-%disabled neurons are not quickly removed, the overhead might cause the training
-%process to be significantly slower than classic neural networks. 
-% To do this, we implemented a \emph{neural garbage collection} mechanism which
-% prunes deactivated neurons on-the-fly,  reducing the processing time
-% and memory overhead. 
-% To support this feature, it is crucial to understand the
-% information flow between neurons and layers in the neural network. 
-% We achieve
-% this by representing such information flow as a graph. 
-% Vertices represent layers,
-% and edges are event-hubs responsible for propagating information about disabled
-% neurons to the relevant layers. 
-% As soon as a layer receive an event, it updates
-% his parameters to reflect the new size. 
-% Each operation is stored in a log that
-% is used later to update other component of the system. 
-% For example some
-% optimizers like Adam [Ref] store state about each parameter, their state needs
-% to be updated the exact same way and at the exact same time as layers in order
-% to obtain apropriate parameter updates.
+\subsection{Additional Optimizations for ShrinkNets}
 
-% \subsubsection{Speeding up Inference}
-% \mpv{This may be moved to discussion or ``other considerations'' or impl details.}
+\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain
+reduced-sized networks while training, which is the first benefit towards faster
+inference. This networks are readily available for inference. However, because
+they include switch layers---and therefore more parameters---they introduce
+unnecessary overhead at inference time. To avoid this overhead, we reduce the
+network parameters by combining each switch layer with its respective network
+layer by multiplying the respective parameters.  \ra{can't we just simply
+prevent the following problem at network design time?}In the unlikely case that a switch
+layer is sandwiched between two non-linearly scalable layers, we leave the
+switch layer as is.
 
-% our post-processing code searches the 
-% network graph to identify a parent or child layer the linear layer closest (child or parent) to every 
-% switch layer and multiplies the weights of that layer by the corresponding
-% switch layer weights.
+\noindent\textbf{Neural Garbage Collection: }ShrinkNets decide on-the-fly which
+neurons to remove. Since ShrinkNets remove a large fraction of neurons, we must
+dynamically resize the network at runtime to not carry on the 
+unnecessary overhead. We implement a neural garbage collection method as part of
+our library which takes care of updating the necessary network layers as well as
+updating optimizer state to reflect the neuron removal.
 
-% Our proposed \textit{Switch Layer} are relevant only during training, and can be
-% removed from the network architecture during inference if they can be ``folded''
-% into the nearest linear layer.
-% Specifically, we provide a post-processing routine that will, for each switch 
-% layer, search the network graph
+%\ra{move to eval:implementation, retrieve the neuran garbace collection and
+%place it somewhere here}
+%We have implemented \textbf{Switch Layers} and the associated training procedure
+%as a library in pytorch~\cite{paszke2017automatic}.  The layer can be freely
+%mixed with other popular layers such as convolutional layers, batchnorm layers,
+%fully connected layers etc.  There are two key challenges that must be overcome
+%while implementing \textbf{Switch Layers}.  
+%First, since ShrinkNets kill off a
+%large fraction of neurons, we must remove the overhead of carrying around dead
+%neurons.  And second, we must update the various network layers and training
+%machinery (e.g.  optimizer state) to reflect the deactivation of neurons.  We
+%address these challenges by augmenting every layer with additional information
+%about neuron status and implementing a \emph{neural garbage collection}
+%mechanism which prunes deactivated neurons on-the-fly and updates the state of
+%the training machinery.
 
-% The sole puropose of \textit{Switch Layer} are to detect which neurons should be
-% killed and which should be left. When the training is over we will never remove
-% more neurons. Therefore, they loose all their interest at inference time. 
-% To
-% improve size and inference time we propose the following method to get rid of
-% them without changing the output of the model (modulo floating point errors).
-% The basic idea is to start from every \textit{Switch Layer} and try to find the
-% nearset linear operator (child or parent) and multiply its weights by the values
-% in the switch layer. For example we can merge Filter layers with surrounding
-% Convolutional layer, Linear layer or even BatchNormalization [ref] if they are
-% before the \textit{Switch Layer}. However we need to be extremely careful not to
-% cross a non-linearity otherwise it would change the output of network.
+%A second implementation challenge we address with ShrinkNets is the potentially
+%higher inference time.  This increase in inference time is both due to the extra
+%computation introduced by switch layers and because our switch layers are not
+%currently optimized for CUDA.  Therefore, for now, our library provides a
+%post-training routine to ``fold'' switch layers into existing, optimized layers.
+%Specifically, for every switch layer, we check if the parent or child of this
+%layer is a linearly scalable layer (e.g. convolutional layer, fully connected
+%layer, batchnormalization layer) and if so, we fold the switch layer into this
+%neighboring layer by multiplying through by the switch weights.  
+%In the unlikely
+%case that a switch layer is sandwiched between two non-linearly scalable layers,
+%we leave the switch layer as is.

### 2018-02-09 paper/ICML/approach.tex
edits

@@
 of \emph{switch layers} added after each layer in the network;  these layers
-allow us to disable certain neurons during training.  Once we've introducd the
-basic method, we explain how to adapt the training procedure to support this new
+allow us to disable certain neurons during training.  We start by introducing the
+basic method, and then explain how to adapt the training procedure to support this new
 layer.
@@
 
-At a high-level, the ShrinkNets approach consists of two interconnected stages.
-The first stage identifies neurons that do not contribute to increasing the
-prediction accuracy of the network and deacivates them. The second stage is
-concerned with actually removing the neurons from the network and shrinking its
-size, therefore leading to faster inference times. We give an overview of both
-stages next:
+At a high-level, out approach consists of two interconnected stages.
+The first stage identifies neurons that do not improve the
+prediction accuracy of the network and deactivates them. The second stage then
+removes neurons from the network, shrinking its
+size and yielding faster inference times. Broadly, these stages work as follows:
 
 \noindent\textbf{Deactivating Neurons On-The-Fly: }During the first stage,
-ShrinkNets applies an on/off switch to every neuron of an initially oversized
+ShrinkNets applies an on/off switch to every neuron of an initially over-sized
 network. We model the on/off switches by multiplying each input (or output) of
-each layer by a parameter $\bm{\theta}$, with values $0$ or $1$. A value of $0$
+each layer by a parameter $\bm{\theta}\in\{0,1\}$. A value of $0$
 will deactivate the neuron, while $1$ will let the signal go through. These
-switches are part of a new layer, called \textbf{switch layer}, which can
-be applied to fully connected as well as convolutional layers.
+switches are part of a new layer, called the \textbf{switch layer}; this layer applies 
+to fully connected as well as convolutional layers.
 
-We want to minimize the number of on switches to reduce the model size as much
-as we can, while preserving prediction accuracy. This can be achieved by jointly
+Our objective is to minimize the number of ``on'' switches to reduce the model size as much
+as possible while preserving prediction accuracy. This can be achieved by jointly
 minimizing the objective of the network and a factor of the L0 norm of the
-vector containing all the on/off switches. Because finding an optimal binary
-assignement is an NP-Hard problem, we allow $\bm{\theta}$ to be a real number
-instead of a 0/1 value, thus constraining the L1 norm as opposed to the L0 norm.
+vector containing all the switches. Because finding an optimal binary
+assignment is an NP-Hard problem, we relax the problem by allowing
+ $\bm{\theta}$ to be a real number
+instead of a binary value and constrain it using the L1 instead of L0 norm.
 
@@
 deactivated by the switch layers are actually removed from the network,
-effectively shrinking the network size. This is what leads to faster inference
+effectively shrinking the network size. This step improves inference
 times, as we demonstrate in our evaluation. We choose to remove neurons at
-training time because we have observed that allows the active neurons to adapt
+training time because we have observed that this allows the remaining active neurons to adapt
 to the new network architecture. Existing techniques focus on neuron removal
 after training, and require an extra fine-tuning process to compensate for the
-removal.
+removal.\srm{cite something?}
 
 In the remainder of this section we describe in detail the switch layer as well
-as how to adapt the training process for ShrinkNets.
+as and the training process for ShrinkNets, and then describe the removal process in Section~\ref{neuron_killing}.
 
@@
 d_n\right)$ where $c$ is the number of neurons in that layer.  For instance, for
-fully connected layers, $n$=0 and the output is single dimensional of size $c$
+fully connected layers, $n$=0 and the output is single dimensional vector of size $c$
 (ignoring batch size for now) while for a 2-D convolutional layer, $n$=2 and $c$
@@
 
-We want to tune the size of $L$ by applying a switch layer, $S$. The switch
+We want to tune the size of $L$ by applying a switch layer, $S$, containing $c$
+switches.  The switch
 layer is parametrized by a vector $\theta \in \mathbb{R}^c$ such that the result
-of applying $S$ to $L(\bm{x})$ is a tensor also of size $\left(c \times d_1
+of applying $S$ to $L(\bm{x})$ is a also a tensor size $\left(c \times d_1
 \times \dots \times d_n\right)$ such that: 
-
 %Suppose we wish to tune the size of $L$ by applying a switch layer.
@@
 %vector 
-
 \begin{equation} 
-S_{\theta}(L(\bm{x}))_{i,...} = \bm{\theta}_iL(\bm{x})_{i, ...}
+S_{\theta}(L(\bm{x}))_{i,...} = \bm{\theta}_iL(\bm{x})_{i, ...} \forall i \in [1\ldots c]
 \end{equation}
-
-Effectively, once passed through the switch layer, each output channel $i$
+Once passed through the switch layer, each output channel $i$
 produced by $L$ is scaled by the corresponding $\theta_i$. Note that when
 $\theta_i = 0$, the $i^{\text{th}}$ channel is multiplied by zero and will not
-contribute to any computations after the switch layer. If this happens, we say
-the switch layer has {\it deactivated} the neuron of layer $L$ corresponding to
-channel $i$.
+contribute to any computation after the switch layer. If this happens, we say
+the switch layer has {\it deactivated} the neuron corresponding to channel $i$ of layer $L$.
 
@@
 %Formally, 
-For training, we need to account for the effect of the swith layers in the loss
+For training, we need to account for the effect of the switch layers on the loss
 function. The effect of switch layers can be expressed in terms of a sparsity constraint
-that pushes values in the $\theta$ vector to 0. Then, given a neural network
+that pushes values in the $\theta$ vector to 0. In this way, given a neural network
 parameterized by weights $\bm{W}$ and switch layer parameters $\bm{\theta}$, we
-optimize the following ShrinkNet loss:
-
+optimize ShrinkNet loss as follows 
 \begin{equation}
+\small
   L_{SN}(\bm{x},\bm{y};\bm{W}, \bm{\theta}) = L(\bm{x}, \bm{y}; \bm{W}) +
@@
 \end{equation}
-
-i.e., the expression augments the regular training loss with a regularization
+This expression augments the regular training loss with a regularization
 term for the switch parameters and another on the network weights.

### 2018-02-09 paper/ICML/evaluation.tex
pass over evaluation

--- 2018-02-09 paper/ICML/evaluation.tex
@@
 The goal of our evaluation is to explore:
+
 \begin{itemize}
-	\item
-Whether, by varying $\lambda$, \textit{ShrinkNets} can efficiently explore (in terms of number of training runs)  the spectrum of high-accuracy models from small to large, on both CNNs and fully connected networks.
-Our results show that, for each network size, we obtain models that perform as well or better than
-\textit{Static Networks}, trained via traditional hyperparameter optimization.
 
-\item Whether, because these  smaller networks are dense, they result in improved inference times on both CPUs and GPUs.
+\item Whether, by varying $\lambda$, \textit{ShrinkNets} can efficiently
+explore (in terms of number of training runs)  the spectrum of high-accuracy
+models from small to large, on both CNNs and fully connected networks.  Our
+results show that, for each network size, we obtain models that perform as well
+or better than \textit{Static Networks}, trained via traditional hyperparameter
+optimization.
 
-\item Whether the ShrinkNets approach results in network architectures that are substantially different than the best network architecutres (in terms of relative number of neurons per layered) identified in the literature.
+\item Whether, because these  smaller networks are dense, they result in
+improved inference times on both CPUs and GPUs.
+
+\item Whether the ShrinkNets approach results in network architectures that are
+substantially different than the best network architecutres (in terms of
+relative number of neurons per layered) identified in the literature.
 
 \item \srm{something else?}
+
 \end{itemize}
 
-\subsection{Performance vs. Traditional Methods}
+\noindent\textbf{Implementation: }We have implemented \textbf{switch Layers} and
+the associated training procedure as a library in
+pytorch~\cite{paszke2017automatic}. The layer can be freely mixed with other
+popular layers such as convolutional layers, batchnorm layers, fully connected
+layers, and used with all the traditional optimizers. We use our implementation
+to evaluate ShrinkNets throughout the evaluation section.
 
-We evaluate ShrinkNets on two datasets:  \texttt{CIFAR10} and \texttt{COVERTYPE}.  In this section, we report how we employed ShrinkNets on these datasets and compare our results to 
-training without ShrinkNets.
+\subsection{Can ShrinkNets achieve good accuracy?}
+%\subsection{Performance vs. Traditional Methods}
 
-\subsubsection{\texttt{CIFAR10}}
+To answer this question we compare ShrinkNets with a traditional network. In
+both cases, we need to perform hyperparameter optimization to explore different
+network architectures. We perform random search, which is an effective technique
+for this purpose \cite{}. We evaluate ShrinkNets on two well-known datasets. One
+for which it is not possible to explore the entire space of network
+architectures (\texttt{CIFAR10}) and one for which it is possible to do so
+(\texttt{COVERTYPE}).
 
-Previous research~\cite{Scardapane2017} that attempts to optimize network size during training
- focused on simple datasets and simple (i.e., fully connected)
-architectures. We believe that self-resizing
-network are most important for problems where the architecture 
-involves many layers, such that that it is impractical to explore the space of all possible
-layer-size configurations. For that reason, we picked \texttt{CIFAR10} \cite{Krizhevsky2009}. It is an
-image classification dataset containing $60000$ color images $(3 \times 32
-\times 32)$, belonging to $10$ different classes, running on  the \texttt{VGG16} network \cite{Srivastava2014}. VGG16
-consists of alternating convolutional layers and \textit{MaxPool} layers
-interleaved by \textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15} and
-\textit{ReLU} \cite{Nair2010}  layers. The two last layers are fully connected
-layers separated by a \textit{ReLU} activation function.
-
-\srm{keep this?}
- Although ShrinkNets supports larger networks and datasets as well (i.e., ImageNet \cite{ILSVRC15}),  the time required to such train models and get statistically significant result was prohibitive -- especially when comparing against classical hyperparameter search over network architecture.
-
-We applied ShrinkNets to the VGG16 network by adding \textit{Switch Layers} after each
-\textit{BatchNorm} layer and each fully connected layer (except the last).
-Recall that ShrinkNets assume that the starting size of the network is an upper bound on the
-optimal size. For this reason, we simply started with a network with double the recommended size for each
-layer as an upper bound (this is larger than what ImageNet, for example uses). Thus, for the
-classification layers we use $5000$ neurons as a starting limit (ImageNet
- uses $4096$ \gl{This is on the top of my head, need to be double checked}).
-
-We assume no prior knowledge on the optimal batch size, learning rate,
-$\lambda$ or weight decay ($\lambda_2$). Instead, we trained a number of models,
- randomly and independently selecting the values of these parameters 
-from a range of reasonable values (\gl{should we make them explicit ?} \srm{yes}).
-We trained using our modified \texttt{PyTorch} \cite{paszke2017automatic} library that
-supports dynamically resized layers (our code is available at \srm{add anonymized link}). Training is done using gradient descent and the
- \textit{Adam} optimizer \cite{DBLP:journals/corr/KingmaB14}. Specifically, 
- we start with
-the learning rate sampled randomly; for every $5$ epochs of non-improvement in
+\noindent\textbf{Setup: }
+We assume no prior knowledge on the optimal batch size, learning rate, $\lambda$
+or weight decay ($\lambda_2$). Instead, we trained a number of models, randomly
+and independently selecting the values of these parameters from a range of
+reasonable values (\gl{should we make them explicit ?} \srm{yes}).  
+%We trained
+%using our modified \texttt{PyTorch} \cite{paszke2017automatic} library that
+%supports dynamically resized layers (our code is available at \srm{add
+%anonymized link}). 
+Training is done using gradient descent and the \textit{Adam}
+optimizer \cite{DBLP:journals/corr/KingmaB14}. Specifically, we start with the
+learning rate sampled randomly; for every $5$ epochs of non-improvement in
 validation accuracy we divide the learning rate by $10$. We stop training after
@@
 first.  \gl{Should I also give the details about the removal strategy we used
-  and the $\gamma$ and threshold I used ? because this is clearly getting
-  boring} \srm{probably not necessary} 
-  For each of the models we trained, we pick the epoch with the best
-validation accuracy and report the corresponding testing accuracy. Because of
-the nature of our method, it can happen that for networks that are aggressively
-compressed, the best validation accuracy is obtained early in  training,
-before the size has converged. To be sure that accuracy measured corresponds to
-the final shape and not the starting shape, we only consider the second half of
-the training when picking the best epoch. For each model, we also measure the
-total size, in terms of number of floating point parameters, excluding the
-\textit{Switch Layers} because as described in \cref{neuron_killing}, these are eliminated
-after training.
+and the $\gamma$ and threshold I used ? because this is clearly getting boring}
+\srm{probably not necessary} For each of the models we trained, we pick the
+epoch with the best validation accuracy and report the corresponding testing
+accuracy. Because of the nature of our method, it can happen that for networks
+that are aggressively compressed, the best validation accuracy is obtained early
+in  training, before the size has converged. To be sure that accuracy measured
+corresponds to the final shape and not the starting shape, we only consider the
+second half of the training when picking the best epoch. For each model, we also
+measure the total size, in terms of number of floating point parameters,
+excluding the \textit{Switch Layers} because as described in
+\cref{neuron_killing}, these are eliminated after training.
 
-We compare against classical (\textit{Static}) networks. In such networks, the number of
-parameters that control the size is large: 13 parameters for the convolutional
-layers and $2$ for the fully connected layers. ShrinkNets effectively fuse
-all these parameters in a single $\lambda$, but in conventional architectures
-where all of these parameters are free, it is infeasible to obtain a reasonable
-sample of a search space of this size. For this reason, we rely on the conventional
- heuristic that the original VGG architecture (and many CNNs) \gl{try to
-  find the paper that introduces this heuristic} user, where \srm{describe what the heuristic is -- doubling of neurons up to apoint?} For \textit{Static Networks}
-we sample the size between $0.1$ and $2$ times the size \srm{size of what?} optimized for ImageNet. \srm{Why are we using ImageNet and not CIFAR10 as the comparison point?}
-We report the same numbers as we did for \textit{ShrinkNets} and we compare the
-two distributions.  
-\srm{I worry that this method of selecting network sizes for Static will of course constrain it to larger sizes and worse perforamance.
-What if we just randomly sample networks?
+%We evaluate ShrinkNets on two datasets:  \texttt{CIFAR10} and
+%\texttt{COVERTYPE}. In this section, we report how we employed ShrinkNets on
+%these datasets and compare our results to training without ShrinkNets.
+
+\subsubsection{Large Network Space: \texttt{CIFAR10}}
+
+%\ra{this is related work}Previous research~\cite{Scardapane2017} that attempts
+%to optimize network size during training focused on simple datasets and simple
+%(i.e., fully connected) architectures. We believe that self-resizing network are
+%most important for problems where the architecture involves many layers, such
+%that that it is impractical to explore the space of all possible layer-size
+%configurations.\ra{until here}
+
+\texttt{CIFAR10} is an image classification dataset containing $60000$ color
+images $(3 \times 32 \times 32)$, belonging to $10$ different classes. We use it
+with the \texttt{VGG16} network \cite{Srivastava2014}, which consists of
+alternating convolutional layers and \textit{MaxPool} layers interleaved by
+\textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15} and \textit{ReLU}
+\cite{Nair2010}  layers.  The two last layers are fully connected layers
+separated by a \textit{ReLU} activation function.
+
+%\srm{keep this?} Although ShrinkNets supports larger networks and datasets as
+%well (i.e., ImageNet \cite{ILSVRC15}),  the time required to such train models
+%and get statistically significant result was prohibitive -- especially when
+%comparing against classical hyperparameter search over network architecture.
+
+We applied ShrinkNets to the VGG16 network by adding \textit{Switch Layers}
+after each \textit{BatchNorm} layer and each fully connected layer (except the
+last).  Recall that ShrinkNets assume that the starting size of the network is
+an upper bound on the optimal size. For this reason, we simply started with a
+network with double the recommended size for each layer as an upper bound (this
+is larger than what ImageNet, for example uses). Thus, for the classification
+layers we use $5000$ neurons as a starting limit (ImageNet uses $4096$ \gl{This
+is on the top of my head, need to be double checked}).
+
+We compare against classical (\textit{Static}) networks. In such networks, the
+number of parameters that control the size is large: 13 parameters for the
+convolutional layers and $2$ for the fully connected layers. ShrinkNets
+effectively fuse all these parameters in a single $\lambda$, but in conventional
+architectures where all of these parameters are free, it is infeasible to obtain
+a reasonable sample of a search space of this size. For this reason, we rely on
+the conventional heuristic that the original VGG architecture (and many CNNs)
+\gl{try to find the paper that introduces this heuristic} use, where
+\srm{describe what the heuristic is -- doubling of neurons up to apoint?} For
+\textit{Static Networks} we sample the size between $0.1$ and $2$ times the size
+\srm{size of what?} optimized for ImageNet. \srm{Why are we using ImageNet and
+not CIFAR10 as the comparison point?} We report the same numbers as we did for
+\textit{ShrinkNets} and we compare the two distributions. \srm{I worry that
+this method of selecting network sizes for Static will of course constrain it to
+larger sizes and worse performance. What if we just randomly sample networks?
 Would it look terrible?}
 
-The results are shown in the top figure of \cref{figure_CIFAR10}.
-Here, the blue dots show the models produced by ShrinkNets, and the orange dots show the models produced for the static networks.
-For each model, we plot its accuracy and model size.
-The lines show the Pareto frontier of models in each of the two optimization settings.
-From the figure, it's apparent that ShrinkNets much more effectively explores the trade-off between model size and accuracy.
- \srm{Would be good to show Lambda values on the figure somehow.  }
- \srm{I thought we were going to summarize with distributional plots instead of Pareto frontiers?}
- \srm{Summarize more quantitatively -- best model performance, model performance drop off for a factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim in the intro, i.e.,
- ``Note that the best performing ShrinkNets models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets model is x times smaller.
-In addition, if we give up just 1\% error, ShrinkNets finds a model that is z times smaller.'' (If we do this, would be good to highlight these points in the figure somehow)}
+The results are shown in the top figure of \cref{figure_CIFAR10}, with blue dots
+indicating ShrinkNet models and orange dots indicating static networks. For each
+model, we plot its accuracy and model size. The lines show the Pareto frontier
+of models in each of the two optimization settings. ShrinkNets explore the
+trade-off between model size and accuracy more effectively. \srm{Would be good
+to show Lambda values on the figure somehow.  } \srm{I thought we were going to
+summarize with distributional plots instead of Pareto frontiers?} 
+%\srm{Summarize
+%more quantitatively -- best model performance, model performance drop off for a
+%factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim
+%in the intro, i.e., ``Note that the best performing ShrinkNets models has 9x.x\%
+%accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets
+%model is x times smaller.  In addition, if we give up just 1\% error, ShrinkNets
+%finds a model that is z times smaller.'' (If we do this, would be good to
+%highlight these points in the figure somehow)}
 
-\subsubsection{\texttt{COVERTYPE} dataset}
+Note that the best performing ShrinkNets models has \ra{xx} accuracy while the
+best static model has \ra{xx} accuracy, while the ShrinkNets model is \ra{xx}
+times smaller. In addition, if we give up just 1\% error, ShrinkNets finds a
+model that is \ra{xx} times smaller.
 
-The second dataset we use for evaluation is the \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset. This dataset
-contains $581012$ descriptions of geographical area (elevation, inclination,
-etc...) and the goal is to predict the type of forest growing in each area. We picked
-this dataset for several reasons. First it is simple, such that we can reach good
-accuracy with only a few fully-connected layers. This important because we want to show that
-\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
-are sampling the entire space of possible network sizes. The second reason is that Scardapane et al~\cite{Scardapane2017}
-also perform their evaluation on this dataset, which allow us to compare the
-results obtained by our method with the method in ~\cite{Scardapane2017}.
+\subsubsection{Small Network Space: \texttt{COVERTYPE}}
 
-The experimental setup on this dataset is similar to {\tt CIFAR10}. We use the same architecture
-as \cite{Scardapane2017}, i.e., three fully-connected layers network with  no
-\textit{Dropout} \cite{Srivastava2014} or \textit{BatchNorm}. \gl{Should we say here that we
-  don't expect Dropout to work here ? I could write an entire paragraph about it
-  if needed}. In this case, for the \textit{Static Networks}, we 
-independently samples the sizes of the three different layers to explore all possible
-architectures.
+The \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset contains $581012$
+descriptions of geographical area (elevation, inclination, etc...) and the goal
+is to predict the type of forest growing in each area. We picked this dataset
+for two reasons. First it is simple, such that we can reach good accuracy with
+only a few fully-connected layers. This is important because we want to show
+that \textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if
+we are sampling the entire space of possible network sizes. Second, Scardapane
+et al~\cite{Scardapane2017} perform their evaluation on this dataset, which
+allows us to compare the results obtained by our method with the method in
+~\cite{Scardapane2017}.
 
-The results are shown in the top figure of \cref{figure_COVER}, with the two optimization methods plotted as before.
-Here, {\it Static} method finds models that perform well at a variety of sizes, because it is able to explore the entire parameter space.
-This is as expected;  the fact that ShrinkNets performs as well as the Static indicates that ShrinkNets is doing an effective job of exploring the parameter space using just the single $\lambda$ parameter.
- \srm{Summarize more quantitatively -- best model performance, model performance drop off for a factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim in the intro, i.e.,
- ``Here, the best performing ShrinkNets models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets model is x times smaller.
-Further, note that ShrinkNets finds a model with 9x.x\% accuracy that is y times than the best performing model.
- Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a model that is z times smaller.'' (If we do this, would be good to highlight these points in the figure somehow)}
+%The experimental setup on this dataset is similar to {\tt CIFAR10}. 
+We compare ShrinkNets against the same architecture
+used in \cite{Scardapane2017}, i.e., a three fully-connected layers network with no
+\textit{Dropout} \cite{Srivastava2014} and no \textit{BatchNorm}. 
+%\gl{Should we say
+%here that we don't expect Dropout to work here ? I could write an entire
+%paragraph about it if needed}. 
+In this case, for the \textit{Static Networks}, we independently sample the
+sizes of the three different layers to explore all possible architectures.
 
-\subsubsection{Discussion}
+The results are shown in the top figure of \cref{figure_COVER}, with the two
+optimization methods plotted as before. Here, {\it Static} method finds models
+that perform well at a variety of sizes, because it is able to explore the
+entire parameter space.  This is as expected;  the fact that ShrinkNets performs
+as well as the Static indicates that ShrinkNets is doing an effective job of
+exploring the parameter space using just the single $\lambda$ parameter.
 
-\srm{we may not need to keep this unless we can think of something more to say}
+Note that the best performing ShrinkNets models has \ra{xx} accuracy while the
+best static model has \ra{xx} accuracy, while the ShrinkNets model is \ra{xx}
+times smaller. In addition, if we give up just 1\% error, ShrinkNets finds a
+model that is \ra{xx} times smaller.
 
-The Pareto frontier in the two figures shows that 
-that  \textit{ShrinkNets} is able find models that both as accurate and smaller than
-\textit{Static Networks}.
-when we sample the entire size space (in the \texttt{COVERTYPE} case),
-\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
-This has two implications. First it reinforces our observation \srm{our observation?} in [ref] that
-showed that the models do not suffer from the non-convexity introduced by the
-multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
-that the parametrization from a $\lambda$ (real value) to the size of the
-size of the network (vector) close to optimal. Indeed, if it was
-not the case then eventually a randomly sampled size would have beaten
-\textit{ShrinkNets} models. \gl{Too strong ?} \srm{I think this is too strong -- we have no evidence this is true, do we?}
+%\srm{Summarize more quantitatively -- best model performance, model performance
+%drop off for a factor of 10 reduction in seize, etc. so that we can repeat a
+%quantitative claim in the intro, i.e., ``Here, the best performing ShrinkNets
+%models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy,
+%while the ShrinkNets model is x times smaller.  Further, note that ShrinkNets
+%finds a model with 9x.x\% accuracy that is y times than the best performing
+%model.  Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a
+%model that is z times smaller.'' (If we do this, would be good to highlight
+%these points in the figure somehow)}
 
-\subsection{Benefits of smaller sizes}
+\subsubsection{Summary}
 
-We showed in the previous experiments that the \textit{ShrinkNets} approach is able to find
-networks with accuracy equal to or better than \textit{Static Networks}. In this experiment we
-want to determine benefits of the smaller size we get.
+We have demonstrated that it is possible to achieve networks with good accuracy
+when using ShrinkNets both when the network space cannot be explored entirely
+(\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
+result is not that ShrinkNets finds networks of good accuracy, but that those
+networks are much smaller than those found by a static method. The impact of the
+network size on inference time is the subject of our next evaluation goal.
+
+%\srm{we may not need to keep this unless we can think of something more to say}
+%
+%The Pareto frontier in the two figures shows that 
+%that \textit{ShrinkNets} is able find models that both as accurate and smaller than
+%\textit{Static Networks}.
+%
+%when we sample the entire size space (in the \texttt{COVERTYPE} case),
+%\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
+%This has two implications. First it reinforces our observation \srm{our observation?} in [ref] that
+%showed that the models do not suffer from the non-convexity introduced by the
+%multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
+%that the parametrization from a $\lambda$ (real value) to the size of the
+%size of the network (vector) close to optimal. Indeed, if it was
+%not the case then eventually a randomly sampled size would have beaten
+%\textit{ShrinkNets} models. \gl{Too strong ?} \srm{I think this is too strong -- we have no evidence this is true, do we?}
+%
+
+\subsection{Can ShrinkNets speed up inference?}
+
+We have demonstrated that ShrinkNets find networks of similar or better accuracy
+than static networks, and much smaller. Here we explore if the reduction in size
+translates into an improvement of the inference time.
+
+%We showed in the previous experiments that the \textit{ShrinkNets} approach is
+%able to find networks with accuracy equal to or better than \textit{Static
+%Networks}. In this experiment we want to determine benefits of the smaller size
+%we get.
 
 For some applications, the absolute best accuracy is not something desirable if
-it implies having enormous models. This observation motivates our methodology:
-for a given target accuracy that you want your model to achieve, we pick the
-smallest that satisfy the constraint. For both \textit{ShrinkNets} and
+it implies having enormous models. This observation motivates our experimental
+methodology: for a given desired target accuracy, we pick the smallest network
+that satisfies the accuracy constraint. For both \textit{ShrinkNets} and
 \textit{Static Networks} we measure multiple metrics and compute the ratio
-between the two. The metrics are interested in are: the final model size (in
+between the two. The metrics we are interested in are: the final model size (in
 number of parameters) and inference speed on CPU and GPU for small batch sizes
@@
 
-Regarding size, the key observation we can make is that size improvements are
-significant for the \texttt{CIFAR10}. In the range of accuracies we are
-interested in, improvements in size go from 4x to 40x. On the \texttt{COVERTYPE}
-dataset even if the compression ratio is always above 1, it hardly exceeds 3x,
-except for very high accuracy where \textit{ShrinkNets} obtained some
-particularly good solutions.
+Regarding size, the key observation is that size improvements are significant
+for the \texttt{CIFAR10}. In the range of accuracies we are interested in,
+improvements in size go from 4x to 40x. On the \texttt{COVERTYPE} dataset even
+if the compression ratio is always above 1, it hardly exceeds 3x, except for
+very high accuracy where \textit{ShrinkNets} obtained some particularly good
+solutions.
 
-We observe that unlike local sparsity compression based method, our method
-translates directly improvement in size to higher bandwidth at inference time.
-In situations where inference is already incredibly fast (\texttt{COVERTYPE}
-with a batch size of $1$ and \texttt{CIFAR10} with a batch size of $1$ on GPU),
-improvements are dominated by noise. However, on machine learning frameworks
-more focused on latency it should be possible to measure them.
+We observe that unlike local sparsity compression based method, our method's
+improvement on size translates directly to higher throughput at inference time.
+\ra{For example, when running on CPU, blah, when running on GPU blah.}
+
+When using a batch size of $1$ on CPU for \texttt{CIFAR10} as well as when using
+a batch of $1$ on GPU, we do not observe any improvement due to the experiment
+being dominated by noise. However, we still expect to find a difference in
+latency if we were using a framework optimized for such goal.\ra{this is a bit
+vague}
+
+%In situations in which inference is already fast (\texttt{COVERTYPE}
+%with a batch size of $1$ and \texttt{CIFAR10} with a batch size of $1$ on GPU),
+%improvements are dominated by noise. However, on machine learning frameworks
+%more focused on latency it should be possible to measure them.
 
@@
 
+\ra{checkpoint}
+
 \subsection{Architectures obtained after convergence}
-
-The previous experiments showed that \textit{ShrinkNets} finds architectures
-the effectively explore the frontier of model size and accuracy. Further, for
-a  given accuracy,
-the size needed is significantly smaller than when we use the \srm{name it} heuristic
- commonly used to size convolutional neural networks. This suggests that this
- conventional heuristic may not in fact be optimal, especially when looking for 
- smaller models. 
-Empirically we observed this to often be the case.  For example, 
-during our experimentations on the \texttt{MNIST}
-\cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017} datasets (not reported here due to space constraints), we observed that
-even though these datasets have the same number of classes, input features, and output
-distributions,  for a fixed $\lambda$ \textit{ShrinkNets} converged to
-considerably bigger networks in the case of \texttt{FashionMNIST}. This
-evidence shows that optimal architecture not only depends on the output
-distribution or shape of the data but actually reflects the dataset.  This makes sense,
-as  \texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.
-
-To illustrate this point on a larger dataset, 
-we show two examples of architectures learned by \textit{ShrinkNets} in Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the best
- test accuracy, with \srm{identical performance to the best static network?}; 
- the bottom shows a network that slightly under-performs the best in terms of accuracy but is
-significantly smaller that the best equivalent \textit{Static Network} \srm{how much smaller?}.
-In the plot, the dashed line shows the number of neurons in each layer of the original VGG net, and the shaded regions show the size of the ShrinkNet as it converges (with the darkest region representing the fully converged network).
-Observe that the final network that is trained looks quite different in the two cases, with the optimal performing network appearing similar to the original VGG net, whereas the shrunken network allocates many fewer neurons to the middle layers, and then additional neurons to the final fewer layers.
 
@@
 
-% \subsection{Neuron Removal strategies [TO be removed]}
-% 
-% In our previous experiment, we showed that the ShrinkNet loss was
-% reasonable in practice, we are now interested in the impact on
-% early pruning. The method we suggest for early prunning uses a
-% parameter $\gamma$ that control the aggressiveness of neuron removal
-% so we will try to evaluate its impact on the final loss achieved by
-% the model and the cost required to train the model. Our cost model
-% is simple and hardware independant, we sum the number of input neurons
-% at each epoch. In theory the cost in time should be asymptotically
-% linear to this metric. To have a baseline we also train the same model
-% but without neuron removal. Keep in mind that this is just in order to
-% have some reference. Indeed, if we were to remove the neurons with small
-% weights it would deteriorate the loss (and picking the threshould would
-% be completely arbitrary). Therefore the baseline is evaluated with all neurons.
-% One could consider it as a "theoretical lower bound" of the best achievable loss.
-% 
-% 
-% We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$).
-We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}.
-In order to reduce the noise in the result, each experiment was performed $30$ times and we display the range arround $\pm$ $1$ standard deviation.
+\ra{the following is interesting, but how is it related to the above?}
+ShrinkNets effectively explores the frontier of model size and accuracy. For a
+given target accuracy, the size needed is significantly smaller than when we use the
+\srm{name it} heuristic commonly used to size convolutional neural networks.
+This suggests that this conventional heuristic may not in fact be optimal,
+especially when looking for smaller models.  Empirically we observed this to
+often be the case.  For example, during our experimentations on the
+\texttt{MNIST} \cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017}
+datasets (not reported here due to space constraints), we observed that even
+though these datasets have the same number of classes, input features, and
+output distributions, for a fixed $\lambda$ \textit{ShrinkNets} converged to
+considerably bigger networks in the case of \texttt{FashionMNIST}. This evidence
+shows that optimal architecture not only depends on the output distribution or
+shape of the data but actually reflects the dataset.  This makes sense, as
+\texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.
+
+To illustrate this point on a larger dataset, we show two examples of
+architectures learned by \textit{ShrinkNets} in
+Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the
+best test accuracy, with \srm{identical performance to the best static
+network?}; the bottom shows a network that slightly under-performs the best in
+terms of accuracy but is significantly smaller that the best equivalent
+\textit{Static Network} \srm{how much smaller?}.  In the plot, the dashed line
+shows the number of neurons in each layer of the original VGG net, and the
+shaded regions show the size of the ShrinkNet as it converges (with the darkest
+region representing the fully converged network).  Observe that the final
+network that is trained looks quite different in the two cases, with the optimal
+performing network appearing similar to the original VGG net, whereas the
+shrunken network allocates many fewer neurons to the middle layers, and then
+additional neurons to the final fewer layers.

### 2018-02-09 paper/ICML/impl.tex
edits

@@
+%!TEX root=paper.tex
+
 \section{ShrinkNets in Practice}
 
-In this section we discuss practical aspects of ShrinkNets.
+In this section we discuss practical aspects of ShrinkNets, including the
+neuron removal  process and several additional optimizations.
 
@@
 
-Switch layers are initialized with weights sampled from $\mathcal{N}(0,1)$, and
-their values change as part of the training process so as to swith \emph{on} or
-{off} neurons. When neurons are deactivated by switch layers, we want to remove
-them to shrink the network size. Because after removing a neuron it will no
-longer contribute to improving prediction accuracy, we must devise strategies
-that remove neurons while being robust to changing values. We observe three
-strategies:
+Switch layers are initialized with weights sampled from $\mathcal{N}(0,1)$;
+their values change as part of the training process so as to switch \emph{on}
+or \emph{off} neurons. When neurons are deactivated by switch layers, we need
+to remove them to actually shrink the network size. Since after removing a
+neuron it will no longer be able to contribute to  prediction accuracy, we
+must devise strategies that remove neurons while remaining robust to changing
+values. We observe three strategies:
 
-\textbf{Threshold strategy}: Under this strategy neurons are removed based on a
-fixed threshold expressed in terms of its absolute value. This is the method
-used by deep compression \cite{}. We found this method is not robust to noise in
-the gradients---which occurs commonly when training networks with stochastic
-gradient descent---because the threshold depends on the scale of each weight.
+\textbf{Threshold strategy}: Under this strategy neurons are removed based on
+a fixed threshold expressed in terms of its absolute value. This is the method
+used by deep compression \cite{}. We found this method is not robust to noise
+in the gradients---which occurs commonly when training networks with
+stochastic gradient descent---because the threshold depends on the scale of
+each weight.
 
-\textbf{Sign change strategy}: Under this strategy neurons are removed when the
-weight value changes its sign. This strategy works well in practice but it is
-also sensible to gradient noise. \ra{explain what's the consequence of that} If
-we sample a gradient that is not representative of the dataset when performing
-gradient descent then we might wrongly kill a neuron.\ra{last sentence is
-unclear}
+\textbf{Sign change strategy}: Under this strategy neurons are removed when
+the weight value changes its sign. This strategy works well in practice but it
+is also sensitive to gradient noise. \ra{explain what's the consequence of
+that} If we sample the gradient in a way that is not fully representative of
+the dataset we might  experience one-time zero crossing which could wrongly
+kill a neuron.
 
-\textbf{Sign variance strategy}: We measure the exponential moving variance of
-the sign ($-1, 1$) of each parameter in the \textit{switch layer}. When the
-value of the exponential moving variances goes over a predefined threshold, we
-consider the parameter is deactivating the neuron, and therefore we remove it.
-This strategy introduces two extra parameters, one to control the behavior of
-the inertia of the variance, and the threshold, but we have found it is the
-best performing in practice.
+\textbf{Sign variance strategy}: Instead of killing  on the first zero
+crossing, we can instead measure the exponential moving variance of the sign
+($-1, 1$) of each parameter in the \textit{switch layer}. When the value of
+the exponential moving variances goes over a predefined threshold, we consider
+the neuron deactivated, and therefore we remove it. This strategy introduces
+two extra parameters, one to control the behavior of the inertia of the
+variance, and the threshold, but we have found it is the best performing in
+practice.
 
-The last two strategies perform the best in practice; they reduce the network
-parameters by an order of magnitude with only a minimal impact on the final
-error obtained by the model.
+The last two strategies perform better than the threshold strategy.  Both
+effectively allow us to shrink the network by varying $\lambda$, and result in
+networks that are both small and perform well.
 
@@
 
-\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain
-reduced-sized networks while training, which is the first benefit towards faster
+\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain reduced-
+sized networks during training, which is the first steps towards faster
 inference. This networks are readily available for inference. However, because
@@
 network parameters by combining each switch layer with its respective network
-layer by multiplying the respective parameters.  \ra{can't we just simply
-prevent the following problem at network design time?}In the unlikely case that a switch
-layer is sandwiched between two non-linearly scalable layers, we leave the
-switch layer as is.
+layer by multiplying the respective parameters before emitting the final
+trained network.   \ra{can't we just simply prevent the following problem at
+network design time?}In the unlikely case that a switch layer is sandwiched
+between two non-linearly scalable layers, we leave the switch layer as is.
 
-\noindent\textbf{Neural Garbage Collection: }ShrinkNets decide on-the-fly which
-neurons to remove. Since ShrinkNets remove a large fraction of neurons, we must
-dynamically resize the network at runtime to not carry on the 
-unnecessary overhead. We implement a neural garbage collection method as part of
-our library which takes care of updating the necessary network layers as well as
-updating optimizer state to reflect the neuron removal.
+\noindent\textbf{Neural Garbage Collection: }ShrinkNets decides on-the-fly
+which neurons to remove. Since ShrinkNets removes a large fraction of neurons,
+we must dynamically resize the network at runtime to not unnecessarily impact
+network training time. We implemented a neural garbage collection method as
+part of our library which takes care of updating the necessary network layers
+as well as updating optimizer state to reflect the neuron removal.
 

### 2018-02-09 paper/ICML/theory.tex

@@
+%!TEX root=paper.tex
 %\subsection{Relation to Group Sparsity}
@@
 i.e., inputs and outputs of layers. For a fully connected layer defined as:
-
+%
 \begin{equation} \label{fully_connected}
@@
 \end{equation}
-
-Removing an input neuron $j$ is equivalent to have $\left(\bm{A}^T\right)_j =
-\bm{0}$. Removing an output neuron $i$ is the same as having $\bm{A}_i = \bm{0}$
+%
+removing an input neuron $j$ is equivalent to having $\left(\bm{A}^T\right)_j =
+\bm{0}$. Removing an output neuron $i$ is the same as setting $\bm{A}_i = \bm{0}$
 and $\bm{b}_i = 0$. Solving optimization problems while trying to set entire
 group of parameters to zero is the goal of group sparsity regularization
-\cite{}. For any partitioning of the set of parameter defining a model in $p$
-groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$ we define it the following
-way:
-
+\cite{xxx}. In  any partitioning of the set of parameters $\theta$ defining a model in $p$
+groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$, group sparsity is defined as: \srm{you used to say ``we define `it' as:'' -- I am assume `it' is group sparsity}
+%
 \begin{equation}
@@
 \end{equation}
-
+%
+\srm{define notation -- what is $\lambda$;  what is $\#\theta$, what is $\Omega$? Where does the square root come from?}
 In fully-connected layers, the groups are either: columns of
@@
 our analysis in the simple one-layer case. In this case, filtering outputs does
-not make sense, this is why we will only consider the former case. The
+not make sense, so we only consider removing inputs. The
 group sparsity regularization then becomes:
-
+%
 \begin{equation} \label{group_sparsity_regularization}
@@
 \end{equation}
-
+%
 Because $\forall i, \#\bm{\theta}_i = n$, \ra{is \# the general way of expressing
-cardinality? why not |x|?}to make the notation simpler, we
+cardinality? why not $|x|$?}to make the notation simpler, we
 embedded $\sqrt{n}$ inside $\lambda$.
@@
 they are related to each other. First let's recall the two problems. The
-original ShrinkNet problem is:
-
+original ShrinkNet problem is \srm{do you mean ``can be defined formally as'' -- we never gave this definition of ShrinkNets.
+Also, you need to explain the formula / notation;  what is $y$, what is $\beta$, what is this equation representing (the optimization function?)}:
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 And the Group Sparsity problem is:
-
+%
 \begin{equation}
@@
 \end{equation}
+%
 
@@
 \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
-(\cref{gps_equivalence}). However if we relax this constraint then shrinknet
+(\cref{gps_equivalence}, see Apendix). However if we relax this constraint then ShrinkNets
 becomes non-convex and has no global minimum
-(\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}). Fortunately,
-by adding an extra term to the ShrinkNet regularization term we can proove that:
-
+(\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}, also in Appendix). Fortunately,
+by adding an extra term to the ShrinkNet regularization term we can prove that:
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 has global minimums for all $p>0$ (\cref{shrinknet_regularized_minimum}).
-This is the reason we defined the \textit{regularized ShrinkNet penalty} earlier
-this way:\ra{the notation is slightly different, better to make it consistent}
-
+This is the reason we defined the \textit{regularized ShrinkNet penalty} above
+as \srm{where?}:\ra{the notation is slightly different, better to make it consistent}
+%
 \begin{equation}
@@
 \end{equation}
-
-In practice we observed that $p=2$ or $p=1$ are good choice, while the latter
-will also introduce additional sparsity in the parameters.
+%
+In practice we observed that $p=2$ or $p=1$ are good a choice; note that the latter
+will also introduce additional sparsity into the parameters. \srm{why?}

### 2018-02-09 paper/ICML/introduction.tex
added overview to intro

@@
 
+XXX people actually don't treat network size as a hyperparameter;  we do!
+
 % {\bf Old introduction:}
@@
 which allows us to optimize the network size as the network is trained. 
+\item \srm{xxx postprocessing techniques to strip out switch layers}
 \item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
@@
 \end{compactenum}
+
+The remaining of this paper is organized as follows. In section
+\ref{sec:relatedwork} we discuss the related work. In section
+\ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
+practical considerations we implemented to make it work in section
+\ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
+and conclude the paper in section \ref{sec:conclusions}.

### 2018-02-09 paper/ICML/introduction.tex
pass on intro -- fleshing out technical details

@@
 both network size and model performance. The key idea is to learn the right
-network size at the same time that we optimize for prediction performance. Our
-approach, called {\it ShrinkNets}, starts with an {\it oversized} network, and
-dynamically shrinks it by eliminating neurons during training time.  Our
-approach has two main benefits.  First, we explore the architecture of models
-that are both small and perform well, rather than starting with a high-
-performance model and making it small.  This allows us to efficiently generate
-a family of smaller and accurate models without an exhaustive and expensive
-hyperparameter search over the number of neurons in each layer. Second, in
-contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are
-not only small, but where the  layers are dense, which means that inference
-time is also improved, e.g., on GPUs.
+network size at the same time that we optimize for prediction performance for a
+specific task. Our approach, called {\it ShrinkNets}, starts with an {\it
+oversized} network, and dynamically shrinks it by eliminating unimportant
+neurons---those that do not contribute to prediction performance---during
+training time. For that, ShrinkNets must detect the unimportant neurons, and
+remove them from the network, thus drastically reducing the network size. The
+removal of entire neurons and not connections is crucial, because it leads to
+dense networks, which lead to better inference performance. To support the
+detection and removal of unimportant neurons we introduce a new layer, called
+\textbf{Switch layer}. Introducing this new layer means we must redefine the
+loss function to account for the sparsity effect it introduces. ShrinkNets has
+two main benefits. First, it explores the architecture of models that are both
+small and perform well, rather than starting with a high-performance model and
+making it small.  This allows us to efficiently generate a family of smaller and
+accurate models without an exhaustive and expensive hyperparameter search over
+the number of neurons in each layer.  Second, in contrast to existing neural
+network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our
+approach results in models that are not only small, but where the layers are
+dense, which means that inference time is also improved, e.g., on GPUs.
 

### 2018-02-09 paper/ICML/appendix.tex

@@
+%!TEX root=paper.tex
 \section{Appendix}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=.7\columnwidth]{regressions}
+\vspace*{-5mm}
+\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
+From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
+
+\end{center}
+\vspace*{-4mm}
+\end{figure}
+
 \subsection{Proofs}
@@
 For each component $k$ of $\bm{\beta_i}$ for some $i$.
-Negating it and negating the $k^{th}$ column of $\bm{A_i}$ do not change the the first part of the objetive because the two factors cancel each other.
+Negating it and negating the $k^{th}$ column of $\bm{A_i}$ do not change the the first part of the objective because the two factors cancel each other.
 The two norms do not change either because by definition the norm is independant of the sign.
@@
 As we showed, Group sparsity share similarities with our method, and we claim
-that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
+that ShrinkNets are a relaxation of Group sparsity.  In this experiment we want
 to compare the two aproaches.  We decided to focus on multi-target linear
@@
 the error and sparsity obtained after convergence. In this context we define
-sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
-absolute value. Regularization parameters were choosed in order to obtain the
+sparsity as the ratio of columns that have all their weights under $10^{-3}$ in
+absolute value. Regularization parameters were choosen in order to obtain the
 widest sparsity spectrum. Loss is normalized depending on the problem to be in
@@
 practice it works as good or better as convex alternatives.
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{regressions}
-\vspace*{-5mm}
-\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
-From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
-
-\end{center}
-\vspace*{-4mm}
-\end{figure}

### 2018-02-09 paper/ICML/impl.tex

@@
 
-\textbf{Sign change strategy}: Under this strategy neurons are removed when
-the weight value changes its sign. This strategy works well in practice but it
-is also sensitive to gradient noise. \ra{explain what's the consequence of
-that} If we sample the gradient in a way that is not fully representative of
-the dataset we might  experience one-time zero crossing which could wrongly
-kill a neuron.
+\textbf{Sign change strategy}: Under this strategy neurons are removed when the
+weight value changes its sign. This strategy works well in practice but it is
+also sensitive to gradient noise. If we sample the gradient in a way that is
+not fully representative of the dataset we might  experience one-time zero
+crossing which could wrongly kill a neuron.
 
@@
 layer by multiplying the respective parameters before emitting the final
-trained network.   \ra{can't we just simply prevent the following problem at
-network design time?}In the unlikely case that a switch layer is sandwiched
+trained network. In the unlikely case that a switch layer is sandwiched
 between two non-linearly scalable layers, we leave the switch layer as is.

### 2018-02-09 paper/ICML/evaluation.tex
edits

@@
 
-\begin{itemize}
+\begin{compactitem}
 
@@
 \item Whether the ShrinkNets approach results in network architectures that are
-substantially different than the best network architecutres (in terms of
+substantially different than the best network architectures (in terms of
 relative number of neurons per layered) identified in the literature.
@@
 
-\end{itemize}
+\end{compactitem}
 
-\noindent\textbf{Implementation: }We have implemented \textbf{switch Layers} and
+\noindent\textbf{Implementation: }We implemented \textbf{switch Layers} and
 the associated training procedure as a library in
@@
 
-\subsubsection{Large Network Space: \texttt{CIFAR10}}
+\subsubsection{Large Network Setting: \texttt{CIFAR10}}
 
@@
 
-\subsubsection{Small Network Space: \texttt{COVERTYPE}}
+\subsubsection{Small Network Setting: \texttt{COVERTYPE}}
 
@@
 
-We have demonstrated that it is possible to achieve networks with good accuracy
+We  demonstrated that it is possible to achieve networks with good accuracy
 when using ShrinkNets both when the network space cannot be explored entirely
@@
 
-We have demonstrated that ShrinkNets find networks of similar or better accuracy
-than static networks, and much smaller. Here we explore if the reduction in size
+The previous experiment showed that ShrinkNets finds networks of similar or better accuracy
+than static networks that are much smaller. We now explore if the reduction in size
 translates into an improvement of the inference time.
@@
 
-For some applications, the absolute best accuracy is not something desirable if
-it implies having enormous models. This observation motivates our experimental
-methodology: for a given desired target accuracy, we pick the smallest network
-that satisfies the accuracy constraint. For both \textit{ShrinkNets} and
-\textit{Static Networks} we measure multiple metrics and compute the ratio
-between the two. The metrics we are interested in are: the final model size (in
-number of parameters) and inference speed on CPU and GPU for small batch sizes
-($1$ input) and large batch sizes (depend on the dataset and hardware). Results
-are shown on \cref{figure_CIFAR10} and \cref{figure_COVER} after the
-distribution of sizes and accuracy. We limit our plot to the ($80-100\%$
-accuracy range because we consider that models with lower accuracy have less
-practical use).
+As noted in the introduction, for some applications, compact models that offer fast inference times
+are as important as absolute accuracy. 
+%This observation motivates our 
+% the experiment approach described in the previous section 
+% and shown in the top of Figure~\ref{figure_CIFAR10} 
+% and~\ref{figure_COVER}:
+% for a  desired target accuracy, the Pareto optimal line shows the smallest
+% network
+% that satisfies achieves a given accuracy. 
+In this section, we study the relationship between accuracy, network size and inference time.
+To do this, we select the smallest model 
+that achieves a given accuracy for the both ShrinkNets and Static approach.
+For each model, we measure the time to run inference with the model.  
+We then compute the ratio of the network size and inference time
+between ShrinkNets and Static at each accuracy level, and plot them on the bottom of 
+ Figure~\ref{figure_CIFAR10} 
+ and~\ref{figure_COVER}.
+We limit our plots to the models with $80-100\%$
+accuracy range because those are the ones that we consider to be practically useful.
 
-Regarding size, the key observation is that size improvements are significant
-for the \texttt{CIFAR10}. In the range of accuracies we are interested in,
-improvements in size go from 4x to 40x. On the \texttt{COVERTYPE} dataset even
-if the compression ratio is always above 1, it hardly exceeds 3x, except for
-very high accuracy where \textit{ShrinkNets} obtained some particularly good
-solutions.
+ The middle plot in each figure shows the ratio of model size between ShrinkNets and Static (values $>$1 mean ShrinkNets are smaller) at different accuracy levels.
+These figures show that is that size improvements are are particularly significant
+for  \texttt{CIFAR10}. In the range of accuracies we are interested in,
+improvements in size go from 4x to 40x. On the \texttt{COVERTYPE} dataset,
+ the compression ratio is always above 1 but it rarely exceeds 3x, except for
+very high accuracies where \textit{ShrinkNets} finds excellent, small
+solutions.  The fact that the  \texttt{COVERTYPE} networks are not dramatically 
+smaller is expected:  as the distribution at the top of Figure~\ref{figure_COVER} shows,
+the static method is able to explore most of the parameter search space, so finds a range
+of models that perform well at different sizes.
 
-We observe that unlike local sparsity compression based method, our method's
-improvement on size translates directly to higher throughput at inference time.
-\ra{For example, when running on CPU, blah, when running on GPU blah.}
+For speedup, we experimented with both CPUs and GPUs, and with different batch sizes, where batch size indicates the number of inputs simultaneously fed to the model for inference.
+For each data set/GPU/CPU combination, we show results with batch size 1, as well as with a batch size large enough to fully utilize the hardware on each dataset and hardware configuration.
+For example, for {\tt CIFAR10} on CPU, a batch size of 64 fully utilizes the CPU, whereas a GPU can execute many more models in parallel, so we use a larger batch size of 1024.
+For {\tt COVERTYPE}, because the model is so much smaller, larger batches are needed to fully utilize the hardware.
+Note that when using a batch size of $1$ on GPU, we do not expect to (and do not) observe any improvement because inference times are very small (typically about 10 $\mu s$), such that setup time dominates overall runtime.
 
-When using a batch size of $1$ on CPU for \texttt{CIFAR10} as well as when using
-a batch of $1$ on GPU, we do not observe any improvement due to the experiment
-being dominated by noise. However, we still expect to find a difference in
-latency if we were using a framework optimized for such goal.\ra{this is a bit
-vague}
+ The bottom four graphs in each figure 
+show the results.  Again, the {\tt CIFAR10} results show the benefit of the ShrinkNets approach
+most dramatically.
+On CPU, speedups range up to 6x depending on the batch size, with many models exceeding 3x speedup.
+In general, speedups are less than compression ratios, due to overheads in problem setup, invocation, and result generation  in Python/PyTorch.
+  On GPU, the speedups are less substantial because the CUDA benchmarking utility that we use for evaluation can choose better algorithms for larger matrices which masks some of our benefit, although they are still often 1.5x--2x faster for large batch sizes.
+The speedup results on {\tt COVERTYPE} are similar to those for network size:  because the networks are not much smaller, they are not much faster either.
+
+A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time.
+\srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?}, at least for larger batches when hardware can be fully utilized.
 
@@
 search over the hyper-parameters the \texttt{COVERTYPE} dataset
-\srm{label the x axes on the bottom plots}
+\srm{label the x axes on the bottom plots; change ``Desired accuracy`` ``Accuracy''}
 }

### 2018-02-09 paper/ICML/related_work.tex
related work, makefile

@@
 \begin{itemize}
-  \item Other techniques for choosing network size (e.g., hyperparmeter optimization) -- manual effort vs optimal techniques -- people actually don't treat network size as a hyperparameter;  we do!
-Also brute force techniques~\cite{nvidia-paper-xxx}
-  \item distillation techniques -- train a big net, then train a smaller net from it 
   \item post-training compression techniques -- brain damage , 
@@
 
-Given the importance of network structure, many techniques have been proposed
-to find the best network structure for a given learning task.  These techniques
-broadly fall into four categories: hyperparameter optimization strategies,
-post-training model compression for inference as well as model simplification,
-techniques to resize models during training, and automated architecture search
-methods.
+Given the importance of network structure, many researchers have explored the
+problem of finding the best network structure for a given learning task.  
+The proposed techniques broadly fall into five categories: 
+random search andbrute force search,
+hyperparameter optimization,
+model compression after training,
+resizing models during training, and 
+automated architecture search methods.
 
@@
 shown to work suprisingly well compared to more complex methods such as those
-based on Bayesian optimization~\cite{Snoek12}.  Techniques such
-as~\cite{Snoek12} model generalization performance via Gaussian
+based on Bayesian optimization~\cite{Snoek12}.
+Brute force search of network sizes is also become more practical due to faster
+and more powerful hardware~\cite{molchanov2016pruning}.
+The more complex methods for hyperparameter optimization include techniques 
+such as~\cite{Snoek12} which model generalization performance via Gaussian
 Processes~\cite{GaussianProcesses} and select hyperparameter combinations that
-come from uncertain areas of the hyperparameter space.  Recently, methods based
+come from uncertain areas of the hyperparameter space.  
+Recently, methods based
 on bandit algorithms (e.g. ~\cite{li2016hyperband, jamieson2016}) have also
-become a popular way to tune hyperparameters.  As noted before, all of the
+become a popular way to tune hyperparameters.
+As noted before, all of the
 above techniques require many tens to hundreds of models to be trained, making
 this process computationally inefficient and slow.
+More practically, the hyperparameter optimization literature does not evaluate
+their methods on network size and instead focuses on optimization hyperparameters
+such as learning rates and weight decay parameters.
 
-In contrast with hyperparameter tuning methods, some methods such as
-DeepCompression~\cite{han2015deepcompression} seek to compress the network to
-make inference more efficient.  This is accomplished by pruning connections and
-quantizing weights.  On similar lines, multiple techniques such
-as~\cite{romero2014fitnets, hinton2015distilling} have been proposed for
-distilling a network into a simpler network or a different model.  Unlike our
+In contrast with size search techniques, there are techniques that 
+reduce network size {\it once the network has been traiend}.
+Popular techniques in this class include optimal brain damage~\cite{Cun} and
+compression techniques such as DeepCompression~\cite{han2015deepcompression}.
+Optimal brain damage identifies connections in a network that are unimportant
+and then prunes these connections.
+DeepCompression takes this one step further and in addition to pruning connections,
+it quantizes weights to make inference extremely efficient.
+% In contrast with hyperparameter tuning methods, some methods such as
+% DeepCompression~\cite{han2015deepcompression} seek to compress the network to
+% make inference more efficient.  This is accomplished by pruning connections and
+% quantizing weights.  
+A different vein of work such as ~\cite{romero2014fitnets, hinton2015distilling}
+proposes techniques for distilling a network into a simpler network or 
+a different model.  Unlike our
 technique which works during training, these techiques are used after training
@@
 
-The techniques closed to our work are those based on group sparsity such as
-~\cite{Scardapane2017}, and those like ~\cite{Philipp} who grow and shrink
+The techniques closest to our proposed method are those based on group sparsity 
+such as ~\cite{Scardapane2017}, and those like~\cite{Philipp} who grow and shrink
 dynamically the size of the network during training.
+
+\cite{Scardapane2017} presents a method that also deactivates neurons using a 
+loss function based on group-sparsity.
+However, the exact details of how their method works are not given, and 
+their experimental results (on a small, fully connected network), 
+are substantially worse than ours as shown in Section~\ref{sec:experiments}.
+~\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
+that adds neurons on the fly and removes neurons via an $l_2$ penalty.
+However, this approach requires a new optimizer and takes longer to converge 
+compared to ShrinkNets.
 

### 2018-02-09 paper/ICML/approach.tex

@@
 network. We model the on/off switches by multiplying each input (or output) of
-each layer by a parameter $\bm{\theta}\in\{0,1\}$. A value of $0$
+each layer by a parameter $\bm{\beta}\in\{0,1\}$. A value of $0$
 will deactivate the neuron, while $1$ will let the signal go through. These
@@
 assignment is an NP-Hard problem, we relax the problem by allowing
- $\bm{\theta}$ to be a real number
+ $\bm{\beta}$ to be a real number
 instead of a binary value and constrain it using the L1 instead of L0 norm.
@@
 deactivated by the switch layers are actually removed from the network,
-effectively shrinking the network size. This step improves inference
-times, as we demonstrate in our evaluation. We choose to remove neurons at
-training time because we have observed that this allows the remaining active neurons to adapt
+effectively shrinking the network size. This step improves inference times, as
+we demonstrate in our evaluation. We choose to remove neurons at training time
+because we have observed that this allows the remaining active neurons to adapt
 to the new network architecture. Existing techniques focus on neuron removal
 after training, and require an extra fine-tuning process to compensate for the
-removal.\srm{cite something?}
+removal.\srm{cite something?} \gl{I think we are fine or we could actually
+cite any of these paper}
 
@@
 switches.  The switch
-layer is parametrized by a vector $\theta \in \mathbb{R}^c$ such that the result
+layer is parametrized by a vector $\beta \in \mathbb{R}^c$ such that the result
 of applying $S$ to $L(\bm{x})$ is a also a tensor size $\left(c \times d_1
@@
 \begin{equation} 
-S_{\theta}(L(\bm{x}))_{i,...} = \bm{\theta}_iL(\bm{x})_{i, ...} \forall i \in [1\ldots c]
+S_{\beta}(L(\bm{x}))_{i,...} = \bm{\beta}_iL(\bm{x})_{i, ...} \forall i \in [1\ldots c]
 \end{equation}
 Once passed through the switch layer, each output channel $i$
-produced by $L$ is scaled by the corresponding $\theta_i$. Note that when
-$\theta_i = 0$, the $i^{\text{th}}$ channel is multiplied by zero and will not
+produced by $L$ is scaled by the corresponding $\bm{\beta}_i$. Note that when
+$\bm{\beta}_i = 0$, the $i^{\text{th}}$ channel is multiplied by zero and will not
 contribute to any computation after the switch layer. If this happens, we say
@@
 function. The effect of switch layers can be expressed in terms of a sparsity constraint
-that pushes values in the $\theta$ vector to 0. In this way, given a neural network
-parameterized by weights $\bm{W}$ and switch layer parameters $\bm{\theta}$, we
+that pushes values in the $\bm{\beta}$ vector to 0. In this way, given a neural network
+parameterized by weights $\bm{\theta}$ and switch layer parameters $\bm{\theta}$, we
 optimize ShrinkNet loss as follows 
@@
 \small
-  L_{SN}(\bm{x},\bm{y};\bm{W}, \bm{\theta}) = L(\bm{x}, \bm{y}; \bm{W}) +
-  \lambda\norm{\theta}_1 + \lambda_2\norm{\bm{W}}_p
+  L_{SN}(\bm{x},\bm{y};\bm{\theta}, \bm{\beta}) = L(\bm{x}, \bm{y}; \bm{\beta}) +
+  \lambda\norm{\beta}_1 + \lambda_2\norm{\bm{\theta}}_p^p
 \end{equation}

### 2018-02-09 paper/ICML/impl.tex
edits

@@
 neuron removal  process and several additional optimizations.
-
-%The previous section described the switch layers, which deactivate neurons
-%on-the-fly. To benefit from ShrinkNets in practice, we must overcome two
-%challenges. First, to effectively reduce the network size we must remove the
-%deactivated neurons. Since removed neurons will no longer contribute to
-%improving prediction accuracy, we must be confident when removing them. Second,
-%for inference, we must remove the switch layers from the network. We describe
-%our solution for both challenges in this section.
 
@@
 must devise strategies that remove neurons while remaining robust to changing
-values. We observe three strategies:
+gradient values. We observe three strategies:
 
@@
 not fully representative of the dataset we might experience one-time zero
-crossing which could wrongly kill a neuron.
+crossing which could wrongly remove a neuron.
 
-\textbf{Sign variance strategy}: Instead of killing  on the first zero
+\textbf{Sign variance strategy}: Instead of removing on the first zero
 crossing, we can instead measure the exponential moving variance of the sign
@@
 effectively allow us to shrink the network by varying $\lambda$, and result in
-networks that are both small and perform well.
-
-%According to our experiments on linear and logistic regressions the
-%two last strategies reduce the number of parameter update performed during
-%training by at least an order of magnitude with only minimal impact on the final
-%error obtained by the model.
+networks that are both small and perform well. We use the third one in our
+evaluation section.
 
@@
 
-\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain reduced-
-sized networks during training, which is the first steps towards faster
+\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain
+reduced-sized networks during training, which is the first steps towards faster
 inference. This networks are readily available for inference. However, because
@@
 network parameters by combining each switch layer with its respective network
-layer by multiplying the respective parameters before emitting the final
-trained network. In the unlikely case that a switch layer is sandwiched
-between two non-linearly scalable layers, we leave the switch layer as is.
+layer by multiplying the respective parameters before emitting the final trained
+network.
 
-\noindent\textbf{Neural Garbage Collection: }ShrinkNets decides on-the-fly
-which neurons to remove. Since ShrinkNets removes a large fraction of neurons,
-we must dynamically resize the network at runtime to not unnecessarily impact
-network training time. We implemented a neural garbage collection method as
-part of our library which takes care of updating the necessary network layers
-as well as updating optimizer state to reflect the neuron removal.
-
-%\ra{move to eval:implementation, retrieve the neuran garbace collection and
-%place it somewhere here}
-%We have implemented \textbf{Switch Layers} and the associated training procedure
-%as a library in pytorch~\cite{paszke2017automatic}.  The layer can be freely
-%mixed with other popular layers such as convolutional layers, batchnorm layers,
-%fully connected layers etc.  There are two key challenges that must be overcome
-%while implementing \textbf{Switch Layers}.  
-%First, since ShrinkNets kill off a
-%large fraction of neurons, we must remove the overhead of carrying around dead
-%neurons.  And second, we must update the various network layers and training
-%machinery (e.g.  optimizer state) to reflect the deactivation of neurons.  We
-%address these challenges by augmenting every layer with additional information
-%about neuron status and implementing a \emph{neural garbage collection}
-%mechanism which prunes deactivated neurons on-the-fly and updates the state of
-%the training machinery.
-
-%A second implementation challenge we address with ShrinkNets is the potentially
-%higher inference time.  This increase in inference time is both due to the extra
-%computation introduced by switch layers and because our switch layers are not
-%currently optimized for CUDA.  Therefore, for now, our library provides a
-%post-training routine to ``fold'' switch layers into existing, optimized layers.
-%Specifically, for every switch layer, we check if the parent or child of this
-%layer is a linearly scalable layer (e.g. convolutional layer, fully connected
-%layer, batchnormalization layer) and if so, we fold the switch layer into this
-%neighboring layer by multiplying through by the switch weights.  
-%In the unlikely
-%case that a switch layer is sandwiched between two non-linearly scalable layers,
-%we leave the switch layer as is.
+\noindent\textbf{Neural Garbage Collection: }ShrinkNets decides on-the-fly which
+neurons to remove. Since ShrinkNets removes a large fraction of neurons, we must
+dynamically resize the network at runtime to not unnecessarily impact network
+training time. We implemented a neural garbage collection method as part of our
+library which takes care of updating the necessary network layers as well as
+updating optimizer state to reflect the neuron removal.

### 2018-02-09 paper/ICML/theory.tex
related work, makefile

@@
 %
+where $\bm{A}$ represents the connections and $\bm{b}$ the bias,
 removing an input neuron $j$ is equivalent to having $\left(\bm{A}^T\right)_j =
@@
 group of parameters to zero is the goal of group sparsity regularization
-\cite{xxx}. In  any partitioning of the set of parameters $\theta$ defining a model in $p$
-groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$, group sparsity is defined as: \srm{you used to say ``we define `it' as:'' -- I am assume `it' is group sparsity}
+\cite{Scardapane2017}. In  any partitioning of the set of parameters $\bm{\theta}$ defining a model in $p$
+groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$, group sparsity is defined as: 
 %
@@
 %
-\srm{define notation -- what is $\lambda$;  what is $\#\theta$, what is $\Omega$? Where does the square root come from?}
+\srm{define notation -- what is $\lambda$;  what is $\#\theta$, what is $\Omega$? Where does the square root come from?} \gl{This is how it is defined in the
+original paper, it would require a few sentences to explain that, do really
+need to do ?}
 In fully-connected layers, the groups are either: columns of
@@
 Because $\forall i, \#\bm{\theta}_i = n$, \ra{is \# the general way of expressing
-cardinality? why not $|x|$?}to make the notation simpler, we
+cardinality?
+why not $|x|$?,}  \gl{In europe |x| is for the abolute value, and I was using it in the notation section that someone removed, therefore there would have been a notation conflict}to make the notation simpler, we
 embedded $\sqrt{n}$ inside $\lambda$.
@@
 Group sparsity and ShrinkNets try to achieve the same goal. We discuss next how
-they are related to each other. First let's recall the two problems. The
-original ShrinkNet problem is \srm{do you mean ``can be defined formally as'' -- we never gave this definition of ShrinkNets.
-Also, you need to explain the formula / notation;  what is $y$, what is $\beta$, what is this equation representing (the optimization function?)}:
+they are related to each other. First let's recall the two problems. In the context of approximating $\bm{y}$ with a linear regression from features $\bm{x}$), the
+original ShrinkNet problem is 
 %
@@
 This is the reason we defined the \textit{regularized ShrinkNet penalty} above
-as \srm{where?}:\ra{the notation is slightly different, better to make it consistent}
+as:
 %
@@
 In practice we observed that $p=2$ or $p=1$ are good a choice; note that the latter
-will also introduce additional sparsity into the parameters. \srm{why?}
+will also introduce additional sparsity into the parameters because the $L_1$ is, 
+thest best convex approximation of the $L_0$ norm.

### 2018-02-09 paper/ICML/evaluation.tex
Address comments in the evaluation

@@
 $400$ epochs or when the learning rate is under $10^{-7}$, whichever comes
-first.  \gl{Should I also give the details about the removal strategy we used
-and the $\gamma$ and threshold I used ? because this is clearly getting boring}
-\srm{probably not necessary} For each of the models we trained, we pick the
+first. For each of the models we trained, we pick the
 epoch with the best validation accuracy and report the corresponding testing
@@
 is larger than what ImageNet, for example uses). Thus, for the classification
-layers we use $5000$ neurons as a starting limit (ImageNet uses $4096$ \gl{This
-is on the top of my head, need to be double checked}).
+layers we use $5000$ neurons as a starting limit.
 
@@
 the conventional heuristic that the original VGG architecture (and many CNNs)
-\gl{try to find the paper that introduces this heuristic} use, where
-\srm{describe what the heuristic is -- doubling of neurons up to apoint?} For
-\textit{Static Networks} we sample the size between $0.1$ and $2$ times the size
-\srm{size of what?} optimized for ImageNet. \srm{Why are we using ImageNet and
-not CIFAR10 as the comparison point?} We report the same numbers as we did for
+use, where the number of channels is doubled every after \textit{MaxPool} laxer.
+For \textit{Static Networks} we sample the size between $0.1$ and $2$ times the size
+original one, optimized for ImageNet. We report the same numbers as we did for
 \textit{ShrinkNets} and we compare the two distributions. \srm{I worry that
@@
 larger sizes and worse performance. What if we just randomly sample networks?
-Would it look terrible?}
+Would it look terrible?} \gl {I don't see any pricatical way of sampling
+reasonable a 13 dimension space if a single point take 1h to be evaluated}
 
@@
 A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time.
-\srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?}, at least for larger batches when hardware can be fully utilized.
+\srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?} \gl{The deep compression in table III shows it very well}, at least for larger batches when hardware can be fully utilized.
 
@@
 given target accuracy, the size needed is significantly smaller than when we use the
-\srm{name it} heuristic commonly used to size convolutional neural networks.
+"channel doubling" heuristic commonly used to size convolutional neural networks.
 This suggests that this conventional heuristic may not in fact be optimal,

### 2018-02-09 paper/ICML/introduction.tex

@@
 
-As neural networks become increasingly widely deployed in a variety of
-applications  -- ranging from improving camera quality on mobile phones
-\cite{googleapple} to language translation \cite{languagetranslation} to text
-auto-completion \cite{autocomplete} -- and on diverse hardware architectures
--- from laptops to phones to embedded sensors --  inference performance and
-model size are becoming as important in learning as metrics measures of
-prediction quality. However, these three aspect of model performance --
-quality, performance and size -- are largely optimized separately today, often
-with suboptimal results.
+Neural networks are increasingly being deployed in a wide variety  of
+applications  and on diverse hardware architectures ranging from laptops to
+phones to embedded sensors. This wide variety of deployment settings means
+that inference time and model size are becoming as important as  prediction
+quality when assessing model performance.  However, these three dimensions of
+performance (model quality, inference time and model size)  are largely
+optimized separately today, often with suboptimal results.
 
@@
 In contrast, in this paper we present a new method to simultaneously optimize
-both network size and model performance. The key idea is to learn the right
+ network size and model performance. The key idea is to learn the right
 network size at the same time that we optimize for prediction performance for a
 specific task. Our approach, called {\it ShrinkNets}, starts with an {\it
-oversized} network, and dynamically shrinks it by eliminating unimportant
+over-sized} network, and dynamically shrinks it by eliminating unimportant
 neurons---those that do not contribute to prediction performance---during
-training time. For that, ShrinkNets must detect the unimportant neurons, and
-remove them from the network, thus drastically reducing the network size. The
+training time. To do this, ShrinkNets must detect the unimportant neurons, and
+remove them from the network. The
 removal of entire neurons and not connections is crucial, because it leads to
-dense networks, which lead to better inference performance. To support the
+dense networks, which in turn leads to better inference performance. To support the
 detection and removal of unimportant neurons we introduce a new layer, called
-\textbf{Switch layer}. Introducing this new layer means we must redefine the
-loss function to account for the sparsity effect it introduces. ShrinkNets has
+\textbf{Switch layer}. Introducing this new layer simply requires us to
+add a term to the
+loss function to optimize the weights of this layer during training. ShrinkNets has
 two main benefits. First, it explores the architecture of models that are both
 small and perform well, rather than starting with a high-performance model and
-making it small.  This allows us to efficiently generate a family of smaller and
+making it small.  It does this using a single new hyperparameter that effectively 
+models the target network size.  This allows us to efficiently generate a family of smaller and
 accurate models without an exhaustive and expensive hyperparameter search over
@@
 dense, which means that inference time is also improved, e.g., on GPUs.
-
-XXX people actually don't treat network size as a hyperparameter;  we do!
 
@@
 \item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
-\item \srm{Some claim about model size vs performance}
 \item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
@@
 accuracy is one some real dataset}
-\item \srm{Something about dense networks and then benefit over optimal brain damage}
 \item \srm{Some claim about inference time}
-\item \srm{Some claim about compatibility with existing compression techniques?}
+\item \srm{Some claim about model size vs performance}
 \end{compactenum}

### 2018-02-09 paper/ICML/appendix.tex
edits

@@
 \vspace*{-5mm}
-\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression.
+\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknets on linear and logistic regression.
 From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
@@
 \subsection{Proofs}
-Unless stated explicitely, all the propositions consider the Multi-Target linear regression problem.
+Unless stated explicitly, all the propositions consider the Multi-Target linear regression problem.
 \begin{proposition}
@@
 \begin{proof}
-  we will split this proof in two different sections. the first one will
-  demonstrate that there is at least one global minimum. and the second
-  will show how to construct $2^k$ distinct solutions from a single global
+  We split the proof into two parts. First, we
+  demonstrate that there is at least one global minimum. Then, we 
+    how to construct $2^k$ distinct solutions from a single global
   minimum.
-  In order to prove this statement we will show that for any solution $\bm{A}$ in the first problem, there exists a solution in the second with the exact same value, and vice-versa.
-  \\ \textbf{Part 1:} We assume we have a potential solution $\bm{A}$ for the first problem and we define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$.
-It is easy to see that the constraint on $\bm{A}'$ is statisfied by construction.
+  In order to prove this second statement, we first show that for any solution $\bm{A}$ to the first problem, there exists a solution in the second with the exact same value, and vice-versa.
+  \\ \textbf{Part 1:} Assume we have a potential solution $\bm{A}$ for the first problem.
+We define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$.
+It is easy to see that the constraint on $\bm{A}'$ is satisfied by construction.
 Now:
@@
   Which concludes the first part.
-  \\ \textbf{Part 2:} Assuming we take an $\bm{A}'$ that satisfy the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
+  \\ \textbf{Part 2:} Assuming we take an $\bm{A}'$ that satisfies the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
 We can apply the same operations in reverse order and obtain an instance of the first problem with the same value.
@@
 We have $f(a, \beta) = \left(y - a\beta x\right)^2$.
-For simplicty let's take $y = 0$ and $x > 0$.
+For simplicty we's take $y = 0$ and $x > 0$.
 If we consider two candidates $s_1 = (0, 2)$ and $s_2 = (2, 0)$, we have $f(s_1) = f(s_2) = 0$.
 However $f(\frac{2}{2}, \frac{2}{2}) = x > \frac{1}{2} f(0, 2) + \frac{1}{2}f(2, 0)$, which break the convexity property.
-Since we showed that a particular case of the problem is non-convex then necessarly the general case cannot be convex.
+Since we showed that a particular case of the problem is non-convex then necessarily the general case cannot be convex.
 \end{proof}
@@
 \begin{proof}
-  We will split this proof in two parts. First we will show that there is at least
+  We  split this proof into two parts. First we show that there is at least
   one global minimum, then we will show how to construct $2^n - 1$ other distinct
@@
 $\Omega_{\lambda, \lambda_2, p}^{rs}$ is trivially coercive.
-Since we have a sum of terms, all bounded by below by $0$ and one of them is coercive, then the entire function admit at least one global minimum.
+Since we have a sum of terms, all bounded by below by $0$ and one of them is coercive, so the entire function admits at least one global minimum.
 \\ \textbf{Part 2:} Let's consider one global minimum.
 For each component $k$ of $\bm{\beta_i}$ for some $i$.
-Negating it and negating the $k^{th}$ column of $\bm{A_i}$ do not change the the first part of the objective because the two factors cancel each other.
-The two norms do not change either because by definition the norm is independant of the sign.
-As a result these two sets of parameter have the same value and by extension also global minimuma.
-It is easy to see that going from this global minimum we can decide to negate or not each element in each $\bm{\beta_i}$.
+Negating it and negating the $k^{th}$ column of $\bm{A_i}$ does not change the the first part of the objective because the two factors cancel each other.
+The two norms do not change either because by definition the norm is independent of the sign.
+As a result these two sets of parameters have the same value and by extension also a global minimum.
+It is easy to see that going from this global minimum, we can decide to negate or not each element in each $\bm{\beta_i}$.
 We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.
@@
 that ShrinkNets are a relaxation of Group sparsity.  In this experiment we want
-to compare the two aproaches.  We decided to focus on multi-target linear
+to compare the two approaches.  We decided to focus on multi-target linear
 regression because in the single target case, groups in the Group Sparsity
@@
 sparsity as the ratio of columns that have all their weights under $10^{-3}$ in
-absolute value. Regularization parameters were choosen in order to obtain the
+absolute value. Regularization parameters were chosen in order to obtain the
 widest sparsity spectrum. Loss is normalized depending on the problem to be in

### 2018-02-09 paper/ICML/paper.tex
Resolve most of the bibliography
Improve plots and multiple small changes
edits
pass over evaluation
pass over related work
added abstract

@@
 \usepackage{graphicx}
+\usepackage{placeins}
 \usepackage{hyperref}
@@
 \usepackage{paralist}
+
 % hyperref makes hyperlinks in the resulting PDF.
@@
 \begin{abstract}
-  Let's write the abstract at the end
+As neural networks are being increasingly deployed in 
+different applications and on different hardware, it has
+become increasingly important to optimize inference time
+and model size along with model accuracy.
+Most current work optimizes model size, model accuracy and
+inference time in different stages and results in suboptimal
+results at the cost of computational inefficiency.
+In this work, we propose a new techique called ShrinkNets that
+optimizes all three of these metrics simultaneously by learning
+optimal network size at training time.
+Specifically our technique presents a new method to simultaneously optimize network size and model performance by neuron-level pruning.
+Neuron-level pruning not only produces much smaller 
+networks for a given accuracy threshold but also produces
+dense weight matrices that are efficient at inference time.
+By applying our technique to a variety of models with both convolutional and fully connected layers, we show that ShrinkNets can reduce XXX by YYY and ZZZ by AAA in only BBB amount of time.
+
 \end{abstract}
@@
 \input{introduction}
+\input{related_work}
 \input{approach}
@@
 \input{evaluation}
-\input{related_work}
-\input{discussion}
+%\input{discussion}
 \input{conclusion}
@@
 \input{appendix}
+\FloatBarrier
 
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-\nocite{OpenML2013}
+\clearpage
 
-\bibliography{custom}
 \bibliographystyle{icml2018}
+\bibliography{custom,general}
 

### 2018-02-09 paper/ICML/related_work.tex
pass over related work

@@
 
-\begin{itemize}
-  \item post-training compression techniques -- brain damage , 
-  \item group sparsity e.g., \cite{Scardapane2017} and non-parametric neural networks -- 
-  \item training dynamics paper: first overfitting and then randomization?, \gl{Here is the ref, if you can introduce it in the flow \cite{Shwartz-Ziv2017}}
-\end{itemize}
+%\begin{itemize}
+%  \item post-training compression techniques -- brain damage , 
+%  \item group sparsity e.g., \cite{Scardapane2017} and non-parametric neural networks -- 
+%  \item training dynamics paper: first overfitting and then randomization?, \gl{Here is the ref, if you can introduce it in the flow \cite{Shwartz-Ziv2017}}
+%\end{itemize}
 
-Given the importance of network structure, many researchers have explored the
-problem of finding the best network structure for a given learning task.  
-The proposed techniques broadly fall into five categories: 
-random search andbrute force search,
-hyperparameter optimization,
-model compression after training,
-resizing models during training, and 
-automated architecture search methods.
+There are several lines of work related to finding a good network structure. We
+describe them next:
 
-The most popular techniques for hyperparameter optimization include simple
-methods such as random search~\cite{BergstraJAMESBERGSTRA2012} which have been
-shown to work suprisingly well compared to more complex methods such as those
-based on Bayesian optimization~\cite{Snoek12}.
-Brute force search of network sizes is also become more practical due to faster
-and more powerful hardware~\cite{molchanov2016pruning}.
-The more complex methods for hyperparameter optimization include techniques 
-such as~\cite{Snoek12} which model generalization performance via Gaussian
-Processes~\cite{GaussianProcesses} and select hyperparameter combinations that
-come from uncertain areas of the hyperparameter space.  
-Recently, methods based
-on bandit algorithms (e.g. ~\cite{li2016hyperband, jamieson2016}) have also
-become a popular way to tune hyperparameters.
-As noted before, all of the
-above techniques require many tens to hundreds of models to be trained, making
-this process computationally inefficient and slow.
-More practically, the hyperparameter optimization literature does not evaluate
-their methods on network size and instead focuses on optimization hyperparameters
-such as learning rates and weight decay parameters.
+%Given the importance of network structure, many researchers have explored the
+%problem of finding the best network structure for a given learning task.  The
+%proposed techniques broadly fall into five categories: random search andbrute
+%force search, hyperparameter optimization, model compression after training,
+%resizing models during training, and automated architecture search methods.
 
-In contrast with size search techniques, there are techniques that 
-reduce network size {\it once the network has been traiend}.
-Popular techniques in this class include optimal brain damage~\cite{Cun} and
-compression techniques such as DeepCompression~\cite{han2015deepcompression}.
-Optimal brain damage identifies connections in a network that are unimportant
-and then prunes these connections.
-DeepCompression takes this one step further and in addition to pruning connections,
-it quantizes weights to make inference extremely efficient.
-% In contrast with hyperparameter tuning methods, some methods such as
-% DeepCompression~\cite{han2015deepcompression} seek to compress the network to
-% make inference more efficient.  This is accomplished by pruning connections and
-% quantizing weights.  
-A different vein of work such as ~\cite{romero2014fitnets, hinton2015distilling}
-proposes techniques for distilling a network into a simpler network or 
-a different model.  Unlike our
-technique which works during training, these techiques are used after training
-and it would be interesting to apply them to ShrinkNets as well. 
-\cite{Abadi2016b} share the common goal of removing entire blocks of parameter to maintain dense matrices, however their method only applies to convolutional layers.
+\noindent\textbf{Hyperparameter optimization techniques: }The most popular
+techniques for hyperparameter optimization include simple methods such as random
+search~\cite{BergstraJAMESBERGSTRA2012} which have been shown to work
+suprisingly well compared to more complex methods such as those based on
+Bayesian optimization~\cite{Snoek12}.  Brute force search of network sizes is
+also become more practical due to faster and more powerful
+hardware~\cite{molchanov2016pruning}.  The more complex methods for
+hyperparameter optimization include techniques such as~\cite{Snoek12} which
+model generalization performance via Gaussian Processes~\cite{GaussianProcesses}
+and select hyperparameter combinations that come from uncertain areas of the
+hyperparameter space. Recently, methods based on bandit algorithms (e.g.
+~\cite{li2016hyperband, jamieson2016}) have also become a popular way to tune
+hyperparameters. With respect to our work, these methods require many tens of
+hundreds of models to be trained, which makes the process computationally
+inefficient and slow. In contrast, with ShrinkNets all the hyperparameters
+related to network size are reduced to a single parameter, as we explain next.
+More importantly, none of the hyperparameter optimization methods focuses on
+finding small networks, which is a crucial property of ShrinkNets, necessary to
+achieve good inference times.
 
-The techniques closest to our proposed method are those based on group sparsity 
-such as ~\cite{Scardapane2017}, and those like~\cite{Philipp} who grow and shrink
-dynamically the size of the network during training.
+%As noted before, all of the above techniques require many tens
+%to hundreds of models to be trained, making this process computationally
+%inefficient and slow.  More practically, the hyperparameter optimization
+%literature does not evaluate their methods on network size and instead focuses
+%on optimization hyperparameters such as learning rates and weight decay
+%parameters.
 
-\cite{Scardapane2017} presents a method that also deactivates neurons using a 
-loss function based on group-sparsity.
-However, the exact details of how their method works are not given, and 
-their experimental results (on a small, fully connected network), 
-are substantially worse than ours as shown in Section~\ref{sec:experiments}.
+\noindent\textbf{Model Compression: }Model compression techniques focus on
+reducing the model size \emph{after} training, in contrast to ShrinkNets, which
+reduces it \emph{while} training. 
+Optimal brain damage~\cite{Cun} identifies connections in a network that are
+unimportant and then prunes these connections.
+DeepCompression~\cite{han2015deepcompression} takes this one step further and in
+addition to pruning connections, it quantizes weights to make inference
+extremely efficient.  A different vein of work such as ~\cite{romero2014fitnets,
+hinton2015distilling} proposes techniques for distilling a network into a
+simpler network or a different model. Because these techniques work after
+training, they are orthogonal and complementary to ShrinkNets. 
+%Unlike our technique which works during
+%training, these techiques are used after training and it would be interesting to
+%apply them to ShrinkNets as well. 
+%\cite{Abadi2016b} share the common goal of
+%removing entire blocks of parameter to maintain dense matrices, however their
+%method only applies to convolutional layers.
+
+\noindent\textbf{Auto-ML: }There is work that focuses on automatically learning
+model architecture through the use of genetic algorithms and reinforcement
+learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
+techniques are focused on learning higher-level architectures (e.g.,
+building blocks for neural network architectures). In particular, they do not
+focus on finding small but well-performing networks for inference, which is the
+goal of ShrinkNets.
+
+\noindent\textbf{Dynamically Sizing Networks: }The techniques closest to our
+proposed method are those based on group sparsity such as
+~\cite{Scardapane2017}, and those like~\cite{Philipp} who grow and shrink
+dynamically the size of the network during training.  \cite{Scardapane2017}
+presents a method that also deactivates neurons using a loss function based on
+group-sparsity.  However, the exact details of how their method works are not
+given, and their experimental results (on a small, fully connected network), are
+substantially worse than ours as shown in Section~\ref{sec:experiments}.
 ~\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
-that adds neurons on the fly and removes neurons via an $l_2$ penalty.
-However, this approach requires a new optimizer and takes longer to converge 
-compared to ShrinkNets.
-
-Finally, there has also been recent work in automatically learning model
-architecture through the use of genetic algorithms and reinforcement learning
-techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}.  These
-techniques are focused more on learning higher-level architectures (e.g.
-building blocks for neural network architectures) as opposed to learning
-network size.
+that adds neurons on the fly and removes neurons via an $l_2$ penalty.  However,
+this approach requires a new optimizer and takes longer to converge compared to
+ShrinkNets.

### 2018-02-09 paper/ICML/paper.tex
added macros
Update paper.tex
added numbers to abstract

@@
 \usepackage{paralist}
+\usepackage{xspace}
 
@@
 \newcommand{\mpv}[1]{\textcolor{green}{{\bf MV:} #1}}
+\newcommand{\shrink}{{\bf ShrinkNets}\xspace}
+\newcommand{\swl}{{\bf SwitchLayer}\xspace}
+\newcommand{\swls}{{\bf SwitchLayers}\xspace}
 % If accepted, instead use the following line for the camera-ready submission:
@@
 \begin{abstract}
-As neural networks are being increasingly deployed in 
-different applications and on different hardware, it has
-become increasingly important to optimize inference time
-and model size along with model accuracy.
-Most current work optimizes model size, model accuracy and
-inference time in different stages and results in suboptimal
-results at the cost of computational inefficiency.
-In this work, we propose a new techique called ShrinkNets that
-optimizes all three of these metrics simultaneously by learning
-optimal network size at training time.
-Specifically our technique presents a new method to simultaneously optimize network size and model performance by neuron-level pruning.
-Neuron-level pruning not only produces much smaller 
-networks for a given accuracy threshold but also produces
-dense weight matrices that are efficient at inference time.
-By applying our technique to a variety of models with both convolutional and fully connected layers, we show that ShrinkNets can reduce XXX by YYY and ZZZ by AAA in only BBB amount of time.
-
+As neural networks are being increasingly deployed in different applications and
+on different hardware, it has become increasingly important to optimize
+inference time and model size along with model accuracy.  Most current work
+optimizes model size, model accuracy and inference time in different stages and
+results in suboptimal results at the cost of computational inefficiency.  In
+this work, we propose a new techique called ShrinkNets that optimizes all three
+of these metrics simultaneously by learning optimal network size at training
+time.  Specifically our technique presents a new method to simultaneously
+optimize network size and model performance by neuron-level pruning.
+Neuron-level pruning not only produces much smaller networks for a given
+accuracy threshold but also produces dense weight matrices that are efficient at
+inference time.  By applying our technique to a variety of models with both
+convolutional and fully connected layers, we show that ShrinkNets can reduce by
+35\% the network size with respect to a static network for \texttt{CIFAR10}, and
+it can achieve speedups during inference time of up to 40X. In addition, the
+most accurate networks found by ShrinkNets are similar or more accurate than
+those found by statically trained networks.  
 \end{abstract}

### 2018-02-09 paper/ICML/introduction.tex

@@
 In summary, our contributions are as follows:
+
 \begin{compactenum}
+
 \item We propose a novel technique based on dynamically switching on and off neurons, 
-which allows us to optimize the network size as the network is trained. 
-\item \srm{xxx postprocessing techniques to strip out switch layers}
-\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
-\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
-showing that 
-ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
-training time compared to existing hyperparameter optimization methods. \srm{Mention the specific 
-model/dataset where this is true.}
-\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
-of neurons. \srm{This claim should be something about how much smaller a network with say 99\%
-accuracy is one some real dataset}
-\item \srm{Some claim about inference time}
-\item \srm{Some claim about model size vs performance}
+which allows us to optimize the network size while the network is trained.
+
+\item We implement our technique so as to remove entire neurons, therefore
+leading not only to small and well-performing networks, but also dense, which
+means higher inference performance.
+
+%\item \srm{xxx postprocessing techniques to strip out switch layers}
+
+\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006}
+and prove that our problem admits many global minima.
+
+\item We demonstrate our claims with both fully-connected and convolutional well
+known neural network architectures. We show that with ShrinkNets for
+\texttt{CIFAR10} we achieve the same accuracy than a traditionally trained
+network while reducing the network size by a factor of $2.2x$. Further, when
+willing to sacrifice only $1$\% of performance, ShrinkNets finds networks which
+are 35\% smaller. All in all, this leads to speedups in inference time of up to
+40X.
+
+%\item We demonstrate the efficacy of our technique on both convolutional and
+%fully-connected neural nets, showing that ShrinkNets finds networks within
+%+/-X\% of best hand-crafted accuracy in XX\% of training time compared to
+%existing hyperparameter optimization methods. \srm{Mention the specific
+%model/dataset where this is true.}
+
+%\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% of
+%neurons. \srm{This claim should be something about how much smaller a network
+%with say 99\% accuracy is one some real dataset}
+%
+%\item \srm{Some claim about inference time}
+%
+%\item \srm{Some claim about model size vs performance}
+
 \end{compactenum}

### 2018-02-09 paper/ICML/related_work.tex
Update related_work.tex
edits

@@
 
-There are several lines of work related to finding a good network structure. We
-describe them next:
+There are several lines of work related to optimizing network structure.
 
@@
 
-\noindent\textbf{Hyperparameter optimization techniques: }The most popular
-techniques for hyperparameter optimization include simple methods such as random
-search~\cite{BergstraJAMESBERGSTRA2012} which have been shown to work
-suprisingly well compared to more complex methods such as those based on
-Bayesian optimization~\cite{Snoek12}.  Brute force search of network sizes is
-also become more practical due to faster and more powerful
-hardware~\cite{molchanov2016pruning}.  The more complex methods for
-hyperparameter optimization include techniques such as~\cite{Snoek12} which
-model generalization performance via Gaussian Processes~\cite{GaussianProcesses}
-and select hyperparameter combinations that come from uncertain areas of the
-hyperparameter space. Recently, methods based on bandit algorithms (e.g.
+\noindent\textbf{Hyperparameter optimization techniques: }
+One way to optimize network architecture is to use 
+hyperparameter optimization.  Although many methods have been 
+proposed, e.g., \cite{BergstraJAMESBERGSTRA2012,Snoek12},
+randomized search has been shown to work surprising well.
+%  Brute force search of network sizes is
+%also become more practical due to faster and more powerful
+%hardware~\cite{molchanov2016pruning}.  
+The more complex methods for
+hyperparameter optimization include techniques, e.g., ~\cite{Snoek12} typically
+ select hyperparameter combinations that come from uncertain areas of the
+hyperparameter space to search efficiency. 
+As a generalization of this,  methods based on bandit algorithms (e.g.
 ~\cite{li2016hyperband, jamieson2016}) have also become a popular way to tune
-hyperparameters. With respect to our work, these methods require many tens of
-hundreds of models to be trained, which makes the process computationally
-inefficient and slow. In contrast, with ShrinkNets all the hyperparameters
-related to network size are reduced to a single parameter, as we explain next.
-More importantly, none of the hyperparameter optimization methods focuses on
-finding small networks, which is a crucial property of ShrinkNets, necessary to
-achieve good inference times.
+hyperparameters by quickly discarding 
+model configurations that perform badly. 
+Although these methods could in theory be used to tune the number of neurons per layer
+of a network, in practice no related work proposes this, because treating each layer as a hyperparameter
+would lead an excessively large search space.
+In contrast, with ShrinkNets the size of the network can be tuned with 
+a single parameter, as we explain in the next section..
+% More importantly, none of the hyperparameter optimization methods focuses on
+% finding small networks, which is a crucial property of ShrinkNets, necessary to
+% achieve good inference times.
 
@@
 simpler network or a different model. Because these techniques work after
-training, they are orthogonal and complementary to ShrinkNets. 
+training, they are orthogonal and complementary to ShrinkNets. Further,
+some of these techniques, e.g.,~\cite{Han2015,Cun}, produce sparse matrices that
+are not likely to improve inference times even though they reduce network size.
 %Unlike our technique which works during
@@
 
-\noindent\textbf{Auto-ML: }There is work that focuses on automatically learning
+\noindent\textbf{Auto-ML: } Some work that focuses on automatically learning
 model architecture through the use of genetic algorithms and reinforcement
@@
 proposed method are those based on group sparsity such as
-~\cite{Scardapane2017}, and those like~\cite{Philipp} who grow and shrink
-dynamically the size of the network during training.  \cite{Scardapane2017}
+~\cite{Scardapane2017}, and those like~\cite{Philipp} that dynamically grow and shrink
+ the size of the network during training.  \cite{Scardapane2017}
 presents a method that also deactivates neurons using a loss function based on
@@
 substantially worse than ours as shown in Section~\ref{sec:experiments}.
-~\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
+\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
 that adds neurons on the fly and removes neurons via an $l_2$ penalty.  However,

### 2018-02-09 paper/ICML/evaluation.tex

@@
 \begin{compactitem}
-
-\item Whether, by varying $\lambda$, \textit{ShrinkNets} can efficiently
+\item Whether, by varying $\lambda$, \shrink can efficiently
 explore (in terms of number of training runs)  the spectrum of high-accuracy
@@
 
-\item Whether the ShrinkNets approach results in network architectures that are
+\item Whether the \shrink approach results in network architectures that are
 substantially different than the best network architectures (in terms of
@@
 
-\noindent\textbf{Implementation: }We implemented \textbf{switch Layers} and
+\noindent\textbf{Implementation: }We implemented \swls and
 the associated training procedure as a library in
@@
 layers, and used with all the traditional optimizers. We use our implementation
-to evaluate ShrinkNets throughout the evaluation section.
+to evaluate \shrink throughout the evaluation section.
 
-\subsection{Can ShrinkNets achieve good accuracy?}
+\subsection{Can \shrink achieve good accuracy?}
 %\subsection{Performance vs. Traditional Methods}
 
-To answer this question we compare ShrinkNets with a traditional network. In
+To answer this question we compare \shrink with a traditional network. In
 both cases, we need to perform hyperparameter optimization to explore different
 network architectures. We perform random search, which is an effective technique
-for this purpose \cite{}. We evaluate ShrinkNets on two well-known datasets. One
+for this purpose \cite{BergstraJAMESBERGSTRA2012}. We evaluate \shrink on two well-known datasets. One
 for which it is not possible to explore the entire space of network
@@
 and independently selecting the values of these parameters from a range of
-reasonable values (\gl{should we make them explicit ?} \srm{yes}).  
+reasonable values.
+ % (\gl{should we make them explicit ?} \srm{yes}).  
 %We trained
@@
 measure the total size, in terms of number of floating point parameters,
-excluding the \textit{Switch Layers} because as described in
+excluding the \swls because as described in
 \cref{neuron_killing}, these are eliminated after training.
@@
 
-We applied ShrinkNets to the VGG16 network by adding \textit{Switch Layers}
+We applied \shrink to the VGG16 network by adding \swls
 after each \textit{BatchNorm} layer and each fully connected layer (except the
-last).  Recall that ShrinkNets assume that the starting size of the network is
+last).  Recall that \shrink assume that the starting size of the network is
 an upper bound on the optimal size. For this reason, we simply started with a
 network with double the recommended size for each layer as an upper bound (this
-is larger than what ImageNet, for example uses). Thus, for the classification
-layers we use $5000$ neurons as a starting limit.
+is larger than what ImageNet, for example uses). 
+% Thus, for the classification
+% layers we use $5000$ neurons as a starting limit.
 
@@
 number of parameters that control the size is large: 13 parameters for the
-convolutional layers and $2$ for the fully connected layers. ShrinkNets
+convolutional layers and $2$ for the fully connected layers. \shrink
 effectively fuse all these parameters in a single $\lambda$, but in conventional
@@
 original one, optimized for ImageNet. We report the same numbers as we did for
-\textit{ShrinkNets} and we compare the two distributions. \srm{I worry that
-this method of selecting network sizes for Static will of course constrain it to
-larger sizes and worse performance. What if we just randomly sample networks?
-Would it look terrible?} \gl {I don't see any pricatical way of sampling
-reasonable a 13 dimension space if a single point take 1h to be evaluated}
+\shrink and we compare the two distributions. 
+% \srm{I worry that
+% this method of selecting network sizes for Static will of course constrain it to
+% larger sizes and worse performance. What if we just randomly sample networks?
+% Would it look terrible?} \gl {I don't see any pricatical way of sampling
+% reasonable a 13 dimension space if a single point take 1h to be evaluated}
 
 The results are shown in the top figure of \cref{figure_CIFAR10}, with blue dots
-indicating ShrinkNet models and orange dots indicating static networks. For each
+indicating models produced by \shrink and orange dots indicating static networks. 
+For each
 model, we plot its accuracy and model size. The lines show the Pareto frontier
 of models in each of the two optimization settings. ShrinkNets explore the
-trade-off between model size and accuracy more effectively. \srm{Would be good
+trade-off between model size and accuracy more effectively. 
+\srm{Would be good
 to show Lambda values on the figure somehow.  } \srm{I thought we were going to

### 2018-02-09 paper/ICML/introduction.tex
edits

@@
 Existing techniques typically aim make a pre-trained neural network smaller
-\cite{something1,something2} by taking one of two approaches:  either by
-applying quantization \cite{quant} or code compilation~\cite{something}
+by taking one of two approaches:  either by
+applying quantization \cite{quant} or code compilation~\cite{ma2016compilation}
 techniques that can be applied blindly to any network, or by analyzing the
 structure of the network and systematically pruning
-connections~\cite{han2015deepcompression,Cun} or neurons~\cite{XXX}
+connections or neurons~\cite{han2015deepcompression,Cun}
 based on some loss function.  Although these techniques can substantially
@@
 which can be substantially slower to execute on modern hardware
-\cite{something}, especially GPUs which do not efficiently support sparse
+\cite{han2015deepcompression}, especially GPUs which do not efficiently support sparse
 linear algebra.  Third, these techniques generally start by optimizing a
@@
 
-The remaining of this paper is organized as follows. In section
-\ref{sec:relatedwork} we discuss the related work. In section
-\ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
-practical considerations we implemented to make it work in section
-\ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
-and conclude the paper in section \ref{sec:conclusions}.
+% The remaining of this paper is organized as follows. In section
+% \ref{sec:relatedwork} we discuss the related work. In section
+% \ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
+% practical considerations we implemented to make it work in section
+% \ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
+% and conclude the paper in section \ref{sec:conclusions}.

### 2018-02-09 paper/ICML/evaluation.tex
Add numbers to the evaluation

@@
 relative number of neurons per layered) identified in the literature.
-
-\item \srm{something else?}
 
@@
 trade-off between model size and accuracy more effectively. 
-\srm{Would be good
-to show Lambda values on the figure somehow.  } \srm{I thought we were going to
-summarize with distributional plots instead of Pareto frontiers?} 
 %\srm{Summarize
@@
 
-Note that the best performing ShrinkNets models has \ra{xx} accuracy while the
-best static model has \ra{xx} accuracy, while the ShrinkNets model is \ra{xx}
-times smaller. In addition, if we give up just 1\% error, ShrinkNets finds a
-model that is \ra{xx} times smaller.
+Note that the best performing ShrinkNets models has $92.07\%$ accuracy which
+is identical to the accuracy of the static network, while the ShrinkNets model
+is $2.22$ times smaller. In addition, if we give up just 1\% error, ShrinkNets
+finds a model that is 35.5 times smaller than any static network that performs
+as good or better.
 
@@
 
-Note that the best performing ShrinkNets models has \ra{xx} accuracy while the
-best static model has \ra{xx} accuracy, while the ShrinkNets model is \ra{xx}
-times smaller. In addition, if we give up just 1\% error, ShrinkNets finds a
-model that is \ra{xx} times smaller.
+Note that the best performing ShrinkNets models has $96.91\%$ accuracy while the
+best static model is only $96.66\%$ accurate, while the ShrinkNets model is $2.51$
+times smaller. In addition, if we give up just 0.5\% error, ShrinkNets finds a
+model that is 38.6 times smaller than any static network with equivalent accuracy.
 
@@
 
-A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time.
-\srm{Can we cite something showing that local sparsity does not improve performance even w/ small nets?} \gl{The deep compression in table III shows it very well}, at least for larger batches when hardware can be fully utilized.
+A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time~\cite{Han2015}.
 
@@
 
-\ra{checkpoint}
-
 \subsection{Architectures obtained after convergence}
@@
 Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the
-best test accuracy, with \srm{identical performance to the best static
-network?}; the bottom shows a network that slightly under-performs the best in
+best test accuracy, with identical performance to the best static
+network; the bottom shows a network that slightly under-performs the best in
 terms of accuracy but is significantly smaller that the best equivalent
-\textit{Static Network} \srm{how much smaller?}.  In the plot, the dashed line
+\textit{Static Network}.  In the plot, the dashed line
 shows the number of neurons in each layer of the original VGG net, and the

### 2018-02-09 paper/ICML/impl.tex

@@
 or \emph{off} neurons. When neurons are deactivated by switch layers, we need
-to remove them to actually shrink the network size. Since after removing a
-neuron it will no longer be able to contribute to  prediction accuracy, we
-must devise strategies that remove neurons while remaining robust to changing
-gradient values. We observe three strategies:
+to remove them to actually shrink the network size.
+In the following we discuss three potential strategies to remove neurons. 
+%Since after removing a neuron it will no longer be able to contribute to  prediction accuracy, we must devise strategies that remove neurons while remaining robust to changing gradient values.
+We observe three strategies:
 
@@
 a fixed threshold expressed in terms of its absolute value. This is the method
-used by deep compression \cite{}. We found this method is not robust to noise
-in the gradients---which occurs commonly when training networks with
+used by deep compression \cite{}. We found this method is very sensitive to the initializaiton 
+and not robust to noise in the gradients---which occurs commonly when training networks with
 stochastic gradient descent---because the threshold depends on the scale of
@@
 \textbf{Sign change strategy}: Under this strategy neurons are removed when the
-weight value changes its sign. This strategy works well in practice but it is
-also sensitive to gradient noise. If we sample the gradient in a way that is
-not fully representative of the dataset we might experience one-time zero
-crossing which could wrongly remove a neuron.
+weight value changes its sign.
+As before this strategy is also sensitive to gradient noise; if we sample the gradient in a way that is not fully representative of the dataset we might experience one-time zero crossing which could wrongly remove a neuron.
 
@@
 two extra parameters, one to control the behavior of the inertia of the
-variance, and the threshold, but we have found it is the best performing in
-practice.
+variance, and the threshold. 
+However, we found that this strategy performs the best in practice and is used throughout our evaluation section.
 
-The last two strategies perform better than the threshold strategy.  Both
-effectively allow us to shrink the network by varying $\lambda$, and result in
-networks that are both small and perform well. We use the third one in our
-evaluation section.
+%The last two strategies perform better than the threshold strategy.
+Both effectively allow us to shrink the network by varying $\lambda$, and result in networks that are both small and perform well.
+We use the third one in our evaluation section.
 
@@
 layer by multiplying the respective parameters before emitting the final trained
-network.
+network. As a result, the final network is a dense network without any switching layers.
 

### 2018-02-09 paper/ICML/introduction.tex

@@
 Of course, the problem of finding compressed or small networks is not new.
-Existing techniques typically aim make a pre-trained neural network smaller
+Existing techniques typically aim to make a pre-trained neural network smaller
 by taking one of two approaches:  either by

### 2018-02-09 paper/ICML/theory.tex
sec.3

@@
 %\subsection{Relation to Group Sparsity}
-\noindent\textbf{Relation to Group Sparsity (LASSO): } ShrinkNets removes neurons,
+\noindent\textbf{Relation to Group Sparsity (LASSO): } \shrink removes neurons,
 i.e., inputs and outputs of layers. For a fully connected layer defined as:
@@
 group of parameters to zero is the goal of group sparsity regularization
-\cite{Scardapane2017}. In  any partitioning of the set of parameters $\bm{\theta}$ defining a model in $p$
-groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$, group sparsity is defined as: 
+\cite{Scardapane2017}. 
+In  any partitioning of the set of parameters $\bm{\theta}$ defining a model in $p$
+groups: $\bm{\theta} = \bigcup_{i=1}^P \bm{\theta}_i$, group sparsity 
+penalty is defined as (where $\lambda$ is the regularization parameter): 
 %
 \begin{equation}
-  \Omega_\lambda^{gp} = \lambda \sum_{i=1}^p \sqrt{\#\bm{\theta_i}} \norm{\bm{\theta_i}}_2 \\
+  \Omega_\lambda^{gp} = \lambda \sum_{i=1}^p \sqrt{\mathbf{card}(\bm{\theta_i}}) \norm{\bm{\theta_i}}_2 \\
 \end{equation}
-%
-\srm{define notation -- what is $\lambda$;  what is $\#\theta$, what is $\Omega$? Where does the square root come from?} \gl{This is how it is defined in the
-original paper, it would require a few sentences to explain that, do really
-need to do ?}
+% \srm{define notation -- what is $\lambda$;  what is $\#\theta$, what is $\Omega$? Where does the square root come from?} \gl{This is how it is defined in the
+% original paper, it would require a few sentences to explain that, do really
+% need to do ?}
 In fully-connected layers, the groups are either: columns of
@@
 not make sense, so we only consider removing inputs. The
-group sparsity regularization then becomes:
+group sparsity regularization then becomes (when $\sqrt{n}$ is folded into the $\lambda$)
 %
@@
 \end{equation}
-%
-Because $\forall i, \#\bm{\theta}_i = n$, \ra{is \# the general way of expressing
-cardinality?
+
+% Because $\forall i, \#\bm{\theta}_i = n$, embedded $\sqrt{n}$ inside $\lambda$.
+%  \ra{is \# the general way of expressing
+% cardinality?
 why not $|x|$?,}  \gl{In europe |x| is for the abolute value, and I was using it in the notation section that someone removed, therefore there would have been a notation conflict}to make the notation simpler, we
-embedded $\sqrt{n}$ inside $\lambda$.
 
-Group sparsity and ShrinkNets try to achieve the same goal. We discuss next how
+Group sparsity and \shrink try to achieve the same goal. We discuss next how
 they are related to each other. First let's recall the two problems. In the context of approximating $\bm{y}$ with a linear regression from features $\bm{x}$), the
-original ShrinkNet problem is 
+original \shrink problem is 
 %
@@
 %
-And the Group Sparsity problem is:
+And the group sparsity problem is:
 %
@@
 \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
-(\cref{gps_equivalence}, see Apendix). However if we relax this constraint then ShrinkNets
+(\cref{gps_equivalence}, see Apendix). However if we relax this constraint then \shrink
 becomes non-convex and has no global minimum
 (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}, also in Appendix). Fortunately,
-by adding an extra term to the ShrinkNet regularization term we can prove that:
+by adding an extra term to the \shrink regularization term we can prove that:
 %
@@
 has global minimums for all $p>0$ (\cref{shrinknet_regularized_minimum}).
-This is the reason we defined the \textit{regularized ShrinkNet penalty} above
-as:
+This is the reason we defined the regularized \shrink penalty above as:
 %

### 2018-02-09 paper/ICML/appendix.tex

@@
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=.7\columnwidth]{regressions}
-\vspace*{-5mm}
-\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknets on linear and logistic regression.
+%\begin{figure}[t]
+%\begin{center}
+%\includegraphics[width=.7\columnwidth]{regressions}
+%\vspace*{-5mm}
+%\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknets on linear and logistic regression.
 From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}
-
-\end{center}
-\vspace*{-4mm}
-\end{figure}
+%
+%\end{center}
+%\vspace*{-4mm}
+%\end{figure}
 
@@
 \end{proof}
-\subsection{Multi-Target Linear and Multi-Class Logistic regressions experiments}
-As we showed, Group sparsity share similarities with our method, and we claim
-that ShrinkNets are a relaxation of Group sparsity.  In this experiment we want
-to compare the two approaches.  We decided to focus on multi-target linear
-regression because in the single target case, groups in the Group Sparsity
-problem would have a size of one ($\bm{A}$ would be a vector in this case).
 
-The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
-\cite{Spyromitros-Xioufis2016} for linear regressions and we will use \texttt{gina\_prior2} \cite{4371065} and
-the \textit{Gas Sensor Array Drift Dataset} \cite{VERGARA2012320} (that we shorten in
-\texttt{gsadd}) for logistic regressions.
-
-For each dataset we fit with different regularization parameters and measure
-the error and sparsity obtained after convergence. In this context we define
-sparsity as the ratio of columns that have all their weights under $10^{-3}$ in
-absolute value. Regularization parameters were chosen in order to obtain the
-widest sparsity spectrum. Loss is normalized depending on the problem to be in
-the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
-our experiments it is clear that ShrinkNets can fit the data closer than Group
-Sparsity for the same amount of sparsity. The fact that we are able to reach
-very low loss demonstrate that even if our objective function is non convex, in
-practice it works as good or better as convex alternatives.
+%\subsection{Multi-Target Linear and Multi-Class Logistic regressions experiments}
+%As we showed, Group sparsity share similarities with our method, and we claim
+%that ShrinkNets are a relaxation of Group sparsity.  In this experiment we want
+%to compare the two approaches.  We decided to focus on multi-target linear
+%regression because in the single target case, groups in the Group Sparsity
+%problem would have a size of one ($\bm{A}$ would be a vector in this case).
+%
+%The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
+%\cite{Spyromitros-Xioufis2016} for linear regressions and we will use \texttt{gina\_prior2} \cite{4371065} and
+%the \textit{Gas Sensor Array Drift Dataset} \cite{VERGARA2012320} (that we shorten in
+%\texttt{gsadd}) for logistic regressions.
+%
+%For each dataset we fit with different regularization parameters and measure
+%the error and sparsity obtained after convergence. In this context we define
+%sparsity as the ratio of columns that have all their weights under $10^{-3}$ in
+%absolute value. Regularization parameters were chosen in order to obtain the
+%widest sparsity spectrum. Loss is normalized depending on the problem to be in
+%the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
+%our experiments it is clear that ShrinkNets can fit the data closer than Group
+%Sparsity for the same amount of sparsity. The fact that we are able to reach
+%very low loss demonstrate that even if our objective function is non convex, in
+%practice it works as good or better as convex alternatives.

### 2018-02-09 paper/ICML/approach.tex

@@
 
-In this section we describe the ShrinkNets approach, which allows us to learn
+In this section we describe the \shrink approach, which allows us to learn
 the network size as part of the training process. The key idea is the addition
-of \emph{switch layers} added after each layer in the network;  these layers
-allow us to disable certain neurons during training.  We start by introducing the
+of \swls after each layer in the network;  these layers
+allow us to selectively deactivate neurons during training.  We start by introducing the
 basic method, and then explain how to adapt the training procedure to support this new
@@
 
-At a high-level, out approach consists of two interconnected stages.
+At a high-level, our approach consists of two interconnected stages.
 The first stage identifies neurons that do not improve the
-prediction accuracy of the network and deactivates them. The second stage then
-removes neurons from the network, shrinking its
-size and yielding faster inference times. Broadly, these stages work as follows:
+prediction accuracy of the network and deactivates them. 
+The second stage then {\it removes} neurons from the network (explicitly
+shrinking weight matrices and updating optimizer state) thus leading to 
+smaller networks and also faster inference times.
 
 \noindent\textbf{Deactivating Neurons On-The-Fly: }During the first stage,
-ShrinkNets applies an on/off switch to every neuron of an initially over-sized
+\shrink applies an on/off switch to every neuron of an initially over-sized
 network. We model the on/off switches by multiplying each input (or output) of
@@
 will deactivate the neuron, while $1$ will let the signal go through. These
-switches are part of a new layer, called the \textbf{switch layer}; this layer applies 
+switches are part of a new layer, called the \swl; this layer applies 
 to fully connected as well as convolutional layers.
@@
 as possible while preserving prediction accuracy. This can be achieved by jointly
-minimizing the objective of the network and a factor of the L0 norm of the
-vector containing all the switches. Because finding an optimal binary
-assignment is an NP-Hard problem, we relax the problem by allowing
- $\bm{\beta}$ to be a real number
-instead of a binary value and constrain it using the L1 instead of L0 norm.
+minimizing the training loss of the network and applying an L0 norm to the 
+$\bm{\beta}$ parameters of the \swl. 
+Since minimizing the L0 norm is an NP-Hard problem, we instead relax the constraint
+to an L1 norm by constraining $\bm{\beta}$ to be a real number
+instead of a binary value.
+% Because finding an optimal binary
+% assignment is an NP-Hard problem, we relax the problem by allowing
+%  $\bm{\beta}$ to be a real number
+% instead of a binary value and constrain it using the L1 instead of L0 norm.
 
@@
 because we have observed that this allows the remaining active neurons to adapt
-to the new network architecture. Existing techniques focus on neuron removal
-after training, and require an extra fine-tuning process to compensate for the
-removal.\srm{cite something?} \gl{I think we are fine or we could actually
-cite any of these paper}
+to the new network architecture and we can avoid a post-training step to prune
+deactivated neurons.
+% Existing techniques focus on neuron removal
+% after training, and require an extra fine-tuning process to compensate for the
+% removal.
+% \srm{cite something?} \gl{I think we are fine or we could actually
+% cite any of these paper}
 
 In the remainder of this section we describe in detail the switch layer as well
-as and the training process for ShrinkNets, and then describe the removal process in Section~\ref{neuron_killing}.
+as and the training process for \shrink, and 
+then describe the removal process in Section~\ref{neuron_killing}.
 
@@
 
-We want to tune the size of $L$ by applying a switch layer, $S$, containing $c$
-switches.  The switch
-layer is parametrized by a vector $\beta \in \mathbb{R}^c$ such that the result
+We want to tune the size of $L$ by applying a \swl, $S$, containing $c$
+switches.  The \swl is parametrized by a vector $\bm{\beta} \in \mathbb{R}^c$ such that the result
 of applying $S$ to $L(\bm{x})$ is a also a tensor size $\left(c \times d_1
@@
 
-We place switch layers after each layer whose size we wish to tune; these are
+We place \swl after each layer whose size we wish to tune; these are
 typically fully connected and convolutional layers. We discuss next how to train
-ShrinkNets.
+\shrink.
 
-\subsection{Training ShrinkNets}
+\subsection{Training \shrink}
 
@@
 %Formally, 
-For training, we need to account for the effect of the switch layers on the loss
-function. The effect of switch layers can be expressed in terms of a sparsity constraint
+For training, we need to account for the effect of the \swls on the loss
+function. The effect of \swls can be expressed in terms of a sparsity constraint
 that pushes values in the $\bm{\beta}$ vector to 0. In this way, given a neural network
 parameterized by weights $\bm{\theta}$ and switch layer parameters $\bm{\theta}$, we
-optimize ShrinkNet loss as follows 
+optimize \shrink loss as follows 
 \begin{equation}
@@
 
-We next analyze why such loss function works to train ShrinkNets and its
+We next analyze why such loss function works to train \shrink and its
 connection to group sparsity:

### 2018-02-09 paper/ICML/evaluation.tex

@@
 
-%\srm{Summarize more quantitatively -- best model performance, model performance
-%drop off for a factor of 10 reduction in seize, etc. so that we can repeat a
-%quantitative claim in the intro, i.e., ``Here, the best performing ShrinkNets
-%models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy,
-%while the ShrinkNets model is x times smaller.  Further, note that ShrinkNets
-%finds a model with 9x.x\% accuracy that is y times than the best performing
-%model.  Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a
-%model that is z times smaller.'' (If we do this, would be good to highlight
-%these points in the figure somehow)}
-
-\subsubsection{Summary}
-
-We  demonstrated that it is possible to achieve networks with good accuracy
-when using ShrinkNets both when the network space cannot be explored entirely
-(\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
-result is not that ShrinkNets finds networks of good accuracy, but that those
-networks are much smaller than those found by a static method. The impact of the
-network size on inference time is the subject of our next evaluation goal.
+\noindent\textbf{Summary.} We demonstrated that it is possible to achieve
+networks with good accuracy when using ShrinkNets both when the network space
+cannot be explored entirely (\texttt{CIFAR10}) as well as when it can, e.g.,
+\texttt{COVERTYPE}. The most important result is not that ShrinkNets finds
+networks of good accuracy, but that those networks are much smaller than those
+found by a static method. The impact of the network size on inference time is
+the subject of our next evaluation goal.
 
@@
 
-\ra{the following is interesting, but how is it related to the above?}
 ShrinkNets effectively explores the frontier of model size and accuracy. For a

### 2018-02-09 paper/ICML/introduction.tex

--- 2018-02-09 paper/ICML/introduction.tex
@@
 Of course, the problem of finding compressed or small networks is not new.
-Existing techniques typically aim make a pre-trained neural network smaller
-by taking one of two approaches:  either by
-applying quantization \cite{quant} or code compilation~\cite{ma2016compilation}
-techniques that can be applied blindly to any network, or by analyzing the
-structure of the network and systematically pruning
+Existing techniques to make a pre-trained neural network smaller can be categorized in two approaches: (1) quantization \cite{quant} and code compilation~\cite{ma2016compilation}, 
+techniques that can be applied blindly to any network, and (2) techniches which analyze the
+structure of the network and systematically prune
 connections or neurons~\cite{han2015deepcompression,Cun}
-based on some loss function.  Although these techniques can substantially
-reduce model size, they have several drawbacks.  First, they often negatively
+based on some loss function. While the first category is always useful, but only has limited 
+impact on the network size, the second category can reduce the model size much more but has several 
+drawbacks:   First, those techniques often negatively
 impact model quality.  Second, they can (surprisingly) negatively impact
@@
 leading not only to small and well-performing networks, but also dense, which
-means higher inference performance.
+means higher inference performance. Furthermore, our switching layers used during training can be 
+savely removed before the model is used for inference, leading to zero additional overhead.
 

### 2018-02-09 paper/ICML/paper.tex

@@
 \newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
+\newcommand{\tim}[1]{\textcolor{red}{{\bf Tim:} #1}}
 \newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Learning Neural Network size with ShrinkNets}
+\icmltitlerunning{ShrinkNets: Learning Network Size while Training}
 
@@
 \twocolumn[
-\icmltitle{Learning Network Size while Training with ShrinkNets}
+\icmltitle{ShrinkNets: Learning Network Size while Training}
 
@@
 \begin{abstract}
-As neural networks are being increasingly deployed in different applications and
+As neural networks are being widely in different applications and
 on different hardware, it has become increasingly important to optimize
 inference time and model size along with model accuracy.  Most current work
-optimizes model size, model accuracy and inference time in different stages and
-results in suboptimal results at the cost of computational inefficiency.  In
-this work, we propose a new techique called ShrinkNets that optimizes all three
+optimizes model size, model accuracy and inference time in different stages, 
+resulting in suboptimal results and computational inefficiency.  In
+this work, we propose a new technique called ShrinkNets that optimizes all three
 of these metrics simultaneously by learning optimal network size at training
@@
 inference time.  By applying our technique to a variety of models with both
-convolutional and fully connected layers, we show that ShrinkNets can reduce by
-35\% the network size with respect to a static network for \texttt{CIFAR10}, and
-it can achieve speedups during inference time of up to 40X. In addition, the
+convolutional and fully connected layers, we show that ShrinkNets can reduce network size
+by 35x in comparison to to a static network on \texttt{CIFAR10}, with
+6x improvement in inference time. In addition, the
 most accurate networks found by ShrinkNets are similar or more accurate than

### 2018-02-09 paper/ICML/paper.tex
changed speedup number
updated abstract

@@
 \begin{abstract}
-As neural networks are being widely in different applications and
-on different hardware, it has become increasingly important to optimize
-inference time and model size along with model accuracy.  Most current work
-optimizes model size, model accuracy and inference time in different stages, 
-resulting in suboptimal results and computational inefficiency.  In
-this work, we propose a new technique called ShrinkNets that optimizes all three
-of these metrics simultaneously by learning optimal network size at training
-time.  Specifically our technique presents a new method to simultaneously
-optimize network size and model performance by neuron-level pruning.
-Neuron-level pruning not only produces much smaller networks for a given
-accuracy threshold but also produces dense weight matrices that are efficient at
-inference time.  By applying our technique to a variety of models with both
-convolutional and fully connected layers, we show that ShrinkNets can reduce network size
-by 35x in comparison to to a static network on \texttt{CIFAR10}, with
-6x improvement in inference time. In addition, the
-most accurate networks found by ShrinkNets are similar or more accurate than
-those found by statically trained networks.  
+As neural networks become widely deployed in different applications and 
+on different
+hardware, it has become increasingly important to optimize inference time and
+model size along with model accuracy.  
+Most current techniques optimize model size,
+model accuracy and inference time in different stages, resulting in suboptimal
+results and computational inefficiency.  
+In this work, we propose a new
+technique called \shrink that optimizes all three of these metrics
+simultaneously.  
+Specifically we present a new method to simultaneously optimize network size and
+model performance by neuron-level pruning during training.  
+Neuron-level pruning not only
+produces much smaller networks for a given accuracy threshold but also produces
+dense weight matrices that are amenable to efficient inference.  
+By applying our
+technique to convolutional as well as fully connected models, we show that 
+\shrink can reduce network size by 35X with a 6X improvement in inference time.
+In addition, the most accurate networks found by \shrink have accuracy that is
+similar to or better than those found by statically-sized networks.  
 \end{abstract}
@@
 
-\clearpage
-
 \bibliographystyle{icml2018}

### 2018-02-09 paper/ICML/introduction.tex
changed speedup number

@@
 Of course, the problem of finding compressed or small networks is not new.
-Existing techniques to make a pre-trained neural network smaller can be categorized in two approaches: (1) quantization \cite{quant} and code compilation~\cite{ma2016compilation}, 
-techniques that can be applied blindly to any network, and (2) techniches which analyze the
-structure of the network and systematically prune
-connections or neurons~\cite{han2015deepcompression,Cun}
-based on some loss function. While the first category is always useful, but only has limited 
-impact on the network size, the second category can reduce the model size much more but has several 
-drawbacks:   First, those techniques often negatively
-impact model quality.  Second, they can (surprisingly) negatively impact
-inference time as they transform dense matrix operations into sparse ones,
-which can be substantially slower to execute on modern hardware
-\cite{han2015deepcompression}, especially GPUs which do not efficiently support sparse
-linear algebra.  Third, these techniques generally start by optimizing a
+Existing techniques to make a pre-trained neural network smaller can be
+categorized in two approaches: (1) quantization \cite{quant} and code
+compilation~\cite{ma2016compilation}, techniques that can be applied blindly to
+any network, and (2) techniches which analyze the structure of the network and
+systematically prune connections or neurons~\cite{han2015deepcompression,Cun}
+based on some loss function. While the first category is always useful, but only
+has limited impact on the network size, the second category can reduce the model
+size much more but has several drawbacks:   First, those techniques often
+negatively impact model quality.  Second, they can (surprisingly) negatively
+impact inference time as they transform dense matrix operations into sparse
+ones, which can be substantially slower to execute on modern hardware
+\cite{han2015deepcompression}, especially GPUs which do not efficiently support
+sparse linear algebra.  Third, these techniques generally start by optimizing a
 particular architecture for prediction performance, and then, as a post-
-processing step, applying compression  to generate a smaller model that meets the
-resource constraints of the deployment setting.  Because the network
-architecture is essentially fixed during this post-processing,   model architectures
-that work better in small settings may be missed -- this is especially true in
-large networks like many-layered CNNs,  where it is infeasible to try explore
-even a small fraction of possible network configurations.
+processing step, applying compression  to generate a smaller model that meets
+the resource constraints of the deployment setting.  Because the network
+architecture is essentially fixed during this post-processing,   model
+architectures that work better in small settings may be missed -- this is
+especially true in large networks like many-layered CNNs,  where it is
+infeasible to try explore even a small fraction of possible network
+configurations.
 
@@
 
-\begin{compactenum}
+%\begin{compactenum}
 
-\item We propose a novel technique based on dynamically switching on and off neurons, 
-which allows us to optimize the network size while the network is trained.
+%\item 
+\noindent\textbf{1.} We propose a novel technique based on dynamically switching
+on and off neurons, which allows us to optimize the network size while the
+network is trained.
 
-\item We implement our technique so as to remove entire neurons, therefore
-leading not only to small and well-performing networks, but also dense, which
-means higher inference performance. Furthermore, our switching layers used during training can be 
-savely removed before the model is used for inference, leading to zero additional overhead.
+\noindent\textbf{2.} We implement our technique so as to remove entire neurons,
+therefore leading not only to small and well-performing networks, but also
+dense, which means higher inference performance. Furthermore, our switching
+layers used during training can be savely removed before the model is used for
+inference, leading to zero additional overhead.
 
@@
 
-\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006}
-and prove that our problem admits many global minima.
+\noindent\textbf{3.} We show that our technique is a relaxation of group
+LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
 
-\item We demonstrate our claims with both fully-connected and convolutional well
-known neural network architectures. We show that with ShrinkNets for
-\texttt{CIFAR10} we achieve the same accuracy than a traditionally trained
-network while reducing the network size by a factor of $2.2x$. Further, when
-willing to sacrifice only $1$\% of performance, ShrinkNets finds networks which
-are 35\% smaller. All in all, this leads to speedups in inference time of up to
-40X.
+\noindent\textbf{4.} We evaluate ShrinkNets with both fully-connected as well as
+convolutional neural networks. For \texttt{CIFAR10}, we achieve the same
+accuracy than a traditionally trained network while reducing the network size by
+a factor of $2.2x$. Further, when willing to sacrifice only $1$\% of
+performance, ShrinkNets finds networks which are 35\% smaller. All in all, this
+leads to speedups in inference time of up to 6x.
 
-%\item We demonstrate the efficacy of our technique on both convolutional and
-%fully-connected neural nets, showing that ShrinkNets finds networks within
-%+/-X\% of best hand-crafted accuracy in XX\% of training time compared to
-%existing hyperparameter optimization methods. \srm{Mention the specific
-%model/dataset where this is true.}
-
-%\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% of
-%neurons. \srm{This claim should be something about how much smaller a network
-%with say 99\% accuracy is one some real dataset}
-%
-%\item \srm{Some claim about inference time}
-%
-%\item \srm{Some claim about model size vs performance}
-
-\end{compactenum}
-
-% The remaining of this paper is organized as follows. In section
-% \ref{sec:relatedwork} we discuss the related work. In section
-% \ref{sec:approach}, we introduce our approach ShrinkNets, followed by the
-% practical considerations we implemented to make it work in section
-% \ref{sec:impl}. Then, we evaluate the approach in section \ref{sec:evaluation}
-% and conclude the paper in section \ref{sec:conclusions}.
+%\end{compactenum}

### 2018-02-09 paper/ICML/related_work.tex

@@
 
-\noindent\textbf{Auto-ML: } Some work that focuses on automatically learning
-model architecture through the use of genetic algorithms and reinforcement
-learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
-techniques are focused on learning higher-level architectures (e.g.,
-building blocks for neural network architectures). In particular, they do not
-focus on finding small but well-performing networks for inference, which is the
-goal of ShrinkNets.
+%\noindent\textbf{Auto-ML: } Some work focuses on automatically learning
+%model architecture through the use of genetic algorithms and reinforcement
+%learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
+%techniques are focused on learning higher-level architectures (e.g., building
+%blocks for neural network architectures). In particular, they require to train
+%full models and may take weeks to converge.
+
+%do not
+%focus on finding small but well-performing networks for inference, which is the
+%goal of ShrinkNets.
+%\tim{Argument is not really convincing, but those techniques require to train
+%full models and might take weeks to converge. }
 

### 2018-02-09 paper/ICML/approach.tex
pass on s3

@@
 \section{The ShrinkNets Approach}
+\label{sec:approach}
 
@@
 At a high-level, our approach consists of two interconnected stages.
-The first stage identifies neurons that do not improve the
+The first one identifies neurons that do not improve the
 prediction accuracy of the network and deactivates them. 
@@
 shrinking weight matrices and updating optimizer state) thus leading to 
-smaller networks and also faster inference times.
+smaller networks and faster inference.
 
@@
 deactivated by the switch layers are actually removed from the network,
-effectively shrinking the network size. This step improves inference times, as
-we demonstrate in our evaluation. We choose to remove neurons at training time
+effectively shrinking the network size. This step improves inference times.
+We choose to remove neurons at training time
 because we have observed that this allows the remaining active neurons to adapt
@@
 deactivated neurons.
+
 % Existing techniques focus on neuron removal
@@
 
-In the remainder of this section we describe in detail the switch layer as well
-as and the training process for \shrink, and 
-then describe the removal process in Section~\ref{neuron_killing}.
+Next we describe in detail the switch layer as well as and the training process
+for \shrink, and then describe the removal process in
+Section~\ref{neuron_killing}.
 

### 2018-02-09 paper/ICML/evaluation.tex
arrows
Replace ShrinkNet with macro

--- 2018-02-09 paper/ICML/evaluation.tex
@@
 only a few fully-connected layers. This is important because we want to show
-that \textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if
+that \shrink find sizes as good as \textit{Static Networks}, even if
 we are sampling the entire space of possible network sizes. Second, Scardapane
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary}
+\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
 \vspace*{-5mm}
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{COVER_FC_summary}
+\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
 \vspace*{-5mm}

### 2018-02-09 paper/ICML/appendix.tex
edits

@@
 
-\subsection{Proofs}
-Unless stated explicitly, all the propositions consider the Multi-Target linear regression problem.
+Here we prove the propositions given in Section~\ref{sec:approach}.  
+%Unless stated explicitly, all the propositions consider the Multi-Target linear regression problem.
 \begin{proposition}
 \label{gps_equivalence}
-  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$
-
+  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$:
+  %
   \begin{align*}
@@
 \end{proposition}
-
+\vspace{-.3in}
 \begin{proof}
@@
   \end{align*}
-  Which concludes the first part.
   \\ \textbf{Part 2:} Assuming we take an $\bm{A}'$ that satisfies the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
@@
 
-\begin{proposition}
-\label{unconstrained_non_convex}
-\begin{equation*}
-     \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2
-\end{equation*}
-is not convex in $\bm{A}$ and $\bm{\beta}$.
+\begin{proposition} \label{unconstrained_non_convex}
+$     \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2
+$ is not convex in $\bm{A}$ and $\bm{\beta}$.
 \begin{proof}
@@
 \label{unconstrained_shrinknet_no_min}
-\begin{equation*}
-     \min_{\bf{A}, \bm{\beta}} \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
-\end{equation*}
+$     \min_{\bf{A}, \bm{\beta}} \norm{\bf{y} - \bf{A}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
+$
 has no solution if $\lambda > 0$.

### 2018-02-09 paper/ICML/evaluation.tex
edits

--- 2018-02-09 paper/ICML/evaluation.tex
@@
 
-The goal of our evaluation is to explore:
-
-\begin{compactitem}
-\item Whether, by varying $\lambda$, \shrink can efficiently
+The goal of our evaluation is to explore (1) whether, by varying $\lambda$, \shrink can efficiently
 explore (in terms of number of training runs)  the spectrum of high-accuracy
@@
 or better than \textit{Static Networks}, trained via traditional hyperparameter
-optimization.
-
-\item Whether, because these  smaller networks are dense, they result in
-improved inference times on both CPUs and GPUs.
-
-\item Whether the \shrink approach results in network architectures that are
+optimization;  (2) whether, because these  smaller networks are dense, they result in
+improved inference times on both CPUs and GPUs; and (3) whether the \shrink approach results in network architectures that are
 substantially different than the best network architectures (in terms of
 relative number of neurons per layered) identified in the literature.
-
-\end{compactitem}
 
@@
 last).  Recall that \shrink assume that the starting size of the network is
-an upper bound on the optimal size. For this reason, we simply started with a
-network with double the recommended size for each layer as an upper bound (this
-is larger than what ImageNet, for example uses). 
+an upper bound on the optimal size. Thus, we started with a
+network with 2x the recommended size for each layer as an upper bound (this
+is larger than what ImageNet uses). 
 % Thus, for the classification
@@
 \begin{minipage}{2.7in}
-\begin{center}
-\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary}
-\vspace*{-5mm}
+\centering
+\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
+\vspace*{-10mm}
 \caption{\label{figure_CIFAR10} Summary of the result of random
 search over the hyper-parameters the \texttt{CIFAR10} dataset}
-\end{center}
-\vspace*{-4mm}
+\vspace*{-5mm}
+\end{minipage}
+\begin{minipage}{.3in}
+~~
 \end{minipage}
 \begin{minipage}{2.7in}
-\begin{center}
-\includegraphics[width=\columnwidth]{COVER_FC_summary}
-\vspace*{-5mm}
+\centering\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
+\vspace*{-10mm}
 \caption{\label{figure_COVER} Summary of the result of random
 search over the hyper-parameters the \texttt{COVERTYPE} dataset
-\srm{label the x axes on the bottom plots; change ``Desired accuracy`` ``Accuracy''}
 }
-\end{center}
-\vspace*{-4mm}
+\vspace*{-5mm}
 \end{minipage}
@@
 } 
+\vspace*{-5mm} 
 \label{fig:network_size_evolution}

### 2018-02-09 paper/ICML/evaluation.tex

@@
 
-\noindent\textbf{Summary.} We demonstrated that it is possible to achieve
-networks with good accuracy when using ShrinkNets both when the network space
-cannot be explored entirely (\texttt{CIFAR10}) as well as when it can, e.g.,
-\texttt{COVERTYPE}. The most important result is not that ShrinkNets finds
-networks of good accuracy, but that those networks are much smaller than those
-found by a static method. The impact of the network size on inference time is
-the subject of our next evaluation goal.
+%\srm{Summarize more quantitatively -- best model performance, model performance
+%drop off for a factor of 10 reduction in seize, etc. so that we can repeat a
+%quantitative claim in the intro, i.e., ``Here, the best performing ShrinkNets
+%models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy,
+%while the ShrinkNets model is x times smaller.  Further, note that ShrinkNets
+%finds a model with 9x.x\% accuracy that is y times than the best performing
+%model.  Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a
+%model that is z times smaller.'' (If we do this, would be good to highlight
+%these points in the figure somehow)}
+
+\subsubsection{Summary}
+
+We  demonstrated that it is possible to achieve networks with good accuracy
+when using ShrinkNets both when the network space cannot be explored entirely
+(\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
+result is not that ShrinkNets finds networks of good accuracy, but that those
+networks are much smaller than those found by a static method. The impact of the
+network size on inference time is the subject of our next evaluation goal.
 
@@
 
+\ra{the following is interesting, but how is it related to the above?}
 ShrinkNets effectively explores the frontier of model size and accuracy. For a

### 2018-02-09 paper/ICML/paper.tex

@@
 technique to convolutional as well as fully connected models, we show that 
-\shrink can reduce network size by 35X with a 6X improvement in inference time.
-In addition, the most accurate networks found by \shrink have accuracy that is
-similar to or better than those found by statically-sized networks.  
+\shrink can reduce network size by 35X with a 6X improvement in inference time with similar accuracy as models found by traditional training techniques.
+
+%By applying our technique to convolutional as well as fully connected models, we show that  \shrink can reduce network size by 35X with a 6X improvement in inference time.
+In addition, the most accurate networks found by \shrink have accuracy that is similar to or better than those found by statically-sized networks.
 \end{abstract}

### 2018-02-09 paper/ICML/approach.tex

@@
 
-In this section we describe the \shrink approach, which allows us to learn
-the network size as part of the training process. The key idea is the addition
-of \swls after each layer in the network;  these layers
-allow us to selectively deactivate neurons during training.  We start by introducing the
-basic method, and then explain how to adapt the training procedure to support this new
-layer.
+In this section we describe the \shrink approach. We discuss first the new \swls
+which are used to deactivate neurons, followed by a description of how we adapt
+the training loss function.
+
+%In this section we describe the \shrink approach, which allows us to learn
+%the network size as part of the training process. The key idea is the addition
+%of \swls after each layer in the network;  these layers
+%allow us to selectively deactivate neurons during training.  We start by introducing the
+%basic method, and then explain how to adapt the training procedure to support this new
+%layer.
 

### 2018-02-09 paper/ICML/evaluation.tex

@@
 model, we plot its accuracy and model size. The lines show the Pareto frontier
-of models in each of the two optimization settings. ShrinkNets explore the
+of models in each of the two optimization settings. \shrink explore the
 trade-off between model size and accuracy more effectively. 
@@
 
-Note that the best performing ShrinkNets models has $92.07\%$ accuracy which
-is identical to the accuracy of the static network, while the ShrinkNets model
-is $2.22$ times smaller. In addition, if we give up just 1\% error, ShrinkNets
+Note that the best performing \shrink models has $92.07\%$ accuracy which
+is identical to the accuracy of the static network, while the \shrink model
+is $2.22$ times smaller. In addition, if we give up just 1\% error, \shrink
 finds a model that is 35.5 times smaller than any static network that performs
@@
 %The experimental setup on this dataset is similar to {\tt CIFAR10}. 
-We compare ShrinkNets against the same architecture
+We compare \shrink against the same architecture
 used in \cite{Scardapane2017}, i.e., a three fully-connected layers network with no
@@
 that perform well at a variety of sizes, because it is able to explore the
-entire parameter space.  This is as expected;  the fact that ShrinkNets performs
-as well as the Static indicates that ShrinkNets is doing an effective job of
+entire parameter space.  This is as expected;  the fact that \shrink performs
+as well as the Static indicates that \shrink is doing an effective job of
 exploring the parameter space using just the single $\lambda$ parameter.
 
-Note that the best performing ShrinkNets models has $96.91\%$ accuracy while the
-best static model is only $96.66\%$ accurate, while the ShrinkNets model is $2.51$
-times smaller. In addition, if we give up just 0.5\% error, ShrinkNets finds a
+Note that the best performing \shrink models has $96.91\%$ accuracy while the
+best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
+times smaller. In addition, if we give up just 0.5\% error, \shrink finds a
 model that is 38.6 times smaller than any static network with equivalent accuracy.
@@
 We  demonstrated that it is possible to achieve networks with good accuracy
-when using ShrinkNets both when the network space cannot be explored entirely
+when using \shrink both when the network space cannot be explored entirely
 (\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
-result is not that ShrinkNets finds networks of good accuracy, but that those
+result is not that \shrink finds networks of good accuracy, but that those
 networks are much smaller than those found by a static method. The impact of the
@@
 
-The previous experiment showed that ShrinkNets finds networks of similar or better accuracy
+The previous experiment showed that \shrink finds networks of similar or better accuracy
 than static networks that are much smaller. We now explore if the reduction in size
@@
 To do this, we select the smallest model 
-that achieves a given accuracy for the both ShrinkNets and Static approach.
+that achieves a given accuracy for the both \shrink and Static approach.
 For each model, we measure the time to run inference with the model.  
 We then compute the ratio of the network size and inference time
-between ShrinkNets and Static at each accuracy level, and plot them on the bottom of 
+between \shrink and Static at each accuracy level, and plot them on the bottom of 
  Figure~\ref{figure_CIFAR10} 
@@
 
- The middle plot in each figure shows the ratio of model size between ShrinkNets and Static (values $>$1 mean ShrinkNets are smaller) at different accuracy levels.
+ The middle plot in each figure shows the ratio of model size between \shrink and Static (values $>$1 mean \shrink are smaller) at different accuracy levels.
 These figures show that is that size improvements are are particularly significant
@@
  the compression ratio is always above 1 but it rarely exceeds 3x, except for
-very high accuracies where \textit{ShrinkNets} finds excellent, small
+very high accuracies where \shrink finds excellent, small
 solutions.  The fact that the  \texttt{COVERTYPE} networks are not dramatically 
@@
  The bottom four graphs in each figure 
-show the results.  Again, the {\tt CIFAR10} results show the benefit of the ShrinkNets approach
+show the results.  Again, the {\tt CIFAR10} results show the benefit of the \shrink approach
 most dramatically.
@@
 \ra{the following is interesting, but how is it related to the above?}
-ShrinkNets effectively explores the frontier of model size and accuracy. For a
+\shrink effectively explores the frontier of model size and accuracy. For a
 given target accuracy, the size needed is significantly smaller than when we use the
@@
 though these datasets have the same number of classes, input features, and
-output distributions, for a fixed $\lambda$ \textit{ShrinkNets} converged to
+output distributions, for a fixed $\lambda$ \shrink converged to
 considerably bigger networks in the case of \texttt{FashionMNIST}. This evidence
@@
 To illustrate this point on a larger dataset, we show two examples of
-architectures learned by \textit{ShrinkNets} in
+architectures learned by \shrink in
 Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the

### 2018-02-09 paper/ICML/evaluation.tex

@@
 
-The goal of our evaluation is to explore (1) whether, by varying $\lambda$, \shrink can efficiently
+The goal of our evaluation is to explore:
+
+\begin{compactitem}
+\item Whether, by varying $\lambda$, \shrink can efficiently
 explore (in terms of number of training runs)  the spectrum of high-accuracy
@@
 or better than \textit{Static Networks}, trained via traditional hyperparameter
-optimization;  (2) whether, because these  smaller networks are dense, they result in
-improved inference times on both CPUs and GPUs; and (3) whether the \shrink approach results in network architectures that are
+optimization.
+
+\item Whether, because these  smaller networks are dense, they result in
+improved inference times on both CPUs and GPUs.
+
+\item Whether the \shrink approach results in network architectures that are
 substantially different than the best network architectures (in terms of
 relative number of neurons per layered) identified in the literature.
+
+\end{compactitem}
 
@@
 last).  Recall that \shrink assume that the starting size of the network is
-an upper bound on the optimal size. Thus, we started with a
-network with 2x the recommended size for each layer as an upper bound (this
-is larger than what ImageNet uses). 
+an upper bound on the optimal size. For this reason, we simply started with a
+network with double the recommended size for each layer as an upper bound (this
+is larger than what ImageNet, for example uses). 
 % Thus, for the classification
@@
 \begin{minipage}{2.7in}
-\centering
+\begin{center}
 \includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
-\vspace*{-10mm}
+\vspace*{-5mm}
 \caption{\label{figure_CIFAR10} Summary of the result of random
 search over the hyper-parameters the \texttt{CIFAR10} dataset}
-\vspace*{-5mm}
-\end{minipage}
-\begin{minipage}{.3in}
-~~
+\end{center}
+\vspace*{-4mm}
 \end{minipage}
 \begin{minipage}{2.7in}
-\centering\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
-\vspace*{-10mm}
+\begin{center}
+\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
+\vspace*{-5mm}
 \caption{\label{figure_COVER} Summary of the result of random
 search over the hyper-parameters the \texttt{COVERTYPE} dataset
+\srm{label the x axes on the bottom plots; change ``Desired accuracy`` ``Accuracy''}
 }
-\vspace*{-5mm}
+\end{center}
+\vspace*{-4mm}
 \end{minipage}
@@
 } 
-\vspace*{-5mm} 
 \label{fig:network_size_evolution}

### 2018-02-09 paper/ICML/introduction.tex

@@
 
-Neural networks are increasingly being deployed in a wide variety  of
+Neural networks are being deployed in a wide variety of
 applications and on diverse hardware architectures ranging from laptops to
@@
 that inference time and model size are becoming as important as  prediction
-quality when assessing model performance.  However, these three dimensions of
-performance (model quality, inference time and model size)  are largely
-optimized separately today, often with suboptimal results.
+accuracy when assessing model quality.  However, these three dimensions of
+performance (prediction accuracy, inference time and model size) are largely
+optimized independently, often with suboptimal results.
 
@@
 Existing techniques to make a pre-trained neural network smaller can be
-categorized in two approaches: (1) quantization \cite{quant} and code
-compilation~\cite{ma2016compilation}, techniques that can be applied blindly to
-any network, and (2) techniches which analyze the structure of the network and
-systematically prune connections or neurons~\cite{han2015deepcompression,Cun}
-based on some loss function. While the first category is always useful, but only
+categorized in two approaches: (1) quantization \cite{Jouppi:2017:IPA:3079856.3080246} and code
+compilation, techniques that can be applied blindly to
+any network, and (2) techniques which analyze the structure of the network and
+systematically prune connections or neurons~\cite{han2015deepcompression,Cun}. 
+While the first category is always useful, but only
 has limited impact on the network size, the second category can reduce the model
@@
 impact inference time as they transform dense matrix operations into sparse
-ones, which can be substantially slower to execute on modern hardware
-\cite{han2015deepcompression}, especially GPUs which do not efficiently support
-sparse linear algebra.  Third, these techniques generally start by optimizing a
+ones, which can be substantially slower to execute on GPUs which do not support
+efficiently sparse linear algebra\cite{han2015deepcompression}. 
+Third, these techniques generally start by optimizing a
 particular architecture for prediction performance, and then, as a post-
@@
  network size and model performance. The key idea is to learn the right
-network size at the same time that we optimize for prediction performance for a
-specific task. Our approach, called {\it ShrinkNets}, starts with an {\it
+network size at the same time that we optimize for prediction performance. 
+Our approach, called \shrink, starts with an {\it
 over-sized} network, and dynamically shrinks it by eliminating unimportant
 neurons---those that do not contribute to prediction performance---during
-training time. To do this, ShrinkNets must detect the unimportant neurons, and
+training time. To do this, \shrink must detect the unimportant neurons, and
 remove them from the network. The
-removal of entire neurons and not connections is crucial, because it leads to
+removal of entire neurons (vs. only connections) is crucial, because it leads to
 dense networks, which in turn leads to better inference performance. To support the
 detection and removal of unimportant neurons we introduce a new layer, called
-\textbf{Switch layer}. Introducing this new layer simply requires us to
+\swl. Introducing this new layer simply requires us to
 add a term to the
-loss function to optimize the weights of this layer during training. ShrinkNets has
+loss function to optimize the parameters of this layer during training. 
+\shrink has
 two main benefits. First, it explores the architecture of models that are both
-small and perform well, rather than starting with a high-performance model and
-making it small.  It does this using a single new hyperparameter that effectively 
-models the target network size.  This allows us to efficiently generate a family of smaller and
-accurate models without an exhaustive and expensive hyperparameter search over
-the number of neurons in each layer.  Second, in contrast to existing neural
+small and perform well, rather than starting with a high-performing model and
+making it small.  \shrink accomplishes this goal by using a single new 
+hyperparameter that effectively models the target network size.  
+% This allows us to efficiently generate a family of smaller and
+% accurate models without requiring an exhaustive and expensive hyperparameter search over
+% the number of neurons in each layer.  
+Second, in contrast to existing neural
 network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our
-approach results in models that are not only small, but where the layers are
-dense, which means that inference time is also improved, e.g., on GPUs.
+approach results in models that are not only small, but where the weight matrices
+are dense, leading to better inference time.
 

### 2018-02-09 paper/ICML/impl.tex
edits
Missing ref

@@
 
-In this section we discuss practical aspects of ShrinkNets, including the
-neuron removal  process and several additional optimizations.
+In this section we discuss practical aspects of \shrink{}, including 
+neuron removal  and several optimizations.
 
@@
 a fixed threshold expressed in terms of its absolute value. This is the method
-used by deep compression \cite{}. We found this method is very sensitive to the initializaiton 
+used by deep compression \cite{Han2015}. We found this method is very sensitive to the initializaiton 
 and not robust to noise in the gradients---which occurs commonly when training networks with

### 2018-02-09 paper/ICML/introduction.tex
Update introduction.tex

@@
 
-Of course, the problem of finding compressed or small networks is not new.
+Of course, the problem of finding faster and smaller networks is not new.
 Existing techniques to make a pre-trained neural network smaller can be
@@
 size much more but has several drawbacks:   First, those techniques often
-negatively impact model quality.  Second, they can (surprisingly) negatively
+negatively impact model quality.  Second, they can also (surprisingly) negatively
 impact inference time as they transform dense matrix operations into sparse

### 2018-02-09 paper/ICML/introduction.tex

@@
 categorized in two approaches: (1) quantization \cite{Jouppi:2017:IPA:3079856.3080246} and code
-compilation, techniques that can be applied blindly to
+compilation, techniques that can be applied  to
 any network, and (2) techniques which analyze the structure of the network and

### 2018-02-09 paper/ICML/appendix.tex
minor notation fixes

@@
 For this proposition we will not restrict ourselves to single layer but the composition of an an arbitrary large ($n$) layers as defined individually as $f_{\bm{A}_i, \bm{\beta}_i, \bm{b}_i}(x) = a(\bm{A_i}\diag{\bm{\beta_i}}\bm{x} + \bm{b_i})$.
-The entire network follows as: $N(\bm{x}) = \left(\bigcirc_{i=1}^n f_{\bm{A_i}, \bm{\beta_i}, \bm{b_i}}\right)(\bm{x})$.
+Suppose the entire network is denoted by the function $N(\bm{x})$.
+% The entire network follows as: $N(\bm{x}) = \left(\bigcirc_{i=1}^n f_{\bm{A_i}, \bm{\beta_i}, \bm{b_i}}\right)(\bm{x})$. 
 For $\lambda > 0$, $\lambda_2 > 0$ and $p > 0$ we have:
@@
   \end{equation*}
-  has at least $2^k$ global minimum where $k = \sum_{i=1}^n \#\bm{\beta_i}$
+  has at least $2^k$ global minimum where $k = \sum_{i=1}^n {\bf card}(\bm{\beta_i})$
 \end{proposition}
@@
 It is easy to see that going from this global minimum, we can decide to negate or not each element in each $\bm{\beta_i}$.
-We have a binary choice for each parameter, there are $k = \sum_{i=1}^n \#\bm{\beta_i}$ parameters, so we have at least $2^k$ global minima.
+We have a binary choice for each parameter, there are $k = \sum_{i=1}^n {\bf card}(\bm{\beta_i})$ parameters, so we have at least $2^k$ global minima.
 

### 2018-02-10 paper/ICML/introduction.tex
edit intro

@@
 
-\noindent\textbf{2.} We implement our technique so as to remove entire neurons,
-therefore leading not only to small and well-performing networks, but also
-dense, which means higher inference performance. Furthermore, our switching
-layers used during training can be savely removed before the model is used for
-inference, leading to zero additional overhead.
+\noindent\textbf{2.} We extend our technique to remove entire neurons,
+ leading not only to smaller networks, but also
+dense matrices, which yield improved inference times as networks shrink. Furthermore, our switching
+layers used during training can be safely removed before the model is used for
+inference, meaning they add no additional overhead at inference time.
 
@@
 convolutional neural networks. For \texttt{CIFAR10}, we achieve the same
-accuracy than a traditionally trained network while reducing the network size by
-a factor of $2.2x$. Further, when willing to sacrifice only $1$\% of
-performance, ShrinkNets finds networks which are 35\% smaller. All in all, this
-leads to speedups in inference time of up to 6x.
+accuracy as a traditionally trained network while reducing the network size by
+a factor of $2.2X$. Further, while sacrificing just $1$\% of
+performance, ShrinkNets finds networks that are 35X smaller. All in all, this
+leads to speedups in inference time of up to 6X.
 

### 2018-02-10 paper/ICML/evaluation.tex
edits
bunch of typos and macros in evaluation

--- 2018-02-09 paper/ICML/evaluation.tex
@@
 
-The goal of our evaluation is to explore (1) whether, by varying $\lambda$, \shrink can efficiently
-explore (in terms of number of training runs)  the spectrum of high-accuracy
-models from small to large, on both CNNs and fully connected networks.  Our
-results show that, for each network size, we obtain models that perform as well
-or better than \textit{Static Networks}, trained via traditional hyperparameter
-optimization;  (2) whether, because these  smaller networks are dense, they result in
-improved inference times on both CPUs and GPUs; and (3) whether the \shrink approach results in network architectures that are
-substantially different than the best network architectures (in terms of
-relative number of neurons per layered) identified in the literature.
+The goal of our evaluation is to explore (1) whether, by varying $\lambda$,
+\shrink can efficiently explore (in terms of number of training runs)  the
+spectrum of high-accuracy models from small to large, on both CNNs and fully
+connected networks.  Our results show that, for each network size, we obtain
+models that perform as well or better than \textit{Static Networks}, trained via
+traditional hyperparameter optimization;  (2) whether, because these  smaller
+networks are dense, they result in improved inference times on both CPUs and
+GPUs; and (3) whether the \shrink approach results in network architectures that
+are substantially different than the best network architectures (in terms of
+relative number of neurons per layer) identified in the literature.
 
@@
 
-To answer this question we compare \shrink with a traditional network. In
-both cases, we need to perform hyperparameter optimization to explore different
+To answer this question we compare \shrink with a traditional network. In both
+cases, we need to perform hyperparameter optimization to explore different
 network architectures. We perform random search, which is an effective technique
-for this purpose \cite{BergstraJAMESBERGSTRA2012}. We evaluate \shrink on two well-known datasets. One
-for which it is not possible to explore the entire space of network
-architectures (\texttt{CIFAR10}) and one for which it is possible to do so
-(\texttt{COVERTYPE}).
+for this purpose \cite{BergstraJAMESBERGSTRA2012}. We evaluate \shrink on two
+well-known datasets. One for which it is not possible to explore the entire
+space of network architectures (\texttt{CIFAR10}) and one for which it is
+possible to do so (\texttt{COVERTYPE}).
 
-\noindent\textbf{Setup: }
-We assume no prior knowledge on the optimal batch size, learning rate, $\lambda$
-or weight decay ($\lambda_2$). Instead, we trained a number of models, randomly
-and independently selecting the values of these parameters from a range of
-reasonable values.
- % (\gl{should we make them explicit ?} \srm{yes}).  
-%We trained
-%using our modified \texttt{PyTorch} \cite{paszke2017automatic} library that
-%supports dynamically resized layers (our code is available at \srm{add
-%anonymized link}). 
-Training is done using gradient descent and the \textit{Adam}
-optimizer \cite{DBLP:journals/corr/KingmaB14}. Specifically, we start with the
-learning rate sampled randomly; for every $5$ epochs of non-improvement in
-validation accuracy we divide the learning rate by $10$. We stop training after
-$400$ epochs or when the learning rate is under $10^{-7}$, whichever comes
-first. For each of the models we trained, we pick the
-epoch with the best validation accuracy and report the corresponding testing
-accuracy. Because of the nature of our method, it can happen that for networks
-that are aggressively compressed, the best validation accuracy is obtained early
-in  training, before the size has converged. To be sure that accuracy measured
-corresponds to the final shape and not the starting shape, we only consider the
-second half of the training when picking the best epoch. For each model, we also
-measure the total size, in terms of number of floating point parameters,
-excluding the \swls because as described in
-\cref{neuron_killing}, these are eliminated after training.
-
-%We evaluate ShrinkNets on two datasets:  \texttt{CIFAR10} and
-%\texttt{COVERTYPE}. In this section, we report how we employed ShrinkNets on
-%these datasets and compare our results to training without ShrinkNets.
+\noindent\textbf{Setup: } We assume no prior knowledge on the optimal batch
+size, learning rate, $\lambda$ or weight decay ($\lambda_2$). Instead, we
+trained a number of models, randomly and independently selecting the values of
+these parameters from a range of reasonable values. Training is done using
+gradient descent and the \textit{Adam} optimizer
+\cite{DBLP:journals/corr/KingmaB14}. Specifically, we start with randomly
+sampled learning
+rate; for every $5$ epochs of non-improvement in validation
+accuracy we divide the learning rate by $10$. We stop training after $400$
+epochs or when the learning rate is under $10^{-7}$, whichever comes first. For
+each of the models we trained, we pick the epoch with the best validation
+accuracy and report the corresponding testing accuracy. Because of the nature of
+our method, it can happen that for networks that are aggressively compressed,
+the best validation accuracy is obtained early in training, before the size has
+converged. To be sure that accuracy measured corresponds to the final shape and
+not the starting shape, we only consider the second half of the training when
+picking the best epoch. For each model, we also measure the total size, in terms
+of number of floating point parameters, excluding the \swls because as described
+in \cref{neuron_killing}, these are eliminated after training.
 
 \subsubsection{Large Network Setting: \texttt{CIFAR10}}
-
-%\ra{this is related work}Previous research~\cite{Scardapane2017} that attempts
-%to optimize network size during training focused on simple datasets and simple
-%(i.e., fully connected) architectures. We believe that self-resizing network are
-%most important for problems where the architecture involves many layers, such
-%that that it is impractical to explore the space of all possible layer-size
-%configurations.\ra{until here}
 
@@
 
-%\srm{keep this?} Although ShrinkNets supports larger networks and datasets as
-%well (i.e., ImageNet \cite{ILSVRC15}),  the time required to such train models
-%and get statistically significant result was prohibitive -- especially when
-%comparing against classical hyperparameter search over network architecture.
-
 We applied \shrink to the VGG16 network by adding \swls
@@
 is larger than what ImageNet uses).
-% Thus, for the classification
-% layers we use $5000$ neurons as a starting limit.
 
@@
 \shrink and we compare the two distributions.
-% \srm{I worry that
-% this method of selecting network sizes for Static will of course constrain it to
-% larger sizes and worse performance. What if we just randomly sample networks?
-% Would it look terrible?} \gl {I don't see any pricatical way of sampling
-% reasonable a 13 dimension space if a single point take 1h to be evaluated}
 
@@
 trade-off between model size and accuracy more effectively.
-%\srm{Summarize
-%more quantitatively -- best model performance, model performance drop off for a
-%factor of 10 reduction in seize, etc. so that we can repeat a quantitative claim
-%in the intro, i.e., ``Note that the best performing ShrinkNets models has 9x.x\%
-%accuracy while the best static model has 9x.x\% accuracy, while the ShrinkNets
-%model is x times smaller.  In addition, if we give up just 1\% error, ShrinkNets
-%finds a model that is z times smaller.'' (If we do this, would be good to
-%highlight these points in the figure somehow)}
 
-Note that the best performing \shrink models has $92.07\%$ accuracy which
+Note that the best performing \shrink model has $92.07\%$ accuracy which
 is identical to the accuracy of the static network, while the \shrink model
 is $2.22$ times smaller. In addition, if we give up just 1\% error, \shrink
-finds a model that is 35.5 times smaller than any static network that performs
+find a model that is 35.5 times smaller than any static network that performs
 as good or better.
@@
 that perform well at a variety of sizes, because it is able to explore the
-entire parameter space.  This is as expected;  the fact that \shrink performs
-as well as the Static indicates that \shrink is doing an effective job of
+entire parameter space.  This is as expected;  the fact that \shrink perform
+as well as the Static indicates that \shrink are doing an effective job of
 exploring the parameter space using just the single $\lambda$ parameter.
@@
 best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
-times smaller. In addition, if we give up just 0.5\% error, \shrink finds a
+times smaller. In addition, if we give up just 0.5\% error, \shrink find a
 model that is 38.6 times smaller than any static network with equivalent accuracy.
-
-%\srm{Summarize more quantitatively -- best model performance, model performance
-%drop off for a factor of 10 reduction in seize, etc. so that we can repeat a
-%quantitative claim in the intro, i.e., ``Here, the best performing ShrinkNets
-%models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy,
-%while the ShrinkNets model is x times smaller.  Further, note that ShrinkNets
-%finds a model with 9x.x\% accuracy that is y times than the best performing
-%model.  Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a
-%model that is z times smaller.'' (If we do this, would be good to highlight
-%these points in the figure somehow)}
 
@@
 (\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
-result is not that \shrink finds networks of good accuracy, but that those
+result is not that \shrink find networks of good accuracy, but that those
 networks are much smaller than those found by a static method. The impact of the
@@
 
-%\srm{we may not need to keep this unless we can think of something more to say}
-%
-%The Pareto frontier in the two figures shows that 
-%that \textit{ShrinkNets} is able find models that both as accurate and smaller than
-%\textit{Static Networks}.
-%
-%when we sample the entire size space (in the \texttt{COVERTYPE} case),
-%\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
-%This has two implications. First it reinforces our observation \srm{our observation?} in [ref] that
-%showed that the models do not suffer from the non-convexity introduced by the
-%multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
-%that the parametrization from a $\lambda$ (real value) to the size of the
-%size of the network (vector) close to optimal. Indeed, if it was
-%not the case then eventually a randomly sampled size would have beaten
-%\textit{ShrinkNets} models. \gl{Too strong ?} \srm{I think this is too strong -- we have no evidence this is true, do we?}
-%
-
 \subsection{Can ShrinkNets speed up inference?}
 
-The previous experiment showed that \shrink finds networks of similar or better accuracy
+The previous experiment showed that \shrink find networks of similar or better accuracy
 than static networks that are much smaller. We now explore if the reduction in size
@@
 
-%We showed in the previous experiments that the \textit{ShrinkNets} approach is
-%able to find networks with accuracy equal to or better than \textit{Static
-%Networks}. In this experiment we want to determine benefits of the smaller size
-%we get.
+As noted in the introduction, for some applications, compact models that offer
+fast inference times are as important as absolute accuracy.
 
-As noted in the introduction, for some applications, compact models that offer fast inference times
-are as important as absolute accuracy. 
 %This observation motivates our 
@@
 % that satisfies achieves a given accuracy.
-In this section, we study the relationship between accuracy, network size and inference time.
-To do this, we select the smallest model 
-that achieves a given accuracy for the both \shrink and Static approach.
-For each model, we measure the time to run inference with the model.  
-We then compute the ratio of the network size and inference time
-between \shrink and Static at each accuracy level, and plot them on the bottom of 
- Figure~\ref{figure_CIFAR10} 
- and~\ref{figure_COVER}.
-We limit our plots to the models with $80-100\%$
-accuracy range because those are the ones that we consider to be practically useful.
 
- The middle plot in each figure shows the ratio of model size between \shrink and Static (values $>$1 mean \shrink are smaller) at different accuracy levels.
-These figures show that is that size improvements are are particularly significant
-for  \texttt{CIFAR10}. In the range of accuracies we are interested in,
-improvements in size go from 4x to 40x. On the \texttt{COVERTYPE} dataset,
+In this section, we study the relationship between accuracy, network size and
+inference time.  To do this, we select the smallest model that achieves a given
+accuracy for the both \shrink and Static approach.  For each model, we measure
+the time to run inference with the model.  We then compute the ratio of the
+network size and inference time between \shrink and Static at each accuracy
+level, and plot them on the bottom of Figure~\ref{figure_CIFAR10}
+and~\ref{figure_COVER}.  We limit our plots to the models with $80-100\%$
+accuracy range because those are the ones that we consider to be practically
+useful.
+
+The middle plot in each figure shows the ratio of model size between \shrink
+and Static (values $>$1 mean \shrink are smaller) at different accuracy levels.
+These figures show that is that size improvements are are particularly
+significant for  \texttt{CIFAR10}. In the range of accuracies we are interested
+in, improvements in size go from 4x to 40x. On the \texttt{COVERTYPE} dataset,
 the compression ratio is always above 1 but it rarely exceeds 3x, except for
-very high accuracies where \shrink finds excellent, small
-solutions.  The fact that the  \texttt{COVERTYPE} networks are not dramatically 
-smaller is expected:  as the distribution at the top of Figure~\ref{figure_COVER} shows,
-the static method is able to explore most of the parameter search space, so finds a range
+very high accuracies where \shrink find excellent, small solutions.  The fact
+that the  \texttt{COVERTYPE} networks are not dramatically smaller is expected:
+as the distribution at the top of Figure~\ref{figure_COVER} shows, the static
+method is able to explore most of the parameter search space, so finds a range
 of models that perform well at different sizes.
 
-For speedup, we experimented with both CPUs and GPUs, and with different batch sizes, where batch size indicates the number of inputs simultaneously fed to the model for inference.
-For each data set/GPU/CPU combination, we show results with batch size 1, as well as with a batch size large enough to fully utilize the hardware on each dataset and hardware configuration.
-For example, for {\tt CIFAR10} on CPU, a batch size of 64 fully utilizes the CPU, whereas a GPU can execute many more models in parallel, so we use a larger batch size of 1024.
-For {\tt COVERTYPE}, because the model is so much smaller, larger batches are needed to fully utilize the hardware.
-Note that when using a batch size of $1$ on GPU, we do not expect to (and do not) observe any improvement because inference times are very small (typically about 10 $\mu s$), such that setup time dominates overall runtime.
+For speedup, we experimented with both CPUs and GPUs, and with different batch
+sizes, where batch size indicates the number of inputs simultaneously fed to the
+model for inference.  For each data set/GPU/CPU combination, we show results
+with batch size 1, as well as with a batch size large enough to fully utilize
+the hardware on each dataset and hardware configuration.  For example, for {\tt
+CIFAR10} on CPU, a batch size of 64 fully utilizes the CPU, whereas a GPU can
+execute many more models in parallel, so we use a larger batch size of 1024.
+For {\tt COVERTYPE}, because the model is so much smaller, larger batches are
+needed to fully utilize the hardware.  Note that when using a batch size of $1$
+on GPU, we do not expect to (and do not) observe any improvement because
+inference times are very small (typically about 10 $\mu s$), such that setup
+time dominates overall runtime.
 
- The bottom four graphs in each figure 
-show the results.  Again, the {\tt CIFAR10} results show the benefit of the \shrink approach
-most dramatically.
-On CPU, speedups range up to 6x depending on the batch size, with many models exceeding 3x speedup.
-In general, speedups are less than compression ratios, due to overheads in problem setup, invocation, and result generation  in Python/PyTorch.
-  On GPU, the speedups are less substantial because the CUDA benchmarking utility that we use for evaluation can choose better algorithms for larger matrices which masks some of our benefit, although they are still often 1.5x--2x faster for large batch sizes.
-The speedup results on {\tt COVERTYPE} are similar to those for network size:  because the networks are not much smaller, they are not much faster either.
+The bottom four graphs in each figure show the results.  Again, the {\tt
+CIFAR10} results show the benefit of the \shrink approach most dramatically.  On
+CPU, speedups range up to 6x depending on the batch size, with many models
+exceeding 3x speedup. In general, speedups are less than compression ratios, due
+to overheads in problem setup, invocation, and result generation  in
+Python/PyTorch.  On GPU, the speedups are less substantial because the CUDA
+benchmarking utility that we use for evaluation can choose better algorithms for
+larger matrices which masks some of our benefit, although they are still often
+1.5x--2x faster for large batch sizes.  The speedup results on {\tt COVERTYPE}
+are similar to those for network size:  because the networks are not much
+smaller, they are not much faster either.
 
-A key takeaway of these speedup results is that, unlike local sparsity compression methods, our methods' improvement on size translates directly to higher throughput at inference time~\cite{Han2015}.
-
-%In situations in which inference is already fast (\texttt{COVERTYPE}
-%with a batch size of $1$ and \texttt{CIFAR10} with a batch size of $1$ on GPU),
-%improvements are dominated by noise. However, on machine learning frameworks
-%more focused on latency it should be possible to measure them.
-
-% \begin{figure}
-% \begin{center}
-% \includegraphics[width=\columnwidth]{neuron_removal}
-% \vspace*{-5mm}
-% \caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$.
-First column is the difference in the final loss in function of the removal factor.
-We plot theoretical baseline as a reference.
-Right column is a proxy of the total cost for training the model (i.e.
-the sum of input neurons at each epoch).
-Each row is a dataset/$\lambda$ combination.
-From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}
-% 
-% \end{center}
-% \vspace*{-4mm}
-% \end{figure}
+A key takeaway of these speedup results is that, unlike local sparsity
+compression methods, our methods' improvement on size translates directly to
+higher throughput at inference time~\cite{Han2015}.
 
@@
 
-\subsection{Architectures obtained after convergence}
-
 \begin{figure}[htb]
 \begin{center}
-\includegraphics[width=.7\columnwidth]{size_evolution}
+\vspace{-.1in}
+\includegraphics[width=.6\columnwidth]{size_evolution}
 \vspace*{-5mm} 
@@
 
-\ra{the following is interesting, but how is it related to the above?}
-\shrink effectively explores the frontier of model size and accuracy. For a
+\subsection{Architectures obtained after convergence}
+\shrink effectively explore the frontier of model size and accuracy. For a
 given target accuracy, the size needed is significantly smaller than when we use the
@@
 architectures learned by \shrink in
-Figure~\ref{fig:network_size_evolution}.  The top plot shows the model with the
+Figure~\ref{fig:network_size_evolution}.  The right arrow shows the model with the
 best test accuracy, with identical performance to the best static
-network; the bottom shows a network that slightly under-performs the best in
+network; the left arrow shows a network that slightly under-performs the best in
 terms of accuracy but is significantly smaller that the best equivalent
@@
 shows the number of neurons in each layer of the original VGG net, and the
-shaded regions show the size of the ShrinkNet as it converges (with the darkest
+shaded regions show the size of the \shrink as it converges (with the darkest
 region representing the fully converged network).  Observe that the final

### 2018-02-10 paper/ICML/theory.tex
minor fixes

@@
 In practice we observed that $p=2$ or $p=1$ are good a choice; note that the latter
-will also introduce additional sparsity into the parameters because the $L_1$ is, 
-thest best convex approximation of the $L_0$ norm.
+will also introduce additional sparsity into the parameters because the $l_1$ is, 
+thest best convex approximation of the $l_0$ norm.

### 2018-02-10 paper/ICML/evaluation.tex
typos

@@
 entire parameter space.  This is as expected;  the fact that \shrink perform
-as well as the Static indicates that \shrink are doing an effective job of
+as well as Static indicates that \shrink are doing an effective job of
 exploring the parameter space using just the single $\lambda$ parameter.
 
-Note that the best performing \shrink models has $96.91\%$ accuracy while the
-best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
+Note that the best performing \shrink models have $96.91\%$ accuracy while the
+best static model is only $96.66\%$ accurate, while the \shrink model is $2.51$
 times smaller. In addition, if we give up just 0.5\% error, \shrink find a
@@
 
-\begin{figure*}[t]\centering
+\begin{figure*}[tb]\centering
 \begin{minipage}{2.7in}
@@
 \end{figure*}
-
-\begin{figure}[htb]
-\begin{center}
-\vspace{-.1in}
-\includegraphics[width=.6\columnwidth]{size_evolution}
-\vspace*{-5mm} 
-\caption{ Evolution of the size of
-  each layer over time (lighter: beginning, darker: end). On top a very large
-  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
-  accuracy. 
-} 
-\label{fig:network_size_evolution}
-\end{center}
-\vspace*{-4mm}
-\end{figure}
 
@@
 additional neurons to the final fewer layers.
+
+\begin{figure}[h]
+\begin{center}
+\vspace{-.1in}
+\includegraphics[width=.6\columnwidth]{size_evolution}
+\vspace*{-5mm} 
+\caption{ Evolution of the size of
+  each layer over time (lighter: beginning, darker: end). On top a very large
+  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
+  accuracy. 
+} 
+\label{fig:network_size_evolution}
+\end{center}
+\vspace*{-4mm}
+\end{figure}

### 2018-02-10 paper/ICML/evaluation.tex
Update evaluation.tex
small fix
edits

--- 2018-02-10 paper/ICML/evaluation.tex
@@
 find a model that is 35.5 times smaller than any static network that performs
-as good or better.
+as good.
 
@@
 times smaller. In addition, if we give up just 0.5\% error, \shrink find a
-model that is 38.6 times smaller than any static network with equivalent accuracy.
+model that is 38.6X smaller than any static network with equivalent accuracy.
 

### 2018-02-10 paper/ICML/impl.tex

@@
 
-\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain
+\noindent\textbf{Preparing for Inference: } With \shrink we obtain
 reduced-sized networks during training, which is the first steps towards faster
@@
 
-\noindent\textbf{Neural Garbage Collection: }ShrinkNets decides on-the-fly which
-neurons to remove. Since ShrinkNets removes a large fraction of neurons, we must
+\noindent\textbf{Neural Garbage Collection: } \shrink decides on-the-fly which
+neurons to remove. Since \shrink removes a large fraction of neurons, we must
 dynamically resize the network at runtime to not unnecessarily impact network

### 2018-02-10 paper/ICML/impl.tex
edit

@@
 to remove them to actually shrink the network size.
-In the following we discuss three potential strategies to remove neurons. 
+In the following we discuss three strategies to decide when to deactivate neurons. 
 %Since after removing a neuron it will no longer be able to contribute to  prediction accuracy, we must devise strategies that remove neurons while remaining robust to changing gradient values.
@@
 a fixed threshold expressed in terms of its absolute value. This is the method
-used by deep compression \cite{Han2015}. We found this method is very sensitive to the initializaiton 
+used by deep compression \cite{Han2015}. We found this method is very sensitive to the initialization 
 and not robust to noise in the gradients---which occurs commonly when training networks with
@@
 
-\textbf{Sign change strategy}: Under this strategy neurons are removed when the
+\textbf{Sign change strategy}: Under this strategy neurons are deactivated when the
 weight value changes its sign.
-As before this strategy is also sensitive to gradient noise; if we sample the gradient in a way that is not fully representative of the dataset we might experience one-time zero crossing which could wrongly remove a neuron.
+As before this strategy is also sensitive to gradient noise; if we sample the gradient in a way that is not fully representative of the dataset we might experience one-time zero crossing which could wrongly deactivate a neuron.
 
@@
 the exponential moving variances goes over a predefined threshold, we consider
-the neuron deactivated, and therefore we remove it. This strategy introduces
+the neuron deactivated. This strategy introduces
 two extra parameters, one to control the behavior of the inertia of the
@@
 \noindent\textbf{Neural Garbage Collection: } \shrink decides on-the-fly which
-neurons to remove. Since \shrink removes a large fraction of neurons, we must
-dynamically resize the network at runtime to not unnecessarily impact network
+neurons to deactivate. Since \shrink deactivate a large fraction of neurons, we must
+dynamically remove these neurons at runtime to not unnecessarily impact network
 training time. We implemented a neural garbage collection method as part of our

### 2018-05-16 paper/NIPS/appendix.tex
Flip the paper to the NIPS template

--- 2018-02-09 paper/ICML/appendix.tex
@@
 
-Here we prove the propositions given in Section~\ref{sec:approach}.  
 %Unless stated explicitly, all the propositions consider the Multi-Target linear regression problem.
@@
   $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$:
+\vspace{-.05in}
   %
-  \begin{align*}
-    & \min_{\bf{A}} \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
-     = &\min_{\bf{A'}, \bm{\beta}} \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1 \\
-     & \text{s.t.} \forall j, 1 \leq j \leq p, \norm{\left(A'^T\right)_j}_2^2 = 1
-  \end{align*}
+  \begin{equation*}
+    \min_{\bf{A}} \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
+     = \begin{cases}
+         \min_{\bf{A'}, \bm{\beta}} \norm{\bm{y} - \bm{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1 \\
+          \text{s.t.} \forall j, 1 \leq j \leq p, \norm{\left(A'^T\right)_j}_2^2 = 1
+        \end{cases}
+  \end{equation*}
 \end{proposition}
-\vspace{-.3in}
+\vspace{-.2in}
 \begin{proof}
-  We split the proof into two parts. First, we
-  demonstrate that there is at least one global minimum. Then, we 
+  First, we prove that there is at least one global minimum. Then, we 
     how to construct $2^k$ distinct solutions from a single global
@@
   In order to prove this second statement, we first show that for any solution $\bm{A}$ to the first problem, there exists a solution in the second with the exact same value, and vice-versa.
-  \\ \textbf{Part 1:} Assume we have a potential solution $\bm{A}$ for the first problem.
+  \vspace{-0.15in}
+  \paragraph{Part 1} Assume we have a potential solution $\bm{A}$ for the first problem.
 We define $\bm{\beta}$ such that $\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and $\bm{A}' = \bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$.
@@
 Now:
-  \begin{align*}
-    & \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 \\
-    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A'^T\right)_j\beta_j}_2 \\
-    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \abs{\beta_j} \cdot 1\\
-    = &\norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
-  \end{align*}
-  \\ \textbf{Part 2:} Assuming we take an $\bm{A}'$ that satisfies the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
+  \vspace{-0.10in}
+  \begin{equation*}
+    \begin{aligned}
+     \norm{\bf{y} - \bf{A}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A^T\right)_j}_2 
+    = \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \norm{\left(A'^T\right)_j\beta_j}_2 \\
+     = \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \sum_{j=1}^p \abs{\beta_j} \cdot 1
+    = \norm{\bf{y} - \bf{A'}\diag{\bm{\beta}}\bf{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
+\end{aligned}
+  \end{equation*}
+  \vspace{-0.25in}
+  \paragraph{Part 2} Assuming we take an $\bm{A}'$ that satisfies the constraint and a $\bm{\beta}$, we can define $\bm{A} = \bm{A'}\diag{\bm{\beta}}$.
 We can apply the same operations in reverse order and obtain an instance of the first problem with the same value.
-  \\ \textbf{Conclusion} There is no way these two problems have different minima,
+  \vspace{-0.15in}
+  \paragraph{Conclusion} There is no way these two problems have different minima,
   because we are able to construct a solution to a problem from the solution
@@
 % The entire network follows as: $N(\bm{x}) = \left(\bigcirc_{i=1}^n f_{\bm{A_i}, \bm{\beta_i}, \bm{b_i}}\right)(\bm{x})$. 
-For $\lambda > 0$, $\lambda_2 > 0$ and $p > 0$ we have:
-  \begin{equation*}
-    \min \norm{\bm{y} - N(\bm{x})}_2^2 + \Omega_{\lambda, \lambda_2, p}^{rs}
-  \end{equation*}
-  has at least $2^k$ global minimum where $k = \sum_{i=1}^n {\bf card}(\bm{\beta_i})$
+For $\lambda > 0$, $\lambda_2 > 0$ and $p > 0$ we have that $\min \norm{\bm{y} - N(\bm{x})}_2^2 + \Omega_{\lambda, \lambda_2, p}^{rs}$ has at least $2^k$ global minimum where $k = \sum_{i=1}^n {\bf card}(\bm{\beta_i})$
 \end{proposition}

### 2018-05-16 paper/NIPS/approach.tex
Flip the paper to the NIPS template

--- 2018-02-09 paper/ICML/approach.tex
@@
 as possible while preserving prediction accuracy. This can be achieved by jointly
-minimizing the training loss of the network and applying an L0 norm to the 
+minimizing the training loss of the network and applying an $l_0$ norm to the 
 $\bm{\beta}$ parameters of the \swl. 
-Since minimizing the L0 norm is an NP-Hard problem, we instead relax the constraint
-to an L1 norm by constraining $\bm{\beta}$ to be a real number
+Since minimizing the $l_0$ norm is an NP-Hard problem, we instead relax the constraint
+to an $l_1$ norm by constraining $\bm{\beta}$ to be a real number
 instead of a binary value.

### 2018-05-16 paper/NIPS/evaluation.tex
Flip the paper to the NIPS template

--- 2018-02-10 paper/ICML/evaluation.tex
@@
 
-\begin{figure*}[t]\centering
-\begin{minipage}{2.7in}
-\centering
-\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
-\vspace*{-10mm}
-\caption{\label{figure_CIFAR10} Summary of the result of random
-search over the hyper-parameters the \texttt{CIFAR10} dataset}
-\vspace*{-5mm}
-\end{minipage}
-\begin{minipage}{.3in}
-~~
-\end{minipage}
-\begin{minipage}{2.7in}
-\centering\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
-\vspace*{-10mm}
-\caption{\label{figure_COVER} Summary of the result of random
-search over the hyper-parameters the \texttt{COVERTYPE} dataset
-}
-\vspace*{-5mm}
-\end{minipage}
-\end{figure*}
-
 \begin{figure}[htb]
@@
 \vspace{-.1in}
-\includegraphics[width=.6\columnwidth]{size_evolution}
+\includegraphics[width=1\columnwidth]{size_evolution}
 \vspace*{-5mm} 
@@
 \vspace*{-4mm}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{minipage}{.49\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{CIFAR10_VGG_summary-arrows}
+  \captionof{figure}{
+\label{figure_CIFAR10} Summary of the result of random
+search over the hyper-parameters the \texttt{CIFAR10} dataset}
+  \label{fig:test1}
+\end{minipage}%
+\hspace*{0.02\textwidth}\begin{minipage}{.49\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{COVER_FC_summary-arrows}
+  \captionof{figure}{
+      \label{figure_COVER} Summary of the result of random
+search over the hyper-parameters the \texttt{COVERTYPE} dataset
+}
+\end{minipage}
 \end{figure}

### 2018-05-16 paper/NIPS/impl.tex
Flip the paper to the NIPS template

%!TEX root=paper.tex

\section{ShrinkNets in Practice}

In this section we discuss practical aspects of \shrink{}, including 
neuron removal  and several optimizations.

\paragraph{On-The-Fly Neuron Removal}
\label{neuron_killing}

Switch layers are initialized with weights sampled from $\mathcal{N}(0,1)$;
their values change as part of the training process so as to switch \emph{on}
or \emph{off} neurons. Using gradient descent, it is very unlikely that
components of $\bm{\beta}$ will eventually reach exactly $0$. In most cases,
irrelevants neurons will see their \swl oscillate between small positive and
negative values influenced solely by the $L_1$ penalty. Our goal is
to detect this situation and effectively set these components to $0$ exactly. We
evaluated multiple screening strategies but the most efficient and flexible one
was the \textbf{Sign variance strategy}: At each update we measure the sign of
each component of $\bm{\beta}$ ($-1$ or $1$). We maintain two metrics: the
exponential moving average (EMA) of its mean and variance. When the variance exceed a
predefined threshold we consider the value has been oscillating for a
sufficiently long and that the neuron does not participate to the output with a
high likelyhood, so we effectively deactivate it. This strategy is parametrized
by two hyper-parameters, the threshold but also the intertial of the EMA.

% When neurons are deactivated by switch layers, we need
% to remove them to actually shrink the network size.
% In the following we discuss three strategies to decide when to deactivate neurons. 
% %Since after removing a neuron it will no longer be able to contribute to  prediction accuracy, we must devise strategies that remove neurons while remaining robust to changing gradient values. We observe three strategies:
% 
% \paragraph{Threshold strategy} Under this strategy neurons are removed based on
% a fixed threshold expressed in terms of its absolute value. This is the method
% used by deep compression \cite{Han2015}. We found this method is very sensitive to the initialization 
% and not robust to noise in the gradients---which occurs commonly when training networks with
% stochastic gradient descent---because the threshold depends on the scale of
% each weight.
% 
% \textbf{Sign change strategy}: Under this strategy neurons are deactivated when the
% weight value changes its sign. As before this strategy is also sensitive to gradient noise; if we sample the gradient in a way that is not fully representative of the dataset we might experience one-time zero crossing which could wrongly deactivate a neuron.

% \textbf{Sign variance strategy}: Instead of removing on the first zero
% crossing, we can instead measure the exponential moving variance of the sign
% ($-1, 1$) of each parameter in the \textit{switch layer}. When the value of
% the exponential moving variances goes over a predefined threshold, we consider
% the neuron deactivated. This strategy introduces
% two extra parameters, one to control the behavior of the inertia of the
% variance, and the threshold. 
% However, we found that this strategy performs the best in practice and is used throughout our evaluation section. 
% 
%The last two strategies perform better than the threshold strategy.  Both effectively allow us to shrink the network by varying $\lambda$, and result in networks that are both small and perform well. We use the third one in our evaluation section.

\paragraph{Preparing for Inference} With \shrink we obtain
reduced-sized networks during training, which is the first steps towards faster
inference. This networks are readily available for inference. However, because
they include switch layers---and therefore more parameters---they introduce
unnecessary overhead at inference time. To avoid this overhead, we reduce the
network parameters by combining each switch layer with its respective network
layer by multiplying the respective parameters before emitting the final trained
network. As a result, the final network is a dense network without any switching layers.

\paragraph{Neural Garbage Collection} \shrink decides on-the-fly which
neurons to deactivate. Since \shrink deactivate a large fraction of neurons, we must
dynamically remove these neurons at runtime to not unnecessarily impact network
training time. We implemented a neural garbage collection method as part of our
library which takes care of updating the necessary network layers as well as
updating optimizer state to reflect the neuron removal.

### 2018-05-16 paper/NIPS/introduction.tex
Flip the paper to the NIPS template

--- 2018-02-10 paper/ICML/introduction.tex
@@
 
-Neural networks are being deployed in a wide variety of
-applications and on diverse hardware architectures ranging from laptops to
+Neural networks are used in an increasing wide variety of
+applications and diverse set of hardware architectures, ranging from laptops to
 phones to embedded sensors. This wide variety of deployment settings means

### 2018-05-16 paper/NIPS/paper.tex
Flip the paper to the NIPS template

--- 2018-02-09 paper/ICML/paper.tex
@@
-%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
-
 \documentclass{article}
 
-% Recommended, but optional, packages for figures and better typesetting:
-\usepackage{microtype}
+% if you need to pass options to natbib, use, e.g.:
+% \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading nips_2018
+
+% ready for submission
+\usepackage[preprint,nonatbib]{nips_2018}
+
+% to compile a preprint version, e.g., for submission to arXiv, add
+% add the [preprint] option:
+% \usepackage[preprint]{nips_2018}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+% \usepackage[final]{nips_2018}
+
+% to avoid loading the natbib package, add option nonatbib:
+% \usepackage[nonatbib]{nips_2018}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{bm}
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{xspace}      % microtypography
 \usepackage{graphicx}
@@
 \usepackage{cleveref}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{bm}
@@
 \usepackage{amsfonts}
-\usepackage{subfigure}
 \usepackage{stmaryrd}
@@
 
-% hyperref makes hyperlinks in the resulting PDF.
-% If your build breaks (sometimes temporarily if a hyperlink spans a page)
-% please comment out the following usepackage line and replace
-% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
-\usepackage{amsmath}
-
-% Attempt to make hyperref and algorithmic work together better:
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
@@
 \newtheorem{proposition}{Proposition}[section]
-
-% Use the following line for the initial blind version submitted for review:
-\usepackage{icml2018}
 \newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
@@
 \newcommand{\swls}{{\bf SwitchLayers}\xspace}
-% If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2018}
 
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{ShrinkNets: Learning Network Size while Training}
+\title{ShrinkNets: Learning Network Size while Training}
+
+% The \author macro works with any number of authors. There are two
+% commands used to separate the names and addresses of multiple
+% authors: \And and \AND.
+%
+% Using \And between authors leaves it to LaTeX to determine where to
+% break the lines. Using \AND forces a line break at that point. So,
+% if LaTeX puts 3 of 4 authors names on the first line, and the last
+% on the second line, try using \AND instead of \And before the third
+% author name.
+
+\author{
+  Guillaume Leclerc, Manasi Vartak, Raul Castro Fernandez, Tim Kraska, Samuel Madden \\
+  Computer Science and Artificial Intelligence Laboratory\\
+  Massachusetts Institute of Technology\\
+  Cambridge, MA 02145 \\
+  \texttt{\{leclerc, mvartak, raulfc, kraska, madden\}@mit.edu} \\
+}
 
 \begin{document}
+% \nipsfinalcopy is no longer used
 
-\twocolumn[
-\icmltitle{ShrinkNets: Learning Network Size while Training}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2018
-% package.
-
-% List of affiliations: The first argument should be a (short)
-% identifier you will use later to specify author affiliations
-% Academic affiliations should list Department, University, City, Region, Country
-% Industry affiliations should list Company, City, Region, Country
-
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
-\icmlsetsymbol{equal}{*}
-
-\begin{icmlauthorlist}
-\icmlauthor{Guillaume Leclerc}{mit,epfl}
-\icmlauthor{Raul Castro Fernandez}{mit}
-\icmlauthor{Manasi Vartak}{mit}
-\icmlauthor{Martin Jaggi}{epfl}
-\icmlauthor{Samuel Madden}{mit}
-\end{icmlauthorlist}
-
-\icmlaffiliation{mit}{Computer Science and Artificial Intelligence Laboratories, Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}
-
-\icmlaffiliation{epfl}{Swiss Federal Institute of Technology, Lausanne, Switzerland}
-
-\icmlcorrespondingauthor{Guillaume Leclerc}{leclerc@mit.edu}
-
-% You may provide any keywords that you
-% find helpful for describing your paper; these are used to populate
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Machine Learning, ICML}
-
-\vskip 0.3in
-]
-
-% this must go after the closing bracket ] following \twocolumn[ ...
-
-% This command actually creates the footnote in the first column
-% listing the affiliations and the copyright notice.
-% The command takes one argument, which is text to display at the start of the footnote.
-% The \icmlEqualContribution command is standard text for equal contribution.
-% Remove it (just {}) if you do not need this facility.
-
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{} % otherwise use the standard text.
+\maketitle
 
 \begin{abstract}
-As neural networks become widely deployed in different applications and 
-on different
-hardware, it has become increasingly important to optimize inference time and
-model size along with model accuracy.  
-Most current techniques optimize model size,
-model accuracy and inference time in different stages, resulting in suboptimal
-results and computational inefficiency.  
-In this work, we propose a new
-technique called \shrink that optimizes all three of these metrics
-simultaneously.  
-Specifically we present a new method to simultaneously optimize network size and
-model performance by neuron-level pruning during training.  
-Neuron-level pruning not only
-produces much smaller networks for a given accuracy threshold but also produces
-dense weight matrices that are amenable to efficient inference.  
-By applying our
-technique to convolutional as well as fully connected models, we show that 
-\shrink can reduce network size by 35X with a 6X improvement in inference time.
-In addition, the most accurate networks found by \shrink have accuracy that is
-similar to or better than those found by statically-sized networks.  
+As neural networks become widely deployed in different applications and on
+different hardware, it has become increasingly important to optimize inference
+time and model size along with model accuracy.  Most current techniques
+optimize model size, model accuracy and inference time in different stages,
+resulting in suboptimal results and computational inefficiency.  In this work,
+we propose a new technique called \shrink that optimizes all three of these
+metrics at the same time.  Specifically we present a new method to
+simultaneously optimize network size and model performance by neuron-level
+pruning during training.  Neuron-level pruning not only produces much smaller
+networks for a given accuracy threshold but also produces dense weight matrices
+that are amenable to efficient inference.  By applying our technique to
+convolutional as well as fully connected models, we show that \shrink can
+reduce network size by 35X with a 6X improvement in inference time with similar
+accuracy as models found by traditional training techniques. 
 \end{abstract}
-
-%\section{Tentative outline}
-%
-% \begin{itemize}
-  % \item We want to figure out what is the proper network size
-  % \item If we had a oversized network and for each neuron we would have an on/off switch, we could optimize the state of each switch to achieve any size/accuracy tradeof (we can prove that, do we care ?)
-  % \item Solving such problem is NP-Hard
-  % \item We could approximate the binary switch by relaxing them and doing L1 loss instead of L0 loss
-  % \item This is the definition of Shrinknets
-  % \item group sparsity tries to achieve a similar goal but with a different formulation
-  % \item How are they related ?
-  % \item If we add a specific constraint on our formulation we obtain the group sparsity one (proven)
-  % \item We conclude that without this constraint our formulation has more degree of freedom
-  % \item What happen when we drop this constraint
-  % \item The problem becomes non-convex and without a global minimum
-  % \item Not having a global minimum is bad, how can we solve that ?
-  % \item Adding an extra regularization parameter allow us to have a global minimum (a lot of them actually)
-  % \item Now we have a framework to switch on and of neurons
-  % \item We are still doing useless computation for neurons that will stay off forever, if we pruned them then we would speed up training
-  % \item Define the strategy to detect "forever dead" neurons
-  % \item (should we talk about the software architecture ?)
-  % \item now we evaluate the system
-  % \item First we show that our system has indeed more freedom than Group sparsity by showing that for any given amount of sparsity it can fit closer than the previous method
-  % \item On the same problem we show that removing neurons on the fly does not dramatically reduce accuracy (we might not be able to see any difference in performance for a linear/logistic regression though)
-  % \item We show that works with Bigger networks (multi layers perceptrons and CNNs), describe the training dynamics, discuss the shape we obtain
-  % \item Show that it is easier to do hyper-parameter optimization on the regularization parameter that the size of each layer.
-I think a nice experiment would be to plot the evolution of the final size of a two layer network (so going from a lambda to two sizes).
-And plot the trajectory in the "size space" as we decrease lambda.
-It would show how the system trades off the budget between the two layer in a nice and visual way
-  % \item Then we evaluate performance
-% \end{itemize}
-
-% \section{Outline2}
-%\begin{itemize}
-%  \item Introduction
-%  \begin{itemize}
-%    \item Finding an appropriately sized network is challenging
-%    \item ML practitioners spend a large amount of time tuning the size of layers
-%    in a network in order to get the best possible accuracy.
-%    \item Many techniques have been proposed for hyperparam opt but these
-%    are computationally expensive and take long to train
-%    \item We propose ShrinkNets, an approach to tune the size of the network 
-%    as it is being trained without incurring the significant costs of 
-%    hyperparameter optimization. 
-%    \item Thus, our contribution are: ...
-%  \end{itemize}
-%  \item Our Approach
-%  \begin{itemize}
-%    \item Assign an on/off switch to each neuron. But this is np-hard, so we
-%    consider a relaxation
-%    \item Formulation
-%    \item Relationship to sparsity
-%    \item Strategies to kill neurons (relation to theory above?)
-%    \item Implementation details
-%  \end{itemize}
-%  \item Related Work
-%  \begin{itemize}
-%    \item Hyperparameter optimization: random, bayesian opt, bandit methods
-%    \item distillation techniques
-%    \item post-training compression techniques
-%    \item group sparsity, non-parametric neural networks
-%    \item training dynamics paper: first overfitting and then randomization?
-%  \end{itemize}
-%  \item Experiments
-%  \begin{itemize}
-%    \item Accuracy obtained by Shrinknets
-%    \item Time taken to reach that accuracy compared with other hyperopt methods
-%    \item Characterize method wrt params
-%    \item Other experiments
-%  \end{itemize}
-%  \item Discussion
-%  \begin{itemize}
-%    \item Where does the method shine?
-%    \item Side-effects of method: smaller networks, time to train
-%    \item Potential extensions/limitations
-%  \end{itemize}
-%  \item Conclusion
-%\end{itemize}
 
@@
 \input{evaluation}
-%\input{discussion}
 \input{conclusion}
-
-\appendix
+\FloatBarrier
 \input{appendix}
-\FloatBarrier
-
-\bibliographystyle{icml2018}
+\bibliographystyle{unsrt}
 \bibliography{custom,general}
-
 \end{document}

### 2018-05-16 paper/NIPS/related_work.tex
Flip the paper to the NIPS template

--- 2018-02-09 paper/ICML/related_work.tex
@@
 hyperparameter optimization. Although many methods have been 
-proposed, e.g., \cite{BergstraJAMESBERGSTRA2012,Snoek12},
-randomized search has been shown to work surprising well.
+proposed for hyperparameter optimization, simple techniques such as randomized
+search have been shown to work suprisingly well in practice~\cite{BergstraJAMESBERGSTRA2012,Snoek12}.
 %  Brute force search of network sizes is
@@
 %hardware~\cite{molchanov2016pruning}.  
-The more complex methods for
-hyperparameter optimization include techniques, e.g., ~\cite{Snoek12} typically
- select hyperparameter combinations that come from uncertain areas of the
-hyperparameter space to search efficiency. 
-As a generalization of this,  methods based on bandit algorithms (e.g.
-~\cite{li2016hyperband, jamieson2016}) have also become a popular way to tune
+The more complex methods include Bayesian techniques such as~\cite{Snoek12} that
+select hyperparameter combinations from uncertain areas of the
+hyperparameter space. 
+Recently, methods based on bandit algorithms (e.g.
+~\cite{li2016hyperband, jamieson2016}) have also been proposed to tune
 hyperparameters by quickly discarding 
 model configurations that perform badly. 
-Although these methods could in theory be used to tune the number of neurons per layer
-of a network, in practice no related work proposes this, because treating each layer as a hyperparameter
-would lead an excessively large search space.
-In contrast, with ShrinkNets the size of the network can be tuned with 
-a single parameter, as we explain in the next section..
+Although these methods can be used to tune the size of each layer in a network, 
+in practice, related work presents limited experimental evidence
+regarding this, likely because treating each layer as a hyperparameter
+would lead to an excessively large search space.
+In contrast, with \shrink, the size of the network can be tuned with 
+a single parameter.
 % More importantly, none of the hyperparameter optimization methods focuses on
@@
 given, and their experimental results (on a small, fully connected network), are
-substantially worse than ours as shown in Section~\ref{sec:experiments}.
+substantially worse than ours as shown in Section 5.
 \cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent

### 2018-05-16 paper/NIPS/theory.tex
Flip the paper to the NIPS template

--- 2018-02-10 paper/ICML/theory.tex
@@
 Group sparsity and \shrink try to achieve the same goal. We discuss next how
-they are related to each other. First let's recall the two problems. In the context of approximating $\bm{y}$ with a linear regression from features $\bm{x}$), the
+they are related to each other. First let's recall the two problems. In the context of approximating $\bm{y}$ with a linear regression from features $\bm{x}$, the
 original \shrink problem is 
@@
 \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
-(\cref{gps_equivalence}, see Apendix). However if we relax this constraint then \shrink
+(\cref{gps_equivalence}, see Appendix). However if we relax this constraint then \shrink
 becomes non-convex and has no global minimum

### 2018-05-16 paper/NIPS/evaluation.tex
Start compressing text

@@
 
-\noindent\textbf{Implementation: }We implemented \swls and
+We implemented \swls and
 the associated training procedure as a library in
@@
 cases, we need to perform hyperparameter optimization to explore different
-network architectures. We perform random search, which is an effective technique
+network sizes. We perform random search, which is an effective technique
 for this purpose \cite{BergstraJAMESBERGSTRA2012}. We evaluate \shrink on two
-well-known datasets. One for which it is not possible to explore the entire
-space of network architectures (\texttt{CIFAR10}) and one for which it is
-possible to do so (\texttt{COVERTYPE}).
+architectures. One for which it is not possible to explore the entire
+space of network architectures (\texttt{VGG}) and one for which it is
+possible to do so (3 layers perceptron).
 
-\noindent\textbf{Setup: } We assume no prior knowledge on the optimal batch
+We assume no prior knowledge on the optimal batch
 size, learning rate, $\lambda$ or weight decay ($\lambda_2$). Instead, we
 trained a number of models, randomly and independently selecting the values of
-these parameters from a range of reasonable values. Training is done using
-gradient descent and the \textit{Adam} optimizer
-\cite{DBLP:journals/corr/KingmaB14}. Specifically, we start with randomly
-sampled learning
-rate; for every $5$ epochs of non-improvement in validation
-accuracy we divide the learning rate by $10$. We stop training after $400$
-epochs or when the learning rate is under $10^{-7}$, whichever comes first. For
-each of the models we trained, we pick the epoch with the best validation
-accuracy and report the corresponding testing accuracy. Because of the nature of
-our method, it can happen that for networks that are aggressively compressed,
-the best validation accuracy is obtained early in training, before the size has
-converged. To be sure that accuracy measured corresponds to the final shape and
-not the starting shape, we only consider the second half of the training when
-picking the best epoch. For each model, we also measure the total size, in terms
-of number of floating point parameters, excluding the \swls because as described
-in \cref{neuron_killing}, these are eliminated after training.
+these parameters from a range of reasonable values. Training is done using the
+\textit{Adam} optimizer \cite{DBLP:journals/corr/KingmaB14}. We start with
+randomly sampled learning rate; we divide the learning rate by $10$ every $5$
+consecutive epochs without improvement. We stop when the learning rate is under
+$10^{-7}$.  We pick the epoch with the best validation accuracy after the size
+of network converged and report the corresponding testing accuracy. We also
+measure the total size, in terms of number of floating point parameters,
+excluding the \swls because as described in \cref{neuron_killing}, these are
+eliminated after training.
 
@@
 images $(3 \times 32 \times 32)$, belonging to $10$ different classes. We use it
-with the \texttt{VGG16} network \cite{Srivastava2014}, which consists of
-alternating convolutional layers and \textit{MaxPool} layers interleaved by
-\textit{BatchNorm} \cite{DBLP:journals/corr/IoffeS15} and \textit{ReLU}
-\cite{Nair2010} layers. The two last layers are fully connected layers
-separated by a \textit{ReLU} activation function.
+with the \texttt{VGG16} network \cite{Srivastava2014}. We applied \shrink to the
+VGG16 network by adding \swls after each \textit{BatchNorm} layer and each fully
+connected layer (except the last). Recall that \shrink assume that the starting
+size of the network is an upper bound on the optimal size. Thus, we started with
+a network with 2x the original size for each layer as an upper bound.
 
-We applied \shrink to the VGG16 network by adding \swls
-after each \textit{BatchNorm} layer and each fully connected layer (except the
-last). Recall that \shrink assume that the starting size of the network is
-an upper bound on the optimal size. Thus, we started with a
-network with 2x the recommended size for each layer as an upper bound (this
-is larger than what ImageNet uses).
-
-We compare against classical (\textit{Static}) networks. In such networks, the
+We compare against a fixed size network. The
 number of parameters that control the size is large: 13 parameters for the
@@
 For \textit{Static Networks} we sample the size between $0.1$ and $2$ times the size
-original one, optimized for ImageNet. We report the same numbers as we did for
+original one, designed for ImageNet. We report the same numbers as we did for
 \shrink and we compare the two distributions.
@@
 The results are shown in the top figure of \cref{figure_CIFAR10}, with blue dots
-indicating models produced by \shrink and orange dots indicating static networks. 
-For each
-model, we plot its accuracy and model size. The lines show the Pareto frontier
-of models in each of the two optimization settings. \shrink explore the
-trade-off between model size and accuracy more effectively.
-
-Note that the best performing \shrink model has $92.07\%$ accuracy which
-is identical to the accuracy of the static network, while the \shrink model
-is $2.22$ times smaller. In addition, if we give up just 1\% error, \shrink
-find a model that is 35.5 times smaller than any static network that performs
-as good.
+indicating models produced by \shrink and orange dots indicating static
+networks.  model, we plot its accuracy and model size. The lines show the Pareto
+frontier of models in each of the two optimization settings. \shrink explore the
+trade-off between model size and accuracy more effectively. Note that the best
+performing \shrink model has $92.07\%$ accuracy which is identical to the
+accuracy of the static network, while the \shrink model is $2.22$ times smaller.
+In addition, if we give up just 1\% error, \shrink find a model that is 35.5
+times smaller than any static network that performs as good.
 
@@
 allows us to compare the results obtained by our method with the method in
-~\cite{Scardapane2017}.
-
-%The experimental setup on this dataset is similar to {\tt CIFAR10}. 
-We compare \shrink against the same architecture
+~\cite{Scardapane2017}. We compare \shrink against the same architecture
 used in \cite{Scardapane2017}, i.e., a three fully-connected layers network with no
@@
 
-The results are shown in the top figure of \cref{figure_COVER}, with the two
-optimization methods plotted as before. Here, {\it Static} method finds models
-that perform well at a variety of sizes, because it is able to explore the
-entire parameter space.  This is as expected;  the fact that \shrink perform
-as well as the Static indicates that \shrink are doing an effective job of
-exploring the parameter space using just the single $\lambda$ parameter.
+The results are shown in the top figure of \cref{figure_COVER}.  Here, {\it Static}
+method finds models that perform well at a variety of sizes, because it is able
+to explore the entire parameter space.  This is as expected;  the fact that
+\shrink perform as well as the Static indicates that \shrink are doing an
+effective job of exploring the parameter space using just the single $\lambda$
+parameter.  Note that the best performing \shrink models has $96.91\%$ accuracy
+while the best static model is only $96.66\%$ accurate, while the \shrink shrink
+model is $2.51$ times smaller. In addition, if we give up just 0.5\% error,
+\shrink find a model that is 38.6X smaller than any static network with
+equivalent accuracy.
 
-Note that the best performing \shrink models has $96.91\%$ accuracy while the
-best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
-times smaller. In addition, if we give up just 0.5\% error, \shrink find a
-model that is 38.6X smaller than any static network with equivalent accuracy.
-
-\subsubsection{Summary}
-
-We  demonstrated that it is possible to achieve networks with good accuracy
-when using \shrink both when the network space cannot be explored entirely
-(\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
-result is not that \shrink find networks of good accuracy, but that those
-networks are much smaller than those found by a static method. The impact of the
-network size on inference time is the subject of our next evaluation goal.
+% \subsubsection{Summary}
+% 
+% We  demonstrated that it is possible to achieve networks with good accuracy
+% when using \shrink both when the network space cannot be explored entirely
+% (\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
+% result is not that \shrink find networks of good accuracy, but that those
+% networks are much smaller than those found by a static method. The impact of the
+% network size on inference time is the subject of our next evaluation goal.
 
@@
 
-The previous experiment showed that \shrink find networks of similar or better accuracy
-than static networks that are much smaller. We now explore if the reduction in size
-translates into an improvement of the inference time.
-
-As noted in the introduction, for some applications, compact models that offer
-fast inference times are as important as absolute accuracy.
-
+The previous experiment showed that \shrink find networks of similar or better
+accuracy than static networks that are much smaller. As noted in the
+introduction, for some applications, compact models that offer fast inference
+times are as important as absolute accuracy.
 %This observation motivates our 
@@
 % that satisfies achieves a given accuracy. 
-
 In this section, we study the relationship between accuracy, network size and
@@
 significant for  \texttt{CIFAR10}. In the range of accuracies we are interested
-in, improvements in size go from 4x to 40x. On the \texttt{COVERTYPE} dataset,
-the compression ratio is always above 1 but it rarely exceeds 3x, except for
-very high accuracies where \shrink find excellent, small solutions.  The fact
+in, improvements in size go from 4x to 40x. The fact
 that the  \texttt{COVERTYPE} networks are not dramatically smaller is expected:
 as the distribution at the top of Figure~\ref{figure_COVER} shows, the static
-method is able to explore most of the parameter search space, so finds a range
-of models that perform well at different sizes.
+method is able to explore most of the parameter search space.
 
-For speedup, we experimented with both CPUs and GPUs, and with different batch
-sizes, where batch size indicates the number of inputs simultaneously fed to the
-model for inference.  For each data set/GPU/CPU combination, we show results
-with batch size 1, as well as with a batch size large enough to fully utilize
-the hardware on each dataset and hardware configuration.  For example, for {\tt
-CIFAR10} on CPU, a batch size of 64 fully utilizes the CPU, whereas a GPU can
-execute many more models in parallel, so we use a larger batch size of 1024.
-For {\tt COVERTYPE}, because the model is so much smaller, larger batches are
-needed to fully utilize the hardware.  Note that when using a batch size of $1$
-on GPU, we do not expect to (and do not) observe any improvement because
-inference times are very small (typically about 10 $\mu s$), such that setup
-time dominates overall runtime.
+For speedup, we experimented with both CPUs and GPUs. For each data set/GPU/CPU
+combination, we show results with batch size 1, as well as with a batch size
+large enough to fully utilize the hardware on each dataset and hardware
+configuration. Note that when using a batch size of $1$ on GPU, we do not expect
+to (and do not) observe any improvement because inference times are very small
+(typically about 10 $\mu s$), such that setup time dominates overall runtime.
 
@@
 larger matrices which masks some of our benefit, although they are still often
-1.5x--2x faster for large batch sizes.  The speedup results on {\tt COVERTYPE}
-are similar to those for network size:  because the networks are not much
-smaller, they are not much faster either.
+1.5x--2x faster for large batch sizes.
 

### 2018-05-16 paper/ICML/plot_random_search.py

@@ -273,7 +273,7 @@ def plot_shape(ax, log, steps=8):
 
 def plot_shapes(dynamic):
     best, good = select_models(dynamic)
-    fig, lines = plt.subplots(2, 1, sharex=True)
+    fig, lines = plt.subplots(1, 2, sharex=True)
     plt.subplots_adjust(wspace=0.05, hspace=0.05)
     plot_shape(lines[0], best)
     plot_shape(lines[1], good)

### 2018-05-17 paper/NIPS/theory.tex
Merge the theory part and the appendix to gain a page

@@
 %
+\vspace{-0.1in}
 \begin{equation}
+    \label{full_def}
   \Omega_\lambda^{gp} = \lambda \sum_{i=1}^p \sqrt{\mathbf{card}(\bm{\theta_i}}) \norm{\bm{\theta_i}}_2 \\
 \end{equation}
+\vspace{-0.2in}
 % \srm{define notation -- what is $\lambda$;  what is $\#\theta$, what is $\Omega$? Where does the square root come from?} \gl{This is how it is defined in the
@@
 % need to do ?}
+
 In fully-connected layers, the groups are either: columns of
@@
 %
+\vspace{-0.1in}
 \begin{equation} \label{group_sparsity_regularization}
@@
 \end{equation}
+\vspace{-0.2in}
 
@@
 Group sparsity and \shrink try to achieve the same goal. We discuss next how
-they are related to each other. First let's recall the two problems. In the context of approximating $\bm{y}$ with a linear regression from features $\bm{x}$, the
-original \shrink problem is 
-%
-\begin{equation}
-  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
-\end{equation}
-%
-And the group sparsity problem is:
-%
-\begin{equation}
-  \min_{\bm{A}} \norm{\bm{y} - \bm{A}\bm{x}}_2^2 + \Omega_\lambda^{gp}
-\end{equation}
-%
+they are related to each other. First let's recall the two problems. In the
+context of approximating $\bm{y}$ with a linear regression from features
+$\bm{x}$, the two problems are:%
+\vspace{-0.25in}
+\begin{multicols}{2}
+    \begin{equation*}
+        \text{\shrink: } \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \lambda \norm{\bm{\beta}}_1
+    \end{equation*}
+    \break
+    \begin{equation*}
+        \text{\textbf{Group sparsity: }}\min_{\bm{A}} \norm{\bm{y} - \bm{A}\bm{x}}_2^2 + \Omega_\lambda^{gp}
+    \end{equation*}
+\end{multicols}
+\vspace{-0.1in}
 
 We can prove that under the condition: $\forall j\in \intint{1, p},
-\norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
-(\cref{gps_equivalence}, see Appendix). However if we relax this constraint then \shrink
-becomes non-convex and has no global minimum
-(\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}, also in Appendix). Fortunately,
-by adding an extra term to the \shrink regularization term we can prove that:
+\norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent by taking
+$\bm{\beta}_j = \norm{\left(\bm{A}^T\right)_j}_2^2$, and replacing $\bm{A}$ by
+$\bm{A}\left(\diag{\bm{\beta}}\right)^{-1}$. However, if we relax this constraint
+then \shrink becomes non-convex and has no global minimum. The latter is true
+because one can divide $\bm{\beta}$ by an arbitrarly large constant and
+multipliying $A$ by the same value. Fortunately, by adding an extra term to the \shrink
+regularization term we can avoid that problem and prove that:
 %
@@
 %
-has global minimums for all $p>0$ (\cref{shrinknet_regularized_minimum}).
-This is the reason we defined the regularized \shrink penalty above as:
-%
-\begin{equation}
-  \Omega_{\lambda, \lambda_2, p}^{rs} = \lambda\norm{\bm{\beta}}_1 + \lambda_2\norm{\bm\theta}_p^p
-\end{equation}
-%
-In practice we observed that $p=2$ or $p=1$ are good a choice; note that the latter
+has global minimums for all $p>0$. More specifically there are at least $2^k$,
+where $k$ is the total number of components in $\bm{\beta}$. Indeed, for any
+solution, one can obtain the same output by flipping any sign in $\bm{\beta}$
+and the corresponding entries in $\bm{A}$.  This is the reason we defined the
+regularized \shrink penalty above in \cref{full_def}.
+In practice, we observed that $p=2$ or $p=1$ are good a choice; note that the latter
 will also introduce additional sparsity into the parameters because the $l_1$ is, 

### 2018-05-17 paper/NIPS/evaluation.tex
Pass on Related Work + Add imageNet

@@
 \caption{ Evolution of the size of
-  each layer over time (lighter: beginning, darker: end). On top a very large
-  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
-  accuracy. 
+  each layer over time (lighter: beginning, darker: end). On the left a VGG
+  network on \texttt{CIFAR10} with $90.5\%$ accuracy. On the right, ResNet-50
+  on \texttt{ImageNet} that yields a top-1 accuracy of $71.57\%$.
 } 
@@
 To illustrate this point on a larger dataset, we show two examples of
-architectures learned by \shrink in
-Figure~\ref{fig:network_size_evolution}.  The right arrow shows the model with the
-best test accuracy, with identical performance to the best static
-network; the left arrow shows a network that slightly under-performs the best in
-terms of accuracy but is significantly smaller that the best equivalent
-\textit{Static Network}.  In the plot, the dashed line
-shows the number of neurons in each layer of the original VGG net, and the
+architectures learned by \shrink. The first one is directly taken from
+Figure~\ref{fig:network_size_evolution} and is typically a good trade-of between
+size and accuracy. The right one is the evolution the ResNet-50 model
+\cite{He2016a} trained on the ImageNet. In the plot, the dashed line
+shows the number of neurons in each layer of the original architecture, and the
 shaded regions show the size of the \shrink as it converges (with the darkest

### 2018-05-17 paper/NIPS/related_work.tex
Pass on Related Work + Add imageNet

@@
 In contrast, with \shrink, the size of the network can be tuned with 
-a single parameter.
+a single parameter. Recently, methods based on reinforcement learning have been
+proposed (\cite{Zoph2017b,Zoph2017a}) and shown to generate very accurate
+networks (NAS-Net). However as stated in \cite{Zoph2017b}, they still used the popular
+heuristic that doubles the number of channels every time the dimension of
+features is reduced without challenging it.
+
+\gl{Add another paragraph on architectures that are small by design ? (MobileNet
+ShuffleNet)}
+
 % More importantly, none of the hyperparameter optimization methods focuses on
@@
 
-\noindent\textbf{Dynamically Sizing Networks: }The techniques closest to our
+\paragraph{Dynamically Sizing Networks}The techniques closest to our
 proposed method are those based on group sparsity such as
-~\cite{Scardapane2017}, and those like~\cite{Philipp} that dynamically grow and shrink
- the size of the network during training.  \cite{Scardapane2017}
+~\cite{Scardapane2017,Alvarez2016a}, nuclear norm \cite{Alvarez2017a} and even
+physics-inspired methods \cite{Wen2017}. In \cite{Wen2016}, authors look beyond
+removing channels and experiment with shape and depth. In ~\cite{Philipp},
+network is dynamically grown and shrunk during training.  \cite{Scardapane2017}
 presents a method that also deactivates neurons using a loss function based on
@@
 given, and their experimental results (on a small, fully connected network), are
-substantially worse than ours as shown in Section 5.
-\cite{Philipp} propose a method called Adaptive Radial-Angular Gradient Descent
-that adds neurons on the fly and removes neurons via an $l_2$ penalty.  However,
-this approach requires a new optimizer and takes longer to converge compared to
-ShrinkNets.
+substantially worse than ours as shown in Section 5.  \cite{Philipp} propose a
+method called Adaptive Radial-Angular Gradient Descent that adds neurons on the
+fly and removes neurons via an $l_2$ penalty.  However, this approach requires a
+new optimizer and takes longer to converge compared to \shrink.
+\cite{Liu} is similar with \shrink in a sense that they both scale each
+channel/neuron by a scalar, however our approach is more general since it can be
+used with any architecture, even if they do not use batch normalization
+\gl{say that they don't do neural garbage collection ?}.
